### 2018-03-09 scripts/analysis.Rmd
stash analysis rmd and pdf

---
title: "Figures"
output:
  pdf_document:
    fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5.5, fig.height = 4.2)
```

```{r read_chunks, cache=FALSE, echo=FALSE}
knitr::read_chunk("01_prepdata.R")
knitr::read_chunk("03_viz.R")
knitr::read_chunk("04_tables.R")
knitr::read_chunk("99_utils.R")
```

```{r source_utils, message=FALSE, results='hide', echo=FALSE, warning=FALSE}

```

```{r prep_nes_lagos, message=FALSE, results='hide', echo=FALSE, warning=FALSE}

```

```{r global_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from the non-hierarchical model posterior relative to raw data."}

```

```{r partition_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from the hierarchical model posteriors relative to raw data. Dark lines and shaded polygons represent the estimates from the lower of the two partition groups (see Table 1)", fig.height=8.4}

```

```{r k_viz, echo=FALSE, message=FALSE}

```

```{r table_1, echo=FALSE, fig.cap="Table 1"}

```

```{r recursive_partitioning_viz, echo=FALSE, eval=FALSE}

```

### 2018-03-09 scripts/01_prepdata.R
stash analysis scripts

@@ -1,0 +1,14 @@
+source("99_utils.R")
+
+
+# ---- prep_nes_lagos ----
+
+nes_iws <- prep_full_nes("../../nes/nes_x_lagos-ne.csv", 
+                         "../../nes/connectivity_metrics.csv")
+
+nes_nws <- prep_full_nes("../../nes/nes_x_lagos-ne.csv", 
+                         "../../nes/connectivity_metrics2.csv")
+
+nes_rf_iws <- make_rf_dt(nes_iws)$nes_rf
+
+nes_rf_nws <- make_rf_dt(nes_nws)$nes_rf

### 2018-03-09 scripts/02_modelling.R

@@ -1,0 +1,1190 @@
+source("99_utils.R")
+source("01_prepdata.R")
+
+# ---- load_packages ----
+
+library(partykit)
+library(data.tree)
+
+library(forcats)
+library(rstan)
+library(nesRdata)
+library(bayesplot)
+library(patchwork)
+library(tidyr)
+library(cowplot)
+library(ggsn)
+library(tidybayes)
+library(akima)
+
+# ---- global_vollenweider ----
+
+# fit <- full_model(nes_iws)
+# saveRDS(fit, "01_Chapter/data/global_vollenweider.rds")
+
+# ---- recursive_partioning ----
+
+# max depth
+# tree3 <- cforest(nes_rf$p_perce ~ ., data = dplyr::select(nes_rf,
+#                                                           maxdept),
+#                control = ctree_control(mincriterion = 0.8,
+#                                        minsplit = 2))
+# saveRDS(tree3, "01_Chapter/data/maxdepth_forest.rds")
+
+# iws closest lake distance
+# nes_rf_iws$inv_closest <- 1 / scale(nes_rf_iws$closest)
+# tree3 <- cforest(nes_rf$p_perce ~ ., data = dplyr::select(nes_rf,
+#                                                 inv_closest),
+#                control = ctree_control(mincriterion = 0.55,
+#                                        minsplit = 3))
+# saveRDS(tree3, "01_Chapter/data/iws/cd_forest.rds")
+# 
+# nes_rf_nws$inv_closest <- 1 / scale(nes_rf_nws$closest)
+# tree3 <- cforest(nes_rf_nws$p_perce ~ ., data = dplyr::select(nes_rf_nws,
+#                                                 inv_closest),
+#                control = ctree_control(mincriterion = 0.45,
+#                                        minsplit = 4))
+# # plot(gettree(tree3))
+# saveRDS(tree3, "01_Chapter/data/nws/cd_forest.rds")
+# inv_inv_closest(-1.51, nes_rf_iws) # 3773.614
+#inv_inv_closest(-1.469, nes_rf_nws) # 2681.288
+
+# stream order ratio
+# tree3 <- cforest(nes_rf$p_perce ~ ., 
+#         data = dplyr::select(nes_rf, 
+#                              stream_), 
+#         control = ctree_control(mincriterion = 0.1))
[…]

### 2018-03-09 scripts/03_viz.R

@@ -1,0 +1,244 @@
+source("01_Chapter/scripts/99_utils.R")
+source("01_Chapter/scripts/01_prepdata.R")
+
+# ---- global_vollenweider_viz ----
+
+full_pred_plot(nes_iws, readRDS("../data/global_vollenweider.rds"))
+
+# ---- recursive_partitioning_viz ----
+
+plot_tree(gettree(readRDS("../data/maxdepth_forest.rds")), 
+          title = "Max Depth")
+
+plot_tree(gettree(readRDS("../data/iws/cd_forest.rds")), 
+          title = "Distance to Closest \n Upstream Lake (standardized)")
+# inv_inv_closest(-1.51, nes_rf_iws) # 3773.614
+plot_tree(gettree(readRDS("../data/nws/cd_forest.rds")), 
+          title = "Distance to Closest \n Upstream Lake (standardized)")
+# inv_inv_closest(-1.469, nes_rf_nws) # 2681.288
+
+plot_tree(gettree(readRDS("../data/iws/sr_forest.rds")), 
+          title = "Stream Order Ratio")
+plot_tree(gettree(readRDS("../data/nws/sr_forest.rds")), 
+          title = "Stream Order Ratio")
+
+plot_tree(gettree(readRDS("../data/iws/linklength_forest.rds")), 
+          title = "Link Length")
+plot_tree(gettree(readRDS("../data/nws/linklength_forest.rds")), 
+          title = "Link Length")
+
+plot_tree(gettree(readRDS("../data/iws/uplakearea_forest.rds")), 
+          title = "Upstream Lake Area")
+# plot_tree(gettree(readRDS("01_Chapter/data/nws/uplakearea_forest.rds")), 
+#           title = "Upstream Lake Area")
+
+plot_tree(gettree(readRDS("../data/iws/baseflow_forest.rds")), 
+          title = "Baseflow")
+
+plot_tree(gettree(readRDS("../data/iws/wetland-cover_forest.rds")), 
+          title = "Wetland Cover")
+
+plot_tree(gettree(readRDS("../data/iws/streamdensity_forest.rds")), 
+          title = "Stream Density")
+
+# ---- partition_vollenweider_viz ----
+
+plot_grid(
+  part_pred_plot(nes_iws, readRDS("../data/md_vollenweider.rds"), 
+                 9, "Max Depth", xl = FALSE), ggplot() + geom_blank(),
[…]

### 2018-03-09 scripts/04_tables.R

@@ -1,0 +1,53 @@
+source("99_utils.R")
+
+# ---- table_1 ----
+table_splits <- function(dir, pat = "forest.rds"){
+  parts  <- list.files(dir, pattern = pat, 
+                           full.names = TRUE, include.dirs = TRUE)
+  pnames <- sapply(parts, function(x) strsplit(basename(x), "_")[[1]][1])
+  splits <- sapply(parts, function(x) get_tree_split(gettree(readRDS(x))))
+  cbind(pnames, splits)
+}
+
+misc_parts <- data.frame(table_splits("../data/"), 
+                         stringsAsFactors = FALSE)
+iws_parts  <- data.frame(table_splits("../data/iws/"), 
+                         stringsAsFactors = FALSE)
+nws_parts  <- data.frame(table_splits("../data/nws/"), 
+                         stringsAsFactors = FALSE)
+
+misc_parts$scale <- "misc"
+iws_parts$scale  <- "iws"
+nws_parts$scale  <- "nws"
+
+rownames(misc_parts) <- rownames(iws_parts) <- rownames(nws_parts) <- NULL
+
+res <- rbind(misc_parts, iws_parts, nws_parts)
+res$splits <- as.numeric(res$splits)
+# res <- res[,1:ncol(res)]
+
+name_key <- data.frame(
+  parameter  = c("Max Depth", "Closest lake distance", 
+                 "Stream order ratio", "Average Link Length", 
+                 "Upstream lake area", "Baseflow", 
+                 "Wetland Cover",
+                 "Stream density"), 
+  pnames = c("maxdepth", "cd", 
+                "sr", "linklength", 
+                "uplakearea", "baseflow", 
+                "wetland-cover", 
+                "streamdensity")
+)
+
+res <- merge(name_key, res)
+
+res[res$pnames == "cd", "splits"] <- c(inv_inv_closest(-1.51, nes_rf_iws),
+                                       inv_inv_closest(-1.49, nes_rf_nws))
+                                       
+# tidyr::spread(res, scale, splits)                                       
+
+write.csv(res, "../figures/table_1.csv", row.names = FALSE)
+
+knitr::kable(res[order(res$pnames, res$scale), 2:ncol(res)], 
+             digits = 2, row.names = FALSE, 
+             col.names = c("Metric", "Split Value", "Scale"))

### 2018-03-09 scripts/99_utils.R

@@ -1,0 +1,250 @@
+
+# ---- source_utils ----
+
+library(LAGOSNE)
+library(dplyr)
+library(brms)
+library(tidybayes)
+library(ggplot2)
+library(cowplot)
+library(data.tree)
+library(partykit)
+library(modelr)
+library(tidyr)
+library(ggridges)
+
+prep_full_nes <- function(nes_x_lagos, conny_metrics_path, join_lagos_gis = FALSE){
+  
+  nes         <- read.csv(system.file("extdata/nes.csv", package = "nesRdata"),
+                          stringsAsFactors = FALSE)
+  nes_x_lagos <- read.csv(nes_x_lagos, stringsAsFactors = FALSE)
+  
+  if(!("storet_code" %in% names(nes_x_lagos))){ # if lagos-ne
+    lg  <- lagosne_load("1.087.1")
+    nes <- dplyr::left_join(nes_x_lagos, nes, by = c("nesid" = "storet_code"))
+    nes <- dplyr::left_join(nes, select(                # lakes.geo
+      lg$lakes.geo,
+      lakeconnection, lagoslakeid, hu12_zoneid, upstream_lakes_4ha_area_ha))
+    nes <- filter(nes, upstream_lakes_4ha_area_ha < 4000000)
+    nes <- dplyr::left_join(nes, select(lg$lakes_limno, # lakes_limno
+                                        lagoslakeid, meandepth, maxdepth))
+    nes <- dplyr::left_join(nes, select(lg$iws.conn,    # iws.conn
+                                        lagoslakeid, iws_streamdensity_streams_density_mperha, 
+                                        iws_wl_allwetlandsdissolved_overlapping_area_pct,
+                                        iws_lakes_overlapping_area_pct
+    ))
+    nes <- dplyr::left_join(nes, select(lg$hu12.chag,   # hu12.chag
+                                        hu12_zoneid, hu12_baseflowindex_mean))
+    nes <- dplyr::left_join(nes, select(lg$iws.lulc,    # iws.lulc
+                                        lagoslakeid, iws_nlcd1992_pct_81, iws_nlcd1992_pct_82))
+    # nes <- dplyr::left_join(nes, select(lg$iws,         # iws
+    #                                     lagoslakeid, iws_ha))
+    nes <- dplyr::left_join(nes, select(lg$locus,       # locus
+                                        lagoslakeid, lake_area_ha))
+    
[…]

### 2018-03-09 scripts/01_prepdata.R
rebuild table, fix related file paths, add additional figures

@@ -1,13 +1,14 @@
-source("99_utils.R")
+source("scripts/99_utils.R")
 
+pre_path <- "/home/jose/Documents/Science/Dissertation/Analysis/nes/"
 
 # ---- prep_nes_lagos ----
 
-nes_iws <- prep_full_nes("../../nes/nes_x_lagos-ne.csv", 
-                         "../../nes/connectivity_metrics.csv")
+nes_iws <- prep_full_nes(file.path(pre_path, "nes_x_lagos-ne.csv"), 
+                         file.path(pre_path, "connectivity_metrics.csv"))
 
-nes_nws <- prep_full_nes("../../nes/nes_x_lagos-ne.csv", 
-                         "../../nes/connectivity_metrics2.csv")
+nes_nws <- prep_full_nes(file.path(pre_path, "nes_x_lagos-ne.csv"), 
+                         file.path(pre_path, "connectivity_metrics2.csv"))
 
 nes_rf_iws <- make_rf_dt(nes_iws)$nes_rf
 

### 2018-03-09 scripts/04_tables.R

@@ -1,4 +1,5 @@
-source("99_utils.R")
+source("scripts/99_utils.R")
+source("scripts/01_prepdata.R")
 
 # ---- table_1 ----
 table_splits <- function(dir, pat = "forest.rds"){
@@ -9,11 +10,11 @@ table_splits <- function(dir, pat = "forest.rds"){
   cbind(pnames, splits)
 }
 
-misc_parts <- data.frame(table_splits("../data/"), 
+misc_parts <- data.frame(table_splits("data/"), 
                          stringsAsFactors = FALSE)
-iws_parts  <- data.frame(table_splits("../data/iws/"), 
+iws_parts  <- data.frame(table_splits("data/iws/"), 
                          stringsAsFactors = FALSE)
-nws_parts  <- data.frame(table_splits("../data/nws/"), 
+nws_parts  <- data.frame(table_splits("data/nws/"), 
                          stringsAsFactors = FALSE)
 
 misc_parts$scale <- "misc"
@@ -43,11 +44,12 @@ res <- merge(name_key, res)
 
 res[res$pnames == "cd", "splits"] <- c(inv_inv_closest(-1.51, nes_rf_iws),
                                        inv_inv_closest(-1.49, nes_rf_nws))
+res <- res[order(res$pnames, res$scale), 2:ncol(res)]
                                        
 # tidyr::spread(res, scale, splits)                                       
 
-write.csv(res, "../figures/table_1.csv", row.names = FALSE)
+write.csv(res, "figures/table_1.csv", row.names = FALSE)
 
-knitr::kable(res[order(res$pnames, res$scale), 2:ncol(res)], 
+knitr::kable(res, 
              digits = 2, row.names = FALSE, 
              col.names = c("Metric", "Split Value", "Scale"))

### 2018-03-12 scripts/analysis.Rmd
fix pred plot ordering, add post hoc plots, add summary table

@@
 ```
+
+```{r graphical_exploratory_analysis, echo=FALSE, message=FALSE, warning=FALSE}
+
+```
+
+## Summary
+
+```{r conceptual_summary, echo=FALSE}
+dt <- data.frame(
+  rbind(
+        c("lakeconnection", "DR_Stream", "higher", "lower", "higher", "lake"), 
+        c("upstream lake area", "lower", "higher", "lower", "higher", "lake"), 
+        c("link_length", "lower", "higher", "lower", "higher", "stream"), 
+        c("baseflow", "higher", "higher", "lower", "higher", "stream"), 
+        c("stream order ratio", "higher", "higher", "lower", "higher", "stream"),
+  c("upstream lake distance", "lower", "higher", "lower", "higher", "lake-stream"), 
+        c("stream density", "higher", "higher", "lower", "higher", "stream")))
+
+names(dt) <- c("metric", "direction", "k", "connectivity", "in_lake_processing", "axis")
+
+knitr::kable(dt, caption = c("Connectivity metric effects on lake processing."))
+```

### 2018-03-12 scripts/02_modelling.R

@@ -180,10 +180,8 @@ m <- readRDS("../data/global_vollenweider.rds")
 # saveRDS(fit, "../data/nws/la_vollenweider.rds")
 
 # Baseflow
-nes$part <- factor(as.numeric(cut(nes$hu12_baseflowindex_mean, 
-                                  c(0, 63.8, Inf), include.highest = TRUE)))
-# fit <- part_model(nes)
-# saveRDS(fit, "01_Chapter/bf_vollenweider.rds")
+# fit <- part_model(nes_iws, "hu12_baseflowindex_mean", 0, 63.8, Inf)
+# saveRDS(fit, "../data/iws/bf_vollenweider.rds")
 #
 # fit <- part_model(nes_nws, "baseflow", 0, 52.94, Inf)
 # saveRDS(fit, "../data/nws/bf_vollenweider.rds")

### 2018-03-12 scripts/03_viz.R

@@ -44,23 +44,23 @@ plot_tree(gettree(readRDS("../data/iws/streamdensity_forest.rds")),
 # ---- partition_vollenweider_viz ----
 
 plot_grid(
-  part_pred_plot(nes_iws, readRDS("../data/md_vollenweider.rds"), 
-                 9, "Max Depth", xl = FALSE),
+  part_pred_plot(nes_iws, readRDS("../data/lc_vollenweider.rds"), 
+                 9, "Lake Connection", xl = FALSE),
   part_pred_plot(nes_iws, readRDS("../data/nws/cd_vollenweider.rds"),
                  9, "Distance to Closest Lake", xl = FALSE, yl = FALSE), 
-  part_pred_plot(nes_iws, readRDS("../data/lc_vollenweider.rds"), 
-                 8, "Lake Connection", xl = FALSE),
+  part_pred_plot(nes_iws, readRDS("../data/md_vollenweider.rds"), 
+                 8, "Max Depth", xl = FALSE),
   part_pred_plot(nes_nws, readRDS("../data/nws/ll_vollenweider.rds"),
                  8, "Link Length", xl = FALSE, yl = FALSE),
-  part_pred_plot(nes_iws, readRDS("../data/iws/sd_vollenweider.rds"),
-                 7, "Stream Density", xl = FALSE), 
-  part_pred_plot(nes_nws, readRDS("../data/nws/la_vollenweider.rds"),
-                 7, "Upstream Lake Area", xl = FALSE, yl = FALSE), 
-  part_pred_plot(nes_nws, readRDS("../data/iws/ll_vollenweider.rds"),
-                 6, "Link Length"),
+  part_pred_plot(nes_iws, readRDS("../data/iws/ll_vollenweider.rds"),
+                 7, "Link Length", xl = FALSE), 
   part_pred_plot(nes_iws, readRDS("../data/lc_vollenweider.rds"), 
-                 6, "Lake Connection", yl = FALSE),
-  nrow = 4, ncol = 2)
+                 7, "Lake Connection", yl = FALSE, xl = FALSE),
+  part_pred_plot(nes_iws, readRDS("../data/iws/bf_vollenweider.rds"),
+                 6, "Baseflow"),
+  part_pred_plot(nes_nws, readRDS("../data/nws/la_vollenweider.rds"),
+                 6, "Upstream Lake Area", yl = FALSE), 
[…]

### 2018-03-12 scripts/01_prepdata.R
add some exploratory plots

@@ -1,3 +1,4 @@
+# setwd("scripts")
 source("99_utils.R")
 
 # ---- prep_nes_lagos ----
@@ -6,9 +7,6 @@ pre_path <- "/home/jose/Documents/Science/Dissertation/Analysis/nes/"
 
 nes_iws <- prep_full_nes(file.path(pre_path, "nes_x_lagos-ne.csv"), 
                          file.path(pre_path, "connectivity_metrics.csv"))
-
-# nes_nws <- prep_full_nes(file.path(pre_path, "nes_x_lagos-ne.csv"), 
-#                          file.path(pre_path, "connectivity_metrics2.csv"))
 
 nes_nws <- prep_full_nes(file.path(pre_path, "nes_x_lagos-ne.csv"), 
                          file.path(pre_path, "connectivity_metrics3.csv"))

### 2018-03-12 scripts/03_viz.R

@@ -60,7 +60,7 @@ plot_grid(
                  6, "Baseflow"),
   part_pred_plot(nes_nws, readRDS("../data/nws/la_vollenweider.rds"),
                  6, "Upstream Lake Area", yl = FALSE), 
-  nrow = 4, ncol = 2, rel_widths = c(1, 0.8))
+  nrow = 4, ncol = 2, rel_widths = c(1, 0.9))
 
 # ---- k_viz ----
 
@@ -224,3 +224,38 @@ plot_grid(md_v_la + theme(legend.position = "none"),
           md_v_ll_nws + theme(legend.position = "none"),
           ll_v_cd_nws + theme(legend.position = "none"),
           legend, ncol = 2, rel_heights = c(1, 1))
+
+plot(nes_iws$hu12_baseflowindex_mean, nes_nws$baseflow)
+abline(0, 1)
+abline(h = 52.94, col = "red")
+abline(v = 63.76, col = "red")
+
+
+plot(nes_iws$iws_streamdensity_streams_density_mperha, nes_nws$stream_density)
+abline(0, 1)
+abline(h = 10.4, col = "red")
+abline(v = 4.43, col = "red")
+
+plot(nes_iws$closest_lake_distance, nes_nws$closest_lake_distance)
+abline(0, 1)
+abline(h = 2776.81, col = "red")
+abline(v = 3773.61, col = "red")
+
+plot(log(nes_iws$upstream_lakes_4ha_area_ha), log(nes_nws$lake_area), 
+     xlim = c(0, 14), 
+     ylim = c(0, 14)) 
+abline(0, 1)
+abline(v = log(153.5), col = "red")
+
+# ---- maps ----
+
+test <- coordinatize(dplyr::filter(nes_nws, closest_lake_distance <= 2776.81), 
+                     "lat", "long")
+test[order(test$p_percent_retention, decreasing = TRUE),]
+test2 <- coordinatize(nes_nws, "lat", "long")
+
+us_states <- st_intersects(us_states(), test2)
+us_states <- us_states()[unlist(lapply(us_states, function(x) length(x) > 0)),]
+plot(us_states$geometry)
+plot(test2$geometry, add = TRUE)
+plot(test$geometry, add = TRUE, col = "red", fill = "red", pch = 19)

### 2018-03-12 scripts/99_utils.R

@@ -12,6 +12,8 @@ library(partykit)
 library(modelr)
 library(tidyr)
 library(ggridges)
+library(USAboundaries)
+library(sf)
 
 prep_full_nes <- function(nes_x_lagos, conny_metrics_path, join_lagos_gis = FALSE){
   

### 2018-03-12 scripts/03_viz.R
use ggplot for exploratory graphs

@@ -1,5 +1,6 @@
+# setwd("scripts")
 # source("scripts/99_utils.R")
-# source("scripts/01_prepdata.R")
+# source("01_prepdata.R")
 
 # ---- global_vollenweider_viz ----
 
@@ -225,33 +226,29 @@ plot_grid(md_v_la + theme(legend.position = "none"),
           ll_v_cd_nws + theme(legend.position = "none"),
           legend, ncol = 2, rel_heights = c(1, 1))
 
-plot(nes_iws$hu12_baseflowindex_mean, nes_nws$baseflow)
-abline(0, 1)
-abline(h = 52.94, col = "red")
-abline(v = 63.76, col = "red")
 
+ggplot() + geom_point(aes(nes_iws$hu12_baseflowindex_mean, nes_nws$baseflow)) + 
+  geom_hline(aes(yintercept = 52.94)) +
+  geom_vline(aes(xintercept = 63.76))
 
-plot(nes_iws$iws_streamdensity_streams_density_mperha, nes_nws$stream_density)
-abline(0, 1)
-abline(h = 10.4, col = "red")
-abline(v = 4.43, col = "red")
+ggplot() + geom_point(aes(nes_iws$iws_streamdensity_streams_density_mperha, 
+                          nes_nws$stream_density)) + 
+  geom_hline(aes(yintercept = 10.4), color = "red") +
+  geom_vline(aes(xintercept = 4.43), color = "red") +
+  geom_abline(aes(slope = 1, intercept = 0))
 
-plot(nes_iws$closest_lake_distance, nes_nws$closest_lake_distance)
-abline(0, 1)
-abline(h = 2776.81, col = "red")
-abline(v = 3773.61, col = "red")
-
-plot(log(nes_iws$upstream_lakes_4ha_area_ha), log(nes_nws$lake_area), 
-     xlim = c(0, 14), 
-     ylim = c(0, 14)) 
-abline(0, 1)
-abline(v = log(153.5), col = "red")
+ggplot() + geom_point(aes(nes_iws$closest_lake_distance, nes_nws$closest_lake_distance)) + 
+  geom_hline(aes(yintercept = 2776.81), color = "red") +
+  geom_vline(aes(xintercept = 3773.61), color = "red") +
+  geom_abline(aes(slope = 1, intercept = 0)) +
+  scale_x_log10() + 
+  scale_y_log10()
 
 # ---- maps ----
 
[…]

### 2018-03-13 scripts/analysis.Rmd
add some exploratory plots
plots on separate pages by adding captions

--- 2018-03-09 scripts/analysis.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5.5, fig.height = 4.2)
+knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5.5, fig.height = 4.2, fig.pos = 'H')
 ```
@@
 
-```{r k_viz, echo=FALSE, message=FALSE}
+```{r k_viz, echo=FALSE, message=FALSE, fig.cap="Distribution of Vollenweider's k in low and high connectivity partitions at the IWS and NWS scales."}
 
@@
 ```
+
+```{r graphical_exploratory_analysis, echo=FALSE, message=FALSE, warning=FALSE, fig.height=8.4, fig.cap="Exploratory plots"}
+
+```
+
+```{r maps, echo=FALSE, fig.cap="Map of lakes with low distance to nearest upstream lake at the NWS scale."}
+
+```
+
+<!-- * Olin Lake has a completely undeveloped shoreline -->
+<!-- * Madison Lake is impaired according to MPCA -->
+
+```{r conceptual_summary, echo=FALSE, fig.cap="Connectivity metric effects on lake processing."}
+dt <- data.frame(
+  rbind(
+        c("lakeconnection", "DR_Stream", "higher", "lower", "higher", "lake"), 
+        c("upstream lake area", "lower", "higher", "lower", "higher", "lake"), 
+        c("link_length", "lower", "higher", "lower", "higher", "stream"), 
+        c("baseflow", "higher", "higher", "lower", "higher", "stream"), 
+        c("stream order ratio", "higher", "higher", "lower", "higher", "stream"),
+  c("upstream lake distance", "lower", "higher", "lower", "higher", "lake-stream"), 
+        c("stream density", "higher", "higher", "lower", "higher", "stream")))
+
+names(dt) <- c("metric", "direction", "k", "connectivity", "in_lake_processing", "axis")
+
+knitr::kable(dt)
+```

### 2018-03-13 scripts/03_viz.R

@@ -224,25 +224,22 @@ plot_grid(md_v_la + theme(legend.position = "none"),
           md_v_ll_iws + theme(legend.position = "none"), 
           md_v_ll_nws + theme(legend.position = "none"),
           ll_v_cd_nws + theme(legend.position = "none"),
-          legend, ncol = 2, rel_heights = c(1, 1))
-
-
-ggplot() + geom_point(aes(nes_iws$hu12_baseflowindex_mean, nes_nws$baseflow)) + 
-  geom_hline(aes(yintercept = 52.94)) +
-  geom_vline(aes(xintercept = 63.76))
-
-ggplot() + geom_point(aes(nes_iws$iws_streamdensity_streams_density_mperha, 
+          ggplot() + geom_point(aes(nes_iws$hu12_baseflowindex_mean, nes_nws$baseflow)) + 
+            geom_hline(aes(yintercept = 52.94)) +
+            geom_vline(aes(xintercept = 63.76)),
+          ggplot() + geom_point(aes(nes_iws$iws_streamdensity_streams_density_mperha, 
                           nes_nws$stream_density)) + 
-  geom_hline(aes(yintercept = 10.4), color = "red") +
-  geom_vline(aes(xintercept = 4.43), color = "red") +
-  geom_abline(aes(slope = 1, intercept = 0))
-
-ggplot() + geom_point(aes(nes_iws$closest_lake_distance, nes_nws$closest_lake_distance)) + 
-  geom_hline(aes(yintercept = 2776.81), color = "red") +
-  geom_vline(aes(xintercept = 3773.61), color = "red") +
-  geom_abline(aes(slope = 1, intercept = 0)) +
-  scale_x_log10() + 
-  scale_y_log10()
+            geom_hline(aes(yintercept = 10.4), color = "red") +
+            geom_vline(aes(xintercept = 4.43), color = "red") +
+            geom_abline(aes(slope = 1, intercept = 0)),
+          ggplot() + geom_point(aes(nes_iws$closest_lake_distance, 
+                                    nes_nws$closest_lake_distance)) + 
+            geom_hline(aes(yintercept = 2776.81), color = "red") +
+            geom_vline(aes(xintercept = 3773.61), color = "red") +
+            geom_abline(aes(slope = 1, intercept = 0)) +
+            scale_x_log10() + 
+            scale_y_log10(), 
+          legend, ncol = 2)
 
 # ---- maps ----
 

### 2018-03-13 scripts/analysis.Rmd
organize summary table

--- 2018-03-09 scripts/analysis.Rmd
@@
 ```
+
+```{r graphical_exploratory_analysis, echo=FALSE, message=FALSE, warning=FALSE, fig.height=8.4, fig.cap="Exploratory plots"}
+
+```
+
+```{r maps, echo=FALSE, fig.cap="Map of lakes with low distance to nearest upstream lake at the NWS scale.", warning=FALSE, message=FALSE}
+
+```
+
+<!-- * Olin Lake has a completely undeveloped shoreline -->
+<!-- * Madison Lake is impaired according to MPCA -->
+
+```{r conceptual_summary, echo=FALSE, fig.cap="Connectivity metric effects on lake processing."}
+dt <- data.frame(
+  rbind(
+    c("closest lake distance", "lower", "higher", "lower", "higher", "lake-stream", "long"), 
+    c("average link length", "lower", "higher", "lower", "higher", "stream", "long"), 
+    c("lakeconnection", "DR_Stream", "higher", "lower", "higher", "lake", "long"), 
+    c("upstream lake area", "lower", "higher", "lower", "higher", "lake", "lat"), 
+    c("stream density", "higher", "higher", "lower", "higher", "stream", "lat"),
+    c("baseflow", "higher", "higher", "lower", "higher", "stream", "lat"), 
+    c("stream order ratio", "higher", "higher", "lower", "higher", "stream", "long")))
+
+names(dt) <- c("metric", "direction", "k", "connectivity", "in_lake_processing", "axis", "connectivity type")
+
+knitr::kable(dt)
+```

### 2018-03-13 scripts/03_viz.R

@@ -245,7 +245,7 @@ plot_grid(md_v_la + theme(legend.position = "none"),
 
 test <- coordinatize(dplyr::filter(nes_nws, closest_lake_distance <= 2776.81), 
                      "lat", "long")
-data.frame(test[order(test$p_percent_retention, decreasing = TRUE), c("state", "name")])
+# data.frame(test[order(test$p_percent_retention, decreasing = TRUE), c("state", "name")])
 test2 <- coordinatize(nes_nws, "lat", "long")
 
 us_states <- st_intersects(us_states(), test2)

### 2018-03-13 scripts/04_tables.R

@@ -1,3 +1,4 @@
+# setwd("scripts")
 source("99_utils.R")
 source("01_prepdata.R")
 
@@ -17,7 +18,7 @@ iws_parts  <- data.frame(table_splits("../data/iws/"),
 nws_parts  <- data.frame(table_splits("../data/nws/"), 
                          stringsAsFactors = FALSE)
 
-misc_parts$scale <- "misc"
+misc_parts$scale <- "focal"
 iws_parts$scale  <- "iws"
 nws_parts$scale  <- "nws"
 
@@ -26,7 +27,7 @@ rownames(misc_parts) <- rownames(iws_parts) <- rownames(nws_parts) <- NULL
 res <- rbind(misc_parts, iws_parts, nws_parts)
 res$splits <- as.numeric(res$splits)
 # res <- res[,1:ncol(res)]
-res <- rbind(res, data.frame(pnames = "lakeconnection", splits = NA, scale = "misc"))
+res <- rbind(res, data.frame(pnames = "lakeconnection", splits = NA, scale = "focal"))
 
 
 name_key <- data.frame(
@@ -64,7 +65,7 @@ d_k <- lapply(list("../data/lc_vollenweider.rds",
             "../data/nws/sr_vollenweider.rds"), delta_k)
 
 d_k <- do.call("rbind", d_k)
-d_k$scale <- c("misc", "misc", rep("iws", 5), rep("nws", 6))
+d_k$scale <- c("focal", "focal", rep("iws", 5), rep("nws", 6))
 
 res <- merge(res, d_k)
 res <- res[order(res$d_k, decreasing = TRUE),]

### 2018-03-16 scripts/03_viz.R
adjust map dot size and scale labels

@@ -257,7 +257,8 @@ partition_splits <- read.csv("../figures/table_1.csv")
 partition_splits <- dplyr::filter(partition_splits, !is.na(splits), 
                                   scale %in% c("nws", "iws"))
 partition_splits <- droplevels(partition_splits)
-levels(partition_splits$pnames2) <- c("cd", "ll", "la", "sd", "bf", "sr")
+partition_splits$pnames2 <- factor(partition_splits$pnames2, 
+                              levels = c("cd", "ll", "la", "sd", "bf", "sr"))
 
 nes_sf    <- coordinatize(nes_nws, "lat", "long")
 us_states <- st_intersects(us_states(), nes_sf)
@@ -277,10 +278,11 @@ lower_iws_maps <- lapply(which(partition_splits$scale == "iws"),
                            
                            ggplot() + 
                              geom_sf(data = us_states) +
-                             geom_sf(data = nes_sf) + 
-                             geom_sf(data = nes_sub, color = "red") + 
+                             geom_sf(data = nes_sf, size = 0.6) + 
+                             geom_sf(data = nes_sub, color = "red", size = 0.6) + 
                              coord_sf(datum = NA) + 
-                             ggtitle(partition_splits[x, "pnames2"])
+                             ggtitle(partition_splits[x, "pnames2"]) + 
+                             theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))
                          })
 
 lower_nws_maps <- lapply(which(partition_splits$scale == "nws"), 
@@ -291,10 +293,11 @@ lower_nws_maps <- lapply(which(partition_splits$scale == "nws"),
                            
                            ggplot() + 
                              geom_sf(data = us_states) +
-                             geom_sf(data = nes_sf) + 
-                             geom_sf(data = nes_sub, color = "red") + 
+                             geom_sf(data = nes_sf, size = 0.6) + 
+                             geom_sf(data = nes_sub, color = "red", size = 0.6) + 
                              coord_sf(datum = NA) + 
-                             ggtitle(partition_splits[x, "pnames2"])
+                             ggtitle(partition_splits[x, "pnames2"]) + 
+                             theme(plot.margin = unit(c(0, 0, 0, 0), "cm"))
[…]

### 2018-03-16 figures/conny_metric_key.tex
towards a connectivity metric cartoon

\documentclass[bigger]{beamer}
\usepackage[orientation=portrait, size=a0, scale=1.4]{beamerposter}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{pgfplots}
\usepackage{tabularx}

\setbeamertemplate{navigation symbols}{}%remove navigation symbols
\setbeamertemplate{caption}{\raggedright\insertcaption\par}

\input{beamer-lake-fig/beamer-lake-fig.tex}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Connectivity Metric Key}
\begin{frame}
  \begin{center}

  % cd %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{columns} [c]     
  \begin{column}{0.3\textwidth}
    \begin{tikzpicture}[scale = 0.6]
        \draw [-,ultra thick, cyan] (2.2,2.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
        \draw [-,ultra thick, cyan] (2.2,2.8) to [out=90,in=0] (1.1,3.1) to [out=270,in=90] (0,3.4);

        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 3.1cm] plot (\x:0.4+rnd*0.2);
        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 3cm, xshift = 2cm] plot (\x:0.6+rnd*0.2);
        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan] plot (\x:1+rnd*0.5);
      \end{tikzpicture}
  \end{column}

  \begin{column}{0.3\textwidth}
    \begin{tikzpicture}[scale = 0.6]
        \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 5cm, xshift = 2cm] plot (\x:0.6+rnd*0.2);
        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan] plot (\x:1+rnd*0.5);
      \end{tikzpicture}
  \end{column}
  \end{columns}

  % ll %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{columns}[c]  
    \begin{column}{0.3\textwidth}
      \begin{tikzpicture}[scale = 0.6]
        % \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
        \draw [-,ultra thick, cyan] (2,3) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
        \draw [-,ultra thick, cyan] (0.5,2.9) to [out=0,in=90] (1.1,1.9) to [out=270,in=90] (0,0);

        \draw [-,ultra thick, cyan] (-1,4) to [out=200,in=0] (-2,3) to [out=290,in=45] (-1.1,1.9) to [out=270,in=90] (0,0);        
        \draw [-,ultra thick, cyan] (-0.5,2.9) to [out=250,in=250] (-1.1,1.9) to [out=270,in=90] (0,0);

        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan] plot (\x:1+rnd*0.5);
      \end{tikzpicture}
    \end{column}

    \begin{column}{0.3\textwidth}
      \begin{tikzpicture}[scale = 0.6]
        %   \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
          \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
          \draw [-,ultra thick, cyan] (0.9,4) to [out=290,in=0] (1.1,1.9) to [out=270,in=90] (0,0);

          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan] plot (\x:1+rnd*0.5);
        \end{tikzpicture}
    \end{column}
    \end{columns}

    % la %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{columns}[c]  
    \begin{column}{0.3\textwidth}
      \begin{tikzpicture}[scale = 0.6]
        % \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
        \draw [-,ultra thick, cyan] (2,3) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
        \draw [-,ultra thick, cyan] (0.5,2.9) to [out=0,in=90] (1.1,1.9) to [out=270,in=90] (0,0);

        \draw [-,ultra thick, cyan] (-1,4) to [out=200,in=0] (-2,3) to [out=290,in=45] (-1.1,1.9) to [out=270,in=90] (0,0);        
        \draw [-,ultra thick, cyan] (-0.5,2.9) to [out=250,in=250] (-1.1,1.9) to [out=270,in=90] (0,0);

        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan] plot (\x:1+rnd*0.5);
      \end{tikzpicture}
    \end{column}

    \begin{column}{0.3\textwidth}
      \begin{tikzpicture}[scale = 0.6]
        %   \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
          \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
          \draw [-,ultra thick, cyan] (0.9,4) to [out=290,in=0] (1.1,1.9) to [out=270,in=90] (0,0);

          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan] plot (\x:1+rnd*0.5);
        \end{tikzpicture}
    \end{column}
    \end{columns}

  \end{center}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2018-03-19 figures/conny_metric_key.tex
add more to conny key diagram

@@
 \documentclass[bigger]{beamer}
-\usepackage[orientation=portrait, size=a0, scale=1.4]{beamerposter}
+\usepackage[orientation=portrait, size=a10, scale=1]{beamerposter}
 \usepackage[utf8]{inputenc}
@@
 
+    \begin{columns} [c]     
+      \begin{column}{0.4\textwidth}        
+      \end{column}
+
+    \begin{column}{0.25\textwidth}
+      \huge{Lower Connectivity}
+    \end{column}
+
+    \begin{column}{0.25\textwidth}
+      \huge{Higher Connectivity}
+    \end{column}
+    \end{columns}
+
   % cd %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
   \begin{columns} [c]     
-  \begin{column}{0.3\textwidth}
-    \begin{tikzpicture}[scale = 0.6]
+    \begin{column}{0.4\textwidth}
+      \huge{\textbf{Closest Lake Distance:} Network distance to the closest upstream lake.}
+    \end{column}
+
+  \begin{column}{0.25\textwidth}
+    \begin{tikzpicture}[scale = 2]
         \draw [-,ultra thick, cyan] (2.2,2.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
@@
 
-  \begin{column}{0.3\textwidth}
-    \begin{tikzpicture}[scale = 0.6]
+  \begin{column}{0.25\textwidth}
+    \begin{tikzpicture}[scale = 2]
         \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
@@
   \begin{columns}[c]  
-    \begin{column}{0.3\textwidth}
-      \begin{tikzpicture}[scale = 0.6]
+    \begin{column}{0.4\textwidth}
+      \huge{\textbf{Average Link Length:} Length of stream reaches where each stream reach starts and ends at a junction divided by the total number of reaches.}
+    \end{column}
+
+    \begin{column}{0.25\textwidth}
+      \begin{tikzpicture}[scale = 2]
+        %\draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
+        \draw [-,ultra thick, cyan] (2,3) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
+        \draw [-,ultra thick, cyan] (0.5,2.9) to [out=0,in=90] (1.1,1.9) to [out=270,in=90] (0,0);
+
+        \draw [-,ultra thick, cyan] (-1.2,3.7) to [out=200,in=0] (-2,3) to [out=290,in=45] (-1.1,1.9) to [out=270,in=90] (0,0);        
+        \draw [-,ultra thick, cyan] (-0.5,2.9) to [out=250,in=250] (-1.1,1.9) to [out=270,in=90] (0,0);
+
+        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan] plot (\x:1+rnd*0.5);
+      \end{tikzpicture}
+    \end{column}
+
+    \begin{column}{0.25\textwidth}
+      \begin{tikzpicture}[scale = 2]
+           %\draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
+          \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+          \draw [-,ultra thick, cyan] (0.9,4) to [out=290,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+
+          \draw [-,ultra thick, cyan] (-2.2,4.8) to [out=90,in=180] (-1.1,1.9) to [out=270,in=90] (0,0);
+          \draw [-,ultra thick, cyan] (-0.9,4) to [out=260,in=180] (-1.1,1.9) to [out=270,in=90] (0,0);
+
+          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan] plot (\x:1+rnd*0.5);
+        \end{tikzpicture}
+    \end{column}
+    \end{columns}
+
+  % la %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \begin{columns}[c]  
+    \begin{column}{0.4\textwidth}
+      \huge{\textbf{Upstream Lake Area:} Total area of upstream lakes limited to lakes that are greater than or equal to 4ha.}
+    \end{column}
+
+    \begin{column}{0.25\textwidth}
+      \begin{tikzpicture}[scale = 2]
+          \draw [-,ultra thick, cyan] (2.2,3.7) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 3.5cm, xshift = 2cm] plot (\x:0.5+rnd*0.2);
+          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan] plot (\x:1+rnd*0.5);
+        \end{tikzpicture}
+    \end{column}
+
+    \begin{column}{0.25\textwidth}
+      \begin{tikzpicture}[scale = 2]
+          \draw [-,ultra thick, cyan] (2.2,4.3) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 3.5cm, xshift = 2cm] plot (\x:0.9+rnd*0.2);
+          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan] plot (\x:1+rnd*0.5);
+        \end{tikzpicture}
+    \end{column}
+    \end{columns}
+
+    % sd %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \begin{columns}[c]  
+    \begin{column}{0.4\textwidth}
+      \huge{\textbf{Stream Density:} }
+    \end{column}
+
+    \begin{column}{0.25\textwidth}
+      \begin{tikzpicture}[scale = 2]
         % \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
@@
 
-    \begin{column}{0.3\textwidth}
-      \begin{tikzpicture}[scale = 0.6]
+    \begin{column}{0.25\textwidth}
+      \begin{tikzpicture}[scale = 2]
         %   \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
@@
 
-    % la %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+    % sr %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
   \begin{columns}[c]  
-    \begin{column}{0.3\textwidth}
-      \begin{tikzpicture}[scale = 0.6]
-        % \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
+    \begin{column}{0.4\textwidth}
+      \huge{\textbf{Stream Order Ratio:} The total number of first order stream reaches divided by the total number of higher order stream reaches.
+In this example the lower connectivity lake has a stream order ratio of 3 whereas the higher connectivity lake has a stream order ratio of 2.}
+    \end{column}
+
+    \begin{column}{0.25\textwidth}
+      \begin{tikzpicture}[scale = 2]
+        \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
         \draw [-,ultra thick, cyan] (2,3) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
@@
         \draw [-,ultra thick, cyan] (-0.5,2.9) to [out=250,in=250] (-1.1,1.9) to [out=270,in=90] (0,0);
+        \draw [-,ultra thick, cyan] (-1.8, 2.1) to [out=250,in=180] (-1,1.5)
 

### 2018-03-19 figures/conny_metric_key.tex
stash draft of conny metric key

@@
     \begin{column}{0.4\textwidth}
-      \huge{\textbf{Stream Density:} }
+      \huge{\textbf{Stream Density:} the length of all streams (minus artificial lines through lakes) divided by the area of watershed.}
     \end{column}
@@
       \begin{tikzpicture}[scale = 2]
-        \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
-        \draw [-,ultra thick, cyan] (2,3) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
+        %\draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
+        \draw [-,ultra thick, cyan] (2,3) to [out=180,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
         \draw [-,ultra thick, cyan] (0.5,2.9) to [out=0,in=90] (1.1,1.9) to [out=270,in=90] (0,0);
+        \draw [-,ultra thick, cyan] (1.8, 2.1) to [out=290,in=0] (1,1.5);
 
-        \draw [-,ultra thick, cyan] (-1,4) to [out=200,in=0] (-2,3) to [out=290,in=45] (-1.1,1.9) to [out=270,in=90] (0,0);        
+        \draw [-,ultra thick, cyan] (-1,4) to [out=200,in=0] (-2,3) to [out=290,in=135] (-1.1,1.9) to [out=270,in=90] (0,0);        
         \draw [-,ultra thick, cyan] (-0.5,2.9) to [out=250,in=250] (-1.1,1.9) to [out=270,in=90] (0,0);
-        \draw [-,ultra thick, cyan] (-1.8, 2.1) to [out=250,in=180] (-1,1.5)
+        \draw [-,ultra thick, cyan] (-1.8, 2.1) to [out=250,in=180] (-1,1.5);
 

### 2018-03-19 scripts/04_tables.R
working version of table 2

@@ -30,7 +30,6 @@ res$splits <- as.numeric(res$splits)
 # res <- res[,1:ncol(res)]
 res <- rbind(res, data.frame(pnames = "lakeconnection", splits = NA, scale = "focal"))
 
-
 name_key <- data.frame(
   parameter  = c("Max Depth", "Closest lake distance", 
                  "Stream order ratio", "Average Link Length", 
@@ -87,10 +86,35 @@ knitr::kable(res,
 
 # ---- table_2 ----
 # table describing basic properties of lake population
-qs <- function(x) quantile(nes_iws[,x], c(0.25, 0.5, 0.75), na.rm = TRUE)
-summary_names <- c("maxdepth", "retention_time_yr", "tp", 
-                   "p_percent_retention", 
-                   "p_surface_area_loading", "surface_area")
+nes_iws$percent_ag <- nes_iws$iws_nlcd1992_pct_81 + nes_iws$iws_nlcd1992_pct_82
+  
+name_key <- data.frame(property = c("maxdepth", "percent_ag", "percent_urban", 
+                                    "tp", "p_percent_retention", 
+                                    "chl", "secchi", "retention_time_yr"),
+                       Characteristic = c("Max Depth (m)", "Ag Landuse (%)", 
+                                          "% Urban", 
+                                       "TP (mg/L)", "P Retention (%)", 
+                                       "Chl (ug/L)", "Secchi (m)", 
+                                       "Residence Time (yr)"))
+
+qs <- function(x) quantile(nes_iws[,x], c(0.5, 0.25, 0.75), na.rm = TRUE)
+summary_names <- c("maxdepth", "percent_ag", 
+                   "tp", "p_percent_retention", 
+                   "secchi", "retention_time_yr")
 res <- lapply(summary_names, qs)
-res <- data.frame(do.call("rbind", res))
+res <- round(data.frame(do.call("rbind", res)), 2)
 res$property <- summary_names
+res <- merge(res, name_key, sort = FALSE)
+res <- res[,c(ncol(res), 2:(ncol(res) - 1))]
+names(res)[2:ncol(res)] <-c("Mean", "LQ", "UQ")
+knitr::kable(res)
+
+# ---- table_3 ----
+# correlation matrix
+
+# splits <- read.csv("../figures/table_1.csv", stringsAsFactors = FALSE)
+# unique(splits$pnames2)
+# dt <- dplyr::bind_rows(nes_iws[,
+#                                ])
+
+

### 2018-03-19 scripts/analysis.Rmd
adjust map dot size and scale labels
working version of table 2
include conny metric key

@@
 
+```{r table_2, echo=FALSE, fig.cap="Table 2"}
+
+```
+
+```{r table_3, echo=FALSE, fig.cap="Table 3"}
+
+```
+
 ```{r recursive_partitioning_viz, echo=FALSE, eval=FALSE}
@@
 
-```{r maps, echo=FALSE, fig.cap="Map of lakes with low distance to nearest upstream lake at the NWS scale.", warning=FALSE, message=FALSE}
+```{r maps, echo=FALSE, fig.cap="Map of lake connectivity partitions.", warning=FALSE, message=FALSE}
 
@@
 ```
+
+```{r fig.cap="Connectivity metric box"}
+knitr::include_graphics("../figures/conny_metric_key.pdf")
+```

### 2018-03-19 scripts/04_tables.R

@@ -137,5 +137,5 @@ nes_sub <- dplyr::bind_rows(nes_iws_sub, nes_nws_sub)
 
 library(corrr)
 
-res <- correlate(nes_sub)
-rplot(res)
+res <- shave(rearrange(correlate(nes_sub)))
+knitr::kable(res, digits = 2)

### 2018-03-19 scripts/04_tables.R
crop conny metric key

@@ -138,4 +138,7 @@ nes_sub <- dplyr::bind_rows(nes_iws_sub, nes_nws_sub)
 library(corrr)
 
 res <- shave(rearrange(correlate(nes_sub)))
+res <- res[apply(res[,2:ncol(res)], 1, function(x) !all(is.na(x))),]
+res <- res[,c(TRUE, apply(res[,2:ncol(res)], 2, function(x) !all(is.na(x))))]
+names(res)[1] <- ""
 knitr::kable(res, digits = 2)

### 2018-03-21 scripts/analysis.Rmd
crop conny metric key
include iws diagram, reorder figs

@@
 
+```{r table_2, echo=FALSE, fig.cap="Table 2"}
+
+```
+
+```{r fig.cap="Watershed diagram", echo=FALSE}
+knitr::include_graphics("../figures/iws_nws.pdf")
+```
+
+```{r fig.cap="Connectivity metric box", echo=FALSE}
+knitr::include_graphics("../figures/conny_metric_key_crop.pdf")
+```
+
+```{r table_3, echo=FALSE, fig.cap="Table 3"}
+
+```
+
 ```{r global_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from the non-hierarchical model posterior relative to raw data."}
@@
 
-```{r table_2, echo=FALSE, fig.cap="Table 2"}
+```{r maps, echo=FALSE, fig.cap="Map of lake connectivity partitions.", warning=FALSE, message=FALSE}
 
@@
 
-```{r table_3, echo=FALSE, fig.cap="Table 3"}
-
-```
+<!-- * Olin Lake has a completely undeveloped shoreline -->
+<!-- * Madison Lake is impaired according to MPCA -->
 
@@
 ```
-
-```{r maps, echo=FALSE, fig.cap="Map of lake connectivity partitions.", warning=FALSE, message=FALSE}
-
-```
-
-<!-- * Olin Lake has a completely undeveloped shoreline -->
-<!-- * Madison Lake is impaired according to MPCA -->
 
@@
 ```
-
-```{r fig.cap="Connectivity metric box"}
-knitr::include_graphics("../figures/conny_metric_key.pdf")
-```

### 2018-03-21 scripts/03_viz.R
add table captions

@@ -319,3 +319,4 @@ plot_grid(
   ncol = 1, labels = c(NA, "iws", NA, "nws"), 
   rel_heights = c(0.2, 1, 0.2, 1), vjust = -0.6, label_colour = "gray")
 
+# ggplot() + geom_point(data = nes_nws, aes(x = lg_long, y = lg_lat, color = baseflow))

### 2018-03-21 scripts/04_tables.R

@@ -82,7 +82,7 @@ res <- res[order(res$d_k, decreasing = TRUE),]
 res <- res[, c(1,2,4,7,8,9)]
 knitr::kable(res, 
              digits = 2, row.names = FALSE, 
-             col.names = c("Abb", "Scale", "Metric", "Connectivity Type", "Split Value", "Delta k"))
+             col.names = c("Abb", "Scale", "Metric", "Connectivity Type", "Split Value", "Delta k"), caption = "Partition cutoff table")
 
 # ---- table_2 ----
 # table describing basic properties of lake population
@@ -107,7 +107,8 @@ res$property <- summary_names
 res <- merge(res, name_key, sort = FALSE)
 res <- res[,c(ncol(res), 2:(ncol(res) - 1))]
 names(res)[2:ncol(res)] <-c("Mean", "LQ", "UQ")
-knitr::kable(res)
+knitr::kable(res, format = 'pandoc', 
+             caption = "Summary of study lake characteristics")
 
 # ---- table_3 ----
 # correlation matrix
@@ -141,4 +142,4 @@ res <- shave(rearrange(correlate(nes_sub)))
 res <- res[apply(res[,2:ncol(res)], 1, function(x) !all(is.na(x))),]
 res <- res[,c(TRUE, apply(res[,2:ncol(res)], 2, function(x) !all(is.na(x))))]
 names(res)[1] <- ""
-knitr::kable(res, digits = 2)
+knitr::kable(res, digits = 2, format = 'pandoc', caption = "Pearson correlation matrix among connectivity metrics")

### 2018-03-21 figures/conny_metric_key.tex
note focal lake, thicker higher order lines

@@
         \draw [-,ultra thick, cyan] (2.2,2.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
-        \draw [-,ultra thick, cyan] (2.2,2.8) to [out=90,in=0] (1.1,3.1) to [out=270,in=90] (0,3.4);
 
-        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 3.1cm] plot (\x:0.4+rnd*0.2);
         \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 3cm, xshift = 2cm] plot (\x:0.6+rnd*0.2);
-        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan] plot (\x:1+rnd*0.5);
+        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
       \end{tikzpicture}
@@
         \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 5cm, xshift = 2cm] plot (\x:0.6+rnd*0.2);
-        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan] plot (\x:1+rnd*0.5);
+        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
       \end{tikzpicture}
@@
     \begin{column}{0.4\textwidth}
-      \huge{\textbf{Average Link Length:} Length of stream reaches where each stream reach starts and ends at a junction divided by the total number of reaches.}
+      \huge{\textbf{Average Link Length:} Sum of the total length of stream reaches between junctions divided by the total number of reaches.}
     \end{column}
@@
         %\draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
-        \draw [-,ultra thick, cyan] (2,3) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
+        \draw [-,ultra thick, cyan] (1.8,2.6) to [out=180,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
         \draw [-,ultra thick, cyan] (0.5,2.9) to [out=0,in=90] (1.1,1.9) to [out=270,in=90] (0,0);
 
-        \draw [-,ultra thick, cyan] (-1.2,3.7) to [out=200,in=0] (-2,3) to [out=290,in=45] (-1.1,1.9) to [out=270,in=90] (0,0);        
-        \draw [-,ultra thick, cyan] (-0.5,2.9) to [out=250,in=250] (-1.1,1.9) to [out=270,in=90] (0,0);
+        \draw [-,ultra thick, cyan] (-1.2,3.4) to [out=200,in=0] (-1.8,2.4) to [out=290,in=110] (-1.1,1.9) to [out=270,in=90] (0,0);        
+        \draw [-,ultra thick, cyan] (-0.5,2.9) to [out=250,in=70] (-1.1,1.9) to [out=270,in=90] (0,0);
 
-        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan] plot (\x:1+rnd*0.5);
+        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
       \end{tikzpicture}
@@
 
-          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan] plot (\x:1+rnd*0.5);
+          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
         \end{tikzpicture}
@@
           \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 3.5cm, xshift = 2cm] plot (\x:0.5+rnd*0.2);
-          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan] plot (\x:1+rnd*0.5);
+          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
         \end{tikzpicture}
@@
       \begin{tikzpicture}[scale = 2]
-          \draw [-,ultra thick, cyan] (2.2,4.3) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+          \draw [-,ultra thick, cyan] (2.2,4.1) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
           \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 3.5cm, xshift = 2cm] plot (\x:0.9+rnd*0.2);
-          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan] plot (\x:1+rnd*0.5);
+          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
         \end{tikzpicture}
@@
 
-        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan] plot (\x:1+rnd*0.5);
+        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
       \end{tikzpicture}
@@
       \begin{tikzpicture}[scale = 2]
-        %\draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
+        % \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
         \draw [-,ultra thick, cyan] (2,3) to [out=180,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
-        \draw [-,ultra thick, cyan] (0.5,2.9) to [out=0,in=90] (1.1,1.9) to [out=270,in=90] (0,0);
+        \draw [-,ultra thick, cyan] (0.5,2.9) to [out=0,in=90] (1.1,1.9);
+        \draw [-, line width = 7pt, cyan] (1.1,1.9) to [out=270,in=90] (0,0);
         \draw [-,ultra thick, cyan] (1.8, 2.1) to [out=290,in=0] (1,1.5);
 
-        \draw [-,ultra thick, cyan] (-1,4) to [out=200,in=0] (-2,3) to [out=290,in=135] (-1.1,1.9) to [out=270,in=90] (0,0);        
+        \draw [-,ultra thick, cyan] (-1,4) to [out=200,in=0] (-2,3) to [out=290,in=135] (-1.1,1.9);
+        \draw [-, line width = 7pt, cyan] (-1.1,1.9) to [out=270,in=90] (0,0);
         \draw [-,ultra thick, cyan] (-0.5,2.9) to [out=250,in=250] (-1.1,1.9) to [out=270,in=90] (0,0);
@@
           \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
-          \draw [-,ultra thick, cyan] (0.9,4) to [out=290,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+          \draw [-, ultra thick, cyan] (0.9,4) to [out=290,in=0] (1.1,1.9);
+          \draw [-,line width=7pt, cyan] (1.1,1.9) to [out=270,in=90] (0,0);
 
-          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan] plot (\x:1+rnd*0.5);
+          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
         \end{tikzpicture}

### 2018-03-21 scripts/04_tables.R
rename table chunks, convert chl units

@@ -84,7 +84,7 @@ knitr::kable(res,
              digits = 2, row.names = FALSE, 
              col.names = c("Abb", "Scale", "Metric", "Connectivity Type", "Split Value", "Delta k"), caption = "Partition cutoff table")
 
-# ---- table_2 ----
+# ---- lake_characteristics_table ----
 # table describing basic properties of lake population
 nes_iws$percent_ag <- nes_iws$iws_nlcd1992_pct_81 + nes_iws$iws_nlcd1992_pct_82
   
@@ -93,7 +93,7 @@ name_key <- data.frame(property = c("maxdepth", "percent_ag", "percent_urban",
                                     "chl", "secchi", "retention_time_yr"),
                        Characteristic = c("Max Depth (m)", "Ag Landuse (%)", 
                                           "% Urban", 
-                                       "TP (mg/L)", "P Retention (%)", 
+                                       "TP (ug/L)", "P Retention (%)", 
                                        "Chl (ug/L)", "Secchi (m)", 
                                        "Residence Time (yr)"))
 
@@ -104,14 +104,21 @@ summary_names <- c("maxdepth", "percent_ag",
 res <- lapply(summary_names, qs)
 res <- round(data.frame(do.call("rbind", res)), 2)
 res$property <- summary_names
+
+# unit conversions
+res[res$property == "tp", 1:3] <- 1000 * res[res$property == "tp", 1:3] # mg to ug
+
 res <- merge(res, name_key, sort = FALSE)
 res <- res[,c(ncol(res), 2:(ncol(res) - 1))]
 names(res)[2:ncol(res)] <-c("Mean", "LQ", "UQ")
+
 knitr::kable(res, format = 'pandoc', 
              caption = "Summary of study lake characteristics")
 
-# ---- table_3 ----
+# ---- cor_mat_table ----
 # correlation matrix
+
+library(corrr)
 
 splits      <- read.csv("../figures/table_1.csv", stringsAsFactors = FALSE)
 nes_iws_sub <- dplyr::select(nes_iws, -lakeconnection)
@@ -135,8 +142,6 @@ nws_key <- nws_key[!duplicated(nws_key),]
 names(nes_nws_sub) <- nws_key$pnames2
 
 nes_sub <- dplyr::bind_rows(nes_iws_sub, nes_nws_sub)
-
-library(corrr)
 
 res <- shave(rearrange(correlate(nes_sub)))
 res <- res[apply(res[,2:ncol(res)], 1, function(x) !all(is.na(x))),]

### 2018-03-23 scripts/03_viz.R
explore pnt vs nonpnt src p loading and retention

@@ -251,6 +251,14 @@ plot_grid(md_v_la + theme(legend.position = "none"),
           
           legend, ncol = 2)
 
+# nes_iws$p_pnt_source <-  rowSums(cbind(nes_iws$p_pnt_source_muni,
+#                                        nes_iws$p_pnt_source_septic,
+#                                        nes_iws$p_pnt_source_industrial), 
+#                                  na.rm = TRUE)
+# 
+# plot(nes_iws$p_pnt_source / 
+#        nes_iws$p_nonpnt_source, nes_iws$p_percent_retention)
+
 # ---- maps ----
 
 partition_splits <- read.csv("../figures/table_1.csv")

### 2018-03-23 scripts/04_tables.R
explore alternative field abbrevations

@@ -2,8 +2,35 @@
 source("99_utils.R")
 source("01_prepdata.R")
 
-# ---- table_1 ----
+# ---- model_results_table ----
 # table showing model results
+
+name_key <- function(){
+  data.frame(
+    parameter  = c("Max Depth", "Closest lake distance", 
+                   "Stream order ratio", "Average Link Length", 
+                   "Upstream lake area", "Baseflow", 
+                   "Wetland Cover",
+                   "Stream density", "Lake Connection"),
+    abb        = c("Max depth", "Closest  \n lake dist.", "S. order \n ratio", 
+                   "Avg. link \n len.", "Up. lake \n area", "Baseflow", 
+                   "W. Cover", "Stream \n density", "Lake Con."), 
+    pnames     = c("maxdepth", "cd", 
+                   "sr", "linklength", 
+                   "uplakearea", "baseflow", 
+                   "wetland-cover", 
+                   "streamdensity", "lakeconnection"), 
+    pnames2 = c("md", "cd", "sr", "ll", "la", "bf", "wc", "sd", "lc"), 
+    nws_names = c("maxdepth", "closest_lake_distance", "stream_order_ratio", 
+                  "link_length", "upstream_lakes_4ha_area_ha", "baseflow", NA, 
+                  "stream_density", "lakeconnection"),
+    iws_names = c("maxdepth", "closest_lake_distance", "stream_order_ratio", 
+                  "link_length", NA, "hu12_baseflowindex_mean", NA, 
+                  "iws_streamdensity_streams_density_mperha", "lakeconnection"),
+    conny_type = c(NA, "long", "long", "long", "lat", "lat", "lat", "lat", "long")
+  )
+}
+
 table_splits <- function(dir, pat = "forest.rds"){
   parts  <- list.files(dir, pattern = pat, 
                            full.names = TRUE, include.dirs = TRUE)
@@ -30,28 +57,7 @@ res$splits <- as.numeric(res$splits)
 # res <- res[,1:ncol(res)]
 res <- rbind(res, data.frame(pnames = "lakeconnection", splits = NA, scale = "focal"))
 
-name_key <- data.frame(
-  parameter  = c("Max Depth", "Closest lake distance", 
[…]

### 2018-03-23 scripts/99_utils.R
towards dual color model prediction plots

@@ -146,29 +146,59 @@ part_pred_plot <- function(nes, fit, ind, title, xl = TRUE, yl = TRUE){
   test     <- split(test, f = test$part)
   test     <- lapply(test, function(x) group_by(x, retention_time_yr))
   
-  res <- ggplot() +
-    stat_lineribbon(data = test[1][[1]], 
-                       aes(x = retention_time_yr, 
-                           y = estimate), .prob = 0.95, size = 0.5) + 
-    stat_lineribbon(data = test[2][[1]], 
-                    aes(x = retention_time_yr, 
-                        y = estimate), .prob = 0.95, alpha = 0.3, size  = 0.5) + 
-    geom_point(data = nes, aes(x = retention_time_yr, 
-                               y = p_percent_retention)) + 
-    scale_x_log10() + ylim(0, 1) + 
-    scale_fill_viridis_d(begin = (1 / 9) * ind) + 
-    theme_pred() + ggtitle(title) +
-    ylab("P Retention (%)") +  xlab("Residence Time (yr)")
+  browser()
   
-  if(!xl){
-    res <- res + theme(axis.title.x = element_blank())
+  gg_format <- function(gg){
+    gg <- gg + geom_point(data = nes, aes(x = retention_time_yr, 
+                               y = p_percent_retention)) +
+      theme(legend.position = "none") + 
+      ylim(0, 1) + scale_x_log10() + ggtitle(title) +
+      ylab("P Retention (%)") + xlab("Residence Time (yr)")
+    
+    if(!xl){
+      gg <- gg + theme(axis.title.x = element_blank())
+    }
+    
+    if(!yl){
+      gg <- gg + theme(axis.title.y = element_blank())
+    }
   }
   
-  if(!yl){
-    res <- res + theme(axis.title.y = element_blank())
-  }
+  # https://stackoverflow.com/a/37623958/3362993
+  gg_1 <- ggplot() + 
+    stat_summary(data = test[1][[1]], geom = "ribbon", 
+                 aes(x = retention_time_yr, y = estimate, 
+                     fill = forcats::fct_rev(ordered(...prob..))), 
+                 fun.data = median_qi, fun.args = list(.prob = 0.95), alpha = 0.3) +
+    stat_summary(data = test[1][[1]], aes(x = retention_time_yr, y = estimate), 
+                 fun.y = median, geom = "line", color = viridis::viridis(1, begin = 1), 
[…]

### 2018-03-23 scripts/99_utils.R
rm stray debug line, fix plot error

@@ -146,8 +146,6 @@ part_pred_plot <- function(nes, fit, ind, title, xl = TRUE, yl = TRUE){
   test     <- split(test, f = test$part)
   test     <- lapply(test, function(x) group_by(x, retention_time_yr))
   
-  browser()
-  
   gg_format <- function(gg){
     gg <- gg + geom_point(data = nes, aes(x = retention_time_yr, 
                                y = p_percent_retention)) +
@@ -162,6 +160,7 @@ part_pred_plot <- function(nes, fit, ind, title, xl = TRUE, yl = TRUE){
     if(!yl){
       gg <- gg + theme(axis.title.y = element_blank())
     }
+    gg
   }
   
   # https://stackoverflow.com/a/37623958/3362993
@@ -192,12 +191,16 @@ part_pred_plot <- function(nes, fit, ind, title, xl = TRUE, yl = TRUE){
     
   gg_1 <- gg_format(gg_1)
   gg_2 <- gg_format(gg_2)
+  
   g1 <- ggplotGrob(gg_1)
   g2 <- ggplotGrob(gg_2)
+  # gtable::gtable_show_layout(g1)
+  # print(g2)
   g2 <- gtable::gtable_filter(g2, "panel")
   
   gg <- gtable::gtable_add_grob(g1, g2, t = 6, l = 4)
   
+  grid::grid.newpage()
   grid::grid.draw(gg)
 }
 

### 2018-03-23 scripts/analysis.Rmd
add table captions
rename table chunks, convert chl units
explore alternative field abbrevations
reize, rescale plots, suppress warnings

@@
 
-```{r table_2, echo=FALSE, fig.cap="Table 2"}
+```{r lake_characteristics_table, echo=FALSE, results='asis'}
 
@@
 
-```{r table_3, echo=FALSE, fig.cap="Table 3"}
+```{r cor_mat_table, echo=FALSE, results='asis'}
 
@@
 
-```{r global_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from the non-hierarchical model posterior relative to raw data."}
+```{r global_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from the non-hierarchical model posterior relative to raw data.", warning=FALSE}
 
@@
 ```{r partition_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from the hierarchical model posteriors relative to raw data.
-Dark lines and shaded polygons represent the estimates from the lower of the two partition groups (see Table 1)", fig.height=8.4}
+Dark lines and shaded polygons represent the estimates from the lower of the two partition groups (see Table 1)", fig.height=8.4, warning=FALSE}
 
@@
 
-```{r table_1, echo=FALSE, fig.cap="Table 1"}
+```{r model_results_table, echo=FALSE, results='asis'}
 

### 2018-03-23 scripts/03_viz.R

@@ -61,7 +61,8 @@ plot_grid(
                  6, "Baseflow"),
   part_pred_plot(nes_nws, readRDS("../data/nws/la_vollenweider.rds"),
                  6, "Upstream Lake Area", yl = FALSE), 
-  nrow = 4, ncol = 2, rel_widths = c(1, 0.9))
+  nrow = 4, ncol = 2, rel_widths = c(1, 0.9), 
+  rel_heights = c(0.75, 0.75, 0.75, 1))
 
 # ---- k_viz ----
 

### 2018-03-23 scripts/99_utils.R

@@ -147,8 +147,7 @@ part_pred_plot <- function(nes, fit, ind, title, xl = TRUE, yl = TRUE){
   test     <- lapply(test, function(x) group_by(x, retention_time_yr))
   
   gg_format <- function(gg){
-    gg <- gg + geom_point(data = nes, aes(x = retention_time_yr, 
-                               y = p_percent_retention)) +
+    gg <- gg + 
       theme(legend.position = "none") + 
       ylim(0, 1) + scale_x_log10() + ggtitle(title) +
       ylab("P Retention (%)") + xlab("Residence Time (yr)")
@@ -165,24 +164,27 @@ part_pred_plot <- function(nes, fit, ind, title, xl = TRUE, yl = TRUE){
   
   # https://stackoverflow.com/a/37623958/3362993
   gg_1 <- ggplot() + 
+    geom_point(data = nes, aes(x = retention_time_yr, 
+                               y = p_percent_retention), 
+               size = 0.9) +
     stat_summary(data = test[1][[1]], geom = "ribbon", 
                  aes(x = retention_time_yr, y = estimate, 
                      fill = forcats::fct_rev(ordered(...prob..))), 
-                 fun.data = median_qi, fun.args = list(.prob = 0.95), alpha = 0.3) +
+                 fun.data = median_qi, fun.args = list(.prob = 0.95), alpha = 0.15) +
     stat_summary(data = test[1][[1]], aes(x = retention_time_yr, y = estimate), 
-                 fun.y = median, geom = "line", color = viridis::viridis(1, begin = 1), 
+                 fun.y = median, geom = "line", color = viridis::viridis(1, begin = 0.5), 
                  size = 0.5) +
-    scale_fill_viridis_d(begin = 1)
+    scale_fill_viridis_d(begin = 0.5)
   
   gg_2 <- ggplot() +
     stat_summary(data = test[2][[1]], geom = "ribbon", 
                  aes(x = retention_time_yr, y = estimate, 
                      fill = forcats::fct_rev(ordered(...prob..))), 
-                 fun.data = median_qi, fun.args = list(.prob = c(0.95)), alpha = 0.3) + 
+                 fun.data = median_qi, fun.args = list(.prob = c(0.95)), alpha = 0.15) + 
     stat_summary(data = test[2][[1]], aes(x = retention_time_yr, y = estimate), 
[…]

### 2018-03-26 scripts/analysis.Rmd
recolor and reorder plot panels

@@
 
-```{r conceptual_summary, echo=FALSE, fig.cap="Connectivity metric effects on lake processing."}
+```{r conceptual_summary, echo=FALSE, fig.cap="Connectivity metric effects on lake processing.", eval=FALSE}
 dt <- data.frame(

### 2018-03-26 scripts/03_viz.R

@@ -47,20 +47,24 @@ plot_tree(gettree(readRDS("../data/iws/streamdensity_forest.rds")),
 plot_grid(
   part_pred_plot(nes_iws, readRDS("../data/lc_vollenweider.rds"), 
                  9, "Lake Connection", xl = FALSE),
-  part_pred_plot(nes_iws, readRDS("../data/nws/cd_vollenweider.rds"),
-                 9, "Distance to Closest Lake", xl = FALSE, yl = FALSE), 
-  part_pred_plot(nes_iws, readRDS("../data/md_vollenweider.rds"), 
-                 8, "Max Depth", xl = FALSE),
   part_pred_plot(nes_nws, readRDS("../data/nws/ll_vollenweider.rds"),
                  8, "Link Length", xl = FALSE, yl = FALSE),
+  
+  part_pred_plot(nes_iws, readRDS("../data/md_vollenweider.rds"), 
+                 8, "Max Depth", xl = FALSE),
+  part_pred_plot(nes_nws, readRDS("../data/nws/cd_vollenweider.rds"),
+                 9, "Distance to Closest Lake", xl = FALSE, yl = FALSE),
+  
   part_pred_plot(nes_iws, readRDS("../data/iws/ll_vollenweider.rds"),
                  7, "Link Length", xl = FALSE), 
-  part_pred_plot(nes_iws, readRDS("../data/lc_vollenweider.rds"), 
-                 7, "Lake Connection", yl = FALSE, xl = FALSE),
+  part_pred_plot(nes_nws, readRDS("../data/nws/sd_vollenweider.rds"),
+                 9, "Stream Density", xl = FALSE, yl = FALSE),
+  
   part_pred_plot(nes_iws, readRDS("../data/iws/bf_vollenweider.rds"),
                  6, "Baseflow"),
-  part_pred_plot(nes_nws, readRDS("../data/nws/la_vollenweider.rds"),
-                 6, "Upstream Lake Area", yl = FALSE), 
+  part_pred_plot(nes_nws, readRDS("../data/lc_vollenweider.rds"), 
+                 7, "Lake Connection", yl = FALSE, xl = FALSE),
+  
   nrow = 4, ncol = 2, rel_widths = c(1, 0.9), 
   rel_heights = c(0.75, 0.75, 0.75, 1))
 
@@ -130,14 +134,14 @@ fit_df_nws <- rbind(
                  c("k1_sr", "k2_sr")))
 
[…]

### 2018-03-26 scripts/04_tables.R

@@ -12,9 +12,9 @@ name_key <- function(){
                    "Upstream lake area", "Baseflow", 
                    "Wetland Cover",
                    "Stream density", "Lake Connection"),
-    abb        = c("Max depth", "Closest  \n lake dist.", "S. order \n ratio", 
-                   "Avg. link \n len.", "Up. lake \n area", "Baseflow", 
-                   "W. Cover", "Stream \n density", "Lake Con."), 
+    abb        = c("Max depth", "Closest lake dist.", "S. order ratio", 
+                   "Avg. link len.", "Up. lake area", "Baseflow", 
+                   "W. Cover", "Stream density", "Lake Con."), 
     pnames     = c("maxdepth", "cd", 
                    "sr", "linklength", 
                    "uplakearea", "baseflow", 
@@ -94,7 +94,7 @@ knitr::kable(res,
              digits = 2, row.names = FALSE, 
              col.names = c("Abb", "Scale", "Metric", 
                            "Connectivity Type", "Split Value", "Delta k"), 
-             caption = "Partition cutoff table")
+             caption = "Results table")
 
 # ---- lake_characteristics_table ----
 # table describing basic properties of lake population
@@ -161,15 +161,14 @@ res <- res[apply(res[,2:ncol(res)], 1, function(x) !all(is.na(x))),]
 res <- res[,c(TRUE, apply(res[,2:ncol(res)], 2, function(x) !all(is.na(x))))]
 names(res)[1] <- ""
 
-# pander::panderOptions('keep.line.breaks', TRUE)
-pander::panderOptions("round", 2)
-pander::panderOptions("missing", '')
-# pander::pander(res, 
-#       caption = "Pearson correlation matrix among connectivity metrics", 
-#       split.cells = c(11, 0.8, 0.8, 0.8, 0.8, 0.8, 0.8))
+options(knitr.kable.NA = '')
+knitr::kable(res, digits = 2, 
+             caption = "Pearson correlation matrix among connectivity metrics.")
 
-pander::pandoc.table(res, style = "grid", keep.line.breaks = TRUE)
-
-# options(knitr.kable.NA = '')
-# knitr::kable(res, digits = 2, format = 'pandoc', 
-#              caption = "Pearson correlation matrix among connectivity metrics")
+# # pander::panderOptions('keep.line.breaks', TRUE)
+# pander::panderOptions("round", 2)
+# pander::panderOptions("missing", '')
[…]

### 2018-03-27 scripts/analysis.Rmd
recolor and align panel plots

@@
 ```{r partition_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from the hierarchical model posteriors relative to raw data.
-Dark lines and shaded polygons represent the estimates from the lower of the two partition groups (see Table 1)", fig.height=8.4, warning=FALSE}
+Lighter colored lines and shaded polygons represent the estimates from the lower of the two partition groups (see Table 3)", fig.height=7, fig.width = 5, warning=FALSE}
 
@@
 
-```{r k_viz, echo=FALSE, message=FALSE, fig.cap="Distribution of Vollenweider's k in low and high connectivity partitions at the IWS and NWS scales."}
+```{r k_viz, echo=FALSE, message=FALSE, fig.cap="Distribution of Vollenweider's k in low and high connectivity partitions at the IWS and NWS scales.", fig.width=6, warning=FALSE}
 
@@
 
-```{r maps, echo=FALSE, fig.cap="Map of lake connectivity partitions.", warning=FALSE, message=FALSE}
+```{r maps, echo=FALSE, fig.cap="Map of lake connectivity partitions where lighter colored lakes have matric values on the lower side of the respective partition in Table 3.", warning=FALSE, message=FALSE}
 

### 2018-03-27 scripts/03_viz.R

@@ -53,7 +53,7 @@ plot_grid(
   part_pred_plot(nes_iws, readRDS("../data/md_vollenweider.rds"), 
                  8, "Max Depth", xl = FALSE),
   part_pred_plot(nes_nws, readRDS("../data/nws/cd_vollenweider.rds"),
-                 9, "Distance to Closest Lake", xl = FALSE, yl = FALSE),
+                 9, "Distance to \n Closest Lake", xl = FALSE, yl = FALSE),
   
   part_pred_plot(nes_iws, readRDS("../data/iws/ll_vollenweider.rds"),
                  7, "Link Length", xl = FALSE), 
@@ -63,10 +63,10 @@ plot_grid(
   part_pred_plot(nes_iws, readRDS("../data/iws/bf_vollenweider.rds"),
                  6, "Baseflow"),
   part_pred_plot(nes_nws, readRDS("../data/lc_vollenweider.rds"), 
-                 7, "Lake Connection", yl = FALSE, xl = FALSE),
+                 7, "Lake Connection", yl = FALSE, xl = TRUE),
   
   nrow = 4, ncol = 2, rel_widths = c(1, 0.9), 
-  rel_heights = c(0.75, 0.75, 0.75, 1))
+  rel_heights = c(0.85, 0.85, 0.85, 1))
 
 # ---- k_viz ----
 
@@ -102,17 +102,30 @@ fit_df_iws$key <- factor(fit_df_iws$key, levels = c("k",
 k_viz_iws <- ggplot(
   fit_df_iws, 
   aes(x = coef, y = key, fill = key)) + 
-    geom_density_ridges(size = 2) + ylab("") + 
-    scale_fill_manual(values = c(viridis::viridis(10)[1], 
-                                 rep(viridis::viridis(10)[2:10], each = 2))) + 
-    cowplot::theme_cowplot() + theme(text = element_text(size = 20), 
+    geom_density_ridges(size = 1, rel_min_height = 0.03) + 
+    scale_fill_manual(values = c("grey", 
+                            rep(c(viridis::viridis(1, begin = 0.5), 
+                                  viridis::viridis(1, begin = 0)), 7))) + 
+    cowplot::theme_cowplot() + theme(text = element_text(size = 14), 
                                      axis.text = element_text(size = 10), 
-                                     axis.line.x = element_line(size = 2, 
+                                     axis.text.y = element_text(size = 8), 
+                                     axis.line.x = element_line(size = 1, 
                                      colour = "black"),
[…]

### 2018-03-27 scripts/99_utils.R

@@ -105,7 +105,8 @@ full_pred_plot <- function(nes, fit){
   ggplot() + 
     stat_lineribbon(data = test, 
                              aes(x = retention_time_yr, 
-                                 y = estimate), .prob = c(0.95)) + 
+                                 y = estimate), .prob = c(0.95), 
+                    fill = "grey", color = "grey", alpha = 0.5) + 
     geom_point(data = nes, aes(x = retention_time_yr, 
                                y = p_percent_retention)) + 
     scale_x_log10() + ylim(0, 1) +

### 2018-03-27 scripts/analysis.Rmd
adjust fig size

@@
 
-```{r global_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from the non-hierarchical model posterior relative to raw data.", warning=FALSE}
+```{r global_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from the non-hierarchical model posterior relative to raw data.", warning=FALSE, fig.width = 4.8, fig.height = 3.6}
 

### 2018-03-27 scripts/04_tables.R
format results table

@@ -89,10 +89,17 @@ res <- res[order(res$d_k, decreasing = TRUE),]
 # pander::pander(res)
 
 res <- res[, c(1,2,4,8,9,10)]
+res <- res[,c(3, 2, 4, 5, 6)]
+
+key2 <- data.frame(conny_type = unique(as.character(res$conny_type)), 
+                   conny_full = c("Longitudinal", "Lateral", NA))
+res <- merge(res, key2, sort = FALSE)
+res <- res[order(res$d_k, decreasing = TRUE),]
+res <- res[,c(2, 3, 6, 4, 5)]
 
 knitr::kable(res, 
              digits = 2, row.names = FALSE, 
-             col.names = c("Abb", "Scale", "Metric", 
+             col.names = c("Metric", "Scale",
                            "Connectivity Type", "Split Value", "Delta k"), 
              caption = "Results table")
 

### 2018-03-28 scripts/analysis.Rmd
align and resize per lno author instructions

--- 2018-03-27 scripts/analysis.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5.5, fig.height = 4.2, fig.pos = 'H')
+knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6, fig.pos = 'H')
 ```
@@
 
-```{r global_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from the non-hierarchical model posterior relative to raw data.", warning=FALSE}
+```{r global_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from the non-hierarchical model posterior relative to raw data.", warning=FALSE, fig.width = 3.5, fig.height = 3.2}
 
@@
 ```{r partition_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from the hierarchical model posteriors relative to raw data.
-Lighter colored lines and shaded polygons represent the estimates from the lower of the two partition groups (see Table 3)", fig.height=7, fig.width = 5, warning=FALSE}
+Lighter colored lines and shaded polygons represent the estimates from the lower of the two partition groups (see Table 3)", fig.width = 4.8, fig.height=5, warning=FALSE}
 
@@
 
-```{r k_viz, echo=FALSE, message=FALSE, fig.cap="Distribution of Vollenweider's k in low and high connectivity partitions at the IWS and NWS scales.", fig.width=6, warning=FALSE}
+```{r k_viz, echo=FALSE, message=FALSE, fig.cap="Distribution of Vollenweider's k in low and high connectivity partitions at the IWS and NWS scales.", fig.width=5, fig.height=3.8, warning=FALSE}
 

### 2018-03-28 scripts/03_viz.R

@@ -46,27 +46,15 @@ plot_tree(gettree(readRDS("../data/iws/streamdensity_forest.rds")),
 
 plot_grid(
   part_pred_plot(nes_iws, readRDS("../data/lc_vollenweider.rds"), 
-                 9, "Lake Connection", xl = FALSE),
+                 9, "Lake connection", xl = FALSE),
   part_pred_plot(nes_nws, readRDS("../data/nws/ll_vollenweider.rds"),
-                 8, "Link Length", xl = FALSE, yl = FALSE),
-  
+                 8, "Link length", xl = FALSE, yl = FALSE),
   part_pred_plot(nes_iws, readRDS("../data/md_vollenweider.rds"), 
-                 8, "Max Depth", xl = FALSE),
+                 8, "Max depth", xl = TRUE),
   part_pred_plot(nes_nws, readRDS("../data/nws/cd_vollenweider.rds"),
-                 9, "Distance to \n Closest Lake", xl = FALSE, yl = FALSE),
-  
-  part_pred_plot(nes_iws, readRDS("../data/iws/ll_vollenweider.rds"),
-                 7, "Link Length", xl = FALSE), 
-  part_pred_plot(nes_nws, readRDS("../data/nws/sd_vollenweider.rds"),
-                 9, "Stream Density", xl = FALSE, yl = FALSE),
-  
-  part_pred_plot(nes_iws, readRDS("../data/iws/bf_vollenweider.rds"),
-                 6, "Baseflow"),
-  part_pred_plot(nes_nws, readRDS("../data/lc_vollenweider.rds"), 
-                 7, "Lake Connection", yl = FALSE, xl = TRUE),
-  
-  nrow = 4, ncol = 2, rel_widths = c(1, 0.9), 
-  rel_heights = c(0.85, 0.85, 0.85, 1))
+                 9, "Distance to \n closest lake", xl = TRUE, yl = FALSE),
+  nrow = 2, ncol = 2, rel_widths = c(1, 0.93), 
+  rel_heights = c(0.88, 1))
 
 # ---- k_viz ----
 
@@ -106,9 +94,9 @@ k_viz_iws <- ggplot(
     scale_fill_manual(values = c("grey", 
                             rep(c(viridis::viridis(1, begin = 0.5), 
                                   viridis::viridis(1, begin = 0)), 7))) + 
-    cowplot::theme_cowplot() + theme(text = element_text(size = 14), 
-                                     axis.text = element_text(size = 10), 
-                                     axis.text.y = element_text(size = 8), 
[…]

### 2018-03-28 scripts/99_utils.R

@@ -87,7 +87,10 @@ prep_full_nes <- function(nes_x_lagos, conny_metrics_path, join_lagos_gis = FALS
 }
 
 theme_pred <- function(){
-  theme(legend.position = "na")
+  theme(legend.position = "na", 
+        axis.text = element_text(size = 10), 
+        axis.title = element_text(size = 12),
+        plot.title = element_text(size = 12))
 }
 
 full_model <- function(nes){
@@ -149,7 +152,10 @@ part_pred_plot <- function(nes, fit, ind, title, xl = TRUE, yl = TRUE){
   
   gg_format <- function(gg){
     gg <- gg + 
-      theme(legend.position = "none") + 
+      theme(legend.position = "none", 
+            plot.title = element_text(size = 12), 
+            axis.title = element_text(size = 12), 
+            axis.text = element_text(size = 10)) + 
       ylim(0, 1) + scale_x_log10() + ggtitle(title) +
       ylab("P Retention (%)") + xlab("Residence Time (yr)")
     
@@ -167,7 +173,7 @@ part_pred_plot <- function(nes, fit, ind, title, xl = TRUE, yl = TRUE){
   gg_1 <- ggplot() + 
     geom_point(data = nes, aes(x = retention_time_yr, 
                                y = p_percent_retention), 
-               size = 0.9) +
+               size = 0.6, color = "gray") +
     stat_summary(data = test[1][[1]], geom = "ribbon", 
                  aes(x = retention_time_yr, y = estimate, 
                      fill = forcats::fct_rev(ordered(...prob..))), 

### 2018-04-02 scripts/03_viz.R
more expo plots, show corr matrix as heatmap

@@ -284,6 +284,25 @@ plot_grid(md_v_la + theme(legend.position = "none"),
                            y = p_percent_retention)), 
           ncol = 2)
 
+# ---- graphical_exploratory_analysis_cont ----
+
+lg <- lagosne_load("1.087.1")
+nes_nws_temp <- dplyr::left_join(nes_nws, select(lg$iws, lagoslakeid, iws_ha))
+
+plot_grid(
+ggplot() + geom_point(data = nes_nws_temp, 
+                      aes(x = iws_ha, y = avg_link_length)) + 
+  xlim(300, 100000) + ylab("Average Link Length") + 
+  xlab("Interlake Watershed Area (ha)") + 
+  geom_hline(aes(yintercept = 2380.09), color = "red"),
+
+ggplot() + geom_point(data = nes_nws_temp, 
+                      aes(x = iws_ha, y = closest_lake_distance)) + 
+  xlim(300, 100000) + ylab("Closest Lake Distance") + 
+  xlab("Interlake Watershed Area (ha)") + 
+  geom_hline(aes(yintercept = 3273.65), color = "red")
+)
+
 # ---- maps ----
 
 partition_splits <- read.csv("../figures/table_1.csv")

### 2018-04-02 scripts/04_tables.R

@@ -27,7 +27,7 @@ name_key <- function(){
     iws_names = c("maxdepth", "closest_lake_distance", "stream_order_ratio", 
                   "link_length", NA, "hu12_baseflowindex_mean", NA, 
                   "iws_streamdensity_streams_density_mperha", "lakeconnection"),
-    conny_type = c(NA, "long", "long", "long", "lat", "lat", "lat", "lat", "long")
+    conny_type = c(NA, "long", "long", "lat", "long", "lat", "lat", "lat", "long")
   )
 }
 
@@ -89,10 +89,10 @@ res <- res[order(res$d_k, decreasing = TRUE),]
 # pander::pander(res)
 
 res <- res[, c(1,2,4,8,9,10)]
-res <- res[,c(3, 2, 4, 5, 6)]
+res <- res[, c(3, 2, 4, 5, 6)]
 
 key2 <- data.frame(conny_type = unique(as.character(res$conny_type)), 
-                   conny_full = c("Longitudinal", "Lateral", NA))
+                   conny_full = c("Lateral", "Longitudinal", NA))
 res <- merge(res, key2, sort = FALSE)
 res <- res[order(res$d_k, decreasing = TRUE),]
 res <- res[,c(2, 3, 6, 4, 5)]
@@ -138,19 +138,36 @@ knitr::kable(res, format = 'pandoc',
 # correlation matrix
 
 library(corrr)
+library(superheat)
 
 splits      <- read.csv("../figures/table_1.csv", stringsAsFactors = FALSE)
+
+nes_iws$p_pnt_source <-  rowSums(cbind(nes_iws$p_pnt_source_muni,
+                                       nes_iws$p_pnt_source_septic,
+                                       nes_iws$p_pnt_source_industrial),
+                                 na.rm = TRUE)
+
+nes_iws$p_pnt_source_pct <- nes_iws$p_pnt_source / 
+  (nes_iws$p_nonpnt_source + nes_iws$p_pnt_source)
+
+lg <- lagosne_load("1.087.1")
+nes_iws <- dplyr::left_join(nes_iws, select(lg$iws, lagoslakeid, iws_ha))
+
+# format iws data
 nes_iws_sub <- dplyr::select(nes_iws, -lakeconnection)
 conny_cols  <- unique(splits$iws_names)[!is.na(unique(splits$iws_names))]
[…]

### 2018-04-02 scripts/analysis.Rmd
more expo plots, show corr matrix as heatmap
heatmap adjustments

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6, fig.pos = 'H')
+knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
 ```
@@
 
-```{r cor_mat_table, echo=FALSE, results='asis'}
+```{r cor_mat_hmap, echo=FALSE, warning=FALSE, out.width="3.5in", fig.cap="Connectivity metric correlation heatmap.", message=FALSE}
 
@@
 
+```{r graphical_exploratory_analysis_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=8.4, fig.cap="Exploratory plots cont"}
+
+```
+
 ```{r conceptual_summary, echo=FALSE, fig.cap="Connectivity metric effects on lake processing.", eval=FALSE}

### 2018-04-02 scripts/03_viz.R

@@ -400,3 +400,96 @@ plot_grid(
 rel_widths = c(0.2, 1), ncol = 2)
 
 # ggplot() + geom_point(data = nes_nws, aes(x = lg_long, y = lg_lat, color = baseflow))
+
+# ---- cor_mat_hmap ----
+# correlation matrix heatmap
+
+library(corrr)
+library(superheat)
+
+splits      <- read.csv("../figures/table_1.csv", stringsAsFactors = FALSE)
+
+nes_iws$p_pnt_source <-  rowSums(cbind(nes_iws$p_pnt_source_muni,
+                                       nes_iws$p_pnt_source_septic,
+                                       nes_iws$p_pnt_source_industrial),
+                                 na.rm = TRUE)
+
+nes_iws$p_pnt_source_pct <- nes_iws$p_pnt_source / 
+  (nes_iws$p_nonpnt_source + nes_iws$p_pnt_source)
+
+lg <- lagosne_load("1.087.1")
+nes_iws <- dplyr::left_join(nes_iws, select(lg$iws, lagoslakeid, iws_ha))
+
+nes_nws$p_pnt_source <-  rowSums(cbind(nes_nws$p_pnt_source_muni,
+                                       nes_nws$p_pnt_source_septic,
+                                       nes_nws$p_pnt_source_industrial),
+                                 na.rm = TRUE)
+
+nes_nws$p_pnt_source_pct <- nes_nws$p_pnt_source / 
+  (nes_nws$p_nonpnt_source + nes_nws$p_pnt_source)
+nes_nws <- dplyr::left_join(nes_nws, select(lg$iws, lagoslakeid, iws_ha))
+
+# format iws data
+nes_iws_sub <- dplyr::select(nes_iws, -lakeconnection)
+conny_cols  <- unique(splits$iws_names)[!is.na(unique(splits$iws_names))]
+conny_cols  <- conny_cols[!(conny_cols %in% "lakeconnection")]
+
+nes_iws_sub <- nes_iws_sub[,c(conny_cols, 
+                              "lake_area_ha", "p_pnt_source_pct", "iws_ha")]
+
+iws_key <- merge(data.frame(iws_names = names(nes_iws_sub)), 
+                 splits[,c("iws_names", "abb")], sort = FALSE)
[…]

### 2018-04-02 scripts/04_tables.R

@@ -133,85 +133,3 @@ names(res)[2:ncol(res)] <-c("Mean", "LQ", "UQ")
 
 knitr::kable(res, format = 'pandoc', 
              caption = "Summary of study lake characteristics")
-
-# ---- cor_mat_table ----
-# correlation matrix
-
-library(corrr)
-library(superheat)
-
-splits      <- read.csv("../figures/table_1.csv", stringsAsFactors = FALSE)
-
-nes_iws$p_pnt_source <-  rowSums(cbind(nes_iws$p_pnt_source_muni,
-                                       nes_iws$p_pnt_source_septic,
-                                       nes_iws$p_pnt_source_industrial),
-                                 na.rm = TRUE)
-
-nes_iws$p_pnt_source_pct <- nes_iws$p_pnt_source / 
-  (nes_iws$p_nonpnt_source + nes_iws$p_pnt_source)
-
-lg <- lagosne_load("1.087.1")
-nes_iws <- dplyr::left_join(nes_iws, select(lg$iws, lagoslakeid, iws_ha))
-
-# format iws data
-nes_iws_sub <- dplyr::select(nes_iws, -lakeconnection)
-conny_cols  <- unique(splits$iws_names)[!is.na(unique(splits$iws_names))]
-conny_cols  <- conny_cols[!(conny_cols %in% "lakeconnection")]
-
-nes_iws_sub <- nes_iws_sub[,c(conny_cols, 
-                              "lake_area_ha", "p_pnt_source_pct", "iws_ha")]
-
-iws_key <- merge(data.frame(iws_names = names(nes_iws_sub)), 
-      splits[,c("iws_names", "abb")], sort = FALSE)
-iws_key <- rbind(iws_key, data.frame(iws_names = c("lake_area_ha", "p_pnt_source_pct", "iws_ha"), abb = c("Lake Area", "Pnt. Src. P", "IWS area")))
-iws_key <- iws_key[!duplicated(iws_key),]
-names(nes_iws_sub) <- iws_key$abb
-
-# format nws data
-nes_nws_sub <- dplyr::select(nes_nws, -lakeconnection)
-conny_cols  <- unique(splits$nws_names)[!is.na(unique(splits$nws_names))]
-conny_cols  <- conny_cols[!(conny_cols %in% "lakeconnection")]
-
-nes_nws_sub <- nes_nws_sub[,conny_cols]
-nws_key <- merge(data.frame(nws_names = names(nes_nws_sub)), 
[…]

### 2018-04-03 scripts/03_viz.R
better heatmap plot

@@ -460,27 +460,34 @@ names(nes_nws_sub) <- nws_key$abb
 nes_sub <- dplyr::bind_rows(nes_iws_sub, nes_nws_sub)
 
 # correlation matrix 
-res <- rearrange(shave(correlate(nes_sub)), method = "SA")
+res <- shave(correlate(nes_sub))
 res <- res[apply(res[,2:ncol(res)], 1, function(x) !all(is.na(x))),]
 res <- res[,c(TRUE, apply(res[,2:ncol(res)], 2, function(x) !all(is.na(x))))]
 names(res)[1] <- ""
 
-res_names_c <- names(res)
-res_f <- data.frame(res)
-res_names_r <- res_f$Var.1
-res_f <- res_f[,-1]
-names(res_f) <- res_names_c[-1]
+res_names_c      <- names(res)
+res_f            <- data.frame(res)
+res_names_r      <- res_f$Var.1
+res_f            <- res_f[,-1]
+names(res_f)     <- res_names_c[-1]
 row.names(res_f) <- res_names_r
-res_f <- res_f[rev(1:nrow(res_f)),]
+# res_f            <- res_f[rev(1:nrow(res_f)),]
+
 
 # names(res) <- 
 #   row.names(res) <- 
 #   sapply(row.names(res), function(x) paste(strwrap(x, 10), collapse="\n "))
 
-test <- superheat(X = res_f, bottom.label.text.angle = 90, 
-          left.label.size = 1.4, bottom.label.size = 1.4, 
-          heat.pal = c("#542788", "white", "#b35806"), 
-          heat.pal.values = c(0, 0.6, 1))
+pheatmap::pheatmap(res_f, na_col = "grey", 
+                   cluster_cols = FALSE, cluster_rows = FALSE, 
+                   color = colorRampPalette(
+                     rev(RColorBrewer::brewer.pal(n = 7, name ="RdBu")))(100))
+
+# test <- superheat(
+#           X = res_f, bottom.label.text.angle = 90, 
+#           left.label.size = 1.4, bottom.label.size = 1.4, 
+#           heat.pal = c("#542788", "white", "#b35806"), 
+#           heat.pal.values = c(0, 0.6, 1))
 
 # options(knitr.kable.NA = '')
 # knitr::kable(res, digits = 2, 

### 2018-04-03 scripts/04_tables.R

@@ -27,7 +27,7 @@ name_key <- function(){
     iws_names = c("maxdepth", "closest_lake_distance", "stream_order_ratio", 
                   "link_length", NA, "hu12_baseflowindex_mean", NA, 
                   "iws_streamdensity_streams_density_mperha", "lakeconnection"),
-    conny_type = c(NA, "long", "long", "lat", "long", "lat", "lat", "lat", "long")
+    conny_type = c(NA, "long", "long", "long", "long", "lat", "lat", "lat", "long")
   )
 }
 
@@ -97,6 +97,7 @@ res <- merge(res, key2, sort = FALSE)
 res <- res[order(res$d_k, decreasing = TRUE),]
 res <- res[,c(2, 3, 6, 4, 5)]
 
+options(knitr.kable.NA = '')
 knitr::kable(res, 
              digits = 2, row.names = FALSE, 
              col.names = c("Metric", "Scale",

### 2018-04-03 scripts/analysis.Rmd
better heatmap plot
additional expl. plot, improve table caption, adjust conny designation

@@
 
-```{r cor_mat_hmap, echo=FALSE, warning=FALSE, out.width="3.5in", fig.cap="Connectivity metric correlation heatmap.", message=FALSE}
+```{r cor_mat_hmap, echo=FALSE, warning=FALSE, fig.width=3.5, fig.height=3.2, fig.cap="Connectivity metric correlation heatmap.", message=FALSE}
 
@@
 
-```{r graphical_exploratory_analysis_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=8.4, fig.cap="Exploratory plots cont"}
+```{r graphical_exploratory_analysis_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3.5, fig.cap="Exploratory plots cont"}
 

### 2018-04-03 scripts/03_viz.R

@@ -300,7 +300,12 @@ ggplot() + geom_point(data = nes_nws_temp,
                       aes(x = iws_ha, y = closest_lake_distance)) + 
   xlim(300, 100000) + ylab("Closest Lake Distance") + 
   xlab("Interlake Watershed Area (ha)") + 
-  geom_hline(aes(yintercept = 3273.65), color = "red")
+  geom_hline(aes(yintercept = 3273.65), color = "red"), 
+
+ggplot() + geom_point(data = nes_nws_temp, 
+                      aes(x = iws_ha, y = p_percent_retention)) + 
+  xlim(300, 100000) + ylab("P Retention") + 
+  xlab("Interlake Watershed Area (ha)")
 )
 
 # ---- maps ----

### 2018-04-03 scripts/04_tables.R

@@ -92,7 +92,7 @@ res <- res[, c(1,2,4,8,9,10)]
 res <- res[, c(3, 2, 4, 5, 6)]
 
 key2 <- data.frame(conny_type = unique(as.character(res$conny_type)), 
-                   conny_full = c("Lateral", "Longitudinal", NA))
+                   conny_full = c("Longitudinal", "Lateral", NA))
 res <- merge(res, key2, sort = FALSE)
 res <- res[order(res$d_k, decreasing = TRUE),]
 res <- res[,c(2, 3, 6, 4, 5)]
@@ -133,4 +133,4 @@ res <- res[,c(ncol(res), 2:(ncol(res) - 1))]
 names(res)[2:ncol(res)] <-c("Mean", "LQ", "UQ")
 
 knitr::kable(res, format = 'pandoc', 
-             caption = "Summary of study lake characteristics")
+             caption = "Summary of study lakes showing the mean, lower quartile (LQ), and upper quartile (UQ) of selected characteristics.")

### 2018-04-03 scripts/03_viz.R
add more exploratory plots

@@ -288,6 +288,13 @@ plot_grid(md_v_la + theme(legend.position = "none"),
 
 lg <- lagosne_load("1.087.1")
 nes_nws_temp <- dplyr::left_join(nes_nws, select(lg$iws, lagoslakeid, iws_ha))
+nes_nws_temp$p_pnt_source <-  rowSums(cbind(nes_nws_temp$p_pnt_source_muni,
+                                       nes_nws_temp$p_pnt_source_septic,
+                                       nes_nws_temp$p_pnt_source_industrial),
+                                 na.rm = TRUE)
+nes_nws_sf    <- coordinatize(nes_nws_temp, "lat", "long")
+us_states <- st_intersects(us_states(), nes_sf)
+us_states <- us_states()[unlist(lapply(us_states, function(x) length(x) > 0)),]
 
 plot_grid(
 ggplot() + geom_point(data = nes_nws_temp, 
@@ -305,8 +312,16 @@ ggplot() + geom_point(data = nes_nws_temp,
 ggplot() + geom_point(data = nes_nws_temp, 
                       aes(x = iws_ha, y = p_percent_retention)) + 
   xlim(300, 100000) + ylab("P Retention") + 
-  xlab("Interlake Watershed Area (ha)")
-)
+  xlab("Interlake Watershed Area (ha)"),
+
+ggplot() + geom_sf(data = us_states) + 
+  geom_sf(data = nes_nws_sf, aes(color = p_pnt_source / (p_nonpnt_source + p_pnt_source))) + theme(legend.direction = "horizontal", legend.position = "bottom") + ggtitle("% pnt source P"),
+
+ggplot() + geom_sf(data = us_states) + 
+  geom_sf(data = nes_nws_sf, aes(color = log(maxdepth))) + theme(legend.direction = "horizontal", legend.position = "bottom") + ggtitle("max depth"), 
+ggplot() + geom_sf(data = us_states) + 
+  geom_sf(data = nes_nws_sf, aes(color = log(iws_ha))) + theme(legend.direction = "horizontal", legend.position = "bottom") + ggtitle("iws area"), 
+ncol = 2)
 
 # ---- maps ----
 
@@ -463,6 +478,8 @@ names(nes_nws_sub) <- nws_key$abb
 
 # combine iws and nws data
 nes_sub <- dplyr::bind_rows(nes_iws_sub, nes_nws_sub)
+# nes_sub <- nes_iws_sub
[…]

### 2018-04-19 data/connectivity_metrics.R
add script for conny metrics calcs

@@ -1,0 +1,219 @@
+cmdargs <- commandArgs(trailingOnly = TRUE)
+
+# ---- prep_network ----
+
+library(concaveman)
+library(vapour)
+library(sf)
+library(nhdR)
+library(dplyr)
+library(mapview)
+library(streamnet)
+library(sp)
+library(LAGOSNE)
+library(ggsn)
+
+pull_iws <- function(lagoslakeid, maxsteps = 15){
+  gdb_path <- path.expand("~/.local/share/LAGOS-GIS/lagos-ne_gis.gpkg")
+  crs <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs"
+  
+  layer_name <- "LAGOS_NE_All_Lakes_4ha"
+  query      <- paste0("SELECT * FROM ", layer_name, 
+                       " WHERE lagoslakeid = '", 
+                       lagoslakeid, "'")
+  
+  lakepoly_geom <- st_as_sfc(vapour_read_geometry(gdb_path, sql = query))
+  lakepoly      <- st_sf(vapour_read_attributes(gdb_path, sql = query), 
+                         geometry = lakepoly_geom, crs = crs)
+  lakepoly <- st_zm(lakepoly)
+  
+  layer_name <- "IWS"
+  query      <- paste0("SELECT * FROM ", layer_name, 
+                       " WHERE lagoslakeid = '", 
+                       lagoslakeid, "'")
+  
+  poly_geom <- st_as_sfc(vapour_read_geometry(gdb_path, sql = query))
+  poly      <- st_sf(vapour_read_attributes(gdb_path, sql = query), 
+                     geometry = poly_geom, crs = crs)
+  poly      <- st_zm(poly)
+  poly      <- st_union(poly, lakepoly)
+  
+  lines <- nhd_plus_query(poly = poly, dsn = "NHDFlowLine", 
+                            approve_all_dl = TRUE)$sp$NHDFlowLine
+  
+  lg        <- lagosne_load("1.087.1")
+  wb_coords <- as.numeric(
+    lake_info(lg, lagoslakeid = lagoslakeid)[,c("nhd_long", "nhd_lat")])
+
+  names(lines) <- tolower(names(lines))
+  extract_network(wb_coords[1], wb_coords[2], lines = lines, maxsteps = maxsteps)
+}
+
[…]

### 2018-04-19 scripts/analysis.Rmd
add more exploratory plots
adjust fig caption

@@
 
-```{r fig.cap="Connectivity metric box", echo=FALSE}
+```{r fig.cap="Definition of connectivity metrics.", echo=FALSE}
 knitr::include_graphics("../figures/conny_metric_key_crop.pdf")
@@
 
-```{r graphical_exploratory_analysis_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3.5, fig.cap="Exploratory plots cont"}
+```{r graphical_exploratory_analysis_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6.3, fig.cap="Exploratory plots cont"}
 

### 2018-04-19 data/connectivity_metrics.R
allow multi file detection

@@ -120,7 +120,8 @@ pull_nws_metrics <- function(lakes){
 flist <-c("data/nes_x_lagos-ne.csv", 
           "../data/nes_x_lagos-ne.csv", 
           "nes_x_lagos-ne.csv")
-nes_x_lagos <- read.csv(flist[sapply(flist, file.exists)], stringsAsFactors = FALSE)
+nes_x_lagos <- read.csv(flist[which.min(sapply(flist, file.exists))], 
+                        stringsAsFactors = FALSE)
 
 # all(nes_x_lagos$lagoslakeid %in% lg$locus$lagoslakeid)
 

### 2018-04-19 data/connectivity_metrics.R
arg take last match

@@ -120,7 +120,7 @@ pull_nws_metrics <- function(lakes){
 flist <-c("data/nes_x_lagos-ne.csv", 
           "../data/nes_x_lagos-ne.csv", 
           "nes_x_lagos-ne.csv")
-nes_x_lagos <- read.csv(flist[which.min(sapply(flist, file.exists))], 
+nes_x_lagos <- read.csv(flist[which.max(sapply(flist, file.exists))], 
                         stringsAsFactors = FALSE)
 
 # all(nes_x_lagos$lagoslakeid %in% lg$locus$lagoslakeid)

### 2018-04-23 scripts/analysis.Rmd
formatting table 1

@@
 ```{r partition_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from the hierarchical model posteriors relative to raw data.
-Lighter colored lines and shaded polygons represent the estimates from the lower of the two partition groups (see Table 3)", fig.width = 4.8, fig.height=5, warning=FALSE}
+Lighter colored lines and shaded polygons represent the estimates from the lower of the two partition groups (see Table 3).", fig.width = 4.8, fig.height=5, warning=FALSE}
 

### 2018-04-23 scripts/04_tables.R

@@ -102,7 +102,7 @@ knitr::kable(res,
              digits = 2, row.names = FALSE, 
              col.names = c("Metric", "Scale",
                            "Connectivity Type", "Split Value", "Delta k"), 
-             caption = "Results table")
+             caption = "Ranking of connectivity metrics according to median effect size.")
 
 # ---- lake_characteristics_table ----
 # table describing basic properties of lake population
@@ -130,7 +130,9 @@ res[res$property == "tp", 1:3] <- 1000 * res[res$property == "tp", 1:3] # mg to 
 
 res <- merge(res, name_key, sort = FALSE)
 res <- res[,c(ncol(res), 2:(ncol(res) - 1))]
-names(res)[2:ncol(res)] <-c("Mean", "LQ", "UQ")
 
-knitr::kable(res, format = 'pandoc', 
-             caption = "Summary of study lakes showing the mean, lower quartile (LQ), and upper quartile (UQ) of selected characteristics.")
+res <- data.frame(res[,1], paste0(res$X50.," (", res$X25., " - ", res$X75., ")"))
+names(res) <-c("", "Mean (IQR)")
+
+knitr::kable(res, format = 'pandoc', align = c("ll"),
+             caption = "Summary of selected study lake characteristics.")

### 2018-04-23 scripts/analysis.Rmd
improve captions, add nws area to correlation fig

--- 2018-04-19 scripts/analysis.Rmd
@@
 
-```{r fig.cap="Watershed diagram", echo=FALSE}
+```{r fig.cap="Diagram showing the inter-lake watershed (IWS) and network watershed (NWS) of three lakes.
+Here the IWS of lake 3 encompasses the IWS of lake 2 because of its small size but not the IWS of lake 1 because it is large.
+In contrast, the NWS of lake 3 extends to the headwaters of the lake chain.", echo=FALSE}
 knitr::include_graphics("../figures/iws_nws.pdf")
@@
 
-```{r fig.cap="Definition of connectivity metrics.", echo=FALSE}
+```{r fig.cap="Connectivity metric definitions and examples of high and low connectivity lakes.", echo=FALSE}
 knitr::include_graphics("../figures/conny_metric_key_crop.pdf")
@@
 
-```{r cor_mat_hmap, echo=FALSE, warning=FALSE, fig.width=3.5, fig.height=3.2, fig.cap="Connectivity metric correlation heatmap.", message=FALSE}
+```{r cor_mat_hmap, echo=FALSE, warning=FALSE, fig.width=3.5, fig.height=3.2, fig.cap="Correlation between connectivity metrics and selected lake characteristics.", message=FALSE}
 
@@
 
-```{r global_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from the non-hierarchical model posterior relative to raw data.", warning=FALSE, fig.width = 3.5, fig.height = 3.2}
+```{r global_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from global model posterior relative to NES data.", warning=FALSE, fig.width = 3.5, fig.height = 3.2}
 
@@
 
-```{r partition_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from the hierarchical model posteriors relative to raw data.
-Lighter colored lines and shaded polygons represent the estimates from the lower of the two partition groups (see Table 3)", fig.width = 4.8, fig.height=5, warning=FALSE}
+```{r partition_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from hierarchical model posteriors relative to NES data.
+Lighter colored lines and lighter colored polygons represent the estimates from the lower of the two partition groups (see Table 2).", fig.width = 4.8, fig.height=5, warning=FALSE}
 
@@
 
-```{r k_viz, echo=FALSE, message=FALSE, fig.cap="Distribution of Vollenweider's k in low and high connectivity partitions at the IWS and NWS scales.", fig.width=5, fig.height=3.8, warning=FALSE}
+```{r k_viz, echo=FALSE, message=FALSE, fig.cap="Distribution of Vollenweider's k in low and high connectivity partitions at the IWS and NWS scales.
+Lighter colors indicate the lower of the two partition groups (see Table 2).", fig.width=5, fig.height=3.8, warning=FALSE}
 
@@
 
-```{r maps, echo=FALSE, fig.cap="Map of lake connectivity partitions where lighter colored lakes have matric values on the lower side of the respective partition in Table 3.", warning=FALSE, message=FALSE}
+```{r maps, echo=FALSE, fig.cap="Map of lake connectivity partitions where lighter colored lakes have metric values on the lower side of their respective partitions (see Table 2).", warning=FALSE, message=FALSE}
 

### 2018-04-23 scripts/01_prepdata.R

@@ -4,12 +4,12 @@ source("99_utils.R")
 # ---- prep_nes_lagos ----
 
 pre_path <- "/home/jose/Documents/Science/Dissertation/Analysis/nes/"
-
 nes_iws <- prep_full_nes(file.path(pre_path, "nes_x_lagos-ne.csv"), 
                          file.path(pre_path, "connectivity_metrics.csv"))
 
+pre_path <- "../data"
 nes_nws <- prep_full_nes(file.path(pre_path, "nes_x_lagos-ne.csv"), 
-                         file.path(pre_path, "connectivity_metrics4.csv"))
+                         file.path(pre_path, "connectivity_metrics_nws.csv"))
 
 nes_rf_iws <- make_rf_dt(nes_iws)$nes_rf
 # make_rf_dt(nes_iws)$nes_rf_name_key

### 2018-04-23 scripts/03_viz.R

@@ -47,19 +47,18 @@ plot_tree(gettree(readRDS("../data/iws/streamdensity_forest.rds")),
 plot_grid(
   plot_grid(
     part_pred_plot(nes_iws, readRDS("../data/lc_vollenweider.rds"), 
-                   9, "Lake connection", xl = FALSE),
+                   9, "Lake connection", xl = TRUE),
     part_pred_plot(nes_nws, readRDS("../data/nws/ll_vollenweider.rds"),
-                   8, "Link length", xl = FALSE, yl = FALSE), 
-    rel_widths = c(1, 0.93), labels = c("IWS", "NWS"), 
-    hjust = c(-4, -2.7), vjust = 2.5),
+                   8, "Link length (NWS)", xl = TRUE, yl = FALSE), 
+    rel_widths = c(1, 0.93)),
   NULL,
   plot_grid(
     part_pred_plot(nes_iws, readRDS("../data/md_vollenweider.rds"), 
                  8, "Max depth", xl = TRUE),
     part_pred_plot(nes_nws, readRDS("../data/nws/cd_vollenweider.rds"),
-                 9, "Distance to \n closest lake", xl = TRUE, yl = FALSE), 
+                 9, "Distance to \n closest lake (NWS)", xl = TRUE, yl = FALSE), 
     rel_widths = c(1, 0.93)), 
-  rel_heights = c(0.91, 0.1, 1), ncol = 1)
+  rel_heights = c(1, 0.05, 1), ncol = 1)
 
 # ---- k_viz ----
 
@@ -469,10 +468,10 @@ conny_cols  <- unique(splits$nws_names)[!is.na(unique(splits$nws_names))]
 conny_cols  <- conny_cols[!(conny_cols %in% "lakeconnection")]
 
 nes_nws_sub <- nes_nws_sub[,c(conny_cols, 
-                              "lake_area_ha", "p_pnt_source_pct", "iws_ha")]
+                              "lake_area_ha", "p_pnt_source_pct", "iws_ha", "nws_ha")]
 nws_key <- merge(data.frame(nws_names = names(nes_nws_sub)), 
                  splits[,c("nws_names", "abb")], sort = FALSE)
-nws_key <- rbind(nws_key, data.frame(nws_names = c("lake_area_ha", "p_pnt_source_pct", "iws_ha"), abb = c("Lake Area", "Pnt. Src. P", "IWS area")))
[…]

### 2018-04-23 scripts/04_tables.R

@@ -96,12 +96,13 @@ key2 <- data.frame(conny_type = unique(as.character(res$conny_type)),
 res <- merge(res, key2, sort = FALSE)
 res <- res[order(res$d_k, decreasing = TRUE),]
 res <- res[,c(2, 3, 6, 4, 5)]
+res <- dplyr::select(res, -splits)
 
 options(knitr.kable.NA = '')
 knitr::kable(res, 
              digits = 2, row.names = FALSE, 
              col.names = c("Metric", "Scale",
-                           "Connectivity Type", "Split Value", "Delta k"), 
+                           "Connectivity Type", "Delta k"), 
              caption = "Ranking of connectivity metrics according to median effect size.")
 
 # ---- lake_characteristics_table ----
@@ -131,8 +132,8 @@ res[res$property == "tp", 1:3] <- 1000 * res[res$property == "tp", 1:3] # mg to 
 res <- merge(res, name_key, sort = FALSE)
 res <- res[,c(ncol(res), 2:(ncol(res) - 1))]
 
-res <- data.frame(res[,1], paste0(res$X50.," (", res$X25., " - ", res$X75., ")"))
-names(res) <-c("", "Mean (IQR)")
+res <- data.frame(res[,1], res$X50., paste0("(", res$X25., " - ", res$X75., ")"))
+names(res) <- c("", "Mean", "IQR")
 
-knitr::kable(res, format = 'pandoc', align = c("ll"),
-             caption = "Summary of selected study lake characteristics.")
+knitr::kable(res, format = 'pandoc', align = c("lll"),
+             caption = "Mean and interquartile range of selected study lake characteristics.")

### 2018-04-23 scripts/99_utils.R

@@ -153,7 +153,7 @@ part_pred_plot <- function(nes, fit, ind, title, xl = TRUE, yl = TRUE){
   gg_format <- function(gg){
     gg <- gg + 
       theme(legend.position = "none", 
-            plot.title = element_text(size = 12, face = "plain"), 
+            plot.title = element_text(size = 10, face = "plain", color = "grey"), 
             axis.title = element_text(size = 12), 
             axis.text = element_text(size = 10)) + 
       ylim(0, 1) + scale_x_log10() + ggtitle(title) +

### 2018-04-23 scripts/03_viz.R
add nws area plots

@@ -322,6 +322,41 @@ ggplot() + geom_sf(data = us_states) +
   geom_sf(data = nes_nws_sf, aes(color = log(iws_ha))) + theme(legend.direction = "horizontal", legend.position = "bottom") + ggtitle("iws area"), 
 ncol = 2)
 
+# ---- graphical_exploratory_analysis_cont_cont ----
+
+lg <- lagosne_load("1.087.1")
+
+nes_nws_temp <- nes_nws
+nes_nws_temp$p_pnt_source <-  rowSums(cbind(nes_nws_temp$p_pnt_source_muni,
+                                            nes_nws_temp$p_pnt_source_septic,
+                                            nes_nws_temp$p_pnt_source_industrial),
+                                      na.rm = TRUE)
+nes_nws_sf    <- coordinatize(nes_nws_temp, "lat", "long")
+us_states <- st_intersects(us_states(), nes_nws_sf)
+us_states <- us_states()[unlist(lapply(us_states, function(x) length(x) > 0)),]
+
+plot_grid(
+  ggplot() + geom_point(data = nes_nws_temp, 
+                        aes(x = nws_ha, y = upstream_lakes_4ha_area_ha)) + 
+    xlim(300, 100000) + ylab("Up. Lk. Area") + 
+    xlab("Network Watershed Area (ha)"),
+  ggplot() + geom_point(data = nes_nws_temp, 
+                        aes(x = nws_ha, y = stream_order_ratio)) + 
+    xlim(300, 100000) + ylab("Stream Order Ratio") + 
+    xlab("Network Watershed Area (ha)"), 
+  
+  ggplot() + geom_point(data = nes_nws_temp, 
+                        aes(x = nws_ha, y = p_percent_retention)) + 
+    xlim(300, 100000) + ylab("P Retention") + 
+    xlab("Network Watershed Area (ha)"),
+  
+  ggplot() + geom_point(data = nes_nws_temp, 
+                        aes(x = nws_ha, 
+                            y = p_pnt_source / (p_nonpnt_source + p_pnt_source))) + 
+    xlim(300, 100000) + ylab("% Pnt Source") + 
+    xlab("Network Watershed Area (ha)"), 
+  ncol = 2)
+
 # ---- maps ----
 
 partition_splits <- read.csv("../figures/table_1.csv")

### 2018-04-30 scripts/03_viz.R
fix figure sizes, label abbrevations, panel labels

@@ -47,16 +47,16 @@ plot_tree(gettree(readRDS("../data/iws/streamdensity_forest.rds")),
 plot_grid(
   plot_grid(
     part_pred_plot(nes_iws, readRDS("../data/lc_vollenweider.rds"), 
-                   9, "Lake connection", xl = TRUE),
+                   9, "A. Effect of lake connection", xl = TRUE),
     part_pred_plot(nes_nws, readRDS("../data/nws/ll_vollenweider.rds"),
-                   8, "Link length (NWS)", xl = TRUE, yl = FALSE), 
+                   8, "B. Effect of link length \n (NWS)", xl = TRUE, yl = FALSE), 
     rel_widths = c(1, 0.93)),
   NULL,
   plot_grid(
     part_pred_plot(nes_iws, readRDS("../data/md_vollenweider.rds"), 
-                 8, "Max depth", xl = TRUE),
+                 8, "C. Effect of max depth", xl = TRUE),
     part_pred_plot(nes_nws, readRDS("../data/nws/cd_vollenweider.rds"),
-                 9, "Distance to \n closest lake (NWS)", xl = TRUE, yl = FALSE), 
+                 9, "D. Effect of distance to \n closest lake (NWS)", xl = TRUE, yl = FALSE), 
     rel_widths = c(1, 0.93)), 
   rel_heights = c(1, 0.05, 1), ncol = 1)
 
@@ -100,7 +100,7 @@ k_viz_iws <- ggplot(
                                   viridis::viridis(1, begin = 0)), 7))) + 
     cowplot::theme_cowplot() + theme(axis.text = element_text(size = 10),
                                      axis.title = element_text(size = 12),
-                               plot.title = element_text(size = 12, face = "plain"),
+                               plot.title = element_text(size = 12, face = "plain", hjust = 0),
                                      axis.line.x = element_line(size = 1, 
                                      colour = "black"),
                                      axis.line.y = element_line(size = 1, 
@@ -157,7 +157,7 @@ k_viz_nws <- ggplot(
                                      viridis::viridis(1, begin = 0)), 8))) + 
   cowplot::theme_cowplot() + theme(axis.text = element_text(size = 10),
                                    axis.title = element_text(size = 12),
-                               plot.title = element_text(size = 12, face = "plain"),
[…]

### 2018-04-30 scripts/04_tables.R

@@ -51,9 +51,9 @@ name_key <- function(){
                    "Upstream lake area", "Baseflow", 
                    "Wetland Cover",
                    "Stream density", "Lake Connection"),
-    abb        = c("Max depth", "Closest lake dist.", "S. order ratio", 
-                   "Avg. link len.", "Up. lake area", "Baseflow", 
-                   "W. Cover", "Stream density", "Lake Con."), 
+    abb        = c("Max depth", "Closest lake distance", "Stream order ratio", 
+                   "Average link length", "Upstream lake area", "Baseflow", 
+                   "Wetland Cover", "Stream density", "Lake Connection"), 
     pnames     = c("maxdepth", "cd", 
                    "sr", "linklength", 
                    "uplakearea", "baseflow", 

### 2018-04-30 scripts/99_utils.R

@@ -157,7 +157,7 @@ part_pred_plot <- function(nes, fit, ind, title, xl = TRUE, yl = TRUE){
   gg_format <- function(gg){
     gg <- gg + 
       theme(legend.position = "none", 
-            plot.title = element_text(size = 10, face = "plain", color = "grey"), 
+            plot.title = element_text(size = 10, face = "plain", color = "black", hjust = 0), 
             axis.title = element_text(size = 12), 
             axis.text = element_text(size = 10)) + 
       ylim(0, 1) + scale_x_log10() + ggtitle(title) +
@@ -309,4 +309,16 @@ delta_k <- function(rds_path){
   data.frame(pnames2 = substring(basename(rds_path), 0, 2), d_k = 
   abs(median(dplyr::filter(dt, key == "k2")$coef) - 
     median(dplyr::filter(dt, key == "k1")$coef)))
+}
+
+break_word <- function(x, max.len){
+  
+  x_split <- stringr::str_split(x, " ")[[1]]
+  n_chars <- sapply(x_split, nchar)
+  
+  first_line  <- cumsum(n_chars + 1) < max.len
+  second_line <- !first_line
+  
+  res <- paste(x_split[first_line], collapse = " ")
+  paste(res, "\n", paste(x_split[second_line], collapse = " "))
 }

### 2018-05-11 scripts/analysis.Rmd
add nws area plots
fix figure sizes, label abbrevations, panel labels
update fig and table captions from gdoc

@@
 
-```{r lake_characteristics_table, echo=FALSE, results='asis'}
+```{r lake_characteristics_table, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
 
@@
 ```{r fig.cap="Diagram showing the inter-lake watershed (IWS) and network watershed (NWS) of three lakes.
-Here the IWS of lake 3 encompasses the IWS of lake 2 because of its small size but not the IWS of lake 1 because it is large.
-In contrast, the NWS of lake 3 extends to the headwaters of the lake chain.", echo=FALSE}
+Here the IWS of lake 3 encompasses the IWS of lake 2 because of it is smaller than 10 ha small size but it does not encompass the IWS of lake 1 because it has an area of at least 10 ha.
+In contrast to the IWS boundaries, the NWS boundaries extend to the headwaters of the lake chain.", echo=FALSE}
 knitr::include_graphics("../figures/iws_nws.pdf")
@@
 
-```{r global_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from global model posterior relative to NES data.", warning=FALSE, fig.width = 3.5, fig.height = 3.2}
+```{r global_vollenweider_viz, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and the global model fit to the data as the median and central 95% interval estimates.", warning=FALSE, fig.width = 3.5, fig.height = 3.2}
 
@@
 
-```{r partition_vollenweider_viz, echo=FALSE, fig.cap="Median and central 95% interval estimates from hierarchical model posteriors relative to NES data.
-Lighter colored lines and lighter colored polygons represent the estimates from the lower of the two partition groups (see Table 2).", fig.width = 4.8, fig.height=5, warning=FALSE}
+```{r partition_vollenweider_viz, echo=FALSE, fig.cap="Residence time (yr) versus P retention (%) for the NES dataset and hierarchical model fits to the data as the median and central 95% interval estimates.
+The green lines and symbols are the estimates from the lower of the two partition groups while the purple lines are estimates for the upper of the two partition groups (see Table 2).", fig.width = 4.8, fig.height=5, warning=FALSE}
 
@@
 
-```{r k_viz, echo=FALSE, message=FALSE, fig.cap="Distribution of Vollenweider's k in low and high connectivity partitions at the IWS and NWS scales.
-Lighter colors indicate the lower of the two partition groups (see Table 2).", fig.width=5, fig.height=3.8, warning=FALSE}
+```{r k_viz, echo=FALSE, message=FALSE, fig.cap="Distribution of the k parameter from the Vollenweider's equation in low and high connectivity partitions at the (A) IWS and (B) NWS scales.
+Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", fig.width=5, fig.height=3.8, warning=FALSE}
 
@@
 
-```{r maps, echo=FALSE, fig.cap="Map of lake connectivity partitions where lighter colored lakes have metric values on the lower side of their respective partitions (see Table 2).", warning=FALSE, message=FALSE}
+```{r maps, echo=FALSE, fig.cap="Maps showing the locations of lake connectivity partitions.
+Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", warning=FALSE, message=FALSE}
 
@@
 
+```{r graphical_exploratory_analysis_cont_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6.3, fig.cap="Exploratory plots cont x 2"}
+
+```
+
 ```{r conceptual_summary, echo=FALSE, fig.cap="Connectivity metric effects on lake processing.", eval=FALSE}

### 2018-05-11 scripts/04_tables.R

@@ -64,4 +64,4 @@ knitr::kable(res,
              digits = 2, row.names = FALSE, 
              col.names = c("Metric", "Scale",
                            "Connectivity Type", "Delta k"), 
-             caption = "Ranking of connectivity metrics according to median effect size.")
+             caption = "Ranking of connectivity metrics and lake depth according to median effect size.")

### 2018-05-23 scripts/analysis.Rmd
drop iws, closes #1

@@
 
-```{r fig.cap="Diagram showing the inter-lake watershed (IWS) and network watershed (NWS) of three lakes.
-Here the IWS of lake 3 encompasses the IWS of lake 2 because of it is smaller than 10 ha small size but it does not encompass the IWS of lake 1 because it has an area of at least 10 ha.
-In contrast to the IWS boundaries, the NWS boundaries extend to the headwaters of the lake chain.", echo=FALSE}
+```{r fig.cap="Diagram showing the lake watershed (LWS) and network watershed (NWS) of three lakes.
+Here the IWS of lake 3 encompasses the LWS of lake 2 because of it is smaller than 10 ha small size but it does not encompass the LWS of lake 1 because it has an area of at least 10 ha.
+In contrast to the LWS boundaries, the NWS boundaries extend to the headwaters of the lake chain.", echo=FALSE}
 knitr::include_graphics("../figures/iws_nws.pdf")
@@
 
-```{r global_vollenweider_viz, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and the global model fit to the data as the median and central 95% interval estimates.", warning=FALSE, fig.width = 3.5, fig.height = 3.2}
+```{r global_vollenweider_viz, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and the global model fit to the data where the solid line and shaded interval represents the median and central 95% interval estimates respectively.", warning=FALSE, fig.width = 3.5, fig.height = 3.2}
 
@@
 
-```{r partition_vollenweider_viz, echo=FALSE, fig.cap="Residence time (yr) versus P retention (%) for the NES dataset and hierarchical model fits to the data as the median and central 95% interval estimates.
+```{r partition_vollenweider_viz, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and hierarchical model fits to the data where the solid lines and shaded intervals represent the median and central 95% model  estimates respectively.
 The green lines and symbols are the estimates from the lower of the two partition groups while the purple lines are estimates for the upper of the two partition groups (see Table 2).", fig.width = 4.8, fig.height=5, warning=FALSE}
@@
 
-```{r k_viz, echo=FALSE, message=FALSE, fig.cap="Distribution of the k parameter from the Vollenweider's equation in low and high connectivity partitions at the (A) IWS and (B) NWS scales.
+```{r k_viz, echo=FALSE, message=FALSE, fig.cap="Distribution of the k parameter from the Vollenweider's equation in low and high connectivity partitions at the (A) LWS and (B) NWS scales.
 Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", fig.width=5, fig.height=3.8, warning=FALSE}

### 2018-05-23 scripts/03_viz.R

@@ -184,7 +184,7 @@ k_viz_nws <- ggplot(
                    "Global")))
 
 plot_grid(
-  k_viz_iws + ggtitle("A. IWS scale") + xlim(0.8, 1.6),
+  k_viz_iws + ggtitle("A. LWS scale") + xlim(0.8, 1.6),
   k_viz_nws + ggtitle("B. NWS scale") + xlim(0.8, 1.6), ncol = 2,
   align = "v")
 
@@ -448,8 +448,8 @@ plot_grid(
             NULL,
             NULL, 
             nrow = 4, ncol = 1,
-            labels = c("IWS:", "", "NWS:", "", ""), 
-            label_colour = "gray", vjust = c(1.2, 0, 2, 0, 0), 
+            labels = c("A. LWS:", "", "B. NWS:", "", ""), 
+            label_colour = "black", vjust = c(1.2, 0, 2, 0, 0), 
             hjust = c(-0.1, 0, -0.12, 0, 0)),
   plot_grid(
     plot_grid(plotlist = lower_iws_maps, 
@@ -459,8 +459,6 @@ plot_grid(
                    ncol = 3, nrow = 2, align = "v"), 
     ncol = 1, rel_heights = c(1, 0.1, 1)), 
 rel_widths = c(0.2, 1), ncol = 2)
-
-# ggplot() + geom_point(data = nes_nws, aes(x = lg_long, y = lg_lat, color = baseflow))
 
 # ---- cor_mat_hmap ----
 # correlation matrix heatmap
@@ -502,7 +500,7 @@ iws_key <- merge(data.frame(iws_names = names(nes_iws_sub)),
                  splits[,c("iws_names", "abb")], sort = FALSE)
 iws_key <- rbind(iws_key, 
                  data.frame(iws_names = c("lake_area_ha", "p_pnt_source_pct", "iws_ha"), 
-                            abb = c("Lake Area", "Point Source P", "IWS area")))
+                            abb = c("Lake Area", "Point Source P", "LWS area")))
 iws_key <- iws_key[!duplicated(iws_key),]
 names(nes_iws_sub) <- iws_key$abb
 
@@ -516,7 +514,7 @@ nes_nws_sub <- nes_nws_sub[,c(conny_cols,
 nws_key <- merge(data.frame(nws_names = names(nes_nws_sub)), 
                  splits[,c("nws_names", "abb")], sort = FALSE)
[…]

### 2018-05-23 scripts/99_utils.R

@@ -79,7 +79,7 @@ prep_full_nes <- function(nes_x_lagos, conny_metrics_path, join_lagos_gis = FALS
   }
   nes <- dplyr::filter(nes, lakeconnection != "Isolated",
                        lakeconnection != "Headwater")
-  nes$lakeconnection <- droplevels(nes$lakeconnection)
+  nes$lakeconnection      <- droplevels(nes$lakeconnection)
   nes$p_percent_retention <- nes$p_percent_retention / 100
   
   nes$tp_in <- nesRdata:::calculate_tp_in(nes)

### 2018-05-23 scripts/table_1.R

@@ -43,12 +43,12 @@ nws_parts  <- data.frame(table_splits("data/nws/"),
                          stringsAsFactors = FALSE)
 
 misc_parts$scale <- "focal"
-iws_parts$scale  <- "iws"
+iws_parts$scale  <- "lws"
 nws_parts$scale  <- "nws"
 
 rownames(misc_parts) <- rownames(iws_parts) <- rownames(nws_parts) <- NULL
 
-res <- rbind(misc_parts, iws_parts, nws_parts)
+res        <- rbind(misc_parts, iws_parts, nws_parts)
 res$splits <- as.numeric(res$splits)
 # res <- res[,1:ncol(res)]
 res <- rbind(res, data.frame(pnames = "lakeconnection", splits = NA, scale = "focal"))
@@ -74,7 +74,7 @@ d_k <- lapply(list("data/lc_vollenweider.rds",
                    "data/nws/sr_vollenweider.rds"), delta_k)
 
 d_k <- do.call("rbind", d_k)
-d_k$scale <- c("focal", "focal", rep("iws", 5), rep("nws", 6))
+d_k$scale <- c("focal", "focal", rep("lws", 5), rep("nws", 6))
 
 res <- merge(res, d_k)
 res <- res[order(res$d_k, decreasing = TRUE),]

### 2018-05-24 scripts/analysis.Rmd
include conceptual figure

@@
 
+```{r fig.cap="Major lake and watershed characteristics, factors, and processes affecting lake P retention.
+Shaded symbols indicate items typically considered in P retention models while open symbols indicate additional items considered in the present study.", echo=FALSE}
+knitr::include_graphics("../figures/conceptual_p-cycle.pdf")
+```
+
+```{r fig.cap="Connectivity metric definitions along with examples of high and low connectivity lakes.", echo=FALSE}
+knitr::include_graphics("../figures/conny_metric_key_crop.pdf")
+```
+
 ```{r fig.cap="Diagram showing the lake watershed (LWS) and network watershed (NWS) of three lakes.
@@
 knitr::include_graphics("../figures/iws_nws.pdf")
-```
-
-```{r fig.cap="Connectivity metric definitions and examples of high and low connectivity lakes.", echo=FALSE}
-knitr::include_graphics("../figures/conny_metric_key_crop.pdf")
 ```

### 2018-05-25 scripts/01_prepdata.R
speed up processing by not repulling data

@@ -12,15 +12,18 @@ if(file.exists("../data")){
   pre_path <- "data"
 }
 
-nes_iws <- prep_full_nes(file.path(pre_path, "nes_x_lagos-ne.csv"), 
+if(!all(sapply(c("nes_iws", "nes_nws", "nes_rf_iws", "nes_rf_nws"), exists))){
+  
+  nes_iws <- prep_full_nes(file.path(pre_path, "nes_x_lagos-ne.csv"), 
                          file.path(pre_path, "connectivity_metrics_iws.csv"))
 
-nes_nws <- prep_full_nes(file.path(pre_path, "nes_x_lagos-ne.csv"), 
+  nes_nws <- prep_full_nes(file.path(pre_path, "nes_x_lagos-ne.csv"), 
                          file.path(pre_path, "connectivity_metrics_nws.csv"))
 
-# RandomForest data
-nes_rf_iws <- make_rf_dt(nes_iws)$nes_rf
-# make_rf_dt(nes_iws)$nes_rf_name_key
+  # RandomForest data
+  nes_rf_iws <- make_rf_dt(nes_iws)$nes_rf
+  # make_rf_dt(nes_iws)$nes_rf_name_key
 
-nes_rf_nws <- make_rf_dt(nes_nws)$nes_rf
-# make_rf_dt(nes_nws)$nes_rf_name_key
+  nes_rf_nws <- make_rf_dt(nes_nws)$nes_rf
+  # make_rf_dt(nes_nws)$nes_rf_name_key
+}

### 2018-05-31 figures/04_global_vollenweider.Rmd
reorg to invididual figure and table Rmds

---
title: "Figures"
output:
  pdf_document:
    fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
```

```{r read_chunks, cache=FALSE, echo=FALSE}
knitr::read_chunk("../scripts/03_viz.R")
knitr::read_chunk("../scripts/99_utils.R")
```

```{r source_utils, message=FALSE, results='hide', echo=FALSE, warning=FALSE}

```

```{r load_data, message=FALSE, results='hide', echo=FALSE, warning=FALSE}
  source("../scripts/01.5_loaddata.R")
```

```{r 04_global_vollenweider, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and the global model fit to the data where the solid line and shaded interval represents the median and central 95% interval estimates respectively.", warning=FALSE, fig.width = 3.5, fig.height = 3.2}

```

### 2018-05-31 figures/05_partition_vollenweider.Rmd
reorg to invididual figure and table Rmds

--- 2018-05-31 figures/04_global_vollenweider.Rmd
@@
 
-```{r 04_global_vollenweider, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and the global model fit to the data where the solid line and shaded interval represents the median and central 95% interval estimates respectively.", warning=FALSE, fig.width = 3.5, fig.height = 3.2}
+```{r 05_partition_vollenweider, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and hierarchical model fits to the data where the solid lines and shaded intervals represent the median and central 95% model  estimates respectively.
+The green lines and symbols are the estimates from the lower of the two partition groups while the purple lines are estimates for the upper of the two partition groups (see Table 2).", fig.width = 4.8, fig.height=5, warning=FALSE}
 

### 2018-05-31 figures/06_k.Rmd
reorg to invididual figure and table Rmds

--- 2018-05-31 figures/04_global_vollenweider.Rmd
@@
 
-```{r 04_global_vollenweider, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and the global model fit to the data where the solid line and shaded interval represents the median and central 95% interval estimates respectively.", warning=FALSE, fig.width = 3.5, fig.height = 3.2}
+```{r 06_k, echo=FALSE, message=FALSE, fig.cap="Distribution of the k parameter from the Vollenweider's equation in low and high connectivity partitions at the (A) LWS and (B) NWS scales.
+Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", fig.width=5, fig.height=3.8, warning=FALSE}
 

### 2018-05-31 figures/07_cor_mat_hmap.Rmd
reorg to invididual figure and table Rmds

--- 2018-05-31 figures/04_global_vollenweider.Rmd
@@
 
-```{r 04_global_vollenweider, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and the global model fit to the data where the solid line and shaded interval represents the median and central 95% interval estimates respectively.", warning=FALSE, fig.width = 3.5, fig.height = 3.2}
+```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.width=3.5, fig.height=3.2, fig.cap="Correlation between connectivity metrics and selected lake characteristics.", message=FALSE}
 

### 2018-05-31 figures/08_maps.Rmd
reorg to invididual figure and table Rmds

--- 2018-05-31 figures/07_cor_mat_hmap.Rmd
@@
 
-```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.width=3.5, fig.height=3.2, fig.cap="Correlation between connectivity metrics and selected lake characteristics.", message=FALSE}
+```{r 08_maps, echo=FALSE, fig.cap="Maps showing the locations of lake connectivity partitions.
+Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", warning=FALSE, message=FALSE}
 

### 2018-05-31 manuscript/figures.Rmd
reorg to invididual figure and table Rmds

--- 2018-05-24 scripts/analysis.Rmd
@@
 
-```{r lake_characteristics_table, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
-
-```
-
 ```{r fig.cap="Major lake and watershed characteristics, factors, and processes affecting lake P retention.
@@
 knitr::include_graphics("../figures/iws_nws.pdf")
-```
-
-```{r cor_mat_hmap, echo=FALSE, warning=FALSE, fig.width=3.5, fig.height=3.2, fig.cap="Correlation between connectivity metrics and selected lake characteristics.", message=FALSE}
-
-```
-
-```{r global_vollenweider_viz, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and the global model fit to the data where the solid line and shaded interval represents the median and central 95% interval estimates respectively.", warning=FALSE, fig.width = 3.5, fig.height = 3.2}
-
-```
-
-```{r partition_vollenweider_viz, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and hierarchical model fits to the data where the solid lines and shaded intervals represent the median and central 95% model  estimates respectively.
-The green lines and symbols are the estimates from the lower of the two partition groups while the purple lines are estimates for the upper of the two partition groups (see Table 2).", fig.width = 4.8, fig.height=5, warning=FALSE}
-
-```
-
-```{r k_viz, echo=FALSE, message=FALSE, fig.cap="Distribution of the k parameter from the Vollenweider's equation in low and high connectivity partitions at the (A) LWS and (B) NWS scales.
-Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", fig.width=5, fig.height=3.8, warning=FALSE}
-
-```
-
-```{r model_results_table, echo=FALSE, results='asis'}
-
-```
-
-```{r maps, echo=FALSE, fig.cap="Maps showing the locations of lake connectivity partitions.
-Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", warning=FALSE, message=FALSE}
-
 ```

### 2018-05-31 tables/01_lake_characteristics_table.Rmd
reorg to invididual figure and table Rmds

--- 2018-05-31 figures/07_cor_mat_hmap.Rmd
@@
 knitr::read_chunk("../scripts/03_viz.R")
+knitr::read_chunk("../scripts/04_tables.R")
 knitr::read_chunk("../scripts/99_utils.R")
@@
 
-```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.width=3.5, fig.height=3.2, fig.cap="Correlation between connectivity metrics and selected lake characteristics.", message=FALSE}
+```{r lake_characteristics_table, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
 

### 2018-05-31 scripts/01.5_loaddata.R

@@ -1,0 +1,2 @@
+nes_nws <- readRDS("../data/nes_nws.rds")
+nes_iws <- readRDS("../data/nes_iws.rds")

### 2018-05-31 scripts/01_prepdata.R

@@ -1,6 +1,8 @@
 # setwd("scripts")
 if(file.exists("99_utils.R")){
   source("99_utils.R")
+}else{
+  source("../scripts/99_utils.R")
 }
 
 # ---- prep_nes_lagos ----
@@ -16,10 +18,15 @@ if(file.exists("../data")){
   
   nes_iws <- prep_full_nes(file.path(pre_path, "nes_x_lagos-ne.csv"), 
                          file.path(pre_path, "connectivity_metrics_iws.csv"))
+  
+  
 
   nes_nws <- prep_full_nes(file.path(pre_path, "nes_x_lagos-ne.csv"), 
                          file.path(pre_path, "connectivity_metrics_nws.csv"))
-
+  
+  saveRDS(nes_iws, "nes_iws.rds")
+  saveRDS(nes_nws, "nes_nws.rds")
+  
   # RandomForest data
   nes_rf_iws <- make_rf_dt(nes_iws)$nes_rf
   # make_rf_dt(nes_iws)$nes_rf_name_key
@@ -27,3 +34,7 @@ if(file.exists("../data")){
   nes_rf_nws <- make_rf_dt(nes_nws)$nes_rf
   # make_rf_dt(nes_nws)$nes_rf_name_key
 # }
+
+  saveRDS(nes_rf_iws, "nes_rf_iws.rds")
+  saveRDS(nes_rf_nws, "nes_rf_nws.rds")
+  

### 2018-05-31 scripts/03_viz.R

@@ -2,7 +2,7 @@
 # source("99_utils.R")
 # source("01_prepdata.R")
 
-# ---- global_vollenweider_viz ----
+# ---- 04_global_vollenweider ----
 
 full_pred_plot(nes_iws, readRDS("../data/global_vollenweider.rds"))
 
@@ -42,7 +42,7 @@ plot_tree(gettree(readRDS("../data/iws/wetland-cover_forest.rds")),
 plot_tree(gettree(readRDS("../data/iws/streamdensity_forest.rds")), 
           title = "Stream Density")
 
-# ---- partition_vollenweider_viz ----
+# ---- 05_partition_vollenweider ----
 
 plot_grid(
   plot_grid(
@@ -60,7 +60,7 @@ plot_grid(
     rel_widths = c(1, 0.93)), 
   rel_heights = c(1, 0.05, 1), ncol = 1)
 
-# ---- k_viz ----
+# ---- 06_k ----
 
 fit_df_iws <- rbind(
   extract_coefs(readRDS("../data/global_vollenweider.rds"), "k"), 
@@ -363,7 +363,7 @@ plot_grid(
     xlab("Network Watershed Area (ha)"), 
   ncol = 2)
 
-# ---- maps ----
+# ---- 08_maps ----
 
 partition_splits <- read.csv("../figures/table_1.csv")
 partition_splits <- dplyr::filter(partition_splits, !is.na(splits), 
@@ -460,7 +460,7 @@ plot_grid(
     ncol = 1, rel_heights = c(1, 0.1, 1)), 
 rel_widths = c(0.2, 1), ncol = 2)
 
-# ---- cor_mat_hmap ----
+# ---- 07_cor_mat_hmap ----
 # correlation matrix heatmap
 
 library(corrr)

### 2018-05-31 scripts/04_tables.R

@@ -29,6 +29,10 @@ summary_names <- c("tp", "chl", "secchi",
                    "p_percent_retention", "retention_time_yr",
                    "surface_area", "maxdepth", "percent_ag", "iws_ha", "nws_ha")
 
+# range(nes_nws$p_percent_retention)
+# range(nes_nws$retention_time_yr)
+# 0.02 * 365
+
 res           <- lapply(summary_names, qs)
 res           <- round(data.frame(do.call("rbind", res)), 2)
 res$property  <- summary_names
@@ -67,7 +71,7 @@ knitr::kable(res, format = 'pandoc', align = c("lll"),
 # ---- model_results_table ----
 # table showing model results
 
-res <- read.csv("table_1.csv", stringsAsFactors = FALSE)
+res <- read.csv("../scripts/table_1.csv", stringsAsFactors = FALSE)
 res <- res[, c("parameter", "scale", "conny_type", "splits", "d_k")]
 
 key2 <- data.frame(conny_type = unique(as.character(res$conny_type)), 

### 2018-05-31 manuscript/appendix.Rmd
more reorg

--- 2018-05-31 manuscript/figures.Rmd
@@
 ```{r read_chunks, cache=FALSE, echo=FALSE}
-knitr::read_chunk("01_prepdata.R")
-knitr::read_chunk("03_viz.R")
-knitr::read_chunk("04_tables.R")
-knitr::read_chunk("99_utils.R")
+knitr::read_chunk("../scripts/01_prepdata.R")
+knitr::read_chunk("../scripts/03_viz.R")
+knitr::read_chunk("../scripts/04_tables.R")
+knitr::read_chunk("../scripts/99_utils.R")
 ```
@@
 
-```{r prep_nes_lagos, message=FALSE, results='hide', echo=FALSE, warning=FALSE}
-
+```{r load_data, message=FALSE, results='hide', echo=FALSE, warning=FALSE}
+  source("../scripts/01.5_loaddata.R")
 ```
-
-```{r fig.cap="Major lake and watershed characteristics, factors, and processes affecting lake P retention.
-Shaded symbols indicate items typically considered in P retention models while open symbols indicate additional items considered in the present study.", echo=FALSE}
-knitr::include_graphics("../figures/conceptual_p-cycle.pdf")
-```
-
-```{r fig.cap="Connectivity metric definitions along with examples of high and low connectivity lakes.", echo=FALSE}
-knitr::include_graphics("../figures/conny_metric_key_crop.pdf")
-```
-
-```{r fig.cap="Diagram showing the lake watershed (LWS) and network watershed (NWS) of three lakes.
-Here the IWS of lake 3 encompasses the LWS of lake 2 because of it is smaller than 10 ha small size but it does not encompass the LWS of lake 1 because it has an area of at least 10 ha.
-In contrast to the LWS boundaries, the NWS boundaries extend to the headwaters of the lake chain.", echo=FALSE}
-knitr::include_graphics("../figures/iws_nws.pdf")
-```
-
-<!-- * Olin Lake has a completely undeveloped shoreline -->
-<!-- * Madison Lake is impaired according to MPCA -->
 

### 2018-05-31 manuscript/figures.Rmd
more reorg

@@
 knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
-```
-
-```{r read_chunks, cache=FALSE, echo=FALSE}
-knitr::read_chunk("01_prepdata.R")
-knitr::read_chunk("03_viz.R")
-knitr::read_chunk("04_tables.R")
-knitr::read_chunk("99_utils.R")
-```
-
-```{r source_utils, message=FALSE, results='hide', echo=FALSE, warning=FALSE}
-
-```
-
-```{r prep_nes_lagos, message=FALSE, results='hide', echo=FALSE, warning=FALSE}
-
 ```
@@
 
-<!-- * Olin Lake has a completely undeveloped shoreline -->
-<!-- * Madison Lake is impaired according to MPCA -->
+```{r 04_global_vollenweider, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and the global model fit to the data where the solid line and shaded interval represents the median and central 95% interval estimates respectively.", warning=FALSE, fig.width = 3.5, fig.height = 3.2}
 
-```{r recursive_partitioning_viz, echo=FALSE, eval=FALSE}
-
+knitr::include_graphics("../figures/04_global_vollenweider-1.pdf")
 ```
 
-```{r graphical_exploratory_analysis, echo=FALSE, message=FALSE, warning=FALSE, fig.height=8.4, fig.cap="Exploratory plots"}
+```{r 05_partition_vollenweider, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and hierarchical model fits to the data where the solid lines and shaded intervals represent the median and central 95% model  estimates respectively.
+The green lines and symbols are the estimates from the lower of the two partition groups while the purple lines are estimates for the upper of the two partition groups (see Table 2).", fig.width = 4.8, fig.height=5, warning=FALSE}
 
+knitr::include_graphics("../figures/05_partition_vollenweider-1.pdf")
 ```
 
-```{r graphical_exploratory_analysis_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6.3, fig.cap="Exploratory plots cont"}
-
+```{r 06_k, echo=FALSE, message=FALSE, fig.cap="Distribution of the k parameter from the Vollenweider's equation in low and high connectivity partitions at the (A) LWS and (B) NWS scales.
+Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", fig.width=5, fig.height=3.8, warning=FALSE}
+knitr::include_graphics("../figures/06_k-1.pdf")
 ```
 
-```{r graphical_exploratory_analysis_cont_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6.3, fig.cap="Exploratory plots cont x 2"}
-
+```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.width=3.5, fig.height=3.2, fig.cap="Correlation between connectivity metrics and selected lake characteristics.", message=FALSE}
+knitr::include_graphics("../figures/07_cor_mat_hmap-1.pdf")
 ```
 
-```{r conceptual_summary, echo=FALSE, fig.cap="Connectivity metric effects on lake processing.", eval=FALSE}
-dt <- data.frame(
-  rbind(
-    c("closest lake distance", "lower", "higher", "lower", "higher", "lake-stream", "long"), 
-    c("average link length", "lower", "higher", "lower", "higher", "stream", "long"), 
-    c("lakeconnection", "DR_Stream", "higher", "lower", "higher", "lake", "long"), 
-    c("upstream lake area", "lower", "higher", "lower", "higher", "lake", "lat"), 
-    c("stream density", "higher", "higher", "lower", "higher", "stream", "lat"),
-    c("baseflow", "higher", "higher", "lower", "higher", "stream", "lat"), 
-    c("stream order ratio", "higher", "higher", "lower", "higher", "stream", "long")))
-
-names(dt) <- c("metric", "direction", "k", "connectivity", "in_lake_processing", "axis", "connectivity type")
-
-knitr::kable(dt)
+```{r 08_maps, echo=FALSE, fig.cap="Maps showing the locations of lake connectivity partitions.
+Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", warning=FALSE, message=FALSE}
+knitr::include_graphics("../figures/08_maps-1.pdf")
 ```

### 2018-05-31 scripts/03_viz.R

@@ -298,7 +298,7 @@ nes_nws_temp$p_pnt_source <-  rowSums(cbind(nes_nws_temp$p_pnt_source_muni,
                                        nes_nws_temp$p_pnt_source_industrial),
                                  na.rm = TRUE)
 nes_nws_sf    <- coordinatize(nes_nws_temp, "lat", "long")
-us_states <- st_intersects(us_states(), nes_sf)
+us_states <- st_intersects(us_states(), nes_nws_sf)
 us_states <- us_states()[unlist(lapply(us_states, function(x) length(x) > 0)),]
 
 plot_grid(

### 2018-06-01 figures/06_k.Rmd
move code to separate rmds, fix k viz margins

@@
 ```{r read_chunks, cache=FALSE, echo=FALSE}
-knitr::read_chunk("../scripts/03_viz.R")
+# knitr::read_chunk("../scripts/03_viz.R")
 knitr::read_chunk("../scripts/99_utils.R")
@@
 
+fit_df_iws <- rbind(
+  extract_coefs(readRDS("../data/global_vollenweider.rds"), "k"), 
+  extract_coefs2(readRDS("../data/lc_vollenweider.rds"), 
+                 c("k1_lc", "k2_lc")),
+  extract_coefs2(readRDS("../data/md_vollenweider.rds"), 
+                 c("k1_md", "k2_md")),
+  extract_coefs2(readRDS("../data/iws/cd_vollenweider.rds"),
+                 c("k1_cd", "k2_cd")),
+  extract_coefs2(readRDS("../data/iws/ll_vollenweider.rds"),
+                 c("k1_ll", "k2_ll")),
+  extract_coefs2(readRDS("../data/iws/bf_vollenweider.rds"),
+                 c("k1_bf", "k2_bf")),
+  extract_coefs2(readRDS("../data/iws/sd_vollenweider.rds"),
+                 c("k1_sd", "k2_sd")),
+  extract_coefs2(readRDS("../data/iws/sr_vollenweider.rds"), 
+                 c("k1_sr", "k2_sr")))
+  #               extract_coefs2(fit_wc, c("k1_wc", "k2_wc")),
+
+# controls ordering of ridge plot
+fit_df_iws$key <- factor(fit_df_iws$key, levels = c("k", 
+                                            "k1_sd", "k2_sd",
+                                            "k1_cd", "k2_cd",
+                                            "k1_sr", "k2_sr",
+                                            "k1_bf", "k2_bf",
+                                            "k1_ll", "k2_ll",
+                                            "k1_md", "k2_md",
+                                            "k1_lc", "k2_lc"))
+#                                             "k1_wc", "k2_wc",
+
+k_viz_iws <- ggplot(
+  fit_df_iws, 
+  aes(x = coef, y = key, fill = key, color = key)) + 
+    geom_density_ridges(size = 1, rel_min_height = 0.03, scale = 1) + 
+    scale_fill_manual(values = c("grey", 
+                            rep(c(viridis::viridis(1, begin = 0.5), 
+                                  viridis::viridis(1, begin = 0)), 7))) +
+    scale_color_manual(values = c("grey", 
+                               rep(c(viridis::viridis(1, begin = 0.5), 
+                                     viridis::viridis(1, begin = 0)), 7))) +
+    cowplot::theme_cowplot() + theme(axis.text = element_text(size = 10),
+                                     axis.title = element_text(size = 12),
+                               plot.title = element_text(size = 12, face = "plain", hjust = 0),
+                                     axis.line.x = element_line(size = 1, 
+                                     colour = "black"),
+                                     axis.line.y = element_line(size = 1, 
+                                                       colour = "black"), 
+                                     legend.position = "none", 
+                                     plot.margin = margin(0.5,0,0,0, "cm")) + 
+  xlab("Coefficient Value") + ylab("") + 
+  scale_y_discrete(breaks = levels(fit_df_iws$key)[
+    c(1, seq(3, length(levels(fit_df_iws$key)), by = 2))], 
+                   labels = rev(c("Lake \n connection",  
+                                                 "Max depth",
+                                                 "Link length",
+                                                 "Baseflow",
+                                                 "Stream \n order ratio",
+                                                 "Closest \n lake distance",
+                                                 "Stream \n density",
+                                                 "Global")))
+
+fit_df_nws <- rbind(
+  extract_coefs(readRDS("../data/global_vollenweider.rds"), "k"), 
+  extract_coefs2(readRDS("../data/lc_vollenweider.rds"), 
+                 c("k1_lc", "k2_lc")),
+  extract_coefs2(readRDS("../data/nws/cd_vollenweider.rds"), 
+                 c("k1_cd", "k2_cd")),
+  extract_coefs2(readRDS("../data/nws/ll_vollenweider.rds"), 
+                 c("k1_ll", "k2_ll")),
+  extract_coefs2(readRDS("../data/nws/la_vollenweider.rds"), 
+                 c("k1_la", "k2_la")),
+  extract_coefs2(readRDS("../data/md_vollenweider.rds"), 
+                 c("k1_md", "k2_md")),
+  extract_coefs2(readRDS("../data/nws/bf_vollenweider.rds"), 
+                 c("k1_bf", "k2_bf")),
+  extract_coefs2(readRDS("../data/nws/sd_vollenweider.rds"), 
+                 c("k1_sd", "k2_sd")),
+  extract_coefs2(readRDS("../data/nws/sr_vollenweider.rds"), 
+                 c("k1_sr", "k2_sr")))
+
+fit_df_nws$key <- factor(fit_df_nws$key, levels = c("k",
+                                                    "k1_sr", "k2_sr",
+                                                    "k1_bf", "k2_bf",
+                                                    "k1_md", "k2_md",
+                                                    "k1_la", "k2_la",
+                                                    "k1_lc", "k2_lc",
+                                                    "k1_sd", "k2_sd",
+                                                    "k1_cd", "k2_cd",
+                                                    "k1_ll", "k2_ll"))
+
+k_viz_nws <- ggplot(
+  fit_df_nws, 
+  aes(x = coef, y = key, fill = key, color = key)) + 
+  geom_density_ridges(size = 1, rel_min_height = 0.03, scale = 1) + 
+  scale_fill_manual(values = c("grey",
+                               rep(c(viridis::viridis(1, begin = 0.5),
+                                     viridis::viridis(1, begin = 0)), 8))) +
+  scale_color_manual(values = c("grey", 
+                               rep(c(viridis::viridis(1, begin = 0.5), 
+                                     viridis::viridis(1, begin = 0)), 8))) +
+  cowplot::theme_cowplot() + theme(axis.text = element_text(size = 10),
+                                   axis.title = element_text(size = 12),
+                               plot.title = element_text(size = 12, face = "plain", hjust = 0),
+                                   axis.line.x = element_line(size = 1, 
+                                                  colour = "black"),
+                                   axis.line.y = element_line(size = 1, 
+                                                  colour = "black"), 
+                                   legend.position = "none", 
+                                   plot.margin = margin(0.5,0,0,-0.7, "cm")) + 
+  xlab("Coefficient Value") +  ylab("") +
+  scale_y_discrete(breaks = levels(fit_df_nws$key)[
+    c(1, seq(3, length(levels(fit_df_nws$key)), by = 2))], 
+    labels = rev(c("Link length",
+                   "Closest \n lake distance",
+                   "Stream \n density",
+                   "Lake \n connection",  
+                   "Upstream \n lake area",
+                   "Max depth",
+                   "Baseflow",
+                   "Stream \n order ratio",
+                   "Global")))
+
+plot_grid(
+  k_viz_iws + ggtitle("A. LWS scale") + xlim(0.8, 1.6),
+  k_viz_nws + ggtitle("B. NWS scale") + xlim(0.8, 1.6), 
+  ncol = 2, align = "v", rel_widths = c(1, 1)) + 
+  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm"))
+
 ```

### 2018-06-01 figures/08_maps.Rmd
move code to separate rmds, fix k viz margins

@@
 
+# ---- 08_maps ----
+
+partition_splits <- read.csv("../figures/table_1.csv")
+partition_splits <- dplyr::filter(partition_splits, !is.na(splits), 
+                                  scale %in% c("nws", "iws"))
+partition_splits <- droplevels(partition_splits)
+partition_splits$pnames2 <- factor(partition_splits$pnames2, 
+                              levels = c("cd", "ll", "la", "sd", "bf", "sr"))
+
+nes_sf    <- coordinatize(nes_nws, "lat", "long")
+us_states <- st_intersects(us_states(), nes_sf)
+us_states <- us_states()[unlist(lapply(us_states, function(x) length(x) > 0)),]
+
+# pull the lower partition group as an sf object
+get_sub <- function(dt, col_name, split_value){
+  coordinatize(
+    dplyr::filter(dt, UQ(rlang::sym(as.character(col_name))) <= split_value), 
+    "lat", "long")
+}
+
+lower_iws_maps <- lapply(which(partition_splits$scale == "iws"), 
+                         function(x) {
+                           nes_sub <- get_sub(nes_iws, 
+                                            partition_splits[x, "iws_names"],
+                                            partition_splits[x, "splits"])
+
+                           ggplot() + 
+                             geom_sf(data = us_states) +
+                             geom_sf(data = nes_sf, 
+                                     color = viridis::viridis(1, begin = 0),
+                                     size = 0.6) + 
+                             geom_sf(data = nes_sub, 
+                                color = viridis::viridis(1, begin = 0.5), 
+                                size = 0.6) + 
+                             coord_sf(datum = NA) + 
+                             ggtitle(break_word(partition_splits[x, "abb"], 12)) + 
+                             theme(plot.margin = unit(c(0, -0.1, 0, -0.1), "cm"),
+                               plot.title = element_text(face = "plain", size = 12))
+                         })
+
+lower_nws_maps <- lapply(which(partition_splits$scale == "nws"), 
+                         function(x) {
+                           nes_sub <- get_sub(nes_nws, 
+                                              partition_splits[x, "nws_names"],
+                                              partition_splits[x, "splits"])
+
+                           nes_sf_temp <- nes_sf
+                           st_geometry(nes_sf_temp) <- NULL
+                           na_rows <- !is.na(
+                    nes_sf_temp[,as.character(partition_splits[x, "nws_names"])])
+
+                           ggplot() + 
+                             geom_sf(data = us_states) +
+                             geom_sf(data = nes_sf, 
+                                     color = viridis::viridis(1, begin = 0),
+                                     size = 0.6) + 
+                             geom_sf(data = nes_sub,
+                                     color = viridis::viridis(1, begin = 0.5), 
+                                     size = 0.6) + 
+                             coord_sf(datum = NA) + 
+                             ggtitle(break_word(partition_splits[x, "abb"], 12)) + 
+                             theme(plot.margin = unit(c(0, -0.1, 0, -0.1), "cm"), 
+                               plot.title = element_text(face = "plain", size  = 12))
+                         })
+
+lower_iws_maps <- lower_iws_maps[
+  match(levels(partition_splits$pnames2), 
+        partition_splits$pnames2[which(partition_splits$scale == "iws")])
+  ]
+
+# lower_iws_maps[1][[1]] <- lower_iws_maps[1][[1]] + 
+#   theme(plot.margin = unit(c(1,0,0,0), "lines"))
+
+lower_nws_maps <- lower_nws_maps[
+  match(levels(partition_splits$pnames2), 
+        partition_splits$pnames2[which(partition_splits$scale == "nws")])
+  ]
+
+plot_grid(
+  plot_grid(NULL,
+            NULL, 
+            NULL,
+            NULL,
+            NULL, 
+            nrow = 4, ncol = 1,
+            labels = c("A. LWS:", "", "B. NWS:", "", ""), 
+            label_colour = "black", vjust = c(1.2, 0, 2, 0, 0), 
+            hjust = c(-0.1, 0, -0.12, 0, 0)),
+  plot_grid(
+    plot_grid(plotlist = lower_iws_maps, 
+                   ncol = 3, nrow = 2, align = "v"),
+    plot_grid(ggplot() + geom_blank()),
+    plot_grid(plotlist = lower_nws_maps,
+                   ncol = 3, nrow = 2, align = "v"), 
+    ncol = 1, rel_heights = c(1, 0.1, 1)), 
+rel_widths = c(0.2, 1), ncol = 2)
 ```

### 2018-06-01 scripts/03_viz.R

@@ -60,134 +60,6 @@ plot_grid(
     rel_widths = c(1, 0.93)), 
   rel_heights = c(1, 0.05, 1), ncol = 1)
 
-# ---- 06_k ----
-
-fit_df_iws <- rbind(
-  extract_coefs(readRDS("../data/global_vollenweider.rds"), "k"), 
-  extract_coefs2(readRDS("../data/lc_vollenweider.rds"), 
-                 c("k1_lc", "k2_lc")),
-  extract_coefs2(readRDS("../data/md_vollenweider.rds"), 
-                 c("k1_md", "k2_md")),
-  extract_coefs2(readRDS("../data/iws/cd_vollenweider.rds"),
-                 c("k1_cd", "k2_cd")),
-  extract_coefs2(readRDS("../data/iws/ll_vollenweider.rds"),
-                 c("k1_ll", "k2_ll")),
-  extract_coefs2(readRDS("../data/iws/bf_vollenweider.rds"),
-                 c("k1_bf", "k2_bf")),
-  extract_coefs2(readRDS("../data/iws/sd_vollenweider.rds"),
-                 c("k1_sd", "k2_sd")),
-  extract_coefs2(readRDS("../data/iws/sr_vollenweider.rds"), 
-                 c("k1_sr", "k2_sr")))
-  #               extract_coefs2(fit_wc, c("k1_wc", "k2_wc")), 
-
-# controls ordering of ridge plot
-fit_df_iws$key <- factor(fit_df_iws$key, levels = c("k", 
-                                            "k1_sd", "k2_sd",
-                                            "k1_cd", "k2_cd",
-                                            "k1_sr", "k2_sr",
-                                            "k1_bf", "k2_bf",
-                                            "k1_ll", "k2_ll",
-                                            "k1_md", "k2_md",
-                                            "k1_lc", "k2_lc"))
-#                                             "k1_wc", "k2_wc",
-
-k_viz_iws <- ggplot(
-  fit_df_iws, 
-  aes(x = coef, y = key, fill = key, color = key)) + 
-    geom_density_ridges(size = 1, rel_min_height = 0.03) + 
-    scale_fill_manual(values = c("grey", 
-                            rep(c(viridis::viridis(1, begin = 0.5), 
-                                  viridis::viridis(1, begin = 0)), 7))) +
-    scale_color_manual(values = c("grey", 
-                               rep(c(viridis::viridis(1, begin = 0.5), 
-                                     viridis::viridis(1, begin = 0)), 7))) +
[…]

### 2018-06-01 figures/08_maps.Rmd
rm colons, crop k viz

@@
             nrow = 4, ncol = 1,
-            labels = c("A. LWS:", "", "B. NWS:", "", ""), 
+            labels = c("A. LWS", "", "B. NWS", "", ""), 
             label_colour = "black", vjust = c(1.2, 0, 2, 0, 0), 

### 2018-06-05 figures/06_k.Rmd
reduce line thickness

@@
   aes(x = coef, y = key, fill = key, color = key)) + 
-    geom_density_ridges(size = 1, rel_min_height = 0.03, scale = 1) + 
+    geom_density_ridges(size = 0.1, rel_min_height = 0.03, scale = 1) + 
     scale_fill_manual(values = c("grey", 
@@
   aes(x = coef, y = key, fill = key, color = key)) + 
-  geom_density_ridges(size = 1, rel_min_height = 0.03, scale = 1) + 
+  geom_density_ridges(size = 0.1, rel_min_height = 0.03, scale = 1) + 
   scale_fill_manual(values = c("grey",

### 2018-06-08 manuscript/appendix.Rmd
make appendix self-contained for make

@@
 ---
-title: "Figures"
+title: "Appendix"
 output:
@@
 ```{r read_chunks, cache=FALSE, echo=FALSE}
-knitr::read_chunk("../scripts/01_prepdata.R")
-knitr::read_chunk("../scripts/03_viz.R")
-knitr::read_chunk("../scripts/04_tables.R")
 knitr::read_chunk("../scripts/99_utils.R")
@@
 ```{r load_data, message=FALSE, results='hide', echo=FALSE, warning=FALSE}
+  if(file.exists("../scripts/01.5_loaddata.R")){
     source("../scripts/01.5_loaddata.R")  
+  }else{
+    source("scripts/01.5_loaddata.R")  
+  }
 ```
@@
 ```{r recursive_partitioning_viz, echo=FALSE, eval=FALSE}
+plot_tree(gettree(readRDS("../data/maxdepth_forest.rds")), 
+          title = "Max Depth")
 
+plot_tree(gettree(readRDS("../data/iws/cd_forest.rds")), 
+          title = "Distance to Closest \n Upstream Lake (standardized)")
+# inv_inv_closest(-1.51, nes_rf_iws) # 3773.614
+plot_tree(gettree(readRDS("../data/nws/cd_forest.rds")), 
+          title = "Distance to Closest \n Upstream Lake (standardized)")
+# inv_inv_closest(-1.469, nes_rf_nws) # 2681.288
+
+plot_tree(gettree(readRDS("../data/iws/sr_forest.rds")), 
+          title = "Stream Order Ratio")
+plot_tree(gettree(readRDS("../data/nws/sr_forest.rds")), 
+          title = "Stream Order Ratio")
+
+plot_tree(gettree(readRDS("../data/iws/linklength_forest.rds")), 
+          title = "Link Length")
+plot_tree(gettree(readRDS("../data/nws/linklength_forest.rds")), 
+          title = "Link Length")
+
+plot_tree(gettree(readRDS("../data/iws/uplakearea_forest.rds")), 
+          title = "Upstream Lake Area")
+# plot_tree(gettree(readRDS("01_Chapter/data/nws/uplakearea_forest.rds")), 
+#           title = "Upstream Lake Area")
+
+plot_tree(gettree(readRDS("../data/iws/baseflow_forest.rds")), 
+          title = "Baseflow")
+
+plot_tree(gettree(readRDS("../data/iws/wetland-cover_forest.rds")), 
+          title = "Wetland Cover")
+
+plot_tree(gettree(readRDS("../data/iws/streamdensity_forest.rds")), 
+          title = "Stream Density")
 ```
@@
 ```{r graphical_exploratory_analysis, echo=FALSE, message=FALSE, warning=FALSE, fig.height=8.4, fig.cap="Exploratory plots"}
+partition_splits <- read.csv("../figures/table_1.csv", stringsAsFactors = FALSE)
 
+nes_iws$p_pnt_source <-  rowSums(cbind(nes_iws$p_pnt_source_muni,
+                                       nes_iws$p_pnt_source_septic,
+                                       nes_iws$p_pnt_source_industrial),
+                                 na.rm = TRUE)
+
+md_v_la <- ggplot(data = nes_iws) + 
+  geom_point(aes(x = maxdepth, 
+                 y = upstream_lakes_4ha_area_ha, color = lakeconnection)) +
+  ylab("Upstream Lake Area (ha)") + xlab("Max Depth (m)") + 
+  geom_vline(data = partition_splits, aes(
+    xintercept = partition_splits$splits[
+      partition_splits$pnames2 == "md" & partition_splits$scale == "focal"])) + 
+  geom_hline(data = partition_splits, aes(
+    yintercept = partition_splits$splits[
+      partition_splits$pnames2 == "la" & partition_splits$scale == "nws"])) + 
+  scale_y_log10()
+
+md_v_ll_iws <- ggplot(data = nes_iws) + 
+  geom_point(aes(x = maxdepth, 
+                 y = link_length, color = lakeconnection)) +
+  ylab("Link Length") + xlab("Max Depth (m)") + 
+  geom_vline(data = partition_splits, aes(
+    xintercept = partition_splits$splits[
+      partition_splits$pnames2 == "md"])) + 
+  geom_hline(data = partition_splits, aes(
+    yintercept = partition_splits$splits[
+      partition_splits$pnames2 == "ll" & partition_splits$scale == "iws"]))
+
+md_v_ll_nws <- ggplot(data = nes_nws) + 
+  geom_point(aes(x = maxdepth, 
+                 y = avg_link_length, color = lakeconnection)) +
+  ylab("Link Length") + xlab("Max Depth (m)") + 
+  geom_vline(data = partition_splits, aes(
+    xintercept = partition_splits$splits[
+      partition_splits$pnames2 == "md"])) + 
+  geom_hline(data = partition_splits, aes(
+    yintercept = partition_splits$splits[
+      partition_splits$pnames2 == "ll" & partition_splits$scale == "nws"]))
+
+md_v_cd_nws <- ggplot(data = nes_nws) + 
+  geom_point(aes(x = maxdepth, 
+                 y = closest_lake_distance, color = lakeconnection)) +
+  ylab("Closest Lake Distance") + xlab("Max Depth (m)") + 
+  geom_vline(data = partition_splits, aes(
+    xintercept = partition_splits$splits[
+      partition_splits$pnames2 == "md"])) + 
+  geom_hline(data = partition_splits, aes(
+    yintercept = partition_splits$splits[
+      partition_splits$pnames2 == "cd" & partition_splits$scale == "nws"]))
+
+ll_v_cd_nws <- ggplot(data = nes_nws) + 
+  geom_point(aes(x = avg_link_length, 
+                 y = closest_lake_distance, color = lakeconnection)) +
+  ylab("Closest Lake Distance") + xlab("Link Length") + 
+  geom_vline(data = partition_splits, aes(
+    xintercept = partition_splits$splits[
+      partition_splits$pnames2 == "ll" & partition_splits$scale == "nws"])) + 
+  geom_hline(data = partition_splits, aes(
+    yintercept = partition_splits$splits[
+      partition_splits$pnames2 == "cd" & partition_splits$scale == "nws"])) + 
+  scale_x_log10() + scale_y_log10() + xlab("log(Link Length)") + ylab("log(cd)")
+
+legend <- get_legend(md_v_la)
+
+plot_grid(md_v_la + theme(legend.position = "none"), 
+          md_v_ll_iws + theme(legend.position = "none"), 
+          md_v_ll_nws + theme(legend.position = "none"),
+          ll_v_cd_nws + theme(legend.position = "none"),
+          ggplot() + geom_point(aes(nes_iws$hu12_baseflowindex_mean, nes_nws$baseflow, color = nes_iws$state %in% c("MAINE", "NEW HAMPSHIRE", "IOWA", "MISSOURI", "OHIO", "ILLINOIS"))) + 
+            geom_hline(aes(yintercept = 53.43)) +
+            geom_vline(aes(xintercept = 63.76)) + 
+            ylab("NWS Baseflow") + xlab("IWS Baseflow") + 
+            theme(legend.position = "none"),
+          ggplot() + geom_point(aes(
+            nes_iws$iws_streamdensity_streams_density_mperha, 
+            nes_nws$stream_density, color = nes_iws$lakeconnection)) + 
+            geom_hline(aes(yintercept = 10.4), color = "red") +
+            geom_vline(aes(xintercept = 4.43), color = "red") +
+            geom_abline(aes(slope = 1, intercept = 0)) + 
+            ylab("NWS Stream Density") + xlab("IWS Stream Density") + 
+            theme(legend.position = "none"),
+
+          ggplot() + geom_point(aes(nes_iws$closest_lake_distance, 
+                                    nes_nws$closest_lake_distance, 
+                                    color = nes_iws$lakeconnection)) + 
+            geom_hline(aes(yintercept = 2776.81), color = "red") +
+            geom_vline(aes(xintercept = 3773.61), color = "red") +
+            geom_abline(aes(slope = 1, intercept = 0)) +
+            scale_x_log10() + 
+            scale_y_log10() + 
+            ylab("NWS Lake Distance") + xlab("IWS Lake Distance") + 
+            theme(legend.position = "none"),
+          ggplot(data = nes_iws) + 
+            geom_point(aes(x = p_pnt_source / (p_nonpnt_source + p_pnt_source), 
+                           y = p_percent_retention)) + 
+            xlab("p_percent_pnt-source"), 
+          ncol = 2)
 ```
@@
 ```{r graphical_exploratory_analysis_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6.3, fig.cap="Exploratory plots cont"}
+lg <- lagosne_load("1.087.1")
+nes_nws_temp <- dplyr::left_join(nes_nws, select(lg$iws, lagoslakeid, iws_ha))
+nes_nws_temp$p_pnt_source <-  rowSums(cbind(nes_nws_temp$p_pnt_source_muni,
+                                       nes_nws_temp$p_pnt_source_septic,
+                                       nes_nws_temp$p_pnt_source_industrial),
+                                 na.rm = TRUE)
+nes_nws_sf    <- coordinatize(nes_nws_temp, "lat", "long")
+us_states <- st_intersects(us_states(), nes_nws_sf)
+us_states <- us_states()[unlist(lapply(us_states, function(x) length(x) > 0)),]
 
+plot_grid(
+ggplot() + geom_point(data = nes_nws_temp, 
+                      aes(x = iws_ha, y = avg_link_length)) + 
+  xlim(300, 100000) + ylab("Average Link Length") + 
+  xlab("Interlake Watershed Area (ha)") + 
+  geom_hline(aes(yintercept = 2380.09), color = "red"),
+
+ggplot() + geom_point(data = nes_nws_temp, 
+                      aes(x = iws_ha, y = closest_lake_distance)) + 
+  xlim(300, 100000) + ylab("Closest Lake Distance") + 
+  xlab("Interlake Watershed Area (ha)") + 
+  geom_hline(aes(yintercept = 3273.65), color = "red"),
+
+ggplot() + geom_point(data = nes_nws_temp, 
+                      aes(x = iws_ha, y = p_percent_retention)) + 
+  xlim(300, 100000) + ylab("P Retention") + 
+  xlab("Interlake Watershed Area (ha)"),
+
+ggplot() + geom_sf(data = us_states) + 
+  geom_sf(data = nes_nws_sf, aes(color = p_pnt_source / (p_nonpnt_source + p_pnt_source))) + theme(legend.direction = "horizontal", legend.position = "bottom") + ggtitle("% pnt source P"),
+
+ggplot() + geom_sf(data = us_states) + 
+  geom_sf(data = nes_nws_sf, aes(color = log(maxdepth))) + theme(legend.direction = "horizontal", legend.position = "bottom") + ggtitle("max depth"), 
+ggplot() + geom_sf(data = us_states) + 
+  geom_sf(data = nes_nws_sf, aes(color = log(iws_ha))) + theme(legend.direction = "horizontal", legend.position = "bottom") + ggtitle("iws area"), 
+ncol = 2)
 ```
 
-```{r graphical_exploratory_analysis_cont_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6.3, fig.cap="Exploratory plots cont x 2"}
+```{r graphical_exploratory_analysis_cont_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=5.3, fig.cap="Exploratory plots cont x 2"}
+lg <- lagosne_load("1.087.1")
 
+nes_nws_temp <- nes_nws
+nes_nws_temp$p_pnt_source <-  rowSums(cbind(nes_nws_temp$p_pnt_source_muni,
+                                            nes_nws_temp$p_pnt_source_septic,
+                                            nes_nws_temp$p_pnt_source_industrial),
+                                      na.rm = TRUE)
+nes_nws_sf    <- coordinatize(nes_nws_temp, "lat", "long")
+us_states <- st_intersects(us_states(), nes_nws_sf)
+us_states <- us_states()[unlist(lapply(us_states, function(x) length(x) > 0)),]
+
+plot_grid(
+  ggplot() + geom_point(data = nes_nws_temp, 
+                        aes(x = nws_ha, y = upstream_lakes_4ha_area_ha)) + 
+    xlim(300, 100000) + ylab("Up. Lk. Area") + 
+    xlab("Network Watershed Area (ha)"),
+  ggplot() + geom_point(data = nes_nws_temp, 
+                        aes(x = nws_ha, y = stream_order_ratio)) + 
+    xlim(300, 100000) + ylab("Stream Order Ratio") + 
+    xlab("Network Watershed Area (ha)"),
+
+  ggplot() + geom_point(data = nes_nws_temp, 
+                        aes(x = nws_ha, y = p_percent_retention)) + 
+    xlim(300, 100000) + ylab("P Retention") + 
+    xlab("Network Watershed Area (ha)"),
+
+  ggplot() + geom_point(data = nes_nws_temp, 
+                        aes(x = nws_ha, 
+                            y = p_pnt_source / (p_nonpnt_source + p_pnt_source))) + 
+    xlim(300, 100000) + ylab("% Pnt Source") + 
+    xlab("Network Watershed Area (ha)"), 
+  ncol = 2)
+```
+
+```{r stream_density-vs-link_length}
+library(magrittr)
+
+dplyr::select(nes_nws, 
+              avg_link_length, 
+              stream_density, 
+              closest_lake_distance) %>%
+dplyr::rename("Average Link Length" = avg_link_length,
+              "Stream Density" = stream_density,
+              "Closest Lake Distance" = closest_lake_distance) %>%
+GGally::ggpairs(columns = c("Average Link Length", 
+                            "Closest Lake Distance", 
+                            "Stream Density"),
+#                axisLabels = "none", 
+                upper = list(continuous = "blank"),
+                diag = list(continuous = "blank"),
+                lower = list(continuous = "points")) +
+  theme(strip.background = element_blank())
+
+ggplot(data = nes_nws) + 
+  geom_point(aes(x = avg_link_length, y = stream_density)) + 
+  ylab("Stream density") + xlab("Average Link Length")
 ```

### 2018-06-08 scripts/01.5_loaddata.R

@@ -1,2 +1,9 @@
-nes_nws <- readRDS("../data/nes_nws.rds")
-nes_iws <- readRDS("../data/nes_iws.rds")
+
+if(file.exists("../data/nes_nws.rds")){
+  pre_path <- "../"
+}else{
+  pre_path <- ""
+}
+
+nes_nws <- readRDS(paste0(pre_path, "data/nes_nws.rds"))
+nes_iws <- readRDS(paste0(pre_path, "data/nes_iws.rds"))

### 2018-06-08 manuscript/appendix.Rmd
add conny metric scatter plots to appendix

@@
 ```{r stream_density-vs-link_length}
-library(magrittr)
-
-dplyr::select(nes_nws, 
+test <- dplyr::select(nes_nws, 
               avg_link_length, 
@@
               "Closest Lake Distance" = closest_lake_distance) %>%
-GGally::ggpairs(columns = c("Average Link Length", 
-                            "Closest Lake Distance", 
-                            "Stream Density"),
-#                axisLabels = "none", 
-                upper = list(continuous = "blank"),
-                diag = list(continuous = "blank"),
-                lower = list(continuous = "points")) +
-  theme(strip.background = element_blank())
+dplyr::mutate(`Closest Lake Distance` = `Closest Lake Distance` / 100, 
+              `Average Link Length` = `Average Link Length` / 100)
 
-ggplot(data = nes_nws) + 
-  geom_point(aes(x = avg_link_length, y = stream_density)) + 
-  ylab("Stream density") + xlab("Average Link Length")
+pair_opts <- theme(axis.text = element_blank(), 
+      axis.ticks = element_blank())
+
+cowplot::plot_grid(
+  ggplot(data = test) + 
+    geom_point(aes(y = `Average Link Length`, x = `Stream Density`)) + 
+    pair_opts,
+  ggplot(data = test) + 
+    geom_point(aes(y = `Average Link Length`, x = `Closest Lake Distance`)) + 
+    ylab("") + pair_opts, 
+  ggplot(data = test) + 
+    geom_point(aes(y = `Closest Lake Distance`, x = `Stream Density`)) +
+    pair_opts,
+  ggplot() + geom_blank(),
+  nrow = 2, ncol = 2)
 ```

### 2018-06-08 scripts/99_utils.R

@@ -18,6 +18,7 @@ library(tidyr)
 library(ggridges)
 library(USAboundaries)
 library(sf)
+library(magrittr)
 
 prep_full_nes <- function(nes_x_lagos, conny_metrics_path, join_lagos_gis = FALSE){
   

### 2018-06-08 figures/08_maps.Rmd
towards a gis iws-nws comparison example

@@
 # ---- 08_maps ----
-
 partition_splits <- read.csv("../figures/table_1.csv")

### 2018-06-08 manuscript/appendix.Rmd
towards a gis iws-nws comparison example

@@
 ```
+
+```{r read_metric_chunks, cache=FALSE, echo=FALSE}
+knitr::read_chunk("../data/connectivity_metrics.R")
+```
+
+```{r load_packages}
+
+```
+
+```{r source_functions}
+
+```
+
+```{r iws_vs_nws-gis, cache = TRUE}
+lagoslakeid <- 6302
+iws <- pull_iws(lagoslakeid, maxsteps = Inf)
+nws <- pull_nws(lagoslakeid, maxsteps = Inf)
+
+library(rayshader)
+library(elevatr)
+library(raster)
+
+test <- elevatr::get_elev_raster(as_Spatial(iws), z = 1)
+
+```
+
+```{r best_partition_maps}
+partition_splits <- read.csv("../figures/table_1.csv")
+partition_splits <- dplyr::filter(partition_splits, !is.na(splits), 
+                                  scale %in% c("nws", "iws"))
+partition_splits <- droplevels(partition_splits)
+partition_splits$pnames2 <- factor(partition_splits$pnames2, 
+                              levels = c("cd", "ll", "la", "sd", "bf", "sr"))
+
+nes_sf    <- coordinatize(nes_nws, "lat", "long")
+us_states <- st_intersects(us_states(), nes_sf)
+us_states <- us_states()[unlist(lapply(us_states, function(x) length(x) > 0)),]
+
+# pull the lower partition group as an sf object
+get_sub <- function(dt, col_name, split_value){
+  coordinatize(
+    dplyr::filter(dt, UQ(rlang::sym(as.character(col_name))) <= split_value), 
+    "lat", "long")
+}
+
+lower_iws_maps <- lapply(which(partition_splits$scale == "iws"), 
+                         function(x) {
+                           nes_sub <- get_sub(nes_iws, 
+                                            partition_splits[x, "iws_names"],
+                                            partition_splits[x, "splits"])
+
+                           ggplot() + 
+                             geom_sf(data = us_states) +
+                             geom_sf(data = nes_sf, 
+                                     color = viridis::viridis(1, begin = 0),
+                                     size = 0.6) + 
+                             geom_sf(data = nes_sub, 
+                                color = viridis::viridis(1, begin = 0.5), 
+                                size = 0.6) + 
+                             coord_sf(datum = NA) + 
+                             ggtitle(break_word(partition_splits[x, "abb"], 12)) + 
+                             theme(plot.margin = unit(c(0, -0.1, 0, -0.1), "cm"),
+                               plot.title = element_text(face = "plain", size = 12))
+                         })
+
+lower_nws_maps <- lapply(which(partition_splits$scale == "nws"), 
+                         function(x) {
+                           nes_sub <- get_sub(nes_nws, 
+                                              partition_splits[x, "nws_names"],
+                                              partition_splits[x, "splits"])
+
+                           nes_sf_temp <- nes_sf
+                           st_geometry(nes_sf_temp) <- NULL
+                           na_rows <- !is.na(
+                    nes_sf_temp[,as.character(partition_splits[x, "nws_names"])])
+
+                           ggplot() + 
+                             geom_sf(data = us_states) +
+                             geom_sf(data = nes_sf, 
+                                     color = viridis::viridis(1, begin = 0),
+                                     size = 0.6) + 
+                             geom_sf(data = nes_sub,
+                                     color = viridis::viridis(1, begin = 0.5), 
+                                     size = 0.6) + 
+                             coord_sf(datum = NA) + 
+                             ggtitle(break_word(partition_splits[x, "abb"], 12)) + 
+                             theme(plot.margin = unit(c(0, -0.1, 0, -0.1), "cm"), 
+                               plot.title = element_text(face = "plain", size  = 12))
+                         })
+
+lower_iws_maps <- lower_iws_maps[
+  match(levels(partition_splits$pnames2), 
+        partition_splits$pnames2[which(partition_splits$scale == "iws")])
+  ]
+
+# lower_iws_maps[1][[1]] <- lower_iws_maps[1][[1]] + 
+#   theme(plot.margin = unit(c(1,0,0,0), "lines"))
+
+lower_nws_maps <- lower_nws_maps[
+  match(levels(partition_splits$pnames2), 
+        partition_splits$pnames2[which(partition_splits$scale == "nws")])
+  ]
+
+plot_grid(
+  plot_grid(NULL,
+            NULL, 
+            NULL,
+            NULL,
+            NULL, 
+            nrow = 4, ncol = 1,
+            labels = c("A. LWS", "", "B. NWS", "", ""), 
+            label_colour = "black", vjust = c(1.2, 0, 2, 0, 0), 
+            hjust = c(-0.1, 0, -0.12, 0, 0)),
+  plot_grid(
+    plot_grid(plotlist = lower_iws_maps, 
+                   ncol = 3, nrow = 2, align = "v"),
+    plot_grid(ggplot() + geom_blank()),
+    plot_grid(plotlist = lower_nws_maps,
+                   ncol = 3, nrow = 2, align = "v"), 
+    ncol = 1, rel_heights = c(1, 0.1, 1)), 
+rel_widths = c(0.2, 1), ncol = 2)
+
+```

### 2018-06-08 data/connectivity_metrics.R

@@ -1,6 +1,6 @@
 cmdargs <- commandArgs(trailingOnly = TRUE)
 
-# ---- prep_network ----
+# ---- load_packages ----
 
 # cran
 library(concaveman)
@@ -15,6 +15,8 @@ library(vapour)
 library(nhdR)
 library(LAGOSNE)
 library(streamnet)
+
+# ---- source_functions ----
 
 pull_iws <- function(lagoslakeid, maxsteps = 15){
   gdb_path <- path.expand("~/.local/share/LAGOS-GIS/lagos-ne_gis.gpkg")
@@ -56,7 +58,7 @@ pull_nws <- function(lagoslakeid, map = FALSE, maxsteps = 15, buffer_dist = 0.01
     print(lagoslakeid)
     lg        <- lagosne_load("1.087.1")
     wb_coords <- as.numeric(
-      lake_info(lg, lagoslakeid = lagoslakeid)[,c("nhd_long", "nhd_lat")])
+      LAGOSNE::lake_info(lg, lagoslakeid = lagoslakeid)[,c("nhd_long", "nhd_lat")])
     
     extract_network(wb_coords[1], wb_coords[2], maxsteps = maxsteps, 
                     buffer_dist = buffer_dist, approve_all_dl = TRUE)

### 2018-06-08 manuscript/appendix.Rmd
workout rayshader elevation map

@@
 
-test <- elevatr::get_elev_raster(as_Spatial(iws), z = 1)
+test <- elevatr::get_elev_raster(as_Spatial(iws), z = 8)
+test2 <- crop(test, nws)
+
+plot(test2)
+plot(iws$geometry, add = TRUE)
+plot(nws$geometry, add = TRUE)
+
+test3 <- as.matrix(test2)
+test4 <- rayshader::rayshade(test3, 
+   anglebreaks = seq(55,65,10), 
+   sunangle = 315, 
+   maxsearch = 100)
+
+ggplot(data = reshape2::melt(test4)) + 
+  geom_tile(aes(x = Var1, y = Var2, fill = value)) +
+  scale_fill_viridis_c() + 
+  theme(legend.position = "none") + 
+  theme_void()
+
+image(test4)
+
+test4 <- raster(test4)
+crs(test4) <- crs(test2)
+
+plot(test4)
+plot(iws$geometry, add = TRUE)
 

### 2018-06-08 manuscript/appendix.Rmd
create demo split map

--- 2018-06-08 manuscript/appendix.Rmd
@@
 
-library(rayshader)
-library(elevatr)
-library(raster)
-
-test <- elevatr::get_elev_raster(as_Spatial(iws), z = 1)
-
 ```
 
-```{r best_partition_maps}
+```{r best_partition_maps, cache=TRUE}
+# setwd("manuscript")
+
 partition_splits <- read.csv("../figures/table_1.csv")
@@
                               levels = c("cd", "ll", "la", "sd", "bf", "sr"))
+partition_splits <- dplyr::filter(partition_splits, d_k > 0.2)
 
@@
 }
-
-lower_iws_maps <- lapply(which(partition_splits$scale == "iws"), 
-                         function(x) {
-                           nes_sub <- get_sub(nes_iws, 
-                                            partition_splits[x, "iws_names"],
-                                            partition_splits[x, "splits"])
-
-                           ggplot() + 
-                             geom_sf(data = us_states) +
-                             geom_sf(data = nes_sf, 
-                                     color = viridis::viridis(1, begin = 0),
-                                     size = 0.6) + 
-                             geom_sf(data = nes_sub, 
-                                color = viridis::viridis(1, begin = 0.5), 
-                                size = 0.6) + 
-                             coord_sf(datum = NA) + 
-                             ggtitle(break_word(partition_splits[x, "abb"], 12)) + 
-                             theme(plot.margin = unit(c(0, -0.1, 0, -0.1), "cm"),
-                               plot.title = element_text(face = "plain", size = 12))
-                         })
 
@@
 
-lower_iws_maps <- lower_iws_maps[
-  match(levels(partition_splits$pnames2), 
-        partition_splits$pnames2[which(partition_splits$scale == "iws")])
-  ]
-
-# lower_iws_maps[1][[1]] <- lower_iws_maps[1][[1]] + 
-#   theme(plot.margin = unit(c(1,0,0,0), "lines"))
-
 lower_nws_maps <- lower_nws_maps[
@@
 
-plot_grid(
-  plot_grid(NULL,
-            NULL, 
-            NULL,
-            NULL,
-            NULL, 
-            nrow = 4, ncol = 1,
-            labels = c("A. LWS", "", "B. NWS", "", ""), 
-            label_colour = "black", vjust = c(1.2, 0, 2, 0, 0), 
-            hjust = c(-0.1, 0, -0.12, 0, 0)),
-  plot_grid(
-    plot_grid(plotlist = lower_iws_maps, 
-                   ncol = 3, nrow = 2, align = "v"),
-    plot_grid(ggplot() + geom_blank()),
-    plot_grid(plotlist = lower_nws_maps,
-                   ncol = 3, nrow = 2, align = "v"), 
-    ncol = 1, rel_heights = c(1, 0.1, 1)), 
-rel_widths = c(0.2, 1), ncol = 2)
+plot_grid(plotlist = lower_nws_maps[2],
+         ncol = 1, nrow = 1, align = "v")
 

### 2018-06-08 manuscript/appendix.Rmd
towards GIS IWS-NWS example

@@
 ```{r iws_vs_nws-gis, cache = TRUE}
-lagoslakeid <- 6302
-iws <- pull_iws(lagoslakeid, maxsteps = Inf)
-nws <- pull_nws(lagoslakeid, maxsteps = Inf)
+# lagoslakeid <- 6302
+# iws <- pull_iws(lagoslakeid, maxsteps = Inf)
+# nws <- pull_nws(lagoslakeid, maxsteps = Inf)
+# saveRDS(iws, "../data/iws_extent.rds")
+# saveRDS(nws, "../data/nws_extent.rds")
 
+iws <- readRDS("../data/iws_extent.rds")
+nws <- readRDS("../data/nws_extent.rds")
+
+iws_outline <- concaveman(st_cast(iws, "POINT"))
+nws_outline <- concaveman(st_cast(nws, "POINT"))
+
+ggplot() + 
+  geom_sf(data = nws) +
+  geom_sf(data = iws) + 
+  geom_sf(data = nws_outline) + 
+  geom_sf(data = iws_outline)
 ```

### 2018-06-08 manuscript/appendix.Rmd
improve GIS IWS-NWS plotting

--- 2018-06-08 manuscript/appendix.Rmd
@@
 ```{r iws_vs_nws-gis, cache = TRUE}
-lagoslakeid <- 6302
-iws <- pull_iws(lagoslakeid, maxsteps = Inf)
-nws <- pull_nws(lagoslakeid, maxsteps = Inf)
+# lagoslakeid <- 6302
+# iws <- pull_iws(lagoslakeid, maxsteps = Inf)
+# nws <- pull_nws(lagoslakeid, maxsteps = Inf)
+# focal_lake <- 
+# upstream_lakes <- 
+# saveRDS(iws, "../data/iws_extent.rds")
+# saveRDS(nws, "../data/nws_extent.rds")
+
+iws <- readRDS("../data/iws_extent.rds")
+nws <- readRDS("../data/nws_extent.rds")
+
+iws_outline <- concaveman(st_cast(iws, "POINT"))
+nws_outline <- concaveman(st_cast(nws, "POINT"))
+
+ggplot() + 
+  geom_sf(data = nws_outline, color = "cyan", size = 2) + 
+  geom_sf(data = iws_outline, color = "cyan", size = 1, linetype = "dashed") + 
+  geom_sf(data = nws) +
+  # geom_sf(data = iws) + 
+  theme_void()
 

### 2018-06-11 figures/06_k.Rmd
align iws and nws panels

--- 2018-05-31 figures/06_k.Rmd
@@
 ```{r source_utils, message=FALSE, results='hide', echo=FALSE, warning=FALSE}
-
+# setwd("scripts")
+# source("99_utils.R")
 ```
@@
 ```{r 06_k, echo=FALSE, message=FALSE, fig.cap="Distribution of the k parameter from the Vollenweider's equation in low and high connectivity partitions at the (A) LWS and (B) NWS scales.
-Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", fig.width=5, fig.height=3.8, warning=FALSE}
+Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", fig.width=7, fig.height=3.8, warning=FALSE}
+
+fit_df_iws <- rbind(
+  extract_coefs(readRDS("../data/global_vollenweider.rds"), "k"), 
+  extract_coefs2(readRDS("../data/lc_vollenweider.rds"), 
+                 c("k1_lc", "k2_lc")),
+  extract_coefs2(readRDS("../data/md_vollenweider.rds"), 
+                 c("k1_md", "k2_md")),
+  extract_coefs2(readRDS("../data/iws/cd_vollenweider.rds"),
+                 c("k1_cd", "k2_cd")),
+  extract_coefs2(readRDS("../data/iws/ll_vollenweider.rds"),
+                 c("k1_ll", "k2_ll")),
+  extract_coefs2(readRDS("../data/iws/bf_vollenweider.rds"),
+                 c("k1_bf", "k2_bf")),
+  extract_coefs2(readRDS("../data/iws/sd_vollenweider.rds"),
+                 c("k1_sd", "k2_sd")),
+  extract_coefs2(readRDS("../data/iws/sr_vollenweider.rds"), 
+                 c("k1_sr", "k2_sr")))
+  #               extract_coefs2(fit_wc, c("k1_wc", "k2_wc")),
+
+# controls ordering of ridge plot
+fit_df_iws$key <- factor(fit_df_iws$key, levels = c("k",
+                                                    "k1_sr", "k2_sr",
+                                                    "k1_bf", "k2_bf",
+                                                    "k1_md", "k2_md",
+                                                    "k1_lc", "k2_lc",
+                                                    "k1_sd", "k2_sd",
+                                                    "k1_cd", "k2_cd",
+                                                    "k1_ll", "k2_ll"))
+
+k_viz_iws <- ggplot(
+  fit_df_iws, 
+  aes(x = coef, y = key, fill = key, color = key)) + 
+    geom_density_ridges(size = 0.1, scale = 1) + 
+    scale_fill_manual(values = c("grey", 
+                            rep(c(viridis::viridis(1, begin = 0.5), 
+                                  viridis::viridis(1, begin = 0)), 7))) +
+    scale_color_manual(values = c("grey", 
+                               rep(c(viridis::viridis(1, begin = 0.5), 
+                                     viridis::viridis(1, begin = 0)), 7))) +
+    cowplot::theme_cowplot() + theme(axis.text = element_text(size = 10),
+                                     axis.title = element_text(size = 12),
+                               plot.title = element_text(size = 12, face = "plain", hjust = 0),
+                                     axis.line.x = element_line(size = 1, 
+                                     colour = "black"),
+                                     axis.line.y = element_line(size = 1, 
+                                                       colour = "black"), 
+                                     legend.position = "none", 
+                                     plot.margin = margin(0.5,0,0,0, "cm")) + 
+  xlab("Coefficient Value") + ylab("") + 
+  scale_y_discrete(breaks = levels(fit_df_iws$key)[
+    c(1, seq(3, length(levels(fit_df_iws$key)), by = 2))], 
+                   labels = rev(c("Link length",
+                   "Closest lake distance",
+                   "Stream density",
+                   "Lake connection", 
+                   "Max depth",
+                   "Baseflow",
+                   "Stream order ratio",
+                   "Global")))
+
+k_viz_iws
+
+fit_df_nws <- rbind(
+  extract_coefs(readRDS("../data/global_vollenweider.rds"), "k"), 
+  extract_coefs2(readRDS("../data/lc_vollenweider.rds"), 
+                 c("k1_lc", "k2_lc")),
+  extract_coefs2(readRDS("../data/nws/cd_vollenweider.rds"), 
+                 c("k1_cd", "k2_cd")),
+  extract_coefs2(readRDS("../data/nws/ll_vollenweider.rds"), 
+                 c("k1_ll", "k2_ll")),
+  extract_coefs2(readRDS("../data/nws/la_vollenweider.rds"), 
+                 c("k1_la", "k2_la")),
+  extract_coefs2(readRDS("../data/md_vollenweider.rds"), 
+                 c("k1_md", "k2_md")),
+  extract_coefs2(readRDS("../data/nws/bf_vollenweider.rds"), 
+                 c("k1_bf", "k2_bf")),
+  extract_coefs2(readRDS("../data/nws/sd_vollenweider.rds"), 
+                 c("k1_sd", "k2_sd")),
+  extract_coefs2(readRDS("../data/nws/sr_vollenweider.rds"), 
+                 c("k1_sr", "k2_sr")))
+
+# align iws and nws panel rows
+fit_df_nws <- dplyr::filter(fit_df_nws, fit_df_nws$key %in% fit_df_iws$key)
+
+fit_df_nws$key <- factor(fit_df_nws$key, levels = c("k",
+                                                    "k1_sr", "k2_sr",
+                                                    "k1_bf", "k2_bf",
+                                                    "k1_md", "k2_md",
+                                                    "k1_lc", "k2_lc",
+                                                    "k1_sd", "k2_sd",
+                                                    "k1_cd", "k2_cd",
+                                                    "k1_ll", "k2_ll"))
+
+k_viz_nws <- ggplot(
+  fit_df_nws, 
+  aes(x = coef, y = key, fill = key, color = key)) + 
+  geom_density_ridges(size = 0.1, rel_min_height = 0.03, scale = 1) + 
+  scale_fill_manual(values = c("grey",
+                               rep(c(viridis::viridis(1, begin = 0.5),
+                                     viridis::viridis(1, begin = 0)), 8))) +
+  scale_color_manual(values = c("grey", 
+                               rep(c(viridis::viridis(1, begin = 0.5), 
+                                     viridis::viridis(1, begin = 0)), 8))) +
+  cowplot::theme_cowplot() + theme(axis.text = element_text(size = 10),
+                                   axis.title = element_text(size = 12),
+                               plot.title = element_text(size = 12, face = "plain", hjust = 0),
+                                   axis.line.x = element_line(size = 1, 
+                                                  colour = "black"),
+                                   axis.line.y = element_line(size = 1, 
+                                                  colour = "black"), 
+                                   legend.position = "none", 
+                                   plot.margin = margin(0.5,0,0,-0.7, "cm")) + 
+  xlab("Coefficient Value") +  ylab("") +
+  scale_y_discrete(breaks = levels(fit_df_nws$key)[
+    c(1, seq(3, length(levels(fit_df_nws$key)), by = 2))], 
+    labels = rev(c("Link length",
+                   "Closest lake distance",
+                   "Stream density",
+                   "Lake connection", 
+                   "Max depth",
+                   "Baseflow",
+                   "Stream order ratio",
+                   "Global")))
+
+k_viz_nws
+
+plot_grid(
+  k_viz_iws + ggtitle("A. LWS scale") + xlim(0.8, 1.6),
+  k_viz_nws + ggtitle("B. NWS scale") + xlim(0.8, 1.6), 
+  ncol = 2, align = "v", rel_widths = c(1, 1)) + 
+  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm"))
 

### 2018-06-11 manuscript/appendix.Rmd
align iws and nws panels

@@
 
-```{r iws_vs_nws-gis, cache = TRUE}
+```{r iws_vs_nws-gis, cache = TRUE, echo=FALSE}
 # lagoslakeid <- 6302
@@
 
-```{r best_partition_maps, cache=TRUE}
+```{r best_partition_maps, cache=TRUE, echo=FALSE}
 # setwd("manuscript")
@@
                                      color = viridis::viridis(1, begin = 0),
-                                     size = 0.6) + 
+                                     size = 1) + 
                              geom_sf(data = nes_sub,
                                      color = viridis::viridis(1, begin = 0.5), 
-                                     size = 0.6) + 
+                                     size = 1) + 
                              coord_sf(datum = NA) + 

### 2018-06-11 manuscript/figures.Rmd
align iws and nws panels

@@
 Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", fig.width=5, fig.height=3.8, warning=FALSE}
-knitr::include_graphics("../figures/06_k-1.pdf")
+knitr::include_graphics("../figures/06_k-3.pdf")
 ```

### 2018-06-11 figures/06_k.Rmd
cleanup iws nws gis ex

@@
   aes(x = coef, y = key, fill = key, color = key)) + 
-  geom_density_ridges(size = 0.1, rel_min_height = 0.03, scale = 1) + 
+  geom_density_ridges(size = 0.1, scale = 1) + 
   scale_fill_manual(values = c("grey",

### 2018-06-11 manuscript/appendix.Rmd
cleanup iws nws gis ex

@@
 
-```{r load_packages}
+```{r load_packages, echo=FALSE}
 
@@
 
-```{r source_functions}
+```{r source_functions, echo=FALSE}
 
@@
 
-```{r iws_vs_nws-gis, cache = TRUE, echo=FALSE}
+```{r iws_vs_nws-gis, cache=TRUE, echo=FALSE, warning=FALSE}
 # lagoslakeid <- 6302
@@
 ggplot() + 
-  geom_sf(data = nws_outline, color = "cyan", size = 2) + 
-  geom_sf(data = iws_outline, color = "cyan", size = 1, linetype = "dashed") + 
+  geom_sf(data = nws_outline, color = "yellow", size = 2) + 
+  geom_sf(data = iws_outline, color = "cyan", size = 2) + 
   geom_sf(data = nws) +
+  coord_sf(crs = st_crs(nws), datum = NA) + 
   # geom_sf(data = iws) + 
@@
                                      color = viridis::viridis(1, begin = 0),
-                                     size = 1) + 
+                                     size = 1.4) + 
                              geom_sf(data = nes_sub,

### 2018-06-11 manuscript/appendix.Rmd
make best partition map in tmap style

@@
 
-```{r source_functions, echo=FALSE}
+```{r source_functions, echo=FALSE, warning=FALSE, message=FALSE}
 
@@
 
-```{r iws_vs_nws-gis, cache=TRUE, echo=FALSE, warning=FALSE}
+```{r iws_vs_nws-gis, cache=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
 # lagoslakeid <- 6302
@@
 
-```{r best_partition_maps, cache=TRUE, echo=FALSE}
-# setwd("manuscript")
+```{r best_partition_maps, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
+library(tmap)
+library(sf)
+library(LAGOSNE)
+library(USAboundaries)
+library(dplyr)
 
-partition_splits <- read.csv("../figures/table_1.csv")
-partition_splits <- dplyr::filter(partition_splits, !is.na(splits), 
-                                  scale %in% c("nws", "iws"))
-partition_splits <- droplevels(partition_splits)
-partition_splits$pnames2 <- factor(partition_splits$pnames2, 
-                              levels = c("cd", "ll", "la", "sd", "bf", "sr"))
-partition_splits <- dplyr::filter(partition_splits, d_k > 0.2)
+results_table <- read.csv("../scripts/table_1.csv", stringsAsFactors = FALSE)
+ll_split <- dplyr::filter(results_table, 
+                          nws_names == "avg_link_length" & 
+                          scale == "nws")$splits
+
+nes_nws <- mutate(nes_nws, grp = ifelse(avg_link_length > ll_split, 
+                                  "High", "Low"))
 
@@
 
-# pull the lower partition group as an sf object
-get_sub <- function(dt, col_name, split_value){
-  coordinatize(
-    dplyr::filter(dt, UQ(rlang::sym(as.character(col_name))) <= split_value), 
-    "lat", "long")
-}
+us <- USAboundaries::us_boundaries()
+us <- us[unlist(lapply(st_intersects(us, nes_sf), function(x) length(x) > 0)),]
+us <- filter(us, stusps != "AR")
 
-lower_nws_maps <- lapply(which(partition_splits$scale == "nws"), 
-                         function(x) {
-                           nes_sub <- get_sub(nes_nws, 
-                                              partition_splits[x, "nws_names"],
-                                              partition_splits[x, "splits"])
+nes_extent <- group_by(us, jurisdiction_type)
+nes_extent <- st_union(nes_extent)
+nes_extent <- as_Spatial(nes_extent)
 
-                           nes_sf_temp <- nes_sf
-                           st_geometry(nes_sf_temp) <- NULL
-                           na_rows <- !is.na(
-                    nes_sf_temp[,as.character(partition_splits[x, "nws_names"])])
+palette <- c(viridis::viridis(1, begin = 0),
+             viridis::viridis(1, begin = 0.5))
 
-                           ggplot() + 
-                             geom_sf(data = us_states) +
-                             geom_sf(data = nes_sf, 
-                                     color = viridis::viridis(1, begin = 0),
-                                     size = 1.4) + 
-                             geom_sf(data = nes_sub,
-                                     color = viridis::viridis(1, begin = 0.5), 
-                                     size = 1) + 
-                             coord_sf(datum = NA) + 
-                             ggtitle(break_word(partition_splits[x, "abb"], 12)) + 
-                             theme(plot.margin = unit(c(0, -0.1, 0, -0.1), "cm"), 
-                               plot.title = element_text(face = "plain", size  = 12))
-                         })
+# palette <- c("black",
+#               "black")
 
-lower_nws_maps <- lower_nws_maps[
-  match(levels(partition_splits$pnames2), 
-        partition_splits$pnames2[which(partition_splits$scale == "nws")])
-  ]
+(m_nes <- tm_shape(us) + tm_polygons() +
+          tm_shape(nes_extent) + tm_borders(lwd = 2) +
+          tm_shape(dplyr::filter(nes_sf, !is.na(grp))) + tm_dots("grp", palette = palette,
+                                 size = 0.15, legend.show = TRUE, 
+                                 title = "Average Link Length")) +
+          # tm_credits("National Eutrophication Survey") +
+          tm_layout(frame = FALSE,
+                    legend.outside = FALSE,
+                    legend.stack = "horizontal")
+```
 
-plot_grid(plotlist = lower_nws_maps[2],
-         ncol = 1, nrow = 1, align = "v")
+```{r plot_tree_example, echo=FALSE, fig.width=2, fig.height=3}
+plot_tree(gettree(readRDS("../data/nws/linklength_forest.rds")), 
+          title = "Link Length")
+```
 
+```{r partition_example_scatter, fig.height=2, fig.width=2.2}
+results_table <- read.csv("../scripts/table_1.csv", stringsAsFactors = FALSE)
+ll_split <- dplyr::filter(results_table, 
+                          nws_names == "avg_link_length" & 
+                          scale == "nws")$splits
+
+nes_nws <- mutate(nes_nws, grp = ifelse(avg_link_length > ll_split, 
+                                  "Higher", "Lower"))
+
+ggplot(data = dplyr::filter(nes_nws, 
+                     !is.na(avg_link_length))) + 
+         geom_point(aes(x = avg_link_length, 
+                                        y = p_percent_retention, 
+                                        color = grp), 
+                                    size = 2) + 
+  scale_color_manual(values = c(viridis::viridis(1, begin = 0), 
+                     viridis::viridis(1, begin = 0.5))) +
+  ylab("P Retention") + xlab("Avg. Link Length") + 
+  geom_vline(xintercept = ll_split) + 
+  theme(legend.position = "none") 
 ```

### 2018-06-11 manuscript/appendix.Rmd
add lakes to gis example

@@
 # nws <- pull_nws(lagoslakeid, maxsteps = Inf)
-# focal_lake <- 
-# upstream_lakes <- 
+# nws_lakes <- pull_lakes(nws)
 # saveRDS(iws, "../data/iws_extent.rds")
 # saveRDS(nws, "../data/nws_extent.rds")
+# saveRDS(nws_lakes, "../data/nws_lakes.rds")
 
@@
 nws <- readRDS("../data/nws_extent.rds")
+nws_lakes <- readRDS("../data/nws_lakes.rds")
+
+nws_lakes <- nws_lakes[order(st_area(nws_lakes), decreasing = TRUE),]
+nws_lakes <- nws_lakes[1:2,]
 
@@
   geom_sf(data = nws) +
+  geom_sf(data = nws_lakes[1,], color = "cyan") +
+  geom_sf(data = nws_lakes[2,], color = "yellow") +
   coord_sf(crs = st_crs(nws), datum = NA) + 
@@
 
-(m_nes <- tm_shape(us) + tm_polygons() +
-          tm_shape(nes_extent) + tm_borders(lwd = 2) +
+m_nes <- tm_shape(us) + tm_polygons() +
+          tm_shape(nes_extent) + tm_borders(lwd = 3) +
           tm_shape(dplyr::filter(nes_sf, !is.na(grp))) + tm_dots("grp", palette = palette,
-                                 size = 0.15, legend.show = TRUE, 
-                                 title = "Average Link Length")) +
+                                 size = 0.2, legend.show = TRUE, 
+                                 title = "Average Link Length") +
           # tm_credits("National Eutrophication Survey") +
@@
                     legend.stack = "horizontal")
+
+save_tmap(m_nes, "../figures/best_partition_maps-1.png",
+          scale = 0.7, width = 3.125)
 ```
@@
                                         color = grp), 
-                                    size = 2) + 
+                                    size = 1.3) + 
   scale_color_manual(values = c(viridis::viridis(1, begin = 0), 

### 2018-06-12 figures/06_k.Rmd
adjust k viz to make lws and nws more comparable

@@
   aes(x = coef, y = key, fill = key, color = key)) + 
-    geom_density_ridges(size = 0.1, scale = 1) + 
+    geom_density_ridges(size = 0.1, scale = 0.7, rel_min_height = 0.01) + 
+    geom_hline(yintercept = seq(1.8, 14.8, by = 2)) +
     scale_fill_manual(values = c("grey", 
@@
                                      viridis::viridis(1, begin = 0)), 7))) +
-    cowplot::theme_cowplot() + theme(axis.text = element_text(size = 10),
+    cowplot::theme_cowplot() + theme(panel.grid.major.y = element_blank(),
+                                     axis.text = element_text(size = 10),
                                      axis.title = element_text(size = 12),
@@
   aes(x = coef, y = key, fill = key, color = key)) + 
-  geom_density_ridges(size = 0.1, scale = 1) + 
+  geom_density_ridges(size = 0.1, scale = 0.7, rel_min_height = 0.01) + 
+  geom_hline(yintercept = seq(1.8, 14.8, by = 2)) +
   scale_fill_manual(values = c("grey",
@@
 plot_grid(
-  k_viz_iws + ggtitle("A. LWS scale") + xlim(0.8, 1.6),
-  k_viz_nws + ggtitle("B. NWS scale") + xlim(0.8, 1.6), 
+  k_viz_iws + ggtitle("Lake Watershed") + xlim(0.8, 1.6),
+  k_viz_nws + ggtitle("Network Watershed") + xlim(0.8, 1.6), 
   ncol = 2, align = "v", rel_widths = c(1, 1)) + 

### 2018-06-12 manuscript/appendix.Rmd
adjust k viz to make lws and nws more comparable

@@
 nws_outline <- concaveman(st_cast(nws, "POINT"))
+lake_1_outline <- concaveman(st_cast(nws_lakes[1,], "POINT"))
+lake_2_outline <- concaveman(st_cast(nws_lakes[2,], "POINT"))
 
@@
   geom_sf(data = nws) +
-  geom_sf(data = nws_lakes[1,], color = "cyan") +
-  geom_sf(data = nws_lakes[2,], color = "yellow") +
+  geom_sf(data = lake_1_outline, color = "cyan") +
+  geom_sf(data = lake_2_outline, color = "yellow") +
   coord_sf(crs = st_crs(nws), datum = NA) + 
@@
 
+palette <- c("black",
+              "black")
+
+m_nes <-  tm_shape(us) + tm_polygons() +
+          tm_shape(nes_extent) + tm_borders(lwd = 3) +
+          tm_shape(dplyr::filter(nes_sf, !is.na(grp))) + tm_dots("grp", palette = palette,
+                                 size = 0.2, legend.show = FALSE, 
+                                 title = "Average Link Length") +
+          # tm_credits("National Eutrophication Survey") +
+          tm_layout(frame = FALSE,
+                    legend.outside = FALSE,
+                    legend.stack = "horizontal")
+
+save_tmap(m_nes, "../figures/best_partition_maps-1.png",
+          scale = 0.7, width = 3.125)
+
+# # # # #
+
 palette <- c(viridis::viridis(1, begin = 0),
              viridis::viridis(1, begin = 0.5))
-
-# palette <- c("black",
-#               "black")
 
@@
 
-save_tmap(m_nes, "../figures/best_partition_maps-1.png",
+save_tmap(m_nes, "../figures/best_partition_maps-2.png",
           scale = 0.7, width = 3.125)

### 2018-06-18 figures/conny_metric_key.tex
recolor and align panel plots
rm uplake area

@@
   % cd %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \begin{columns} [c]     
-    \begin{column}{0.4\textwidth}
+  \begin{columns}    
+    \begin{column}[b]{0.4\textwidth}
       \huge{\textbf{Closest Lake Distance:} Network distance to the closest upstream lake.}
@@
 
-  \begin{column}{0.25\textwidth}
+  \begin{column}[b]{0.25\textwidth}
     \begin{tikzpicture}[scale = 2]
@@
   % ll %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \begin{columns}[c]  
-    \begin{column}{0.4\textwidth}
+  \begin{columns} 
+    \begin{column}[b]{0.4\textwidth}
       \huge{\textbf{Average Link Length:} Sum of the total length of stream reaches between junctions divided by the total number of reaches.}
@@
 
-    \begin{column}{0.25\textwidth}
+    \begin{column}[b]{0.25\textwidth}
       \begin{tikzpicture}[scale = 2]
@@
   % la %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \begin{columns}[c]  
-    \begin{column}{0.4\textwidth}
-      \huge{\textbf{Upstream Lake Area:} Total area of upstream lakes limited to lakes that are greater than or equal to 4ha.}
-    \end{column}
-
-    \begin{column}{0.25\textwidth}
-      \begin{tikzpicture}[scale = 2]
-          \draw [-,ultra thick, cyan] (2.2,3.7) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
-          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 3.5cm, xshift = 2cm] plot (\x:0.5+rnd*0.2);
-          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
-        \end{tikzpicture}
-    \end{column}
-
-    \begin{column}{0.25\textwidth}
-      \begin{tikzpicture}[scale = 2]
-          \draw [-,ultra thick, cyan] (2.2,4.1) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
-          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 3.5cm, xshift = 2cm] plot (\x:0.9+rnd*0.2);
-          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
-        \end{tikzpicture}
-    \end{column}
-    \end{columns}
+  % \begin{columns}[b]  
+  %   \begin{column}{0.4\textwidth}
+  %     \huge{\textbf{Upstream Lake Area:} Total area of upstream lakes limited to lakes that are greater than or equal to 4ha.}
+  %   \end{column}
+  % 
+  %   \begin{column}{0.25\textwidth}
+  %     \begin{tikzpicture}[scale = 2]
+  %         \draw [-,ultra thick, cyan] (2.2,3.7) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+  %         \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 3.5cm, xshift = 2cm] plot (\x:0.5+rnd*0.2);
+  %         \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
+  %       \end{tikzpicture}
+  %   \end{column}
+  % 
+  %   \begin{column}{0.25\textwidth}
+  %     \begin{tikzpicture}[scale = 2]
+  %         \draw [-,ultra thick, cyan] (2.2,4.1) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+  %         \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 3.5cm, xshift = 2cm] plot (\x:0.9+rnd*0.2);
+  %         \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
+  %       \end{tikzpicture}
+  %   \end{column}
+  %   \end{columns}
 
     % sd %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \begin{columns}[c]  
+  \begin{columns}[b]  
     \begin{column}{0.4\textwidth}
@@
 
+  % \rule{0.9\textwidth}{0.8pt}
+
   % sr %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \begin{columns}[c]  
+  \begin{columns}[b]  
     \begin{column}{0.4\textwidth}

### 2018-06-18 scripts/02_modelling.R
add iws up lake area model

@@ -48,7 +48,7 @@ library(akima)
 # inv_inv_closest(-1.51, nes_rf_iws) # 3773.614
 # inv_inv_closest(-1.448, nes_rf_nws) # 2681.288
 
-# stream order ratio
+# iws stream order ratio
 # tree3 <- cforest(nes_rf$p_perce ~ ., 
 #         data = dplyr::select(nes_rf, 
 #                              stream_), 
@@ -62,7 +62,7 @@ library(akima)
 # plot(gettree(tree3))
 # saveRDS(tree3, "../data/nws/sr_forest.rds")
 
-# average link length
+# iws average link length
 # tree3 <- cforest(nes_rf$p_perce ~ .,
 #                  data = dplyr::select(nes_rf,
 #                                       link_le),
@@ -76,13 +76,15 @@ library(akima)
 # plot(gettree(tree3))
 # saveRDS(tree3, "../data/nws/linklength_forest.rds")
 
-# upstream lake area
-# tree3 <- cforest(nes_rf$p_perce ~ .,
+# iws upstream lake area
+# tree3 <- cforest(nes_rf_iws$p_perce ~ .,
 #                  data = dplyr::select(nes_rf_iws,
 #                                                 upstrea),
 #                  control = ctree_control(mincriterion = 0.7))
-# saveRDS(tree3, "01_Chapter/data/iws/uplakearea_forest.rds")
-# 
+# plot(gettree(tree3))
+# saveRDS(tree3, "../data/iws/uplakearea_forest.rds")
+
+# nws upstream lake area
 # tree3 <- cforest(nes_rf_nws$p_perce ~ .,
 #                  data = dplyr::select(nes_rf_nws,
 #                                                 upstrea),
@@ -175,6 +177,8 @@ m <- readRDS("../data/global_vollenweider.rds")
 #                                 "2" = "1")
 
 # Upstream lake area
+# fit <- part_model(nes_iws, "upstream_lakes_4ha_area_ha", 0, 279, Inf, na_var = 1)
+# saveRDS(fit, "../data/iws/la_vollenweider.rds")
 # fit <- part_model(nes_nws, "upstream_lakes_4ha_area_ha", 0, 153.5, Inf, na_var = 1)
 # saveRDS(fit, "../data/nws/la_vollenweider.rds")
 

### 2018-06-18 figures/06_k.Rmd
propagate lws lake area to figures

@@
                  c("k1_md", "k2_md")),
+  extract_coefs2(readRDS("../data/iws/la_vollenweider.rds"),
+                 c("k1_la", "k2_la")),
   extract_coefs2(readRDS("../data/iws/cd_vollenweider.rds"),
@@
                                                     "k1_cd", "k2_cd",
-                                                    "k1_ll", "k2_ll"))
+                                                    "k1_ll", "k2_ll", 
+                                                    "k1_la", "k2_la"))
 
@@
                             rep(c(viridis::viridis(1, begin = 0.5), 
-                                  viridis::viridis(1, begin = 0)), 7))) +
+                                  viridis::viridis(1, begin = 0)), 8))) +
     scale_color_manual(values = c("grey", 
                                rep(c(viridis::viridis(1, begin = 0.5), 
-                                     viridis::viridis(1, begin = 0)), 7))) +
+                                     viridis::viridis(1, begin = 0)), 8))) +
     cowplot::theme_cowplot() + theme(panel.grid.major.y = element_blank(),
@@
                    "Lake connection", 
+                   "Upstream lake area",
                    "Max depth",
@@
                  c("k1_ll", "k2_ll")),
+  extract_coefs2(readRDS("../data/nws/la_vollenweider.rds"), 
+                 c("k1_la", "k2_la")),
   extract_coefs2(readRDS("../data/nws/la_vollenweider.rds"), 

### 2018-06-18 manuscript/figures.Rmd
propagate lws lake area to figures

@@
 ```{r fig.cap="Major lake and watershed characteristics, factors, and processes affecting lake P retention.
-Shaded symbols indicate items typically considered in P retention models while open symbols indicate additional items considered in the present study.", echo=FALSE}
-knitr::include_graphics("../figures/conceptual_p-cycle.pdf")
+Shaded symbols indicate items typically considered in P retention models while open symbols indicate additional items considered in the present study.", echo=FALSE, fig.width=1}
+knitr::include_graphics("../figures/conceptual_p-cycle_pt2.pdf")
 ```

### 2018-06-18 scripts/01_prepdata.R

@@ -2,7 +2,11 @@
 if(file.exists("99_utils.R")){
   source("99_utils.R")
 }else{
-  source("../scripts/99_utils.R")
+  if(file.exists("../scripts/99_utils.R")){
+    source("../scripts/99_utils.R")  
+  }else{
+    source("scripts/99_utils.R")  
+  }
 }
 
 # ---- prep_nes_lagos ----

### 2018-06-18 scripts/table_1.R

@@ -21,7 +21,7 @@ name_key <- function(){
                   "avg_link_length", "upstream_lakes_4ha_area_ha", "baseflow", NA, 
                   "stream_density", "lakeconnection"),
     iws_names = c("maxdepth", "closest_lake_distance", "stream_order_ratio", 
-                  "link_length", NA, "hu12_baseflowindex_mean", NA, 
+                  "link_length", "upstream_lakes_4ha_area_ha", "hu12_baseflowindex_mean", NA, 
                   "iws_streamdensity_streams_density_mperha", "lakeconnection"),
     conny_type = c(NA, "long", "long", "long", "long", "lat", "lat", "lat", "long")
   )
@@ -65,6 +65,7 @@ d_k <- lapply(list("data/lc_vollenweider.rds",
                    "data/iws/sd_vollenweider.rds",
                    "data/iws/bf_vollenweider.rds",
                    "data/iws/ll_vollenweider.rds",
+                   "data/iws/la_vollenweider.rds",
                    "data/iws/sr_vollenweider.rds", 
                    "data/nws/cd_vollenweider.rds", 
                    "data/nws/ll_vollenweider.rds", 
@@ -74,7 +75,7 @@ d_k <- lapply(list("data/lc_vollenweider.rds",
                    "data/nws/sr_vollenweider.rds"), delta_k)
 
 d_k <- do.call("rbind", d_k)
-d_k$scale <- c("focal", "focal", rep("lws", 5), rep("nws", 6))
+d_k$scale <- c("focal", "focal", rep("lws", 6), rep("nws", 6))
 
 res <- merge(res, d_k)
 res <- res[order(res$d_k, decreasing = TRUE),]

### 2018-06-26 scripts/05_result-stats.R
calculate proportion of total possible lakes

@@ -26,3 +26,16 @@ R2 <- round(1 - (1/(1 + k[2:4,2] * (median_tau^median_x))), 2)
 paste0("At median water residence time, k, and tau lakes with shorter and 
       longer link lengths respectively had a P retention of ", 
        R1, " and ", R2, ".")
+
+# ---- number_of_study_lakes ----
+
+if(file.exists("../data")){
+  pre_path <- "../data"
+}else{
+  pre_path <- "data"
+}
+
+dt <- read.csv(file.path(pre_path, "nes_x_lagos-ne.csv"), stringsAsFactors = FALSE)
+
+paste("We measured connectivity in", nrow(nes_iws), 
+      "out of", nrow(dt), "lakes")

### 2018-06-26 figures/06_k.Rmd
cleanup fig captions, and formatting

@@
 
-```{r 06_k, echo=FALSE, message=FALSE, fig.cap="Distribution of the k parameter from the Vollenweider's equation in low and high connectivity partitions at the (A) LWS and (B) NWS scales.
+```{r 06_k, echo=FALSE, message=FALSE, fig.cap="Distribution of the k parameter from the Vollenweider equation in low and high connectivity partitions at the (A) lake watershed and (B) network watershed scales.
 Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", fig.width=7, fig.height=3.8, warning=FALSE}
@@
                                      axis.title = element_text(size = 12),
-                               plot.title = element_text(size = 12, face = "plain", hjust = 0),
+                               plot.title = element_text(size = 12, face = "bold", hjust = 0),
                                      axis.line.x = element_line(size = 1, 
@@
                                    axis.title = element_text(size = 12),
-                               plot.title = element_text(size = 12, face = "plain", hjust = 0),
+                               plot.title = element_text(size = 12, face = "bold", hjust = 0),
                                    axis.line.x = element_line(size = 1, 
@@
 plot_grid(
-  k_viz_iws + ggtitle("Lake Watershed") + xlim(0.8, 1.6),
-  k_viz_nws + ggtitle("Network Watershed") + xlim(0.8, 1.6), 
+  k_viz_iws + ggtitle("A. Lake Watershed") + xlim(0.8, 1.6),
+  k_viz_nws + ggtitle("B. Network Watershed") + xlim(0.8, 1.6), 
   ncol = 2, align = "v", rel_widths = c(1, 1)) + 

### 2018-06-26 scripts/99_utils.R

@@ -160,7 +160,7 @@ part_pred_plot <- function(nes, fit, ind, title, xl = TRUE, yl = TRUE){
   gg_format <- function(gg){
     gg <- gg + 
       theme(legend.position = "none", 
-            plot.title = element_text(size = 10, face = "plain", color = "black", hjust = 0), 
+            plot.title = element_text(size = 10, face = "bold", color = "black", hjust = 0), 
             axis.title = element_text(size = 12), 
             axis.text = element_text(size = 10)) + 
       ylim(0, 1) + scale_x_log10() + ggtitle(title) +

### 2018-07-03 manuscript/appendix.Rmd
add nla comparison

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
+knitr::opts_chunk$set(echo = FALSE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
 ```
@@
 
-```{r plot_tree_example, echo=FALSE, fig.width=2, fig.height=3}
+```{r plot_tree_example, echo=FALSE, fig.width=2, fig.height=3, eval=FALSE}
 plot_tree(gettree(readRDS("../data/nws/linklength_forest.rds")), 
@@
 
-```{r partition_example_scatter, fig.height=2, fig.width=2.2}
+```{r partition_example_scatter, fig.height=4, fig.width=4.2, warning=FALSE}
 results_table <- read.csv("../scripts/table_1.csv", stringsAsFactors = FALSE)
@@
 ```
+
+```{r nes_vs_nla, message=FALSE, warning=FALSE}
+nla <- nla_load(2012)
+
+tp <- select(nla$waterchem_wide, PTL_RESULT, UID) %>%
+      left_join(select(nla$wide_siteinfo, AREA_HA, SITE_ID, UID)) %>%
+      group_by(SITE_ID) %>%
+      summarize(tp = median(PTL_RESULT), area = median(AREA_HA) / 100)
+
+chl  <- select(nla$chla_wide, CHLX_RESULT, UID)  %>%
+        left_join(select(nla$wide_siteinfo, SITE_ID, UID)) %>%
+        group_by(SITE_ID) %>%
+        summarize(chl = median(CHLX_RESULT))
+
+secchi  <- select(nla$secchi, SECCHI, SITE_ID)  %>%
+           group_by(SITE_ID) %>%
+           summarize(secchi = median(SECCHI))
+
+depth <- select(nla$wide_phab, DEPTH_AT_STATION, SITE_ID)  %>%
+           group_by(SITE_ID) %>%
+           summarize(depth = median(DEPTH_AT_STATION))
+
+nla <- reduce(list(tp, chl, secchi, depth), left_join)
+# skimr::skim(res)
+nla <- gather(select(nla, -SITE_ID), variable, value)
+nla$id <- "nla"
+
+nes <- select(nes_iws, tp, area = surface_area, chl, secchi, depth = maxdepth)
+nes$tp <- 1000 * nes$tp # mg to ug
+nes <- gather(nes, variable, value)
+nes$id <- "nes"
+
+res <- rbind(nla, nes)
+
+# ggplot(data = dplyr::filter(res, variable == "chl"), aes(y = id, x = value + 0.1)) + 
+#   geom_density_ridges() + 
+#   scale_x_log10()
+
+ggplot(data = res, aes(y = id, x = value + 0.1)) + 
+  geom_density_ridges() + 
+  scale_x_log10() + 
+  facet_wrap(~variable) + 
+  theme(axis.title = element_blank())
+```

### 2018-07-03 scripts/99_utils.R

@@ -1,6 +1,7 @@
 
 # ---- source_utils ----
 
+library(nlaR)
 library(pheatmap)
 library(superheat)
 library(corrr)
@@ -19,6 +20,7 @@ library(ggridges)
 library(USAboundaries)
 library(sf)
 library(magrittr)
+library(purrr)
 
 prep_full_nes <- function(nes_x_lagos, conny_metrics_path, join_lagos_gis = FALSE){
   

### 2018-07-03 figures/06_k.Rmd
mention k on x axis

@@
                                      plot.margin = margin(0.5,0,0,0, "cm")) + 
-  xlab("Coefficient Value") + ylab("") + 
+  xlab("k Value") + ylab("") + 
   scale_y_discrete(breaks = levels(fit_df_iws$key)[
@@
                                    plot.margin = margin(0.5,0,0,-0.7, "cm")) + 
-  xlab("Coefficient Value") +  ylab("") +
+  xlab("k Value") +  ylab("") +
   scale_y_discrete(breaks = levels(fit_df_nws$key)[

### 2018-07-03 scripts/05_result-stats.R
attempt to retrive nhd version

@@ -39,3 +39,14 @@ dt <- read.csv(file.path(pre_path, "nes_x_lagos-ne.csv"), stringsAsFactors = FAL
 
 paste("We measured connectivity in", nrow(nes_iws), 
       "out of", nrow(dt), "lakes")
+
+# ---- nhd_version ----
+
+library(sf)
+
+test_gdb <- "~/.local/share/nhdR/NHDH_DC.gdb"
+# st_layers(test_gdb)
+View(st_read(test_gdb, "NHDSourceCitation"))
+View(st_read(test_gdb, "NHDStatus"))
+View(st_read(test_gdb, "NHDMetadata"))
+

### 2018-07-03 scripts/99_utils.R
reverse legend

@@ -220,6 +220,7 @@ part_pred_plot <- function(nes, fit, ind, title, xl = TRUE, yl = TRUE, add_legen
     if(rev_legend){
       dummy_df <- data.frame(connectivity = c("high", "low"), 
                              foobar = c(1,2), stringsAsFactors = FALSE)
+      dummy_df$connectivity <- factor(dummy_df$connectivity, levels = c("low", "high"))
     }
     
     dummy_legend <- ggplot(dummy_df) + 

### 2018-07-12 figures/04_global_vollenweider.Rmd
combine best panel from fig 5 with fig 4

@@
 
-```{r 04_global_vollenweider, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and the global model fit to the data where the solid line and shaded interval represents the median and central 95% interval estimates respectively.", warning=FALSE, fig.width = 3.5, fig.height = 3.2}
+```{r 04_global_vollenweider, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and the global model fit to the data where the solid line and shaded interval represents the median and central 95% interval estimates respectively.", warning=FALSE, fig.width = 5.5, fig.height = 3}
 

### 2018-07-12 manuscript/figures.Rmd
combine best panel from fig 5 with fig 4

@@
 
-```{r 04_global_vollenweider, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and the global model fit to the data where the solid line and shaded interval represents the median and central 95% interval estimates respectively.", warning=FALSE, fig.width = 3.5, fig.height = 3.2}
+```{r 04_global_vollenweider, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and the global model fit to the data where the solid line and shaded interval represents the median and central 95% interval estimates respectively.", warning=FALSE}
 

### 2018-07-12 scripts/03_viz.R

@@ -4,7 +4,12 @@
 
 # ---- 04_global_vollenweider ----
 
-full_pred_plot(nes_iws, readRDS("../data/global_vollenweider.rds"))
+plot_grid(
+  full_pred_plot(nes_iws, readRDS("../data/global_vollenweider.rds")),
+  part_pred_plot(nes_nws, readRDS("../data/nws/ll_vollenweider.rds"),
+                 8, "B.", xl = TRUE, yl = FALSE), 
+  rel_widths = c(1, 0.9), 
+  rel_heights = c(1, 1))
 
 # ---- recursive_partitioning_viz ----
 

### 2018-07-12 scripts/99_utils.R

@@ -97,7 +97,7 @@ theme_pred <- function(){
   theme(legend.position = "na", 
         axis.text = element_text(size = 10), 
         axis.title = element_text(size = 12),
-        plot.title = element_text(size = 12))
+        plot.title = element_text(size = 10, face = "bold", color = "black", hjust = 0))
 }
 
 full_model <- function(nes){
@@ -118,11 +118,12 @@ full_pred_plot <- function(nes, fit){
                                  y = estimate), .prob = c(0.95), 
                     fill = "grey", color = "grey", alpha = 0.5) + 
     geom_point(data = nes, aes(x = retention_time_yr, 
-                               y = p_percent_retention)) + 
+                               y = p_percent_retention), 
+               size = 0.6, color = "grey") + 
     scale_x_log10() + ylim(0, 1) +
     scale_fill_discrete("grey") + 
     theme_pred() + 
-    ylab("P retention") + xlab("Residence time (yr)")
+    ylab("P retention") + xlab("Residence time (yr)") + ggtitle("A.")
 }
 
 # na_var: value assigned to rows with NAs
@@ -227,15 +228,15 @@ part_pred_plot <- function(nes, fit, ind, title, xl = TRUE, yl = TRUE, add_legen
       geom_line(aes(x = connectivity, y = foobar, color = connectivity)) + 
       scale_color_manual(values = c(viridis::viridis(1, begin = 0), 
                                     viridis::viridis(1, begin = 0.5))) + 
-      theme(legend.position = c(0.75, 0.8), 
+      theme(legend.position = c(0.7, 0.8), 
             legend.title = element_text(size = 7, face = "bold"), 
             legend.text = element_text(size = 7)) + 
       labs(color = legend_title)
     dl <- ggplotGrob(dummy_legend)
     legend <- gtable::gtable_filter(dl, "guide-box")
     gg_1 <- gg_1 + annotation_custom(grob = legend, 
-                                     ymax = 0.3, 
-                                     xmax = 0.5)
+                                     ymax = 0.28, 
+                                     xmax = 0.8)
   }
   
   g1 <- ggplotGrob(gg_1)

### 2018-07-12 manuscript/appendix.Rmd
move fig 5 to the appendix

@@
 ```
+
+```{r 05_partition_vollenweider, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and hierarchical model fits to the data where the solid lines and shaded intervals represent the median and central 95% model  estimates respectively.
+The green lines and symbols are the estimates from the lower of the two partition groups while the purple lines are estimates for the upper of the two partition groups (see Table 2).", fig.width = 4.8, fig.height=5, warning=FALSE}
+
+knitr::include_graphics("../figures/05_partition_vollenweider-1.pdf")
+```

### 2018-07-12 manuscript/figures.Rmd
move fig 5 to the appendix

@@
 
-```{r 05_partition_vollenweider, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and hierarchical model fits to the data where the solid lines and shaded intervals represent the median and central 95% model  estimates respectively.
-The green lines and symbols are the estimates from the lower of the two partition groups while the purple lines are estimates for the upper of the two partition groups (see Table 2).", fig.width = 4.8, fig.height=5, warning=FALSE}
-
-knitr::include_graphics("../figures/05_partition_vollenweider-1.pdf")
-```
-
 ```{r 06_k, echo=FALSE, message=FALSE, fig.cap="Distribution of the k parameter from the Vollenweider's equation in low and high connectivity partitions at the (A) LWS and (B) NWS scales.

### 2018-07-12 figures/07_cor_mat_hmap.Rmd
add correlation values to hmap fig

@@
 
-```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.width=3.5, fig.height=3.2, fig.cap="Correlation between connectivity metrics and selected lake characteristics.", message=FALSE}
+```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.width=4, fig.height=3.7, fig.cap="Correlation between connectivity metrics and selected lake characteristics.", message=FALSE}
 

### 2018-07-12 manuscript/figures.Rmd
add correlation values to hmap fig

@@
 
-```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.width=3.5, fig.height=3.2, fig.cap="Correlation between connectivity metrics and selected lake characteristics.", message=FALSE}
+```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.cap="Correlation between connectivity metrics and selected lake characteristics.", message=FALSE}
 knitr::include_graphics("../figures/07_cor_mat_hmap-1.pdf")

### 2018-07-12 scripts/03_viz.R

@@ -323,10 +323,19 @@ row.names(res_f) <- res_names_r
 #   row.names(res) <- 
 #   sapply(row.names(res), function(x) paste(strwrap(x, 10), collapse="\n "))
 
+fnc = function(var, decimal.places) {
+  var = sprintf(paste0("%1.",decimal.places,"f"), var)
+  var[var=="NA"] <- ""
+  var <- gsub("-", "", var)
+  var
+}
+
 pheatmap::pheatmap(res_f, na_col = "grey", 
                    cluster_cols = FALSE, cluster_rows = FALSE, 
                    color = colorRampPalette(
-                     rev(RColorBrewer::brewer.pal(n = 7, name ="RdBu")))(100))
+                     rev(RColorBrewer::brewer.pal(n = 7, name ="RdBu")))(100), 
+                   display_numbers = apply(res_f, 2, function(x) fnc(x, 2)), 
+                   fontsize_number = 6)
 
 # test <- superheat(
 #           X = res_f, bottom.label.text.angle = 90, 

### 2018-07-12 figures/08_maps.Rmd
add sample sizes to results table

@@
 # pull the lower partition group as an sf object
-get_sub <- function(dt, col_name, split_value){
-  coordinatize(
-    dplyr::filter(dt, UQ(rlang::sym(as.character(col_name))) <= split_value), 
-    "lat", "long")
-}
-
 lower_iws_maps <- lapply(which(partition_splits$scale == "iws"), 

### 2018-07-12 scripts/04_tables.R

@@ -85,13 +85,14 @@ knitr::kable(res, format = 'pandoc', align = c("lllll"),
 # table showing model results
 
 res <- read.csv("../scripts/table_1.csv", stringsAsFactors = FALSE)
-res <- res[, c("parameter", "units", "scale", "conny_type", "splits", "d_k")]
+res <- res[, c("parameter", "units", "scale", "conny_type", "d_k", "splits", "n_low", "n_high")]
 
 key2 <- data.frame(conny_type = unique(as.character(res$conny_type)), 
                    conny_full = c("Longitudinal", "Lateral", "-"))
 res <- merge(res, key2, sort = FALSE)
 res <- res[order(res$d_k, decreasing = TRUE),]
-res <- res[,c(2, 3, 4, 5, 6)]
+
+res <- res[,c(2, 3, 4, 5, 6, 7, 8)]
 
 # splits
 # res <- dplyr::select(res, -splits)
@@ -100,9 +101,14 @@ res$splits[!is.na(res$splits)] <- sapply(res$splits[!is.na(res$splits)],
                                            as.character(round(x, 0))
                                            }else{as.character(round(x, 2))})
 
+library(kableExtra)
+
 options(knitr.kable.NA = "-")
-knitr::kable(res, 
+knitr::kable(res, format = "latex", escape = FALSE, booktabs = TRUE,
              digits = 2, row.names = FALSE, 
-             col.names = c("Metric", "Units", "Scale", "Split Value", "Delta k"), 
-             align = c("lllcc"),
-             caption = "Classification and ranking of connectivity metrics, lake depth, and their partition split values according to median effect size.")
+             col.names = c("Metric", "Units", "Scale", 
+                           "Delta k", "Split Value", "N", "N"), 
+             align = c("lllcccc"),
+             caption = "Classification and ranking of connectivity metrics, lake depth, and their partition split values according to median effect size.") %>% 
+  kable_styling() %>%
+  add_header_above(c(" " = 5, "Low Connectivity" = 1, "High Connectivity" = 1))

### 2018-07-12 scripts/99_utils.R

@@ -356,3 +356,17 @@ break_word <- function(x, max.len){
   res <- paste(x_split[first_line], collapse = " ")
   paste(res, "\n", paste(x_split[second_line], collapse = " "))
 }
+
+get_sub <- function(dt, col_name, split_value){
+  coordinatize(
+    dplyr::filter(dt, UQ(rlang::sym(as.character(col_name))) <= split_value), 
+    "lat", "long")
+}
+
+get_sub2 <- function(dt, col_name, split_value){
+  if(is.na(split_value)){
+    table(dt[,col_name]) 
+  }else{
+    dplyr::filter(dt, UQ(rlang::sym(as.character(col_name))) <= split_value)
+  }
+}

### 2018-07-12 scripts/table_1.R

@@ -81,5 +81,26 @@ d_k$scale <- c("focal", "focal", rep("lws", 6), rep("nws", 6))
 res <- merge(res, d_k)
 res <- res[order(res$d_k, decreasing = TRUE),]
 
-write.csv(res[, c(1,2,4,5,6,7,8,9,10,11)], 
+get_sample_size <- function(x){
+  if(is.na(x$splits)){
+    sub <- get_sub2(nes_iws, as.character(x$iws_names), x$splits)
+    as.numeric(c(sub[which.min(sub)], sub[which.max(sub)]))
+  }else{
+    if(x$scale == "nws"){
+      sub <- get_sub2(nes_nws, as.character(x$nws_names), x$splits)
+      c(nrow(sub), nrow(nes_nws) - nrow(sub))
+    }else{
+      sub <- get_sub2(nes_iws, as.character(x$iws_names), x$splits)
+      c(nrow(sub), nrow(nes_iws) - nrow(sub))
+    }
+  }
+}
+
+sample_sizes <- data.frame(suppressWarnings(do.call("rbind", 
+                        lapply(seq_len(nrow(res)), 
+                               function(x) get_sample_size(res[x,])))))
+
+res[,c("n_low", "n_high")] <- sample_sizes
+
+write.csv(res[, c(1,2,4,5,6,7,8,9,10,11,12,13)], 
           "scripts/table_1.csv", row.names = FALSE)

### 2018-07-12 manuscript/figures.Rmd
shrink conceptual fig

@@
 ```{r fig.cap="Major lake and watershed characteristics, factors, and processes affecting lake P retention.
-Shaded symbols indicate items typically considered in P retention models while open symbols indicate additional items considered in the present study.", echo=FALSE, fig.width=1}
+Shaded symbols indicate items typically considered in P retention models while open symbols indicate additional items considered in the present study.", echo=FALSE, fig.width=1,out.height="4in"}
 knitr::include_graphics("../figures/conceptual_p-cycle_pt2.pdf")

### 2018-07-12 figures/06_k.Rmd
order k figure by connectivity not metric value

@@
                                                     "k1_bf", "k2_bf",
-                                                    "k1_md", "k2_md",
-                                                    "k1_lc", "k2_lc",
-                                                    "k1_sd", "k2_sd",
+                                                    "k2_md", "k1_md",
+                                                    "k1_la", "k2_la",
+                                                    "k2_lc", "k1_lc",
+                                                    "k2_sd", "k1_sd",
                                                     "k1_cd", "k2_cd",
-                                                    "k1_ll", "k2_ll", 
-                                                    "k1_la", "k2_la"))
+                                                    "k1_ll", "k2_ll"))
+# k2  = higher metric value
+# right = higher connectivity, purple
 
@@
     geom_density_ridges(size = 0.1, scale = 0.7, rel_min_height = 0.01) + 
-    geom_hline(yintercept = seq(1.8, 14.8, by = 2)) +
+    geom_hline(yintercept = seq(1.8, 16.8, by = 2)) +
     scale_fill_manual(values = c("grey", 
@@
   geom_density_ridges(size = 0.1, scale = 0.7, rel_min_height = 0.01) + 
-  geom_hline(yintercept = seq(1.8, 14.8, by = 2)) +
+  geom_hline(yintercept = seq(1.8, 16.8, by = 2)) +
   scale_fill_manual(values = c("grey",

### 2018-07-12 scripts/99_utils.R

@@ -181,12 +181,14 @@ part_pred_plot <- function(nes, fit, ind, title, xl = TRUE, yl = TRUE, add_legen
     }
     gg
   }
-  
+  # browser()
   # https://stackoverflow.com/a/37623958/3362993
   gg_1 <- ggplot() + 
     geom_point(data = nes, aes(x = retention_time_yr, 
-                               y = p_percent_retention), 
-               size = 0.6, color = "gray") +
+                               y = p_percent_retention, color = part, shape = part), 
+               size = 0.6) +
+    scale_color_manual(values = c(viridis::viridis(1, begin = 0.5), 
+                                  viridis::viridis(1, begin = 0))) +
     stat_summary(data = test[1][[1]], geom = "ribbon", 
                  aes(x = retention_time_yr, y = estimate, 
                      fill = forcats::fct_rev(ordered(...prob..))), 

### 2018-07-12 figures/08_maps.Rmd
make colors indicate connecitivity not metric magnitude in maps

--- 2018-06-01 figures/08_maps.Rmd
@@
 
+nes_sf    <- coordinatize(nes_nws, "lat", "long")
+us_states <- st_intersects(us_states(), nes_sf)
+us_states <- us_states()[unlist(lapply(us_states, function(x) length(x) > 0)),]
+
 partition_splits <- read.csv("../figures/table_1.csv")
@@
 
-nes_sf    <- coordinatize(nes_nws, "lat", "long")
-us_states <- st_intersects(us_states(), nes_sf)
-us_states <- us_states()[unlist(lapply(us_states, function(x) length(x) > 0)),]
+metric_order_key <- data.frame(
+  pnames2 = c("sr", "bf", "la", "sd", "cd", "ll"), 
+  higher_connectivity = c("higher", "higher", "higher", "lower", "higher", "higher"))
+
+partition_splits <- left_join(partition_splits, metric_order_key)
 
 # pull the lower partition group as an sf object
-get_sub <- function(dt, col_name, split_value){
-  coordinatize(
-    dplyr::filter(dt, UQ(rlang::sym(as.character(col_name))) <= split_value), 
-    "lat", "long")
-}
-
 lower_iws_maps <- lapply(which(partition_splits$scale == "iws"), 
                          function(x) {
+                           # x <- which(partition_splits$scale == "iws")[3]
                            nes_sub <- get_sub(nes_iws, 
                                           partition_splits[x, "iws_names"],
-                                            partition_splits[x, "splits"])
+                                          partition_splits[x, "splits"], 
+                                          partition_splits[x, "higher_connectivity"])
 
@@
                          function(x) {
+                           # x <- which(partition_splits$scale == "nws")[1]
                            nes_sub <- get_sub(nes_nws, 
                                           partition_splits[x, "nws_names"],
-                                              partition_splits[x, "splits"])
+                                          partition_splits[x, "splits"], 
+                                          partition_splits[x, "higher_connectivity"])
 
@@
                          })
+
+partition_splits$pnames2 <- factor(partition_splits$pnames2, 
+                                   levels = c("ll", "cd", "sd", "la", "bf", "sr"))
 

### 2018-07-12 scripts/99_utils.R

@@ -359,10 +359,16 @@ break_word <- function(x, max.len){
   paste(res, "\n", paste(x_split[second_line], collapse = " "))
 }
 
-get_sub <- function(dt, col_name, split_value){
-  coordinatize(
-    dplyr::filter(dt, UQ(rlang::sym(as.character(col_name))) <= split_value), 
-    "lat", "long")
+get_sub <- function(dt, col_name, split_value, higher_connectivity){
+  if(higher_connectivity == "higher"){
+    coordinatize(
+      dplyr::filter(dt, UQ(rlang::sym(as.character(col_name))) <= split_value), 
+      "lat", "long")
+  }else{
+    coordinatize(
+      dplyr::filter(dt, UQ(rlang::sym(as.character(col_name))) > split_value), 
+      "lat", "long")
+  }
 }
 
 get_sub2 <- function(dt, col_name, split_value){

### 2018-07-13 scripts/04_tables.R
make standalone png versions of the tables

@@ -78,8 +78,7 @@ res$X75. <- paste0(res$X75., spaces)
 res        <- data.frame(res[,1], res$min, res$X50., res$max, paste0(res$X25., " - ", res$X75.))
 names(res) <- c("", "Min", "Median", "Max", "IQR")
 
-knitr::kable(res, format = 'pandoc', align = c("lllll"),
-             caption = "Min, median, max, and interquartile range of selected lake characteristics.")
+knitr::kable(res, format = 'pandoc', align = c("lllll"))
 
 # ---- model_results_table ----
 # table showing model results
@@ -108,7 +107,6 @@ knitr::kable(res, format = "latex", escape = FALSE, booktabs = TRUE,
              digits = 2, row.names = FALSE, 
              col.names = c("Metric", "Units", "Scale", 
                            "Delta k", "Split Value", "N", "N"), 
-             align = c("lllcccc"),
-             caption = "Classification and ranking of connectivity metrics, lake depth, and their partition split values according to median effect size.") %>% 
+             align = c("lllcccc")) %>% 
   kable_styling() %>%
   add_header_above(c(" " = 5, "Low Connectivity" = 1, "High Connectivity" = 1))

### 2018-07-18 manuscript/appendix.Rmd
towards appendix cleanup

@@
 
-```{r graphical_exploratory_analysis, echo=FALSE, message=FALSE, warning=FALSE, fig.height=8.4, fig.cap="Exploratory plots"}
+```{r graphical_exploratory_analysis, echo=FALSE, message=FALSE, warning=FALSE, fig.height=8.4, fig.cap="Exploratory plots", eval=FALSE}
 partition_splits <- read.csv("../figures/table_1.csv", stringsAsFactors = FALSE)
@@
 
-```{r graphical_exploratory_analysis_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6.3, fig.cap="Exploratory plots cont"}
+```{r graphical_exploratory_analysis_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6.3, fig.cap="Exploratory plots cont", eval=FALSE}
 lg <- lagosne_load("1.087.1")
@@
 
-```{r graphical_exploratory_analysis_cont_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=5.3, fig.cap="Exploratory plots cont x 2"}
+```{r graphical_exploratory_analysis_cont_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=5.3, fig.cap="Exploratory plots cont x 2", eval=FALSE}
 lg <- lagosne_load("1.087.1")
@@
 
-```{r stream_density-vs-link_length}
+```{r stream_density-vs-link_length, eval=FALSE}
 test <- dplyr::select(nes_nws, 
@@
 
-```{r iws_vs_nws-gis, cache=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
+```{r iws_vs_nws-gis, cache=TRUE, echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}
 # lagoslakeid <- 6302
@@
 
-```{r best_partition_maps, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
+```{r best_partition_maps, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
 library(tmap)
@@
 
-```{r plot_tree_example, echo=FALSE, fig.width=2, fig.height=3, eval=FALSE}
+```{r plot_tree_example, echo=FALSE, fig.width=2, fig.height=3, eval=FALSE, eval=FALSE}
 plot_tree(gettree(readRDS("../data/nws/linklength_forest.rds")), 
@@
 
-```{r partition_example_scatter, fig.height=4, fig.width=4.2, warning=FALSE}
+```{r partition_example_scatter, fig.height=4, fig.width=4.2, warning=FALSE, eval=FALSE}
 results_table <- read.csv("../scripts/table_1.csv", stringsAsFactors = FALSE)

### 2018-07-18 scripts/99_utils.R
cleaner figure pdf to png

@@ -116,10 +116,10 @@ full_pred_plot <- function(nes, fit){
     stat_lineribbon(data = test, 
                              aes(x = retention_time_yr, 
                                  y = estimate), .prob = c(0.95), 
-                    fill = "grey", color = "grey", alpha = 0.5) + 
+                    fill = "grey", color = "black", alpha = 0.5) + 
     geom_point(data = nes, aes(x = retention_time_yr, 
                                y = p_percent_retention), 
-               size = 0.6, color = "grey") + 
+               size = 0.6, color = "black") + 
     scale_x_log10() + ylim(0, 1) +
     scale_fill_discrete("grey") + 
     theme_pred() + 

### 2018-07-18 manuscript/appendix.Rmd
towards a cleaned up appendix

@@
 
-```{r nes_vs_nla, message=FALSE, warning=FALSE}
+```{r nes_vs_nla, fig.cap="Comparison of selected lake characteristics among the stratified random sampling design of the National Lakes Assessment (nla) and the haphazard sampling of the National Eutrophication Survey (nes) lakes analyzed in the present study."}
+# , message=FALSE, warning=FALSE
 nla <- nla_load(2012)

### 2018-07-19 figures/07_cor_mat_hmap.Rmd
figure sizes are reasonable now

@@
 
-```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.width=4, fig.height=3.7, fig.cap="Correlation between connectivity metrics and selected lake characteristics.", message=FALSE}
+```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.width=4.3, fig.height=4, fig.cap="Correlation between connectivity metrics and selected lake characteristics.", message=FALSE}
 

### 2018-07-19 manuscript/figures.Rmd
figure sizes are reasonable now

@@
     fig_caption: yes
+    keep_tex: yes
 ---
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
+knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/", fig.width = 5, fig.height = 6, dev = c("pdf"))
 ```

### 2018-07-20 figures/02_conny_metric_key.tex
number tex figures

--- 2018-03-21 figures/conny_metric_key.tex
@@
   % cd %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \begin{columns} [c]     
-    \begin{column}{0.4\textwidth}
-      \huge{\textbf{Closest Lake Distance:} Network distance to the closest upstream lake.}
+  \begin{columns}    
+    \begin{column}[b]{0.4\textwidth}
+      \huge{\textbf{A. Closest Lake Distance:} Network distance to the closest upstream lake.}
     \end{column}
 
-  \begin{column}{0.25\textwidth}
+  \begin{column}[b]{0.25\textwidth}
     \begin{tikzpicture}[scale = 2]
@@
   % ll %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \begin{columns}[c]  
-    \begin{column}{0.4\textwidth}
-      \huge{\textbf{Average Link Length:} Sum of the total length of stream reaches between junctions divided by the total number of reaches.}
+  \begin{columns} 
+    \begin{column}[b]{0.4\textwidth}
+      \huge{\textbf{B. Average Link Length:} Sum of the total length of stream reaches between junctions divided by the total number of reaches.}
     \end{column}
 
-    \begin{column}{0.25\textwidth}
+    \begin{column}[b]{0.25\textwidth}
       \begin{tikzpicture}[scale = 2]
@@
   % la %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \begin{columns}[c]  
+  \begin{columns}[b]
     \begin{column}{0.4\textwidth}
-      \huge{\textbf{Upstream Lake Area:} Total area of upstream lakes limited to lakes that are greater than or equal to 4ha.}
+      \huge{\textbf{C. Upstream Lake Area:} Total area of upstream lakes limited to lakes that are greater than or equal to 4ha.}
     \end{column}
@@
     % sd %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \begin{columns}[c]  
+  \begin{columns}[b]  
     \begin{column}{0.4\textwidth}
-      \huge{\textbf{Stream Density:} the length of all streams (minus artificial lines through lakes) divided by the area of watershed.}
+      \huge{\textbf{D. Stream Density:} the length of all streams (minus artificial lines through lakes) divided by the area of watershed.}
     \end{column}
@@
 
+  % \rule{0.9\textwidth}{0.8pt}
+
   % sr %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \begin{columns}[c]  
+  \begin{columns}[b]  
     \begin{column}{0.4\textwidth}
-      \huge{\textbf{Stream Order Ratio:} The total number of first order stream reaches divided by the total number of higher order stream reaches.
+      \huge{\textbf{E.
+Stream Order Ratio:} The total number of first order stream reaches divided by the total number of higher order stream reaches.
 In this example the lower connectivity lake has a stream order ratio of 3 whereas the higher connectivity lake has a stream order ratio of 2.}

### 2018-07-20 manuscript/figures.Rmd
number tex figures

@@
 Shaded symbols indicate items typically considered in P retention models while open symbols indicate additional items considered in the present study.", echo=FALSE, fig.width=1,out.height="4in"}
-knitr::include_graphics("../figures/conceptual_p-cycle_pt2.pdf")
+knitr::include_graphics("../figures/01_conceptual_p-cycle_pt2.pdf")
 ```
@@
 ```{r fig.cap="Connectivity metric definitions along with examples of high and low connectivity lakes.", echo=FALSE}
-knitr::include_graphics("../figures/conny_metric_key_crop.pdf")
+knitr::include_graphics("../figures/02_conny_metric_key_crop_small.pdf")
 ```
@@
 In contrast to the LWS boundaries, the NWS boundaries extend to the headwaters of the lake chain.", echo=FALSE}
-knitr::include_graphics("../figures/iws_nws.pdf")
+knitr::include_graphics("../figures/03_iws_nws.pdf")
 ```

### 2018-09-11 figures/06_k.Rmd
lno calls for lower case panel letters
add significance stars to figure 7

@@
 Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", fig.width=7, fig.height=3.8, warning=FALSE}
+
+model_signif <- read.csv("../scripts/model_signif.csv", 
+                         stringsAsFactors = FALSE)
 
@@
 
+iws_labels_raw <- data.frame(parameter = rev(c(
+                   "Link length",
+                   "Closest lake distance",
+                   "Stream density",
+                   "Lake connection", 
+                   "Upstream lake area",
+                   "Max depth",
+                   "Baseflow",
+                   "Stream order ratio",
+                   "Global")), stringsAsFactors = FALSE) %>%
+  mutate(parameter_alt = parameter)
+iws_labels_raw$parameter_alt[iws_labels_raw$parameter == "Link length"] <- 
+  "Average link length"
+
+signif_star <- function(x){
+  if(!is.na(x)){
+    if(x){
+      "*"
+    }else{
+      ""
+    }
+  }else{
+    ""
+  }
+}
+
+iws_labels <- left_join(iws_labels_raw, model_signif, 
+                        by = c("parameter_alt" = "parameter")) %>%
+  filter(scale == "iws" | is.na(scale)) %>%
+  arrange(match(parameter, iws_labels_raw$parameter)) %>%
+  mutate(signif = sapply(signif, signif_star)) %>%
+  mutate(parameter = paste0(parameter, signif)) %>%
+  select(parameter)
+
+nws_labels <- left_join(iws_labels_raw, model_signif, 
+                        by = c("parameter_alt" = "parameter")) %>%
+  filter(scale == "nws" | is.na(scale)) %>%
+  arrange(match(parameter, iws_labels_raw$parameter)) %>%
+  mutate(signif = sapply(signif, signif_star)) %>%
+  mutate(parameter = paste0(parameter, signif)) %>%
+  select(parameter)
+
 k_viz_iws <- ggplot(
@@
     c(1, seq(3, length(levels(fit_df_iws$key)), by = 2))], 
-                   labels = rev(c("Link length",
-                   "Closest lake distance",
-                   "Stream density",
-                   "Lake connection", 
-                   "Upstream lake area",
-                   "Max depth",
-                   "Baseflow",
-                   "Stream order ratio",
-                   "Global")))
+                   labels = iws_labels$parameter)
 
@@
     c(1, seq(3, length(levels(fit_df_nws$key)), by = 2))], 
-    labels = rev(c("Link length",
-                   "Closest lake distance",
-                   "Stream density",
-                   "Lake connection", 
-                   "Upstream lake area",
-                   "Max depth",
-                   "Baseflow",
-                   "Stream order ratio",
-                   "Global")))
+    labels = nws_labels$parameter)
 
@@
 plot_grid(
-  k_viz_iws + ggtitle("A. Lake Watershed") + xlim(0.8, 1.6),
-  k_viz_nws + ggtitle("B. Network Watershed") + xlim(0.8, 1.6), 
+  k_viz_iws + ggtitle("a. Lake Watershed") + xlim(0.8, 1.6),
+  k_viz_nws + ggtitle("b. Network Watershed") + xlim(0.8, 1.6), 
   ncol = 2, align = "v", rel_widths = c(1, 1)) + 

### 2018-09-11 scripts/05_result-stats.R

@@ -6,6 +6,7 @@ source("01_prepdata.R")
 library(dplyr)
 library(magrittr)
 
+# setwd("scripts")
 dt           <- read.csv("../figures/table_1.csv")
 
 p_retention_by_grp <- function(rds_path){
@@ -70,13 +71,33 @@ rds_paths <- list("../data/lc_vollenweider.rds", #1
                   "../data/nws/sd_vollenweider.rds", 
                   "../data/nws/sr_vollenweider.rds")
 
-res <- lapply(rds_paths, p_retention_by_grp)
+stringr::str_extract("../data/nws/sr_vollenweider.rds", 
+                     "(?<=data/)(.+)(?=/.)")
+
+res        <- lapply(rds_paths, p_retention_by_grp)
 names(res) <- make.names(rds_paths)
-lapply(res, function(x) any(abs(x$effect_sizes) < 0.009))
 
 paste0("At median water residence time, k, and tau lakes with shorter and 
       longer link lengths respectively had a P retention of ", 
        res$...data.nws.ll_vollenweider.rds$p_retention[1], " and ", res$...data.nws.ll_vollenweider.rds$p_retention[2], ".")
+
+res_signif  <- data.frame(path = unlist(rds_paths), stringsAsFactors = FALSE) %>%
+  mutate(scale = stringr::str_extract(path, "(?<=data/)(.+)(?=/.)"), 
+         metric = stringr::str_extract(path, "(.{2})(?=_)"), 
+         signif = unlist(lapply(res, function(x){
+           !any(abs(x$effect_sizes) < 0.009)})))
+
+variable_key <- read.csv("../scripts/table_1.csv", 
+                         stringsAsFactors = FALSE)
+
+res_signif <- left_join(res_signif, 
+                        distinct(dplyr::select(variable_key, 
+                                               pnames2, parameter), 
+                                 pnames2, .keep_all = TRUE), 
+                             by = c("metric" = "pnames2"))
+
+write.csv(dplyr::select(res_signif, parameter, scale, signif), 
+          "model_signif.csv", row.names = FALSE)
 
 # ---- number_of_study_lakes ----
 

### 2018-09-14 figures/06_k.Rmd
bold significantly different k distributions

@@
 
+colorado <- function(src) {
+  # https://stackoverflow.com/a/39695859/3362993
+  src_levels <- src                                 # retrieve the levels in their order
+  boulder <- src_levels[grep("\\*", src_levels)]
+  brave <- seq_len(length(src_levels)) %in% grep("\\*", src_levels)                       # make sure everything we want to make bold is actually in the factor levels
+  b_pos <- purrr::map_int(boulder, ~which(.==src_levels)) # then find out where they are
+  b_vec <- rep("plain", length(src_levels))               # make'm all plain first
+  b_vec[b_pos] <- "bold"                                  # make our targets bold
+  b_vec                                                   # return the new vector
+}
+
 iws_labels <- left_join(iws_labels_raw, model_signif, 
@@
                                      axis.text = element_text(size = 10),
+                                     axis.text.y = element_text(size = 10, 
+                                                face = colorado(iws_labels$parameter)),
                                      axis.title = element_text(size = 12),
@@
   cowplot::theme_cowplot() + theme(axis.text = element_text(size = 10),
+                                   axis.text.y = element_text(size = 10, 
+                                                face = colorado(nws_labels$parameter)),
                                    axis.title = element_text(size = 12),

### 2018-09-17 figures/02_conny_metric_key.tex
reorder stream and lake based metrics
improve lower conn sd

@@
 
+  % la %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \begin{columns}[b]
+    \begin{column}{0.4\textwidth}
+      \huge{\textbf{C. Upstream Lake Area:} Total area of upstream lakes limited to lakes that are greater than or equal to 4ha.}
+    \end{column}
+
+    \begin{column}{0.25\textwidth}
+      \begin{tikzpicture}[scale = 2]
+          \draw [-,ultra thick, cyan] (2.2,3.7) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 3.5cm, xshift = 2cm] plot (\x:0.5+rnd*0.2);
+          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
+        \end{tikzpicture}
+    \end{column}
+
+    \begin{column}{0.25\textwidth}
+      \begin{tikzpicture}[scale = 2]
+          \draw [-,ultra thick, cyan] (2.2,4.1) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 3.5cm, xshift = 2cm] plot (\x:0.9+rnd*0.2);
+          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
+        \end{tikzpicture}
+    \end{column}
+    \end{columns}
+
   % ll %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-  % la %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \begin{columns}[b]
-    \begin{column}{0.4\textwidth}
-      \huge{\textbf{C. Upstream Lake Area:} Total area of upstream lakes limited to lakes that are greater than or equal to 4ha.}
-    \end{column}
-
-    \begin{column}{0.25\textwidth}
-      \begin{tikzpicture}[scale = 2]
-          \draw [-,ultra thick, cyan] (2.2,3.7) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
-          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 3.5cm, xshift = 2cm] plot (\x:0.5+rnd*0.2);
-          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
-        \end{tikzpicture}
-    \end{column}
-
-    \begin{column}{0.25\textwidth}
-      \begin{tikzpicture}[scale = 2]
-          \draw [-,ultra thick, cyan] (2.2,4.1) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
-          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 3.5cm, xshift = 2cm] plot (\x:0.9+rnd*0.2);
-          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
-        \end{tikzpicture}
-    \end{column}
-    \end{columns}
-
     % sd %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
       \begin{tikzpicture}[scale = 2]
-        % \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
-        \draw [-,ultra thick, cyan] (2,3) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
-        \draw [-,ultra thick, cyan] (0.5,2.9) to [out=0,in=90] (1.1,1.9) to [out=270,in=90] (0,0);
+          % \draw[step=1cm,gray,very thin] (-4,-4) grid (4,4);
+          \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+          \draw [-,ultra thick, cyan] (0.9,4) to [out=290,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
 
-        \draw [-,ultra thick, cyan] (-1,4) to [out=200,in=0] (-2,3) to [out=290,in=45] (-1.1,1.9) to [out=270,in=90] (0,0);        
-        \draw [-,ultra thick, cyan] (-0.5,2.9) to [out=250,in=250] (-1.1,1.9) to [out=270,in=90] (0,0);
+          \draw [-,ultra thick, cyan] (2.4,3.4) to [out=290,in=40] (1.95,3);
+          \draw [-,ultra thick, cyan] (0.6,3.3) to [out=40,in=190] (1,3.8);
+          \draw [-,ultra thick, cyan] (1.8,4.4) to [out=290,in=70] (2.12,4);
 

### 2018-09-18 scripts/03_viz.R
include wrt in heatmap

@@ -291,12 +291,19 @@ nes_nws_sub <- dplyr::select(nes_nws, -lakeconnection)
 conny_cols  <- unique(splits$nws_names)[!is.na(unique(splits$nws_names))]
 conny_cols  <- conny_cols[!(conny_cols %in% "lakeconnection")]
 
+
 nes_nws_sub <- nes_nws_sub[,c(conny_cols, 
-                              "lake_area_ha", "p_total", "p_pnt_source_pct", "iws_ha", "nws_ha")]
+                              "lake_area_ha", "p_total", 
+                              "p_pnt_source_pct", "iws_ha", 
+                              "nws_ha", "retention_time_yr")]
 nws_key <- merge(data.frame(nws_names = names(nes_nws_sub)), 
                  splits[,c("nws_names", "abb")], sort = FALSE)
-nws_key <- rbind(nws_key, data.frame(nws_names = c("lake_area_ha", "p_total", "p_pnt_source_pct", "iws_ha", "nws_ha"), 
-                                     abb = c("Lake Area", "P Loading", "Point Source P", "LWS area", "NWS area")))
+nws_key <- rbind(nws_key, data.frame(nws_names = c("lake_area_ha", "p_total", 
+                                                   "p_pnt_source_pct", "iws_ha", 
+                                                   "nws_ha", "retention_time_yr"), 
+                                     abb = c("Lake Area", "P Loading", 
+                                             "Point Source P", "LWS area", 
+                                             "NWS area", "W. Res. Time")))
 nws_key <- nws_key[!duplicated(nws_key),]
 names(nes_nws_sub) <- nws_key$abb
 

### 2018-09-18 manuscript/figures.Rmd
reorder figures
align fig 1 dashes and symbols with caption

@@
 
-```{r fig.cap="Major lake and watershed characteristics, factors, and processes affecting lake P retention.
-Shaded symbols indicate items typically considered in P retention models while open symbols indicate additional items considered in the present study.", echo=FALSE, fig.width=1,out.height="4in"}
+```{r fig.cap="Figure 1: Major lake and watershed P factors affecting lake P retention.
+Shaded symbols indicate tangible factors that are typically considered in P retention models while open symbols indicate additional factors specific to the present study.
+Dashed lines indicate inferred linkages, which cannot be tested with available data, but are otherwise discussed herein.
+The abbreviation ‘W.
+Res.
+Time’ is water residence time.", echo=FALSE, fig.width=1,out.height="4in"}
 knitr::include_graphics("../figures/01_conceptual_p-cycle_pt2.pdf")
@@
 
+```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.cap="Correlation between connectivity metrics and selected lake characteristics.", message=FALSE}
+knitr::include_graphics("../figures/07_cor_mat_hmap-1.pdf")
+```
+
+```{r 08_maps, echo=FALSE, fig.cap="Maps showing the locations of lake connectivity partitions.
+Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", warning=FALSE, message=FALSE}
+knitr::include_graphics("../figures/08_maps-1.pdf")
+```
+
 ```{r 04_global_vollenweider, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and the global model fit to the data where the solid line and shaded interval represents the median and central 95% interval estimates respectively.", warning=FALSE}
@@
 ```
-
-```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.cap="Correlation between connectivity metrics and selected lake characteristics.", message=FALSE}
-knitr::include_graphics("../figures/07_cor_mat_hmap-1.pdf")
-```
-
-```{r 08_maps, echo=FALSE, fig.cap="Maps showing the locations of lake connectivity partitions.
-Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", warning=FALSE, message=FALSE}
-knitr::include_graphics("../figures/08_maps-1.pdf")
-```

### 2018-09-25 scripts/99_utils.R
move signif star fxn to utils

@@ -386,3 +386,15 @@ get_sub2 <- function(dt, col_name, split_value){
     dplyr::filter(dt, UQ(rlang::sym(as.character(col_name))) <= split_value)
   }
 }
+
+signif_star <- function(x){
+  if(!is.na(x)){
+    if(x){
+      "*"
+    }else{
+      ""
+    }
+  }else{
+    ""
+  }
+}

### 2018-09-25 scripts/04_tables.R
star significant results in table 2

@@ -82,9 +82,16 @@ knitr::kable(res, format = 'pandoc', align = c("lllll"))
 
 # ---- model_results_table ----
 # table showing model results
+# setwd("scripts/")
+library(dplyr)
+library(kableExtra)
 
 res <- read.csv("../scripts/table_1.csv", stringsAsFactors = FALSE)
 res <- res[, c("parameter", "units", "scale", "conny_type", "d_k", "splits", "n_low", "n_high")]
+model_signif <- read.csv("../scripts/model_signif.csv", 
+                         stringsAsFactors = FALSE)
+model_signif$scale[model_signif$scale == "iws"] <- "lws"
+model_signif$scale[is.na(model_signif$scale)] <- "focal"
 
 key2 <- data.frame(conny_type = unique(as.character(res$conny_type)), 
                    conny_full = c("Longitudinal", "Lateral", "-"))
@@ -100,7 +107,10 @@ res$splits[!is.na(res$splits)] <- sapply(res$splits[!is.na(res$splits)],
                                            as.character(round(x, 0))
                                            }else{as.character(round(x, 2))})
 
-library(kableExtra)
+res <- left_join(res, model_signif, by = c("parameter", "scale")) %>%
+  mutate(signif = sapply(signif, signif_star)) %>%
+  mutate(d_k = paste0(round(d_k, 2), signif)) %>%
+  dplyr::select(-signif)
 
 options(knitr.kable.NA = "-")
 knitr::kable(res, format = "latex", escape = FALSE, booktabs = TRUE,
@@ -110,3 +120,4 @@ knitr::kable(res, format = "latex", escape = FALSE, booktabs = TRUE,
              align = c("lllcccc")) %>% 
   kable_styling() %>%
   add_header_above(c(" " = 5, "Low Connectivity" = 1, "High Connectivity" = 1))
+  

### 2018-09-26 figures/02_conny_metric_key.tex
add stream/lake metric labels
better branch angle for sd
top align text labels
reletter panels
add spacing, resize subheaders
emphasize network distances

@@
 
-    \begin{columns} [c]     
+% labels
+    \begin{columns}[b]     
       \begin{column}{0.4\textwidth}        
@@
 
-  % cd %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% spacer  
   \begin{columns}    
     \begin{column}[b]{0.4\textwidth}
+      \vspace{2em}
+    \end{column}
+
+  \begin{column}[b]{0.25\textwidth}
+  \end{column}
+
+  \begin{column}[b]{0.25\textwidth}
+  \end{column}
+  \end{columns}
+
+% lake label  
+  \begin{columns}[T]    
+    \begin{column}{0.4\textwidth}
+      {\fontsize{65}{65}\textbf{Lake-based Metrics}}
+      \vspace{3em}
+    \end{column}
+
+  \begin{column}{0.25\textwidth}
+  \end{column}
+
+  \begin{column}{0.25\textwidth}
+  \end{column}
+  \end{columns}
+
+  % cd %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \begin{columns}[T]    
+    \begin{column}{0.4\textwidth}
       \huge{\textbf{A. Closest Lake Distance:} Network distance to the closest upstream lake.}
@@
 
-  \begin{column}[b]{0.25\textwidth}
+  \begin{column}{0.25\textwidth}
+  \vspace{2em}
     \begin{tikzpicture}[scale = 2]
-        \draw [-,ultra thick, cyan] (2.2,2.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+        %\draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
+        \draw[-,ultra thick, cyan] plot [smooth, tension = 1] coordinates {(2.2,2.8) (1.3,1.6) (-0.3,2.7) (0,0)};
 
@@
 
-  \begin{column}[b]{0.25\textwidth}
+  \begin{column}{0.25\textwidth}
     \begin{tikzpicture}[scale = 2]
@@
 
+% spacer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{columns}    
+    \begin{column}[b]{0.4\textwidth}
+    \vspace{2em}
+    \end{column}
+
+  \begin{column}[b]{0.25\textwidth}
+  \end{column}
+
+  \begin{column}[b]{0.25\textwidth}
+  \end{column}
+  \end{columns}
+
   % la %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \begin{columns}[b]
+  \begin{columns}[T]
     \begin{column}{0.4\textwidth}
-      \huge{\textbf{C. Upstream Lake Area:} Total area of upstream lakes limited to lakes that are greater than or equal to 4ha.}
+      \huge{\textbf{B. Upstream Lake Area:} Total area of upstream lakes limited to lakes that are greater than or equal to 4ha.}
     \end{column}
@@
 
-  % ll %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{columns}    
     \begin{column}[b]{0.4\textwidth}
-      \huge{\textbf{B. Average Link Length:} Sum of the total length of stream reaches between junctions divided by the total number of reaches.}
+    \vspace{4em}
     \end{column}
@@
   \begin{column}[b]{0.25\textwidth}
+  \end{column}
+
+  \begin{column}[b]{0.25\textwidth}
+  \end{column}
+  \end{columns}
+
+\begin{columns}    
+    \begin{column}[b]{0.4\textwidth}
+      {\fontsize{65}{65}\textbf{Stream-based Metrics}}
+      \vspace{2em}
+    \end{column}
+
+  \begin{column}[b]{0.25\textwidth}
+  \end{column}
+
+  \begin{column}[b]{0.25\textwidth}
+  \end{column}
+  \end{columns}
+
+  % ll %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  \begin{columns}[T] 
+    \begin{column}{0.4\textwidth}
+      \huge{\textbf{C . Average Link Length:} Sum of the total length of stream reaches between junctions divided by the total number of reaches.}
+    \end{column}
+
+    \begin{column}{0.25\textwidth}
+      \vspace{1em}
       \begin{tikzpicture}[scale = 2]
@@
 
-    \begin{column}[b]{0.25\textwidth}
+    \begin{column}{0.25\textwidth}
+      \vspace{-3em}
       \begin{tikzpicture}[scale = 2]
@@
 
+    % spacer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+  \begin{columns}    
+    \begin{column}[b]{0.4\textwidth}
+    \vspace{2em}
+    \end{column}
+
+  \begin{column}[b]{0.25\textwidth}
+  \end{column}
+
+  \begin{column}[b]{0.25\textwidth}
+  \end{column}
+  \end{columns}
+
     % sd %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \begin{columns}[b]  
+  \begin{columns}[T]  
     \begin{column}{0.4\textwidth}
@@
           \draw [-,ultra thick, cyan] (2.4,3.4) to [out=290,in=40] (1.95,3);
-          \draw [-,ultra thick, cyan] (0.6,3.3) to [out=40,in=190] (1,3.8);
+          \draw [-,ultra thick, cyan] (0.5,4.1) to [out=310,in=190] (1,3.8);
           \draw [-,ultra thick, cyan] (1.8,4.4) to [out=290,in=70] (2.12,4);
@@
 
+  % spacer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+  \begin{columns}    
+    \begin{column}[b]{0.4\textwidth}
+    \vspace{2em}
+    \end{column}
+
+  \begin{column}[b]{0.25\textwidth}
+  \end{column}
+
+  \begin{column}[b]{0.25\textwidth}
+  \end{column}
+  \end{columns}
+
   % sr %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-  \begin{columns}[b]  
+  \begin{columns}[T]  
     \begin{column}{0.4\textwidth}
@@
     \begin{column}{0.25\textwidth}
+    \vspace{1em}
       \begin{tikzpicture}[scale = 2]
@@
     \begin{column}{0.25\textwidth}
+    \vspace{-2em}
       \begin{tikzpicture}[scale = 2]

### 2018-09-26 figures/02_conny_metric_key.tex
emphasize connectivity differences

@@
     \begin{column}{0.25\textwidth}
-      \vspace{1em}
+      \vspace{3em}
       \begin{tikzpicture}[scale = 2]
         %\draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
-        \draw [-,ultra thick, cyan] (1.8,2.6) to [out=180,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
-        \draw [-,ultra thick, cyan] (0.5,2.9) to [out=0,in=90] (1.1,1.9) to [out=270,in=90] (0,0);
+        \draw [-,ultra thick, cyan] (1.6,2.4) to [out=180,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
+        \draw [-,ultra thick, cyan] (0.58,2.3) to [out=0,in=90] (1.1,1.9) to [out=270,in=90] (0,0);
 
-        \draw [-,ultra thick, cyan] (-1.2,3.4) to [out=200,in=0] (-1.8,2.4) to [out=290,in=110] (-1.1,1.9) to [out=270,in=90] (0,0);        
-        \draw [-,ultra thick, cyan] (-0.5,2.9) to [out=250,in=70] (-1.1,1.9) to [out=270,in=90] (0,0);
+        \draw [-,ultra thick, cyan] (-1.2,2.75) to [out=200,in=0] (-1.6,2.4) to [out=290,in=110] (-1.1,1.9) to [out=270,in=90] (0,0);        
+        \draw [-,ultra thick, cyan] (-0.58,2.3) to [out=250,in=70] (-1.1,1.9) to [out=270,in=90] (0,0);
 
@@
       \begin{tikzpicture}[scale = 2]
-          % \draw[step=1cm,gray,very thin] (-4,-4) grid (4,4);
+          %\draw[step=1cm,gray,very thin] (-4,-4) grid (4,4);
           \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
@@
 
-          \draw [-,ultra thick, cyan] (2.4,3.4) to [out=290,in=40] (1.95,3);
-          \draw [-,ultra thick, cyan] (0.5,4.1) to [out=310,in=190] (1,3.8);
-          \draw [-,ultra thick, cyan] (1.8,4.4) to [out=290,in=70] (2.12,4);
+          \draw [-,ultra thick, cyan] (2.9,3.4) to [out=290,in=40] (1.95,3);
+          \draw [-,ultra thick, cyan] (0.2,3.9) to [out=310,in=190] (1.25,3.2);
+          \draw [-,ultra thick, cyan] (1.6,4.8) to [out=290,in=85] (2.07,3.6);
 
@@
     \begin{column}{0.25\textwidth}
-    \vspace{1em}
+    \vspace{2em}
       \begin{tikzpicture}[scale = 2]

### 2018-10-10 manuscript/appendix.Rmd
towards including milstead reanalysis

--- 2018-07-18 manuscript/appendix.Rmd
@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
+knitr::opts_chunk$set(echo = FALSE, fig.path = "../figures/", fig.width = 5, fig.height = 5)
 ```
@@
 ```{r partition_example_scatter, fig.height=4, fig.width=4.2, warning=FALSE, eval=FALSE}
+# setwd("manuscript")
 results_table <- read.csv("../scripts/table_1.csv", stringsAsFactors = FALSE)
@@
 
-```{r nes_vs_nla, message=FALSE, warning=FALSE}
+```{r 05_partition_vollenweider, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and hierarchical model fits to the data where the solid lines and shaded intervals represent the median and central 95% model  estimates respectively.
+The green lines and symbols are the estimates from the lower of the two partition groups while the purple lines are estimates for the upper of the two partition groups (see Table 2).", fig.width = 4.8, fig.height=5, warning=FALSE, eval=FALSE}
+
+knitr::include_graphics("../figures/05_partition_vollenweider-1.pdf")
+```
+
+```{r milstead_reanalysis}
+library(cowplot)
+library(ggplot2)
+library(sf)
+library(nhdR)
+library(LAGOSNE)
+library(maps)
+library(dplyr)
+
+## load data ####
+# setwd("scripts")
+milstead_path <- "data/milstead_2013.csv"
+
+if(!file.exists(milstead_path)){
+  library(fulltext)
+  query <- ft_search(query = "Estimating Summer Nutrient Concentrations in
+                      Northeastern Lakes from SPARROW Load Predictions and Modeled
+                      Lake Depth and Volume", from = "plos")
+  doi <- ft_links(query)$plos$ids
+  milstead <- read.csv(ft_get_si(doi, 1))
+
+  states <- sf::st_as_sf(map("state", plot = FALSE, fill = TRUE))
+  nhd_plus <- nhdR::nhd_plus_load(c(1,2), dsn = "NHDWaterbody")
+  nhd_plus <- st_transform(nhd_plus, st_crs(states))
+  states <- states[which(sapply(
+             sf::st_covers(states, nhd_plus),
+             function(x) length(x)) > 0),]
+
+  nhd <- nhdR::nhd_load(state.abb[tolower(state.name) %in% states$ID], "NHDWaterbody")
+  nhd$GNIS_ID <- sapply(as.character(nhd$GNIS_ID), function(x) substring(x, 3, nchar(x)))
+  nhd <- nhd[!is.na(nhd$ReachCode),]
+  lg <- lagosne_load("1.087.1")
+
+  milstead_j       <- dplyr::left_join(milstead, nhd_plus, by = c("WB_ID" = "COMID")) %>%
+    dplyr::left_join(nhd, by = c("REACHCODE" = "ReachCode")) %>%
+    dplyr::left_join(lg$iws.conn, by = c("Permanent_Identifier" = "iws_nhdid")) %>%
+    dplyr::left_join(lg$locus, by = c("Permanent_Identifier" = "nhdid"))
+  milstead_j <- milstead_j[complete.cases(milstead_j[,c("nhd_lat", "nhd_long")]),]
+  milstead_j    <- milstead_j[,nchar(names(milstead_j)) < 30]
+
+  write.csv(milstead, milstead_path, row.names = FALSE)
+}
+
+milstead    <- read.csv(milstead_path, stringsAsFactors = FALSE)
+milstead$Rp <- 1 - (milstead$Poutput / milstead$Pinput)
+milstead <- milstead[milstead$hrt > 0,] 
+milstead <- milstead[milstead$Area > 0.04,] # rm less than 4 ha
+
+# library(magrittr)
+# glm.fit <- milstead %>% dplyr::group_by(lakeconnectivity) %>% dplyr::do(fit = glm(Rp ~ hrt, family = "binomial", data = .))
+# 
+# broom::tidy(glm.fit, fit)
+# glm.stats <- as.data.frame(broom::glance(glm.fit, fit))
+# # https://ww2.coastal.edu/kingw/statistics/R-tutorials/logistic.html
+# 1 - pchisq(glm.stats$null.deviance - glm.stats$deviance, 1)
+
+# ggplot(data = milstead[!is.na(milstead$lakeconnectivity),], aes(x = lakeconnectivity, y = hrt)) + geom_boxplot(notch = TRUE) + scale_y_log10()
+
+yr_labels <- c("1e-07", "1e-05", 
+               as.character(10/365), 
+               as.character(2/12), as.character(6/12), 
+               "2", "10")
+
+format_labels <- function(x, mult_factor){
+  gsub("\\.+$", "\\1", gsub("0+$", "\\1",
+    trimws(format(round(as.numeric(x), 6) * 
+      mult_factor, scientific = FALSE)), perl = TRUE))
+  }
+
+day_labels   <- ceiling(as.numeric(
+  format_labels(yr_labels, 365)) / 10) * 10
+minute_labels  <- ceiling(as.numeric(
+  format_labels(yr_labels, 365 * 24 * 60)) / 10) * 10
+month_labels  <- round(as.numeric(
+  format_labels(yr_labels, 12)), 0)
+
+mixed_labels <- paste0(
+      c(minute_labels[1:2], day_labels[3], month_labels[4:5], yr_labels[6:7]), 
+      c(" min", " min", " days", " months", " months", " years", " years"))
+
+quants <- exp(quantile(log(milstead[, "hrt"])))
+
+gg_fit_single <- 
+  ggplot(data = milstead, 
+    aes(x = hrt, y = Rp)) + geom_point(size = 0.9) +
+  scale_x_log10(labels = mixed_labels, 
+    breaks = as.numeric(yr_labels), limits = c(1 / 365, 11)) +
+  stat_smooth(method = "glm", method.args = list(family = "binomial"), 
+              se = TRUE) +
+  scale_color_brewer(palette = "Set1") +
+  cowplot::theme_cowplot() + 
+  theme(legend.position = "none", legend.title = element_blank(), legend.text = element_text()) +
+  xlab("Residence Time") +
+  ylab("P Retention (%)") + 
+  geom_segment(data = data.frame(x = quants[c(2, 4)], y = c(0.8, 0.8)), 
+               aes(x = x, y = c(0, 0), xend = x, yend = y), 
+               color = "gray42", size = 1.5, linetype = 2)
+
+if(!interactive()){
+  ggsave("milstead_single.pdf", gg_fit_single, height = 5)
+}
+
+# milstead <- droplevels(milstead[milstead$lakeconnectivity != "Isolated",])
+gg_fit_multi <- ggplot(data = milstead, aes(x = hrt, y = Rp)) +
+  geom_point(size = 0.9) +
+  scale_x_log10(labels = mixed_labels, 
+                breaks = as.numeric(yr_labels), limits = c(1 / 365, 11)) +
+  stat_smooth(method = "glm", method.args = list(family = "binomial"), 
+              se = TRUE, aes(color = lakeconnectivity), 
+              data = milstead) +
+  scale_color_brewer(palette = "Set1") +
+  cowplot::theme_cowplot() + 
+  theme(legend.title = element_blank(), legend.position = c(0.13, 0.8),
+        legend.text = element_text()) +
+  xlab("Residence Time") +
+  ylab("P Retention (%)") + 
+  geom_segment(data = data.frame(x = quants[c(2, 4)], y = c(0.8, 0.8)), 
+               aes(x = x, y = c(0, 0), xend = x, yend = y), 
+               color = "gray42", size = 1.5, linetype = 2)
+
+if(!interactive()){  
+  ggsave("milstead_multi.pdf", gg_fit_multi, height = 5)
+}
+
+# legend <- get_legend(gg_fit_multi)
+gg <- plot_grid(gg_fit_single, gg_fit_multi, scale = c(1, 1), rel_widths = c(3, 3), nrow = 1)
+
+if(!interactive()){
+  ggsave("milstead_conny.pdf", gg, height = 3.5, width = 7)
+}
+
+# ggsave("milstead_conny_nogroup.pdf", gg)
+
+# hist(log(x))
+# hist(log(dt[dt$variable == "x_raw", "value"]))
+
+nes <- read.csv("/home/jose/R/scripts/NES/nes_data.csv")
+nes <- nes[!is.na(nes$retention_time),]
+
+nes$retention_time[nes$retention_time_units == "days" & 
+  !is.na(nes$retention_time_units)] <- 
+  nes$retention_time[nes$retention_time_units == "days" & 
+                       !is.na(nes$retention_time_units)] / 365
+
+dt <- data.frame(variable = "Milstead", 
+          reshape2::melt(milstead[,"hrt"]))
+
+# quants <- exp(quantile(log(dt$value)))
+# format_labels(quants, 365)
+# format_labels(quants, 12)
+
+dt <- rbind(dt, 
+        data.frame(variable = "NES", 
+          reshape2::melt(nes[, c("retention_time")])))
+
+# dt$value <- log(dt$value)
+
+dens <- density(dt[dt$variable == "Milstead", "value"])
+dens <- data.frame(x = dens$x, y = dens$y)
+
+gg <- ggplot(data = dt, aes(x = value)) +
+  geom_density(aes(linetype = variable), alpha = 0.5, size = 1.55) + 
+  scale_x_log10(breaks = as.numeric(yr_labels)[c(3, 5, 7)], 
+                labels = mixed_labels[c(3, 5, 7)]) + 
+  cowplot::theme_cowplot() + theme(legend.position = c(0.15, 0.8), legend.title = element_blank(), legend.text = element_text()) +
+  xlab("Residence Time") + 
+  geom_segment(data = data.frame(x = quants[c(2, 4)], y = c(0.266, 0.48)), 
+               aes(x = x, y = 0, xend = x, yend = y), size = 1.55)
+
+if(!interactive()){  
+  ggsave("hrt_density.pdf", gg, height = 4)
+}
+
+# nes_fit_single <- ggplot(data = nes, aes(x = retention_time, y = p_percent_retention)) +
+#   geom_point() +
+#   scale_x_log10(labels = mixed_labels[c(2:4)], breaks = c(1e-05, 1e-02, 1e+01)) +
+#   stat_smooth(method = "glm", method.args = list(family = "binomial"), se = TRUE) +
+#   scale_color_brewer(palette = "Set1") +
+#   cowplot::theme_cowplot() + 
+#   theme(legend.position = "none", legend.title = element_blank(), legend.text = element_text()) +
+#   xlab("Residence Time") +
+#   ylab("P Retention (%)")
+```
+
+```{r p-retention_vs_percent-ag, fig.cap="P retention versus percent agriculture in network watersheds.", fig.width = 3, fig.height = 3}
+nes_nws$percent_ag <- nes_iws$iws_nlcd1992_pct_81 + nes_iws$iws_nlcd1992_pct_82
+
+ggplot() + 
+  geom_point(data = nes_nws, aes(x = percent_ag, y = p_percent_retention)) +
+  xlab("Percent Agriculture") + ylab("P Retention")
+
+```
+
+```{r nes_vs_nla, fig.cap="Comparison of selected lake characteristics among the stratified random sampling design of the National Lakes Assessment (nla) and the haphazard sampling of the National Eutrophication Survey (nes) lakes analyzed in the present study.", fig.height=4}
+# , message=FALSE, warning=FALSE
 nla <- nla_load(2012)
@@
 ```
-
-```{r 05_partition_vollenweider, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and hierarchical model fits to the data where the solid lines and shaded intervals represent the median and central 95% model  estimates respectively.
-The green lines and symbols are the estimates from the lower of the two partition groups while the purple lines are estimates for the upper of the two partition groups (see Table 2).", fig.width = 4.8, fig.height=5, warning=FALSE}
-
-knitr::include_graphics("../figures/05_partition_vollenweider-1.pdf")
-```

### 2018-10-11 manuscript/appendix.Rmd
try building milstead

--- 2018-07-18 manuscript/appendix.Rmd
@@
 
-```{r nes_vs_nla, message=FALSE, warning=FALSE}
+```{r 05_partition_vollenweider, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and hierarchical model fits to the data where the solid lines and shaded intervals represent the median and central 95% model  estimates respectively.
+The green lines and symbols are the estimates from the lower of the two partition groups while the purple lines are estimates for the upper of the two partition groups (see Table 2).", fig.width = 4.8, fig.height=5, warning=FALSE, eval=FALSE}
+
+knitr::include_graphics("../figures/05_partition_vollenweider-1.pdf")
+```
+
+```{r milstead_reanalysis}
+library(cowplot)
+library(ggplot2)
+library(sf)
+library(nhdR)
+library(LAGOSNE)
+library(maps)
+library(dplyr)
+
+## load data ####
+milstead_path <- "data/milstead_2013.csv"
+# unlink(milstead_path)
+
+if(!file.exists(milstead_path)){
+  states <- sf::st_as_sf(map("state", plot = FALSE, fill = TRUE))
+  nhd_plus <- nhdR::nhd_plus_load(c(1,2), dsn = "NHDWaterbody")
+  nhd_plus <- st_transform(nhd_plus, st_crs(states))
+  states <- states[which(sapply(
+             sf::st_covers(states, nhd_plus),
+             function(x) length(x)) > 0),]
+
+  nhd <- nhdR::nhd_load(state.abb[tolower(state.name) %in% states$ID], "NHDWaterbody")
+  nhd$GNIS_ID <- sapply(as.character(nhd$GNIS_ID), function(x) substring(x, 3, nchar(x)))
+  nhd <- nhd[!is.na(nhd$ReachCode),]
+  st_geometry(nhd) <- NULL
+  lg <- lagosne_load("1.087.1")
+
+  library(fulltext)
+  query <- ft_search(query = "Estimating Summer Nutrient Concentrations in
+                      Northeastern Lakes from SPARROW Load Predictions and Modeled
+                      Lake Depth and Volume", from = "plos")
+  doi <- ft_links(query)$plos$ids
+  milstead <- read.csv(ft_get_si(doi, 1))
+
+  # paused here
+  milstead_j <- dplyr::left_join(milstead, 
+                  dplyr::select(nhd_plus, COMID, REACHCODE), 
+                by = c("WB_ID" = "COMID")) %>%
+    dplyr::left_join(
+        dplyr::select(nhd, Permanent_Identifier, ReachCode), 
+      by = c("REACHCODE" = "ReachCode")) %>%
+    dplyr::left_join(
+        dplyr::select(lg$lakes.geo, lakeconnection, lakes_nhdid), 
+      by = c("Permanent_Identifier" = "lakes_nhdid")) %>%
+    dplyr::left_join(
+        dplyr::select(lg$locus, nhdid, nhd_lat, nhd_long), 
+      by = c("Permanent_Identifier" = "nhdid"))
+  milstead_j <- milstead_j[complete.cases(milstead_j[,c("nhd_lat", "nhd_long")]),]
+  milstead_j <- milstead_j[,nchar(names(milstead_j)) < 30] 
+  milstead_j <- milstead_j[, -which(names(milstead_j) == "geometry")]
+
+  write.csv(milstead_j, milstead_path, row.names = FALSE)
+}
+
+md    <- read.csv(milstead_path, stringsAsFactors = FALSE)
+md$Rp <- 1 - (as.numeric(md$Poutput) / as.numeric(md$Pinput))
+md    <- md[md$Rp >= 0 & md$Rp <= 1,]
+md$hrt <- as.numeric(md$hrt)
+md     <- md[md$hrt > 0,] 
+md     <- md[md$Area > 0.04,] # rm less than 4 ha
+
+# library(magrittr)
+# glm.fit <- milstead %>% dplyr::group_by(lakeconnectivity) %>% dplyr::do(fit = glm(Rp ~ hrt, family = "binomial", data = .))
+# 
+# broom::tidy(glm.fit, fit)
+# glm.stats <- as.data.frame(broom::glance(glm.fit, fit))
+# # https://ww2.coastal.edu/kingw/statistics/R-tutorials/logistic.html
+# 1 - pchisq(glm.stats$null.deviance - glm.stats$deviance, 1)
+
+# ggplot(data = milstead[!is.na(milstead$lakeconnectivity),], aes(x = lakeconnectivity, y = hrt)) + geom_boxplot(notch = TRUE) + scale_y_log10()
+
+yr_labels <- c("1e-07", "1e-05", 
+               as.character(10/365), 
+               as.character(2/12), as.character(6/12), 
+               "2", "10")
+
+format_labels <- function(x, mult_factor){
+  gsub("\\.+$", "\\1", gsub("0+$", "\\1",
+    trimws(format(round(as.numeric(x), 6) * 
+      mult_factor, scientific = FALSE)), perl = TRUE))
+  }
+
+day_labels   <- ceiling(as.numeric(
+  format_labels(yr_labels, 365)) / 10) * 10
+minute_labels  <- ceiling(as.numeric(
+  format_labels(yr_labels, 365 * 24 * 60)) / 10) * 10
+month_labels  <- round(as.numeric(
+  format_labels(yr_labels, 12)), 0)
+
+mixed_labels <- paste0(
+      c(minute_labels[1:2], day_labels[3], month_labels[4:5], yr_labels[6:7]), 
+      c(" min", " min", " days", " months", " months", " years", " years"))
+
+quants <- exp(quantile(log(md[, "hrt"]), na.rm = TRUE))
+
+gg_fit_single <- 
+  ggplot(data = md, 
+    aes(x = hrt, y = Rp)) + geom_point(size = 0.9) +
+  scale_x_log10(labels = mixed_labels, 
+    breaks = as.numeric(yr_labels), limits = c(1 / 365, 11)) +
+  stat_smooth(method = "glm", method.args = list(family = "binomial"), 
+              se = TRUE) +
+  scale_color_brewer(palette = "Set1") +
+  cowplot::theme_cowplot() + 
+  theme(legend.position = "none", legend.title = element_blank(), legend.text = element_text()) +
+  xlab("Residence Time") +
+  ylab("P Retention (%)") + 
+  geom_segment(data = data.frame(x = quants[c(2, 4)], y = c(0.8, 0.8)), 
+               aes(x = x, y = c(0, 0), xend = x, yend = y), 
+               color = "gray42", size = 1.5, linetype = 2)
+
+# if(!interactive()){
+#   ggsave("milstead_single.pdf", gg_fit_single, height = 5)
+# }
+
+# milstead <- droplevels(milstead[milstead$lakeconnectivity != "Isolated",])
+gg_fit_multi <- ggplot(data = md, aes(x = hrt, y = Rp)) +
+  geom_point(size = 0.9) +
+  scale_x_log10(labels = mixed_labels, 
+                breaks = as.numeric(yr_labels), limits = c(1 / 365, 11)) +
+  stat_smooth(method = "glm", method.args = list(family = "binomial"), 
+              se = TRUE, aes(color = lakeconnection), 
+              data = md) +
+  scale_color_brewer(palette = "Set1") +
+  cowplot::theme_cowplot() + 
+  theme(legend.title = element_blank(), legend.position = c(0.13, 0.8),
+        legend.text = element_text()) +
+  xlab("Residence Time") +
+  ylab("P Retention (%)") + 
+  geom_segment(data = data.frame(x = quants[c(2, 4)], y = c(0.8, 0.8)), 
+               aes(x = x, y = c(0, 0), xend = x, yend = y), 
+               color = "gray42", size = 1.5, linetype = 2)
+
+if(!interactive()){  
+  gg_fit_multi
+}
+
+# legend <- get_legend(gg_fit_multi)
+# gg <- plot_grid(gg_fit_single, gg_fit_multi, scale = c(1, 1), rel_widths = c(3, 3), nrow = 1)
+# 
+# if(!interactive()){
+#   ggsave("milstead_conny.pdf", gg, height = 3.5, width = 7)
+# }
+
+# ggsave("milstead_conny_nogroup.pdf", gg)
+
+# hist(log(x))
+# hist(log(dt[dt$variable == "x_raw", "value"]))
+
+# nes <- read.csv("/home/jose/R/scripts/NES/nes_data.csv")
+# nes <- nes[!is.na(nes$retention_time),] 
+# 
+# nes$retention_time[nes$retention_time_units == "days" & 
+#   !is.na(nes$retention_time_units)] <- 
+#   nes$retention_time[nes$retention_time_units == "days" & 
+#                        !is.na(nes$retention_time_units)] / 365
+# 
+# dt <- data.frame(variable = "Milstead", 
+#           reshape2::melt(milstead[,"hrt"]))
+# 
+# # quants <- exp(quantile(log(dt$value)))
+# # format_labels(quants, 365)
+# # format_labels(quants, 12)
+# 
+# dt <- rbind(dt, 
+#         data.frame(variable = "NES", 
+#           reshape2::melt(nes[, c("retention_time")])))  
+# 
+# # dt$value <- log(dt$value)
+# 
+# dens <- density(dt[dt$variable == "Milstead", "value"])
+# dens <- data.frame(x = dens$x, y = dens$y)
+# 
+# gg <- ggplot(data = dt, aes(x = value)) +
+#   geom_density(aes(linetype = variable), alpha = 0.5, size = 1.55) + 
+#   scale_x_log10(breaks = as.numeric(yr_labels)[c(3, 5, 7)], 
+#                 labels = mixed_labels[c(3, 5, 7)]) + 
+#   cowplot::theme_cowplot() + theme(legend.position = c(0.15, 0.8), legend.title = element_blank(), legend.text = element_text()) +
+#   xlab("Residence Time") + 
+#   geom_segment(data = data.frame(x = quants[c(2, 4)], y = c(0.266, 0.48)), 
+#                aes(x = x, y = 0, xend = x, yend = y), size = 1.55)
+# 
+# if(!interactive()){  
+#   ggsave("hrt_density.pdf", gg, height = 4)
+# }
+# 
+# # nes_fit_single <- ggplot(data = nes, aes(x = retention_time, y = p_percent_retention)) +
+# #   geom_point() +
+# #   scale_x_log10(labels = mixed_labels[c(2:4)], breaks = c(1e-05, 1e-02, 1e+01)) +
+# #   stat_smooth(method = "glm", method.args = list(family = "binomial"), se = TRUE) +
+# #   scale_color_brewer(palette = "Set1") +
+#   cowplot::theme_cowplot() + 
+#   theme(legend.position = "none", legend.title = element_blank(), legend.text = element_text()) +
+#   xlab("Residence Time") +
+#   ylab("P Retention (%)")
+```
+
+```{r p-retention_vs_percent-ag, fig.cap="P retention versus percent agriculture in network watersheds.", fig.width = 3, fig.height = 3}
+nes_nws$percent_ag <- nes_iws$iws_nlcd1992_pct_81 + nes_iws$iws_nlcd1992_pct_82
+
+ggplot() + 
+  geom_point(data = nes_nws, aes(x = percent_ag, y = p_percent_retention)) +
+  xlab("Percent Agriculture") + ylab("P Retention")
+
+```
+
+```{r nes_vs_nla, fig.cap="Comparison of selected lake characteristics among the stratified random sampling design of the National Lakes Assessment (nla) and the haphazard sampling of the National Eutrophication Survey (nes) lakes analyzed in the present study.", fig.height=4}
+# , message=FALSE, warning=FALSE
 nla <- nla_load(2012)

### 2018-10-11 manuscript/appendix.Rmd
finish out milstead reanalysis

@@
 
-```{r milstead_reanalysis}
+```{r milstead_reanalysis, fig.cap="Relationship between residence time and phosphorus retention for inland lakes with surface area greater than 4 ha in Northeastern USA (New England).
+Vertical dashed lines denote lakes with intermediate residence times (within the interquartile range).
+Best fit lines are colored based on whether they have upstream lake connections (DR_LakeStream), or upstream stream connection (DR_Stream), are headwater lakes, or are isolated lakes.
+Data from Milstead et al.
+(2013).", fig.width = 5, fig.height = 4}
 library(cowplot)
@@
 ## load data ####
-milstead_path <- "data/milstead_2013.csv"
+milstead_path <- "../data/milstead_2013.csv"
 # unlink(milstead_path)
@@
 
-if(!interactive()){  
+# if(!interactive()){  
   gg_fit_multi
-}
+# }
 

### 2018-10-15 figures/06_k.Rmd
move signif star fxn to utils
change network to lake network

@@
 
-signif_star <- function(x){
-  if(!is.na(x)){
-    if(x){
-      "*"
-    }else{
-      ""
-    }
-  }else{
-    ""
-  }
-}
-
 colorado <- function(src) {
@@
     cowplot::theme_cowplot() + theme(panel.grid.major.y = element_blank(),
-                                     axis.text = element_text(size = 10),
-                                     axis.text.y = element_text(size = 10, 
+                                     axis.text = element_text(size = 9),
+                                     axis.text.y = element_text(size = 8, 
                                                 face = colorado(iws_labels$parameter)),
-                                     axis.title = element_text(size = 12),
-                               plot.title = element_text(size = 12, face = "bold", hjust = 0),
+                                     axis.title = element_text(size = 10),
+                               plot.title = element_text(size = 9, face = "bold", hjust = 0),
                                      axis.line.x = element_line(size = 1, 
@@
                                      viridis::viridis(1, begin = 0)), 8))) +
-  cowplot::theme_cowplot() + theme(axis.text = element_text(size = 10),
-                                   axis.text.y = element_text(size = 10, 
+  cowplot::theme_cowplot() + theme(axis.text = element_text(size = 9),
+                                   axis.text.y = element_text(size = 8, 
                                                 face = colorado(nws_labels$parameter)),
-                                   axis.title = element_text(size = 12),
-                               plot.title = element_text(size = 12, face = "bold", hjust = 0),
+                                   axis.title = element_text(size = 10),
+                               plot.title = element_text(size = 9, face = "bold", hjust = 0),
                                    axis.line.x = element_line(size = 1, 
@@
   k_viz_iws + ggtitle("a. Lake Watershed") + xlim(0.8, 1.6),
-  k_viz_nws + ggtitle("b. Network Watershed") + xlim(0.8, 1.6), 
+  k_viz_nws + ggtitle("b. Lake Network Watershed") + xlim(0.8, 1.6), 
   ncol = 2, align = "v", rel_widths = c(1, 1)) + 

### 2018-10-15 figures/beamer-lake-fig/beamer-lake-fig.tex
change network to lake network

%% beamer-lake-fig.tex
%%
%% Copyright (C) 2016 - 2017  Joseph Stachelek
%%
%% This file is part of beamer-lake-fig repository.
%%
%% beamer-lake-fig is free software: you can redistribute it
%% and/or modify it under the terms of the GNU General Public License as
%% published by the Free Software Foundation, either version 2 of the
%% License, or (at your option) any later version.
%%
%% beamer-lake-fig is distributed in the hope that it will be
%% useful, but WITHOUT ANY WARRANTY; without even the implied warranty of
%% MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the GNU General
%% Public License for more details.
%%
%% You should have received a copy of the GNU General Public License along with
%% beamer-lake-fig.  If not, see <http://www.gnu.org/licenses/>.

\PassOptionsToPackage{x11names}{xcolor}
\usetikzlibrary{decorations.pathmorphing,calc}

\usepackage{subfiles}
\usepackage{pbox}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{colortbl}

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\def\mystrut(#1,#2){\vrule height #1 depth #2 width 0pt}

\newcolumntype{C}[1]{%
   >{\mystrut(3ex,2ex)\centering}%
   p{#1}%
   <{}}

\newcolumntype{K}[1]{%
 >{\vbox to 5ex\bgroup\vfill\centering}%
 p{#1}%
 <{\egroup}}

% \definecolor{darkgreen}{rgb}{0.13,0.62,0.25}
\definecolor{darkgreen}{RGB}{23,155,51}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{lakediagramgreen}
\def\lakediagramgreen[#1]{
\begin{tikzpicture}[scale = #1]
% https://tex.stackexchange.com/questions/95044/create-diagrams-in-latex-with-tikz

% Define some reference points 
% The figure is drawn a bit bigger, and then clipped to the following dimensions:
\coordinate (clipping area) at (10, 7);
\clip (0,0) rectangle (clipping area);

% Next reference points are relative to the lower left corner of the clipping area
\coordinate (water level) at (0, 6);
\coordinate (bottom)      at (5, 1.3);     % (bottom of the pit)
\coordinate (ground1)     at (0, 5);       % (left shore)
\coordinate (ground2)     at (10, 5);      % (right shore)

% Coordinates of the bigger area really drawn
\coordinate (lower left)  at ([xshift=-5mm, yshift=-5mm] 0,0);
\coordinate (upper right) at ([xshift=5mm,  yshift=5mm] clipping area);

% Draw the water and ripples
\draw [draw=blue!80!black, decoration={bumps, mirror, segment length=6mm}, decorate,
     bottom color=cyan!60!black, top color=darkgreen!20!white] 
  (lower left) rectangle (water level-|upper right);

% Draw the ground
\draw [draw=brown!30!black, fill=brown] 
  (lower left) -- (lower left|-ground1)  --
  (ground1) .. controls ($(ground1)!.3!(bottom)$) and (bottom-|ground1) ..
  (bottom) .. controls (bottom-|ground2) and ($(ground2)!.3!(bottom)$) .. 
  (ground2) -- (ground2-|upper right) -- (lower left-|upper right) -- cycle;

% \draw[dotted](0,0) rectangle (clipping area);

% labels
\draw[>=stealth, ->, line width = 0.7mm] (0, 5.5) -- (3, 5.5) node at (1.5, 4.8) {Inputs};
\draw[>=stealth, ->, line width = 0.2mm] (8, 5.5) -- (10, 5.5) node at (8.5, 4.8) {Outputs};

\end{tikzpicture}
}

\section{lakediagramblue}
\def\lakediagramblue[#1]{
\begin{tikzpicture}[scale = #1]
% https://tex.stackexchange.com/questions/95044/create-diagrams-in-latex-with-tikz

% Define some reference points 
% The figure is drawn a bit bigger, and then clipped to the following dimensions:
\coordinate (clipping area) at (10, 7);
\clip (0,0) rectangle (clipping area);

% Next reference points are relative to the lower left corner of the clipping area
\coordinate (water level) at (0, 6);
\coordinate (bottom)      at (5, 1.3);     % (bottom of the pit)
\coordinate (ground1)     at (0, 5);       % (left shore)
\coordinate (ground2)     at (10, 5);      % (right shore)

% Coordinates of the bigger area really drawn
\coordinate (lower left)  at ([xshift=-5mm, yshift=-5mm] 0,0);
\coordinate (upper right) at ([xshift=5mm,  yshift=5mm] clipping area);

% Draw the water and ripples
\draw [draw=blue!80!black, decoration={bumps, mirror, segment length=6mm}, decorate,
     bottom color=cyan!60!black, top color=blue!20!white] 
  (lower left) rectangle (water level-|upper right);

% Draw the ground
\draw [draw=brown!30!black, fill=brown] 
  (lower left) -- (lower left|-ground1)  --
  (ground1) .. controls ($(ground1)!.3!(bottom)$) and (bottom-|ground1) ..
  (bottom) .. controls (bottom-|ground2) and ($(ground2)!.3!(bottom)$) .. 
  (ground2) -- (ground2-|upper right) -- (lower left-|upper right) -- cycle;

% \draw[dotted](0,0) rectangle (clipping area);

% labels
\draw[>=stealth, ->, line width = 0.5mm] (0, 5.5) -- (3, 5.5) node at (1.5, 4.8) {Inputs};
\draw[>=stealth, ->, line width = 0.5mm] (8, 5.5) -- (10, 5.5) node at (8.5, 4.8) {Outputs};

\end{tikzpicture}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{isolated}
\def\isolated[#1]{
  \begin{tikzpicture}[scale = #1]
    \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan] plot (\x:1+rnd*0.5);
    \node at (0, 0) {Isolated};
  \end{tikzpicture}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{headwater}
\def\headwater[#1]{
  \begin{tikzpicture}[scale = #1]
    \draw [-,ultra thick, cyan] (0,0) to [out=90,in=0] (0.2,-2) to [out=180,in=90] (-1,-3);
    \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan] (0,3) plot (\x:1+rnd*0.5);
    \node at (0, 0) {Headwater};
  \end{tikzpicture}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{primary}
\def\primary[#1]{
  \begin{tikzpicture}[scale = #1]
    \draw [-,ultra thick, cyan] (-1,3) to [out=270,in=180] (0.2,2) to [out=0,in=90] (0,0);
    \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan] (0,-3) plot (\x:1+rnd*0.5);
    \node at (0, 0) {Primary};
  \end{tikzpicture}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{secondary}
\def\secondary[#1]{
  \begin{tikzpicture}[scale = #1]
    \draw [-,ultra thick, cyan] (-1,3) to [out=270,in=180] (0.2,2) to [out=0,in=90] (0,0.3) to [out=90,in=0] (0,-1) to [out=90,in=0] (0.2,-2) to [out=180,in=90] (-1,-3);
    \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan,yshift=20] plot (\x:0.5+rnd*0.25);
    \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan,yshift=-50] plot (\x:0.8+rnd*0.5);
    \node at (0,-1.7) {Secondary};
  \end{tikzpicture}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{connectivitydiagram}
\def\connectivitydiagram[#1]{
\begin{columns}

  \begin{column}{0.25\textwidth}
    \secondary[#1]
  \end{column}

  \begin{column}{0.25\textwidth}
    \primary[#1]
  \end{column}

  \begin{column}{0.25\textwidth}
    \headwater[#1]
  \end{column}

  \begin{column}{0.25\textwidth}
    \isolated[#1]
  \end{column}

\end{columns}

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{secondaryprofile}
\def\secondaryprofile[#1]#2{
\begin{tikzpicture}[scale = #1]
  \draw [-,line width = 5, #2!100!black] (0.9,0) to [out=0,in=180] (1.55,0);
  \draw [-,line width = 5, dashed, #2!100!black] (5.5,0) to [out=0,in=180] (6.2,0);
  % \node at (2, 1) {Secondary};
\fill[
  top color=#2!100,
  bottom color=#2!40,
  shading=axis,
  opacity=0.45
  ] 
  (0,0) circle (1cm and 0.25cm);
\fill[
  left color=#2!50!black,
  right color=#2!50!black,
  middle color=#2!100,
  shading=axis,
  opacity=0.25
  ] 
  (1,0) {[rounded corners=45pt] -- (0,-2)} -- (-1,0) arc (180:360:1cm and 0.25cm);

\fill[
  top color=#2!100,
  bottom color=#2!40,
  shading=axis,
  opacity=0.45,
  xshift=100
  ] 
  (0,0) circle (2cm and 0.5cm);
\fill[
  left color=#2!50!black,
  right color=#2!50!black,
  middle color=#2!100,
  shading=axis,
  opacity=0.25,
  xshift=100
  ] 
  (2,0) {[rounded corners=45pt] -- (0,-3)} -- (-2,0) arc (180:360:2cm and 0.5cm);
\end{tikzpicture}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{secondaryprofileflatequal}
\def\secondaryprofileflatequal[#1]#2{
\begin{tikzpicture}[scale = #1]
  \draw [fill=#2, ultra thick] (0.1,-.3) rectangle (1.7,0.1);
  \draw [fill=#2, ultra thick] (5.3,0.1) rectangle (6.2,-0.3);
  % \node at (2, 1) {Secondary};
\draw
  [fill=#2,
  ultra thick,
  xshift=-50
  ] 
  (0,0) circle (2cm and 0.5cm);
\draw
  [fill=#2,
  ultra thick,
  xshift=-50
  ] 
  (2,0) {[rounded corners=45pt] -- (0,-3)} -- (-2,0) arc (180:360:2cm and 0.5cm);

\draw
  [fill = #2,
  ultra thick,
  xshift=100
  ] 
  (0,0) circle (2cm and 0.5cm);
\draw
  [fill = #2,
  ultra thick,
  xshift=100
  ] 
  (2,0) {[rounded corners=45pt] -- (0,-3)} -- (-2,0) arc (180:360:2cm and 0.5cm);
\end{tikzpicture}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{primaryprofileflatequal}
\def\primaryprofileflatequal[#1]#2{
\begin{tikzpicture}[scale = #1]
  \draw [fill=#2, ultra thick] (1.8,-.3) rectangle (3.2,0.1);
  \draw [fill=#2, ultra thick] (-1.8,0.1) rectangle (-3.2,-0.3);
  % \node at (2, 1) {Secondary};
\draw
  [fill=#2,
  ultra thick
  ] 
  (0,0) circle (2cm and 0.5cm);
\clip (-2,-3) rectangle (2,0);
\draw
  [fill=#2,
  ultra thick
  ] 
  (2,0) {[rounded corners=45pt] -- (0,-3)} -- (-2,0) arc (180:360:2cm and 0.5cm);

\end{tikzpicture}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{headwaterprofileflatequal}
\def\headwaterprofileflatequal[#1]#2{
\begin{tikzpicture}[scale = #1]
  \draw [fill=#2, ultra thick] (1.8,-.3) rectangle (3.2,0.1);
  % \node at (2, 1) {Secondary};
\draw
  [fill=#2,
  ultra thick
  ] 
  (0,0) circle (2cm and 0.5cm);
\clip (-2,-3) rectangle (2,0);
\draw
  [fill=#2,
  ultra thick
  ] 
  (2,0) {[rounded corners=45pt] -- (0,-3)} -- (-2,0) arc (180:360:2cm and 0.5cm);

\end{tikzpicture}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{isolatedprofileflatequal}
\def\isolatedprofileflatequal[#1]#2{
\begin{tikzpicture}[scale = #1]
\draw
  [fill=#2,
  ultra thick
  ] 
  (0,0) circle (2cm and 0.5cm);
\clip (-2,-3) rectangle (2,0);
\draw
  [fill=#2,
  ultra thick
  ] 
  (2,0) {[rounded corners=45pt] -- (0,-3)} -- (-2,0) arc (180:360:2cm and 0.5cm);

\end{tikzpicture}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{headwaterprofile}
\def\headwaterprofile[#1]#2{
\begin{tikzpicture}[scale = #1]
  \draw [-,line width = 5, #2!100!black] (1.95,0) to [out=0,in=180] (2.7,0);
  % \node at (0.4, 1) {Headwater};
\fill[
  top color=#2!100,
  bottom color=#2!40,
  shading=axis,
  opacity=0.45
  ] 
  (0,0) circle (2cm and 0.5cm);
\fill[
  left color=#2!50!black,
  right color=#2!50!black,
  middle color=#2!100,
  shading=axis,
  opacity=0.25
  ] 
  (2,0) {[rounded corners=45pt] -- (0,-3)} -- (-2,0) arc (180:360:2cm and 0.5cm);
\end{tikzpicture}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{primaryprofile}
\def\primaryprofile[#1]#2{
\begin{tikzpicture}[scale = #1]
  \draw [-,line width = 5, #2!100!black] (-2,0) to [out=0,in=180] (-2.7,0);
  \draw [-,line width = 5, dashed, #2!100!black] (2,0) to [out=0,in=180] (2.7,0);
  % \node at (0.4, 1) {Primary};
\fill[
  top color=#2!100,
  bottom color=#2!40,
  shading=axis,
  opacity=0.45
  ] 
  (0,0) circle (2cm and 0.5cm);
\fill[
  left color=#2!50!black,
  right color=#2!50!black,
  middle color=#2!100,
  shading=axis,
  opacity=0.25
  ] 
  (2,0) {[rounded corners=45pt] -- (0,-3)} -- (-2,0) arc (180:360:2cm and 0.5cm);
\end{tikzpicture}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{isolatedprofile}
\def\isolatedprofile[#1]#2{
\begin{tikzpicture}[scale = #1]
\fill[
  top color=#2!100,
  bottom color=#2!40,
  shading=axis,
  opacity=0.45
  ] 
  (0,0) circle (2cm and 0.5cm);
\fill[
  left color=#2!50!black,
  right color=#2!50!black,
  middle color=#2!100,
  shading=axis,
  opacity=0.25
  ] 
  (2,0) {[rounded corners=45pt] -- (0,-3)} -- (-2,0) arc (180:360:2cm and 0.5cm);
\end{tikzpicture}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{primaryprofileplus}
\def\primaryprofileplus{
\begin{tikzpicture}[scale = 0.8]
  \draw [-,line width=3pt, cyan!40] (-2,0) to [out=0,in=180] (-3.25,0);
  \draw [-,thick, dashed, darkgreen!40] (2,0) to [out=0,in=180] (3.25,0);
  \node at (0.2, 1) {Primary};
\fill[
  top color=darkgreen!100,
  bottom color=darkgreen!40,
  shading=axis,
  opacity=0.45
  ] 
  (0,0) circle (2cm and 0.5cm);
\fill[
  left color=darkgreen!50!black,
  right color=darkgreen!50!black,
  middle color=darkgreen!100,
  shading=axis,
  opacity=0.25
  ] 
  (2,0) {[rounded corners=45pt] -- (0,-3)} -- (-2,0) arc (180:360:2cm and 0.5cm);
\end{tikzpicture}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{secondaryprofileplus}
\def\secondaryprofileplus{
\begin{tikzpicture}[scale = 0.8]
  \draw [-,line width=3pt, cyan!40] (-1,0) to [out=0,in=180] (-2.25,0);
  \draw [-,line width=3pt, cyan!40] (1,0) to [out=0,in=180] (2.25,0);
  \draw [-,line width=3pt, dashed, cyan!40] (6,0) to [out=0,in=180] (7.25,0);
  \node at (2, 1) {Secondary};
\fill[
  top color=cyan!100,
  bottom color=cyan!40,
  shading=axis,
  opacity=0.45
  ] 
  (0,0) circle (1cm and 0.25cm);
\fill[
  left color=cyan!50!black,
  right color=cyan!50!black,
  middle color=cyan!100,
  shading=axis,
  opacity=0.25
  ] 
  (1,0) {[rounded corners=45pt] -- (0,-2)} -- (-1,0) arc (180:360:1cm and 0.25cm);

\fill[
  top color=cyan!100,
  bottom color=cyan!40,
  shading=axis,
  opacity=0.45,
  xshift=120
  ] 
  (0,0) circle (2cm and 0.5cm);
\fill[
  left color=cyan!50!black,
  right color=cyan!50!black,
  middle color=cyan!100,
  shading=axis,
  opacity=0.25,
  xshift=120
  ] 
  (2,0) {[rounded corners=45pt] -- (0,-3)} -- (-2,0) arc (180:360:2cm and 0.5cm);
\end{tikzpicture}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{primaryprofileblue}
\def\primaryprofileblue{
\begin{tikzpicture}[scale = 0.8]
  \draw [-,line width=5pt, cyan!40] (-2,0) to [out=0,in=180] (-3.25,0);
  \draw [-,line width=5pt, dashed, cyan!40] (2,0) to [out=0,in=180] (3.25,0);
  \node at (0.2, 1) {Low retention};
\fill[
  top color=cyan!100,
  bottom color=cyan!40,
  shading=axis,
  opacity=0.45
  ] 
  (0,0) circle (2cm and 0.5cm);
\fill[
  left color=cyan!50!black,
  right color=cyan!50!black,
  middle color=cyan!100,
  shading=axis,
  opacity=0.25
  ] 
  (2,0) {[rounded corners=45pt] -- (0,-3)} -- (-2,0) arc (180:360:2cm and 0.5cm);
\end{tikzpicture}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{primaryprofilegreen}
\def\primaryprofilegreen{
\begin{tikzpicture}[scale = 0.8]
  \draw [-,line width=5pt, cyan!40] (-2,0) to [out=0,in=180] (-3.25,0);
  \draw [-,thick, dashed, darkgreen!40] (2,0) to [out=0,in=180] (3.25,0);
  \node at (0.2, 1) {High retention};
\fill[
  top color=darkgreen!100,
  bottom color=darkgreen!40,
  shading=axis,
  opacity=0.45
  ] 
  (0,0) circle (2cm and 0.5cm);
\fill[
  left color=darkgreen!50!black,
  right color=darkgreen!50!black,
  middle color=darkgreen!100,
  shading=axis,
  opacity=0.25
  ] 
  (2,0) {[rounded corners=45pt] -- (0,-3)} -- (-2,0) arc (180:360:2cm and 0.5cm);
\end{tikzpicture}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{isolatedflux}
\def\isolatedflux[#1]#2{
\begin{tikzpicture}[scale = #1]
  \node at (1.5, 1) {#2};

\pgfsetarrowsend{latex}
\pgfsetlinewidth{1ex}

\node at (3, 5) {Evaporation};
\pgfpathmoveto{\pgfpoint{0cm}{1cm}}
\pgfpathlineto{\pgfpoint{0cm}{4cm}}
\pgfusepath{stroke}

\node at (-3, 5) {Precipitation};
\pgfpathmoveto{\pgfpoint{-1cm}{4cm}}
\pgfpathlineto{\pgfpoint{-1cm}{1cm}}
\pgfusepath{stroke}

\fill[
  top color=cyan!100,
  bottom color=cyan!40,
  shading=axis,
  opacity=0.45
  ] 
  (0,0) circle (2cm and 0.5cm);
\fill[
  left color=cyan!50!black,
  right color=cyan!50!black,
  middle color=cyan!100,
  shading=axis,
  opacity=0.25
  ] 
  (2,0) {[rounded corners=45pt] -- (0,-3)} -- (-2,0) arc (180:360:2cm and 0.5cm);
\end{tikzpicture}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{isolatedwireframe}
\def\isolatedwireframe[#1]{
\begin{tikzpicture}[scale = #1]

  % \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);

  \draw (0,0) circle (2cm and 0.5cm);
  \draw (2,0) {[rounded corners=45pt] -- (0,-3)} -- (-2,0) arc (180:360:2cm and 0.5cm);

  \pgfsetarrowsend{latex}
  \pgfsetlinewidth{1ex}

  \node[rotate=-90] at (0.6, 2){Evaporation};
  \node[rotate=-90] at (-0.6, 2){Precipitation};
  \node at (1.5, -2.1){Groundwater};
  \node at (-1.5, -2.1){Groundwater};

  % GW out
  \pgfpathmoveto{\pgfpoint{1cm}{-1.5cm}}
  \pgfpathlineto{\pgfpoint{2cm}{-2cm}}
  \pgfusepath{stroke}

  % GW in
  \pgfpathmoveto{\pgfpoint{-2cm}{-2cm}}
  \pgfpathlineto{\pgfpoint{-1cm}{-1.5cm}}
  \pgfusepath{stroke}

  % SW out
  % \node at (3, -0.5){Outflow};
  % \pgfpathmoveto{\pgfpoint{2.2cm}{0cm}}
  % \pgfpathlineto{\pgfpoint{4cm}{0cm}}
  % \pgfusepath{stroke}

  % SW in
  % \node at (-3, -0.5){Inflow};
  % \pgfpathmoveto{\pgfpoint{-4cm}{0cm}}
  % \pgfpathlineto{\pgfpoint{-2.2cm}{0cm}}
  % \pgfusepath{stroke}

  % Runoff in
  \node at (-3, 0.4){Runoff};
  \pgfpathmoveto{\pgfpoint{-3cm}{0cm}}
  \pgfpathlineto{\pgfpoint{-2.2cm}{0cm}}
  \pgfusepath{stroke}

  \pgfpathmoveto{\pgfpoint{0.26cm}{1cm}}
  \pgfpathlineto{\pgfpoint{0.26cm}{3cm}}
  \pgfusepath{stroke}

  \pgfpathmoveto{\pgfpoint{-0.3cm}{3cm}}
  \pgfpathlineto{\pgfpoint{-0.3cm}{1cm}}
  \pgfusepath{stroke}

\end{tikzpicture}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{secondarywireframe}
\def\secondarywireframe[#1]{
\begin{tikzpicture}[scale = #1]

  \draw[step=1cm,gray,very thin] (-7,-3) grid (7,4);

  \draw [-,line width=3pt] (0,0) to [out=0,in=180] (1.25,0);
  \draw (-1,0) circle (1cm and 0.25cm);
  \draw (0,0) {[rounded corners=45pt] -- (-1,-2)} -- (-2,0) arc (180:360:1cm and 0.25cm);
  \draw[xshift=120] (-1,0) circle (2cm and 0.5cm);
  \draw[xshift=120] (1,0) {[rounded corners=45pt] -- (-1,-3)} -- (-3,0) arc (180:360:2cm and 0.5cm);

  \pgfsetarrowsend{latex}
  \pgfsetlinewidth{1ex}

  % GW out
  \node at (4.9, -2.1){Groundwater};
  \pgfpathmoveto{\pgfpoint{4.2cm}{-1.5cm}}
  \pgfpathlineto{\pgfpoint{5.2cm}{-2cm}}
  \pgfusepath{stroke}

  % GW in
  \node at (1.5, -2.1){Groundwater};
  \pgfpathmoveto{\pgfpoint{1.2cm}{-2cm}}
  \pgfpathlineto{\pgfpoint{2.2cm}{-1.5cm}}
  \pgfusepath{stroke}

  % SW out
  \node at (5.6, -0.5){Outflow};
  \pgfpathmoveto{\pgfpoint{5.2cm}{0cm}}
  \pgfpathlineto{\pgfpoint{7cm}{0cm}}
  \pgfusepath{stroke}

  % SW in
  \node at (-2.3, -0.5){Inflow};
  \pgfpathmoveto{\pgfpoint{-3.4cm}{0cm}}
  \pgfpathlineto{\pgfpoint{-2cm}{0cm}}
  \pgfusepath{stroke}

  % Runoff in
  \node at (-2.3, 1){Runoff};
  \pgfpathmoveto{\pgfpoint{-2.8cm}{0.6cm}}
  \pgfpathlineto{\pgfpoint{-2cm}{0.6cm}}
  \pgfusepath{stroke}

  % Evaporation
  \node[rotate=-90] at (3.7, 2){Evaporation};
  \pgfpathmoveto{\pgfpoint{3.36cm}{1cm}}
  \pgfpathlineto{\pgfpoint{3.36cm}{3cm}}
  \pgfusepath{stroke}

  % Precip
  \node[rotate=-90] at (2.4, 2){Precipitation};
  \pgfpathmoveto{\pgfpoint{2.8cm}{3cm}}
  \pgfpathlineto{\pgfpoint{2.8cm}{1cm}}
  \pgfusepath{stroke}

\end{tikzpicture}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{watershedconnectivity}
% See Soranno et al., 2015, Plos One
\def\watershedconnectivity[#1]{
\begin{columns}

  \begin{column}{0.7\textwidth}
    \begin{tikzpicture}[scale = #1]
      %\draw[step=1cm,gray,very thin] (-4,-2) grid (4,9);

      % streamlines
      % lake 3
        % center
      \draw [-,ultra thick, cyan] (-0.6, 3.2) to [out=270,in=180] (0.2,2) to [out=0,in=90] (0,0);
      \draw [-,ultra thick, cyan] (0.2, 3.2) to [out=270,in=90] (-0.1,2.2) to [out=0,in=180] (0.2,2) to [out=0,in=90] (0,0);
        % right
      \draw [-,ultra thick, cyan] (2.2,3.5) to [out=90,in=0] (1.1,1.1) to [out=270,in=90] (0,0);
        % left
      \draw [-,ultra thick, cyan] (-1.9, 2) to [out=270,in=90] (-1.1,1.1) to [out=270,in=90] (0,0);

      % lake 2
      \draw [-,ultra thick, darkgreen] % 
        (-0.3,6.5) to % 
        [out=270,in=90] (0.5, 4.9) to % 
        [out=270,in=90] (0,4);

      % lake 1
      \draw [-,ultra thick, yellow] % 
        (0.3, 7.8) to % 
        [out=90,in=270] (1.2, 8.2);

      \draw [-,ultra thick, yellow] % 
        (0.3, 8) to % 
        [out=90,in=270] (0, 8.5) to % 
        [out=90,in=270] (0.5, 9);

      \draw [-,ultra thick, yellow] % 
        (-0.4, 7.5) to % 
        [out=90,in=270] (-0.6, 8.5) to % 
        [out=90,in=270] (-1.5, 9);

      \draw [-,ultra thick, yellow] % 
        (-0.4, 7.3) to % 
        [out=90,in=270] (-1.5, 8);

      % lakes
      \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan] (0,-3) plot (\x:1.1+rnd*0.5);
      \node at (0, 0) {3};

      \draw[darkgreen, ultra thick, domain=0:350, smooth cycle, fill=darkgreen, yshift=4cm] (0,-3) plot (\x:0.5+rnd*0.5);
      \node at (0, 4) {2};

      \draw[yellow, ultra thick, domain=0:350, smooth cycle, yshift=7cm, fill=yellow] (0,-3) plot (\x:1.1+rnd*0.5);
      \node at (0, 7) {1};

      % iws
      \draw[yellow,ultra thick,dashed] % 
      (-0.2, 5.6) to %
      (-1.1, 6.2) to %
      (-3.05, 7.5) to %
      (-1.9, 9) to %
      (1.9, 9) to %
      (3.05, 7.5) to %
      (1.1, 6.2) to %
      (0.2, 5.6);

      \draw[darkgreen,ultra thick,dashed] % 
      (-0.8, 3.4) to % 
      (-1.5, 4.2) to %
      (-3, 7.5) to %
      (-1.1, 6.2) to %
      (-0.5, 5.6) to (0.5, 5.6) to%      
      (1.1, 6.2) to % 
      (3, 7.5) to %
      (1.5, 4.2) to % 
      (0.8, 3.4);

      \draw[cyan,ultra thick,dashed] % 
      (-1.1,-0.4) to % 
      (-1.5, 0.2) to %
      (-3, 7.5) to %
      (-1.1, 6.2) to %
      (-0.5, 5.6) to (0.5, 5.6) to % 
      (1.1, 6.2) to % 
      (3, 7.5) to %
      (1.5, 0.2) to (1.1, -0.4);

      \draw [cyan, thick, decorate, decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt, align=center, anchor=center]
      (3,-1.2) -- (3,7.2) node [cyan,midway,xshift=1.3cm] {\footnotesize
      Lake \\ \footnotesize Watershed\\ \footnotesize 3};

      \draw [cyan, thick, decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt, align=center, anchor=center]
      (5.4,-1.2) -- (5.4,9) node [cyan,midway,xshift=1.3cm] {\footnotesize
      Lake \\ \footnotesize Network \\ \footnotesize Watershed\\ \footnotesize 3};

      \draw [darkgreen, thick, decorate, decoration={brace,amplitude=10pt,raise=4pt},yshift=0pt]
      (-3.1,3) -- (-3.1,7.2) node [darkgreen,midway,xshift=-1.3cm, align=center] {\footnotesize
      Lake \\ \footnotesize Watershed\\ \footnotesize 2};

      \draw [darkgreen, thick, decorate, decoration={brace,amplitude=10pt,raise=4pt},yshift=0pt, align=center, anchor=center]
      (-5.5,3) -- (-5.5,9) node [darkgreen,midway,xshift=-1.3cm, align=center] {\footnotesize
      Lake \\ \footnotesize
      Network \\ \footnotesize Watershed\\ \footnotesize 2};

    \end{tikzpicture}
  \end{column}  
\end{columns}

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-10-17 manuscript/appendix.Rmd
cleanup appendix, placeholder for milstead text

@@
 
-```{r recursive_partitioning_viz, echo=FALSE, eval=FALSE}
-plot_tree(gettree(readRDS("../data/maxdepth_forest.rds")), 
-          title = "Max Depth")
-
-plot_tree(gettree(readRDS("../data/iws/cd_forest.rds")), 
-          title = "Distance to Closest \n Upstream Lake (standardized)")
-# inv_inv_closest(-1.51, nes_rf_iws) # 3773.614
-plot_tree(gettree(readRDS("../data/nws/cd_forest.rds")), 
-          title = "Distance to Closest \n Upstream Lake (standardized)")
-# inv_inv_closest(-1.469, nes_rf_nws) # 2681.288
-
-plot_tree(gettree(readRDS("../data/iws/sr_forest.rds")), 
-          title = "Stream Order Ratio")
-plot_tree(gettree(readRDS("../data/nws/sr_forest.rds")), 
-          title = "Stream Order Ratio")
-
-plot_tree(gettree(readRDS("../data/iws/linklength_forest.rds")), 
-          title = "Link Length")
-plot_tree(gettree(readRDS("../data/nws/linklength_forest.rds")), 
-          title = "Link Length")
-
-plot_tree(gettree(readRDS("../data/iws/uplakearea_forest.rds")), 
-          title = "Upstream Lake Area")
-# plot_tree(gettree(readRDS("01_Chapter/data/nws/uplakearea_forest.rds")), 
-#           title = "Upstream Lake Area")
-
-plot_tree(gettree(readRDS("../data/iws/baseflow_forest.rds")), 
-          title = "Baseflow")
-
-plot_tree(gettree(readRDS("../data/iws/wetland-cover_forest.rds")), 
-          title = "Wetland Cover")
-
-plot_tree(gettree(readRDS("../data/iws/streamdensity_forest.rds")), 
-          title = "Stream Density")
-```
-
-```{r graphical_exploratory_analysis, echo=FALSE, message=FALSE, warning=FALSE, fig.height=8.4, fig.cap="Exploratory plots", eval=FALSE}
-partition_splits <- read.csv("../figures/table_1.csv", stringsAsFactors = FALSE)
-
-nes_iws$p_pnt_source <-  rowSums(cbind(nes_iws$p_pnt_source_muni,
-                                       nes_iws$p_pnt_source_septic,
-                                       nes_iws$p_pnt_source_industrial),
-                                 na.rm = TRUE)
-
-md_v_la <- ggplot(data = nes_iws) + 
-  geom_point(aes(x = maxdepth, 
-                 y = upstream_lakes_4ha_area_ha, color = lakeconnection)) +
-  ylab("Upstream Lake Area (ha)") + xlab("Max Depth (m)") + 
-  geom_vline(data = partition_splits, aes(
-    xintercept = partition_splits$splits[
-      partition_splits$pnames2 == "md" & partition_splits$scale == "focal"])) + 
-  geom_hline(data = partition_splits, aes(
-    yintercept = partition_splits$splits[
-      partition_splits$pnames2 == "la" & partition_splits$scale == "nws"])) + 
-  scale_y_log10()
-
-md_v_ll_iws <- ggplot(data = nes_iws) + 
-  geom_point(aes(x = maxdepth, 
-                 y = link_length, color = lakeconnection)) +
-  ylab("Link Length") + xlab("Max Depth (m)") + 
-  geom_vline(data = partition_splits, aes(
-    xintercept = partition_splits$splits[
-      partition_splits$pnames2 == "md"])) + 
-  geom_hline(data = partition_splits, aes(
-    yintercept = partition_splits$splits[
-      partition_splits$pnames2 == "ll" & partition_splits$scale == "iws"]))
-
-md_v_ll_nws <- ggplot(data = nes_nws) + 
-  geom_point(aes(x = maxdepth, 
-                 y = avg_link_length, color = lakeconnection)) +
-  ylab("Link Length") + xlab("Max Depth (m)") + 
-  geom_vline(data = partition_splits, aes(
-    xintercept = partition_splits$splits[
-      partition_splits$pnames2 == "md"])) + 
-  geom_hline(data = partition_splits, aes(
-    yintercept = partition_splits$splits[
-      partition_splits$pnames2 == "ll" & partition_splits$scale == "nws"]))
-
-md_v_cd_nws <- ggplot(data = nes_nws) + 
-  geom_point(aes(x = maxdepth, 
-                 y = closest_lake_distance, color = lakeconnection)) +
-  ylab("Closest Lake Distance") + xlab("Max Depth (m)") + 
-  geom_vline(data = partition_splits, aes(
-    xintercept = partition_splits$splits[
-      partition_splits$pnames2 == "md"])) + 
-  geom_hline(data = partition_splits, aes(
-    yintercept = partition_splits$splits[
-      partition_splits$pnames2 == "cd" & partition_splits$scale == "nws"]))
-
-ll_v_cd_nws <- ggplot(data = nes_nws) + 
-  geom_point(aes(x = avg_link_length, 
-                 y = closest_lake_distance, color = lakeconnection)) +
-  ylab("Closest Lake Distance") + xlab("Link Length") + 
-  geom_vline(data = partition_splits, aes(
-    xintercept = partition_splits$splits[
-      partition_splits$pnames2 == "ll" & partition_splits$scale == "nws"])) + 
-  geom_hline(data = partition_splits, aes(
-    yintercept = partition_splits$splits[
-      partition_splits$pnames2 == "cd" & partition_splits$scale == "nws"])) + 
-  scale_x_log10() + scale_y_log10() + xlab("log(Link Length)") + ylab("log(cd)")
-
-legend <- get_legend(md_v_la)
-
-plot_grid(md_v_la + theme(legend.position = "none"), 
-          md_v_ll_iws + theme(legend.position = "none"), 
-          md_v_ll_nws + theme(legend.position = "none"),
-          ll_v_cd_nws + theme(legend.position = "none"),
-          ggplot() + geom_point(aes(nes_iws$hu12_baseflowindex_mean, nes_nws$baseflow, color = nes_iws$state %in% c("MAINE", "NEW HAMPSHIRE", "IOWA", "MISSOURI", "OHIO", "ILLINOIS"))) + 
-            geom_hline(aes(yintercept = 53.43)) +
-            geom_vline(aes(xintercept = 63.76)) + 
-            ylab("NWS Baseflow") + xlab("IWS Baseflow") + 
-            theme(legend.position = "none"),
-          ggplot() + geom_point(aes(
-            nes_iws$iws_streamdensity_streams_density_mperha, 
-            nes_nws$stream_density, color = nes_iws$lakeconnection)) + 
-            geom_hline(aes(yintercept = 10.4), color = "red") +
-            geom_vline(aes(xintercept = 4.43), color = "red") +
-            geom_abline(aes(slope = 1, intercept = 0)) + 
-            ylab("NWS Stream Density") + xlab("IWS Stream Density") + 
-            theme(legend.position = "none"),
-
-          ggplot() + geom_point(aes(nes_iws$closest_lake_distance, 
-                                    nes_nws$closest_lake_distance, 
-                                    color = nes_iws$lakeconnection)) + 
-            geom_hline(aes(yintercept = 2776.81), color = "red") +
-            geom_vline(aes(xintercept = 3773.61), color = "red") +
-            geom_abline(aes(slope = 1, intercept = 0)) +
-            scale_x_log10() + 
-            scale_y_log10() + 
-            ylab("NWS Lake Distance") + xlab("IWS Lake Distance") + 
-            theme(legend.position = "none"),
-          ggplot(data = nes_iws) + 
-            geom_point(aes(x = p_pnt_source / (p_nonpnt_source + p_pnt_source), 
-                           y = p_percent_retention)) + 
-            xlab("p_percent_pnt-source"), 
-          ncol = 2)
-```
-
-```{r graphical_exploratory_analysis_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=6.3, fig.cap="Exploratory plots cont", eval=FALSE}
-lg <- lagosne_load("1.087.1")
-nes_nws_temp <- dplyr::left_join(nes_nws, select(lg$iws, lagoslakeid, iws_ha))
-nes_nws_temp$p_pnt_source <-  rowSums(cbind(nes_nws_temp$p_pnt_source_muni,
-                                       nes_nws_temp$p_pnt_source_septic,
-                                       nes_nws_temp$p_pnt_source_industrial),
-                                 na.rm = TRUE)
-nes_nws_sf    <- coordinatize(nes_nws_temp, "lat", "long")
-us_states <- st_intersects(us_states(), nes_nws_sf)
-us_states <- us_states()[unlist(lapply(us_states, function(x) length(x) > 0)),]
-
-plot_grid(
-ggplot() + geom_point(data = nes_nws_temp, 
-                      aes(x = iws_ha, y = avg_link_length)) + 
-  xlim(300, 100000) + ylab("Average Link Length") + 
-  xlab("Interlake Watershed Area (ha)") + 
-  geom_hline(aes(yintercept = 2380.09), color = "red"),
-
-ggplot() + geom_point(data = nes_nws_temp, 
-                      aes(x = iws_ha, y = closest_lake_distance)) + 
-  xlim(300, 100000) + ylab("Closest Lake Distance") + 
-  xlab("Interlake Watershed Area (ha)") + 
-  geom_hline(aes(yintercept = 3273.65), color = "red"),
-
-ggplot() + geom_point(data = nes_nws_temp, 
-                      aes(x = iws_ha, y = p_percent_retention)) + 
-  xlim(300, 100000) + ylab("P Retention") + 
-  xlab("Interlake Watershed Area (ha)"),
-
-ggplot() + geom_sf(data = us_states) + 
-  geom_sf(data = nes_nws_sf, aes(color = p_pnt_source / (p_nonpnt_source + p_pnt_source))) + theme(legend.direction = "horizontal", legend.position = "bottom") + ggtitle("% pnt source P"),
-
-ggplot() + geom_sf(data = us_states) + 
-  geom_sf(data = nes_nws_sf, aes(color = log(maxdepth))) + theme(legend.direction = "horizontal", legend.position = "bottom") + ggtitle("max depth"), 
-ggplot() + geom_sf(data = us_states) + 
-  geom_sf(data = nes_nws_sf, aes(color = log(iws_ha))) + theme(legend.direction = "horizontal", legend.position = "bottom") + ggtitle("iws area"), 
-ncol = 2)
-```
-
-```{r graphical_exploratory_analysis_cont_cont, echo=FALSE, message=FALSE, warning=FALSE, fig.height=5.3, fig.cap="Exploratory plots cont x 2", eval=FALSE}
-lg <- lagosne_load("1.087.1")
-
-nes_nws_temp <- nes_nws
-nes_nws_temp$p_pnt_source <-  rowSums(cbind(nes_nws_temp$p_pnt_source_muni,
-                                            nes_nws_temp$p_pnt_source_septic,
-                                            nes_nws_temp$p_pnt_source_industrial),
-                                      na.rm = TRUE)
-nes_nws_sf    <- coordinatize(nes_nws_temp, "lat", "long")
-us_states <- st_intersects(us_states(), nes_nws_sf)
-us_states <- us_states()[unlist(lapply(us_states, function(x) length(x) > 0)),]
-
-plot_grid(
-  ggplot() + geom_point(data = nes_nws_temp, 
-                        aes(x = nws_ha, y = upstream_lakes_4ha_area_ha)) + 
-    xlim(300, 100000) + ylab("Up. Lk. Area") + 
-    xlab("Network Watershed Area (ha)"),
-  ggplot() + geom_point(data = nes_nws_temp, 
-                        aes(x = nws_ha, y = stream_order_ratio)) + 
-    xlim(300, 100000) + ylab("Stream Order Ratio") + 
-    xlab("Network Watershed Area (ha)"),
-
-  ggplot() + geom_point(data = nes_nws_temp, 
-                        aes(x = nws_ha, y = p_percent_retention)) + 
-    xlim(300, 100000) + ylab("P Retention") + 
-    xlab("Network Watershed Area (ha)"),
-
-  ggplot() + geom_point(data = nes_nws_temp, 
-                        aes(x = nws_ha, 
-                            y = p_pnt_source / (p_nonpnt_source + p_pnt_source))) + 
-    xlim(300, 100000) + ylab("% Pnt Source") + 
-    xlab("Network Watershed Area (ha)"), 
-  ncol = 2)
-```
-
-```{r stream_density-vs-link_length, eval=FALSE}
-test <- dplyr::select(nes_nws, 
-              avg_link_length, 
-              stream_density, 
-              closest_lake_distance) %>%
-dplyr::rename("Average Link Length" = avg_link_length,
-              "Stream Density" = stream_density,
-              "Closest Lake Distance" = closest_lake_distance) %>%
-dplyr::mutate(`Closest Lake Distance` = `Closest Lake Distance` / 100, 
-              `Average Link Length` = `Average Link Length` / 100)
-
-pair_opts <- theme(axis.text = element_blank(), 
-      axis.ticks = element_blank())
-
-cowplot::plot_grid(
-  ggplot(data = test) + 
-    geom_point(aes(y = `Average Link Length`, x = `Stream Density`)) + 
-    pair_opts,
-  ggplot(data = test) + 
-    geom_point(aes(y = `Average Link Length`, x = `Closest Lake Distance`)) + 
-    ylab("") + pair_opts, 
-  ggplot(data = test) + 
-    geom_point(aes(y = `Closest Lake Distance`, x = `Stream Density`)) +
-    pair_opts,
-  ggplot() + geom_blank(),
-  nrow = 2, ncol = 2)
-```
-
-```{r conceptual_summary, echo=FALSE, fig.cap="Connectivity metric effects on lake processing.", eval=FALSE}
-dt <- data.frame(
-  rbind(
-    c("closest lake distance", "lower", "higher", "lower", "higher", "lake-stream", "long"), 
-    c("average link length", "lower", "higher", "lower", "higher", "stream", "long"), 
-    c("lakeconnection", "DR_Stream", "higher", "lower", "higher", "lake", "long"), 
-    c("upstream lake area", "lower", "higher", "lower", "higher", "lake", "lat"), 
-    c("stream density", "higher", "higher", "lower", "higher", "stream", "lat"),
-    c("baseflow", "higher", "higher", "lower", "higher", "stream", "lat"), 
-    c("stream order ratio", "higher", "higher", "lower", "higher", "stream", "long")))
-
-names(dt) <- c("metric", "direction", "k", "connectivity", "in_lake_processing", "axis", "connectivity type")
-
-knitr::kable(dt)
-```
-
 ```{r read_metric_chunks, cache=FALSE, echo=FALSE}
@@
 
-```{r load_packages, echo=FALSE}
+```{r load_packages, echo=FALSE, warning=FALSE, message=FALSE}
 
@@
 
-```{r iws_vs_nws-gis, cache=TRUE, echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}
-# lagoslakeid <- 6302
-# iws <- pull_iws(lagoslakeid, maxsteps = Inf)
-# nws <- pull_nws(lagoslakeid, maxsteps = Inf)
-# nws_lakes <- pull_lakes(nws)
-# saveRDS(iws, "../data/iws_extent.rds")
-# saveRDS(nws, "../data/nws_extent.rds")
-# saveRDS(nws_lakes, "../data/nws_lakes.rds")
-
-iws <- readRDS("../data/iws_extent.rds")
-nws <- readRDS("../data/nws_extent.rds")
-nws_lakes <- readRDS("../data/nws_lakes.rds")
-
-nws_lakes <- nws_lakes[order(st_area(nws_lakes), decreasing = TRUE),]
-nws_lakes <- nws_lakes[1:2,]
-
-iws_outline <- concaveman(st_cast(iws, "POINT"))
-nws_outline <- concaveman(st_cast(nws, "POINT"))
-lake_1_outline <- concaveman(st_cast(nws_lakes[1,], "POINT"))
-lake_2_outline <- concaveman(st_cast(nws_lakes[2,], "POINT"))
-
-ggplot() + 
-  geom_sf(data = nws_outline, color = "yellow", size = 2) + 
-  geom_sf(data = iws_outline, color = "cyan", size = 2) + 
-  geom_sf(data = nws) +
-  geom_sf(data = lake_1_outline, color = "cyan") +
-  geom_sf(data = lake_2_outline, color = "yellow") +
-  coord_sf(crs = st_crs(nws), datum = NA) + 
-  # geom_sf(data = iws) + 
-  theme_void()
-
-```
-
-```{r best_partition_maps, cache=TRUE, echo=FALSE, message=FALSE, warning=FALSE, eval=FALSE}
-library(tmap)
-library(sf)
-library(LAGOSNE)
-library(USAboundaries)
-library(dplyr)
-
-results_table <- read.csv("../scripts/table_1.csv", stringsAsFactors = FALSE)
-ll_split <- dplyr::filter(results_table, 
-                          nws_names == "avg_link_length" & 
-                          scale == "nws")$splits
-
-nes_nws <- mutate(nes_nws, grp = ifelse(avg_link_length > ll_split, 
-                                  "High", "Low"))
-
-nes_sf    <- coordinatize(nes_nws, "lat", "long")
-us_states <- st_intersects(us_states(), nes_sf)
-us_states <- us_states()[unlist(lapply(us_states, function(x) length(x) > 0)),]
-
-us <- USAboundaries::us_boundaries()
-us <- us[unlist(lapply(st_intersects(us, nes_sf), function(x) length(x) > 0)),]
-us <- filter(us, stusps != "AR")
-
-nes_extent <- group_by(us, jurisdiction_type)
-nes_extent <- st_union(nes_extent)
-nes_extent <- as_Spatial(nes_extent)
-
-palette <- c("black",
-              "black")
-
-m_nes <-  tm_shape(us) + tm_polygons() +
-          tm_shape(nes_extent) + tm_borders(lwd = 3) +
-          tm_shape(dplyr::filter(nes_sf, !is.na(grp))) + tm_dots("grp", palette = palette,
-                                 size = 0.2, legend.show = FALSE, 
-                                 title = "Average Link Length") +
-          # tm_credits("National Eutrophication Survey") +
-          tm_layout(frame = FALSE,
-                    legend.outside = FALSE,
-                    legend.stack = "horizontal")
-
-save_tmap(m_nes, "../figures/best_partition_maps-1.png",
-          scale = 0.7, width = 3.125)
-
-# # # # #
-
-palette <- c(viridis::viridis(1, begin = 0),
-             viridis::viridis(1, begin = 0.5))
-
-m_nes <- tm_shape(us) + tm_polygons() +
-          tm_shape(nes_extent) + tm_borders(lwd = 3) +
-          tm_shape(dplyr::filter(nes_sf, !is.na(grp))) + tm_dots("grp", palette = palette,
-                                 size = 0.2, legend.show = TRUE, 
-                                 title = "Average Link Length") +
-          # tm_credits("National Eutrophication Survey") +
-          tm_layout(frame = FALSE,
-                    legend.outside = FALSE,
-                    legend.stack = "horizontal")
-
-save_tmap(m_nes, "../figures/best_partition_maps-2.png",
-          scale = 0.7, width = 3.125)
-```
-
-```{r plot_tree_example, echo=FALSE, fig.width=2, fig.height=3, eval=FALSE, eval=FALSE}
-plot_tree(gettree(readRDS("../data/nws/linklength_forest.rds")), 
-          title = "Link Length")
-```
-
-```{r partition_example_scatter, fig.height=4, fig.width=4.2, warning=FALSE, eval=FALSE}
-# setwd("manuscript")
-results_table <- read.csv("../scripts/table_1.csv", stringsAsFactors = FALSE)
-ll_split <- dplyr::filter(results_table, 
-                          nws_names == "avg_link_length" & 
-                          scale == "nws")$splits
-
-nes_nws <- mutate(nes_nws, grp = ifelse(avg_link_length > ll_split, 
-                                  "Higher", "Lower"))
-
-ggplot(data = dplyr::filter(nes_nws, 
-                     !is.na(avg_link_length))) + 
-         geom_point(aes(x = avg_link_length, 
-                                        y = p_percent_retention, 
-                                        color = grp), 
-                                    size = 1.3) + 
-  scale_color_manual(values = c(viridis::viridis(1, begin = 0), 
-                     viridis::viridis(1, begin = 0.5))) +
-  ylab("P Retention") + xlab("Avg. Link Length") + 
-  geom_vline(xintercept = ll_split) + 
-  theme(legend.position = "none") 
-```
-
-```{r 05_partition_vollenweider, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and hierarchical model fits to the data where the solid lines and shaded intervals represent the median and central 95% model  estimates respectively.
-The green lines and symbols are the estimates from the lower of the two partition groups while the purple lines are estimates for the upper of the two partition groups (see Table 2).", fig.width = 4.8, fig.height=5, warning=FALSE, eval=FALSE}
-
-knitr::include_graphics("../figures/05_partition_vollenweider-1.pdf")
-```
+milstead reanalysis
 
@@
 Data from Milstead et al.
-(2013).", fig.width = 5, fig.height = 4}
+(2013).", fig.width = 5, fig.height = 4, warning=FALSE, message=FALSE}
 library(cowplot)
@@
   theme(legend.title = element_blank(), legend.position = c(0.13, 0.8),
-        legend.text = element_text()) +
+        legend.text = element_text(), legend.background = element_rect(fill = "white")) +
   xlab("Residence Time") +
@@
 
-# if(!interactive()){  
 gg_fit_multi
-# }
-
-# legend <- get_legend(gg_fit_multi)
-# gg <- plot_grid(gg_fit_single, gg_fit_multi, scale = c(1, 1), rel_widths = c(3, 3), nrow = 1)
-# 
-# if(!interactive()){
-#   ggsave("milstead_conny.pdf", gg, height = 3.5, width = 7)
-# }
-
-# ggsave("milstead_conny_nogroup.pdf", gg)
-
-# hist(log(x))
-# hist(log(dt[dt$variable == "x_raw", "value"]))
-
-# nes <- read.csv("/home/jose/R/scripts/NES/nes_data.csv")
-# nes <- nes[!is.na(nes$retention_time),] 
-# 
-# nes$retention_time[nes$retention_time_units == "days" & 
-#   !is.na(nes$retention_time_units)] <- 
-#   nes$retention_time[nes$retention_time_units == "days" & 
-#                        !is.na(nes$retention_time_units)] / 365
-# 
-# dt <- data.frame(variable = "Milstead", 
-#           reshape2::melt(milstead[,"hrt"]))
-# 
-# # quants <- exp(quantile(log(dt$value)))
-# # format_labels(quants, 365)
-# # format_labels(quants, 12)
-# 
-# dt <- rbind(dt, 
-#         data.frame(variable = "NES", 
-#           reshape2::melt(nes[, c("retention_time")])))  
-# 
-# # dt$value <- log(dt$value)
-# 
-# dens <- density(dt[dt$variable == "Milstead", "value"])
-# dens <- data.frame(x = dens$x, y = dens$y)
-# 
-# gg <- ggplot(data = dt, aes(x = value)) +
-#   geom_density(aes(linetype = variable), alpha = 0.5, size = 1.55) + 
-#   scale_x_log10(breaks = as.numeric(yr_labels)[c(3, 5, 7)], 
-#                 labels = mixed_labels[c(3, 5, 7)]) + 
-#   cowplot::theme_cowplot() + theme(legend.position = c(0.15, 0.8), legend.title = element_blank(), legend.text = element_text()) +
-#   xlab("Residence Time") + 
-#   geom_segment(data = data.frame(x = quants[c(2, 4)], y = c(0.266, 0.48)), 
-#                aes(x = x, y = 0, xend = x, yend = y), size = 1.55)
-# 
-# if(!interactive()){  
-#   ggsave("hrt_density.pdf", gg, height = 4)
-# }
-# 
-# # nes_fit_single <- ggplot(data = nes, aes(x = retention_time, y = p_percent_retention)) +
-# #   geom_point() +
-# #   scale_x_log10(labels = mixed_labels[c(2:4)], breaks = c(1e-05, 1e-02, 1e+01)) +
-# #   stat_smooth(method = "glm", method.args = list(family = "binomial"), se = TRUE) +
-# #   scale_color_brewer(palette = "Set1") +
-#   cowplot::theme_cowplot() + 
-#   theme(legend.position = "none", legend.title = element_blank(), legend.text = element_text()) +
-#   xlab("Residence Time") +
-#   ylab("P Retention (%)")
 ```
 
-```{r p-retention_vs_percent-ag, fig.cap="P retention versus percent agriculture in network watersheds.", fig.width = 3, fig.height = 3}
+```{r p-retention_vs_percent-ag, fig.cap="P retention versus percent agriculture in network watersheds.", fig.width = 3, fig.height = 3, warning=FALSE, message=FALSE}
 nes_nws$percent_ag <- nes_iws$iws_nlcd1992_pct_81 + nes_iws$iws_nlcd1992_pct_82
@@
 
-```{r nes_vs_nla, fig.cap="Comparison of selected lake characteristics among the stratified random sampling design of the National Lakes Assessment (nla) and the haphazard sampling of the National Eutrophication Survey (nes) lakes analyzed in the present study.", fig.height=4}
+```{r nes_vs_nla, fig.cap="Comparison of selected lake characteristics among the stratified random sampling design of the National Lakes Assessment (nla) and the haphazard sampling of the National Eutrophication Survey (nes) lakes analyzed in the present study.", fig.height=4, warning=FALSE, message=FALSE}
 # , message=FALSE, warning=FALSE

### 2018-10-17 manuscript/appendix.Rmd
draft appendix text

@@
     fig_caption: yes
+bibliography: bibliography.bib
 ---
@@
 
-milstead reanalysis
+## Figure \ref{fig:fig1}
 
-```{r milstead_reanalysis, fig.cap="Relationship between residence time and phosphorus retention for inland lakes with surface area greater than 4 ha in Northeastern USA (New England).
+It is difficult to thoroughly examine the uncertainties surrounding the relationship between water residence time and lake P retention because empirical measures of these quantities do not exist for many lakes.
+One of the few sources of this data is modelling studies which produce largely unverified estimates of water residence time and P retention [@milsteadEstimatingSummerNutrient2013].
+Such model output data may not be appropriate for statistical P retention modelling because P retention and water residence time values do not represent independent estimates.
+As an alternative, we performed a more qualtiative analysis simply fitting separate smoothed functions to lakes of differing connectivity.
+Specifically, we used the connectivity data provided in LAGOS-NE [@sorannoLAGOSNEMultiscaledGeospatial2017] and described in detail by [@fergusFreshwaterLandscapeLake2017] where lakes are treated similarly based on whether they have upstream lake connections (DR_LakeStream), or upstream stream connections (DR_Stream), are headwater lakes, or are isolated lakes.
+
+## Figure \ref{fig:fig2}
+
+Our study lakes encompassed a range of land-use cover types and nutrient levels (Table 1).
+Although, lake watersheds were variable with respect to agricultural land use cover, we did not observe a strong relationship with lake P retention.
+
+## Figure \ref{fig:fig3}
+
+On average, the water quality (total phosphorus, chlorophyll concentration, and Secchi depth) of the lakes in our study are similar to other US lakes as measured by the stratified random sampling design of the National Lakes Assessment (NLA) lake population (USEPA 2012).
+However, our lakes are substantially larger and deeper than most NLA lakes.
+
+## References
+
+```{r milstead_reanalysis, fig.cap="\\label{fig:fig1}Relationship between residence time and phosphorus retention for inland lakes with surface area greater than 4 ha in Northeastern USA (New England).
 Vertical dashed lines denote lakes with intermediate residence times (within the interquartile range).
-Best fit lines are colored based on whether they have upstream lake connections (DR_LakeStream), or upstream stream connection (DR_Stream), are headwater lakes, or are isolated lakes.
+Best fit lines are colored based on whether they have upstream lake connections (DR_LakeStream), or upstream stream connections (DR_Stream), are headwater lakes, or are isolated lakes.
 Data from Milstead et al.
-(2013).", fig.width = 5, fig.height = 4, warning=FALSE, message=FALSE}
-library(cowplot)
+(2013).", fig.width = 5.5, fig.height = 4, warning=FALSE, message=FALSE}
+
 library(ggplot2)
@@
 
-# if(!interactive()){
-#   ggsave("milstead_single.pdf", gg_fit_single, height = 5)
-# }
-
-# milstead <- droplevels(milstead[milstead$lakeconnectivity != "Isolated",])
 gg_fit_multi <- ggplot(data = md, aes(x = hrt, y = Rp)) +
@@
   cowplot::theme_cowplot() + 
-  theme(legend.title = element_blank(), legend.position = c(0.13, 0.8),
-        legend.text = element_text(), legend.background = element_rect(fill = "white")) +
+  theme(legend.title = element_blank(), legend.position = c(0.02, 0.8),
+        legend.text = element_text(), 
+        legend.background = element_rect(fill = "white"), 
+        axis.text.x = element_text(size = 10)) +
   xlab("Residence Time") +
@@
 
-```{r p-retention_vs_percent-ag, fig.cap="P retention versus percent agriculture in network watersheds.", fig.width = 3, fig.height = 3, warning=FALSE, message=FALSE}
+```{r p-retention_vs_percent-ag, fig.cap="\\label{fig:fig2}P retention versus percent agriculture in network watersheds.", fig.width = 3, fig.height = 3, warning=FALSE, message=FALSE}
 nes_nws$percent_ag <- nes_iws$iws_nlcd1992_pct_81 + nes_iws$iws_nlcd1992_pct_82
@@
 
-```{r nes_vs_nla, fig.cap="Comparison of selected lake characteristics among the stratified random sampling design of the National Lakes Assessment (nla) and the haphazard sampling of the National Eutrophication Survey (nes) lakes analyzed in the present study.", fig.height=4, warning=FALSE, message=FALSE}
+```{r nes_vs_nla, fig.cap="\\label{fig:fig3}Comparison of selected lake characteristics among the stratified random sampling design of the National Lakes Assessment (nla) and the haphazard sampling of the National Eutrophication Survey (nes) lakes analyzed in the present study.", fig.height=4, warning=FALSE, message=FALSE}
 # , message=FALSE, warning=FALSE

### 2018-10-18 manuscript/appendix.Rmd
wordsmithing

@@
 
-It is difficult to thoroughly examine the uncertainties surrounding the relationship between water residence time and lake P retention because empirical measures of these quantities do not exist for many lakes.
-One of the few sources of this data is modelling studies which produce largely unverified estimates of water residence time and P retention [@milsteadEstimatingSummerNutrient2013].
-Such model output data may not be appropriate for statistical P retention modelling because P retention and water residence time values do not represent independent estimates.
-As an alternative, we performed a more qualtiative analysis simply fitting separate smoothed functions to lakes of differing connectivity.
-Specifically, we used the connectivity data provided in LAGOS-NE [@sorannoLAGOSNEMultiscaledGeospatial2017] and described in detail by [@fergusFreshwaterLandscapeLake2017] where lakes are treated similarly based on whether they have upstream lake connections (DR_LakeStream), or upstream stream connections (DR_Stream), are headwater lakes, or are isolated lakes.
+It is difficult to examine the uncertainties surrounding the relationship between water residence time and lake P retention because empirical measures of these quantities do not exist for many lakes.
+One of the few comprehensive sources of these data is modelling studies which produce largely unverified estimates of water residence time and P retention [@milsteadEstimatingSummerNutrient2013].
+Such model output data may not be appropriate for statistical P retention modelling because P retention and water residence time values are not independently estimated.
+As an alternative, we performed a more qualitative analysis fitting separate smoothed functions to lakes of differing connectivity (see appendix source code for details).
+Specifically, we used the connectivity data provided in LAGOS-NE [@sorannoLAGOSNEMultiscaledGeospatial2017] and described in detail by [@fergusFreshwaterLandscapeLake2017] where lakes are grouped based on whether they have upstream lake connections (DR_LakeStream), or upstream stream connections (DR_Stream), are headwater lakes, or are isolated lakes.
 
@@
 
-Our study lakes encompassed a range of land-use cover types and nutrient levels (Table 1).
-Although, lake watersheds were variable with respect to agricultural land use cover, we did not observe a strong relationship with lake P retention.
+Our study lakes encompassed a range of land-use cover types and nutrient levels.
+Here, we examined whether a strong relationship of lake P retention with agricultural land use cover could be obscuring relationships with connectivity metrics.
+We used P retention data from the National Eutrophication Survey [@stachelek_national_2017] and land cover data from the 1992 National Land Cover Database clipped to lake watersheds and available in the LAGOS-NE dataset [@sorannoLAGOSNEMultiscaledGeospatial2017].
 
@@
 
-On average, the water quality (total phosphorus, chlorophyll concentration, and Secchi depth) of the lakes in our study are similar to other US lakes as measured by the stratified random sampling design of the National Lakes Assessment (NLA) lake population (USEPA 2012).
-However, our lakes are substantially larger and deeper than most NLA lakes.
+Although our study considered many lakes spread across a broad spatial extent, we wanted to assess whether their basic characteristics were representative of lakes in general.
+We compared water quality (total phosphorus, chlorophyll concentration, and Secchi depth) of the lakes in our study with other US lakes as measured by the stratified random sampling design of the National Lakes Assessment (NLA) lake population [@usepa_nla2012].
+Our lakes are similar in most respects except that they are substantially larger and deeper than most NLA lakes.
 

### 2018-10-19 manuscript/figures.Rmd
copy figure captions, add tex math

--- 2018-07-19 manuscript/figures.Rmd
@@
 
-```{r fig.cap="Major lake and watershed characteristics, factors, and processes affecting lake P retention.
-Shaded symbols indicate items typically considered in P retention models while open symbols indicate additional items considered in the present study.", echo=FALSE, fig.width=1,out.height="4in"}
-knitr::include_graphics("../figures/conceptual_p-cycle_pt2.pdf")
+```{r fig.cap="Major lake and watershed factors affecting lake P retention.
+Shaded symbols indicate factors typically considered in P retention models whereas open symbols indicate additional factors specific to the present study.
+Dashed lines indicate inferred relationships, which cannot be tested with available data, but are otherwise discussed herein.", echo=FALSE, fig.width=1,out.height="4in"}
+knitr::include_graphics("../figures/01_conceptual_p-cycle_pt2.pdf")
 ```
 
-```{r fig.cap="Connectivity metric definitions along with examples of high and low connectivity lakes.", echo=FALSE}
-knitr::include_graphics("../figures/conny_metric_key_crop.pdf")
+```{r fig.cap="Connectivity metric definitions along with simplified examples of high and low connectivity lakes that might arise from a binary classification.
+Here, high connectivity lakes with respect to both lake-stream-based and stream-based metrics are associated with lower barriers to in-stream transport.
+For stream-based metrics, high connectivity lakes are associated with more direct transport of P from terrestrial runoff to streams.
+We use the term “first order stream” to describe a headwater stream.", echo=FALSE}
+knitr::include_graphics("../figures/02_conny_metric_key_crop_small.pdf")
 ```
 
-```{r fig.cap="Diagram showing the lake watershed (LWS) and network watershed (NWS) of three lakes.
-Here the IWS of lake 3 encompasses the LWS of lake 2 because of it is smaller than 10 ha small size but it does not encompass the LWS of lake 1 because it has an area of at least 10 ha.
-In contrast to the LWS boundaries, the NWS boundaries extend to the headwaters of the lake chain.", echo=FALSE}
-knitr::include_graphics("../figures/iws_nws.pdf")
+```{r fig.cap="Diagram showing the lake watershed and lake network watershed of three lakes.
+Here the lake watershed of lake 3 encompasses the lake watershed of lake 2 because it is smaller than 10 ha but it does not encompass the lake watershed of lake 1 because it has an area of at least 10 ha.
+In contrast to the lake watershed boundaries, the lake network watershed boundaries extend to the headwaters of the lake chain.", echo=FALSE}
+knitr::include_graphics("../figures/03_iws_nws.pdf")
 ```
 
-```{r 04_global_vollenweider, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and the global model fit to the data where the solid line and shaded interval represents the median and central 95% interval estimates respectively.", warning=FALSE}
+```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.cap="Correlation among connectivity metrics and selected lake characteristics.
+NWS is the lake network watershed extent whereas LWS is the lake watershed extent.
+Connectivity metrics are defined in Figure 2.", message=FALSE}
+knitr::include_graphics("../figures/07_cor_mat_hmap-1.pdf")
+```
+
+```{r 08_maps, echo=FALSE, fig.cap="Locations of lakes of different connectivity classes at the (A) lake watershed and (B) lake network watershed extent.
+Low connectivity lakes are represented by green symbols, and high connectivity lakes are represented by purple symbols.
+NWS is the lake network watershed extent.
+LWS is the lake watershed extent.
+Connectivity metrics are defined in Figure 2.", warning=FALSE, message=FALSE}
+knitr::include_graphics("../figures/08_maps-1.pdf")
+```
+
+```{r 04_global_vollenweider, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and the global model fit to the data ($R^{2}$ = 0.34, n = 129) where the solid line and shaded interval represents the median and central 95% interval estimates respectively (A).
+As above except that solid lines and shaded interval estimates represent hierarchical model fits to the data ($R^{2}$ = 0.41, n = 129) based on network watershed average link length, which had the strongest association of any connectivity metric relative to P retention (B).
+Equations for these lines at median water residence time for low and high connectivity lakes are: Rp = 1 - (1 / (1 + 1.32 $\\tau^{0.4}$)) and Rp = 1 - (1 / (1 + 1.08 $\\tau^{0.4}$)) respectively.", warning=FALSE}
 
@@
 
-```{r 06_k, echo=FALSE, message=FALSE, fig.cap="Distribution of the k parameter from the Vollenweider's equation in low and high connectivity partitions at the (A) LWS and (B) NWS scales.
-Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", fig.width=5, fig.height=3.8, warning=FALSE}
+```{r 06_k, echo=FALSE, message=FALSE, fig.cap="Distribution of the k parameter from Eq.
+1 in lakes of differing connectivity, depth, or baseflow at the (A) lake watershed and (B) lake network watershed extents.
+Green lines indicate lower connectivity lakes while purple lines indicate higher connectivity lakes.
+For maximum depth, green lines indicate deeper lakes.
+For baseflow, green lines indicate higher baseflow.
+Connectivity metrics are defined in Figure 2.
+Labels associated with models where differences in k translated to significant differences in P retention are bolded and starred.", fig.width=5, fig.height=3.8, warning=FALSE}
 knitr::include_graphics("../figures/06_k-3.pdf")
 ```
-
-```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.cap="Correlation between connectivity metrics and selected lake characteristics.", message=FALSE}
-knitr::include_graphics("../figures/07_cor_mat_hmap-1.pdf")
-```
-
-```{r 08_maps, echo=FALSE, fig.cap="Maps showing the locations of lake connectivity partitions.
-Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", warning=FALSE, message=FALSE}
-knitr::include_graphics("../figures/08_maps-1.pdf")
-```

### 2018-10-19 manuscript/grayscale_figures.Rmd
add grayscale figures target

--- 2018-10-19 manuscript/figures.Rmd
@@
 Dashed lines indicate inferred relationships, which cannot be tested with available data, but are otherwise discussed herein.", echo=FALSE, fig.width=1,out.height="4in"}
-knitr::include_graphics("../figures/01_conceptual_p-cycle_pt2.pdf")
+knitr::include_graphics("../figures/grayscale/gray_01_conceptual_p-cycle_pt2.pdf")
 ```
@@
 We use the term “first order stream” to describe a headwater stream.", echo=FALSE}
-knitr::include_graphics("../figures/02_conny_metric_key_crop_small.pdf")
+knitr::include_graphics("../figures/grayscale/gray_02_conny_metric_key_crop_small.pdf")
 ```
@@
 In contrast to the lake watershed boundaries, the lake network watershed boundaries extend to the headwaters of the lake chain.", echo=FALSE}
-knitr::include_graphics("../figures/03_iws_nws.pdf")
+knitr::include_graphics("../figures/grayscale/gray_03_iws_nws.pdf")
 ```
@@
 Connectivity metrics are defined in Figure 2.", message=FALSE}
-knitr::include_graphics("../figures/07_cor_mat_hmap-1.pdf")
+knitr::include_graphics("../figures/grayscale/gray_07_cor_mat_hmap-1.pdf")
 ```
@@
 Connectivity metrics are defined in Figure 2.", warning=FALSE, message=FALSE}
-knitr::include_graphics("../figures/08_maps-1.pdf")
+knitr::include_graphics("../figures/grayscale/gray_08_maps-1.pdf")
 ```
@@
 
-knitr::include_graphics("../figures/04_global_vollenweider-1.pdf")
+knitr::include_graphics("../figures/grayscale/gray_04_global_vollenweider-1.pdf")
 ```
@@
 Labels associated with models where differences in k translated to significant differences in P retention are bolded and starred.", fig.width=5, fig.height=3.8, warning=FALSE}
-knitr::include_graphics("../figures/06_k-3.pdf")
+knitr::include_graphics("../figures/grayscale/gray_06_k-3.pdf")
 ```

### 2018-12-11 scripts/03_viz.R
add p retention to heatmap

@@ -277,14 +277,17 @@ conny_cols  <- unique(splits$iws_names)[!is.na(unique(splits$iws_names))]
 conny_cols  <- conny_cols[!(conny_cols %in% "lakeconnection")]
 
 nes_iws_sub <- nes_iws_sub[,c(conny_cols, 
-                              "lake_area_ha", "p_pnt_source_pct", "iws_ha")]
+                              "lake_area_ha", "p_pnt_source_pct", "iws_ha", 
+                              "p_percent_retention")]
 
 iws_key <- merge(data.frame(iws_names = names(nes_iws_sub)), 
                  splits[,c("iws_names", "abb")], sort = FALSE)
 iws_key <- rbind(iws_key, 
                  data.frame(iws_names = c("lake_area_ha", 
-                                          "p_pnt_source_pct", "iws_ha"), 
-                            abb = c("Lake Area", "Point Source P", "LWS area")))
+                                          "p_pnt_source_pct", "iws_ha", 
+                                          "p_percent_retention"), 
+                            abb = c("Lake Area", "Point Source P", "LWS area", 
+                                    "P Retention")))
 iws_key <- iws_key[!duplicated(iws_key),]
 names(nes_iws_sub) <- iws_key$abb
 
@@ -297,15 +300,18 @@ conny_cols  <- conny_cols[!(conny_cols %in% "lakeconnection")]
 nes_nws_sub <- nes_nws_sub[,c(conny_cols, 
                               "lake_area_ha", "p_total", 
                               "p_pnt_source_pct", "iws_ha", 
-                              "nws_ha", "retention_time_yr")]
+                              "nws_ha", "retention_time_yr", 
+                              "p_percent_retention")]
 nws_key <- merge(data.frame(nws_names = names(nes_nws_sub)), 
                  splits[,c("nws_names", "abb")], sort = FALSE)
 nws_key <- rbind(nws_key, data.frame(nws_names = c("lake_area_ha", "p_total", 
                                                    "p_pnt_source_pct", "iws_ha", 
-                                                   "nws_ha", "retention_time_yr"), 
+                                                   "nws_ha", "retention_time_yr", 
+                                                   "p_percent_retention"), 
                                      abb = c("Lake Area", "P Loading", 
                                              "Point Source P", "LWS area", 
-                                             "NWS area", "Water Residence Time")))
[…]

### 2018-12-11 scripts/03_viz.R
use color blind safe palette

@@ -376,7 +376,7 @@ pheatmap::pheatmap(res_f, na_col = "grey",
                    cluster_cols = FALSE, cluster_rows = FALSE, 
                    color = colorRampPalette(
                      rev(
-                       RColorBrewer::brewer.pal(n = 7, name ="RdBu")[2:6]
+                       RColorBrewer::brewer.pal(n = 7, name ="BrBG")[2:6]
                       ))(100), 
                    display_numbers = apply(res_f, 2, function(x) fnc(x, 2)), 
                    fontsize_number = 6)

### 2018-12-19 figures/06_k.Rmd
lws to subwatersheds, nws to watersheds

@@
 plot_grid(
-  k_viz_iws + ggtitle("a. Lake Watershed") + xlim(0.8, 1.6),
-  k_viz_nws + ggtitle("b. Lake Network Watershed") + xlim(0.8, 1.6), 
+  k_viz_iws + ggtitle("a. Lake Subwatershed") + xlim(0.8, 1.6),
+  k_viz_nws + ggtitle("b. Lake Watershed") + xlim(0.8, 1.6), 
   ncol = 2, align = "v", rel_widths = c(1, 1)) + 

### 2018-12-19 figures/08_maps.Rmd
lws to subwatersheds, nws to watersheds

@@
             nrow = 4, ncol = 1,
-            labels = c("A. LWS", "", "B. NWS", "", ""), 
+            labels = c("A. SWS", "", "B. WS", "", ""), 
             label_colour = "black", vjust = c(1.2, 0, 2, 0, 0), 

### 2018-12-19 figures/beamer-lake-fig/beamer-lake-fig.tex
lws to subwatersheds, nws to watersheds

@@
       \draw [cyan, thick, decorate, decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt, align=center, anchor=center]
-      (3,-1.2) -- (3,7.2) node [cyan,midway,xshift=1.3cm] {\footnotesize
+      (3,-1.2) -- (3,7.2) node [cyan,midway,xshift=1.5cm] {\footnotesize
+      Lake \\ \footnotesize Subwatershed\\ \footnotesize 3};
+
+      \draw [cyan, thick, decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt, align=center, anchor=center]
+      (6.1,-1.2) -- (6.1,9) node [cyan,midway,xshift=1.3cm] {\footnotesize
       Lake \\ \footnotesize Watershed\\ \footnotesize 3};
 
-      \draw [cyan, thick, decorate,decoration={brace,amplitude=10pt,mirror,raise=4pt},yshift=0pt, align=center, anchor=center]
-      (5.4,-1.2) -- (5.4,9) node [cyan,midway,xshift=1.3cm] {\footnotesize
-      Lake \\ \footnotesize Network \\ \footnotesize Watershed\\ \footnotesize 3};
-
       \draw [darkgreen, thick, decorate, decoration={brace,amplitude=10pt,raise=4pt},yshift=0pt]
-      (-3.1,3) -- (-3.1,7.2) node [darkgreen,midway,xshift=-1.3cm, align=center] {\footnotesize
-      Lake \\ \footnotesize Watershed\\ \footnotesize 2};
+      (-3.1,3) -- (-3.1,7.2) node [darkgreen,midway,xshift=-1.5cm, align=center] {\footnotesize
+      Lake \\ \footnotesize Subwatershed\\ \footnotesize 2};
 
       \draw [darkgreen, thick, decorate, decoration={brace,amplitude=10pt,raise=4pt},yshift=0pt, align=center, anchor=center]
-      (-5.5,3) -- (-5.5,9) node [darkgreen,midway,xshift=-1.3cm, align=center] {\footnotesize
-      Lake \\ \footnotesize
-      Network \\ \footnotesize Watershed\\ \footnotesize 2};
+      (-6.1,3) -- (-6.1,9) node [darkgreen,midway,xshift=-1.3cm, align=center] {\footnotesize
+      Lake \\ \footnotesize Watershed\\ \footnotesize 2};
 

### 2018-12-19 manuscript/appendix.Rmd
lws to subwatersheds, nws to watersheds

@@
 
-```{r p-retention_vs_percent-ag, fig.cap="\\label{fig:fig2}P retention versus percent agriculture in network watersheds.", fig.width = 3, fig.height = 3, warning=FALSE, message=FALSE}
+```{r p-retention_vs_percent-ag, fig.cap="\\label{fig:fig2}P retention versus percent agriculture in lake watersheds.", fig.width = 3, fig.height = 3, warning=FALSE, message=FALSE}
 nes_nws$percent_ag <- nes_iws$iws_nlcd1992_pct_81 + nes_iws$iws_nlcd1992_pct_82

### 2018-12-19 manuscript/figures.Rmd
lws to subwatersheds, nws to watersheds

@@
 
-```{r fig.cap="Diagram showing the lake watershed and lake network watershed of three lakes.
-Here the lake watershed of lake 3 encompasses the lake watershed of lake 2 because it is smaller than 10 ha but it does not encompass the lake watershed of lake 1 because it has an area of at least 10 ha.
-In contrast to the lake watershed boundaries, the lake network watershed boundaries extend to the headwaters of the lake chain.", echo=FALSE}
+```{r fig.cap="Diagram showing the lake subwatershed and lake watershed of three lakes.
+Here the lake subwatershed of lake 3 encompasses the lake subwatershed of lake 2 because it is smaller than 10 ha but it does not encompass the lake subwatershed of lake 1 because it has an area of at least 10 ha.
+In contrast to the lake subwatershed boundaries, the lake watershed boundaries extend to the headwaters of the lake chain.", echo=FALSE}
 knitr::include_graphics("../figures/03_iws_nws.pdf")
@@
 ```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.cap="Correlation among connectivity metrics and selected lake characteristics.
-NWS is the lake network watershed extent whereas LWS is the lake watershed extent.
+WS is the lake watershed extent whereas SWS is the lake subwatershed extent.
 Connectivity metrics are defined in Figure 2.", message=FALSE}
@@
 
-```{r 08_maps, echo=FALSE, fig.cap="Locations of lakes of different connectivity classes at the (A) lake watershed and (B) lake network watershed extent.
+```{r 08_maps, echo=FALSE, fig.cap="Locations of lakes of different connectivity classes at the (A) lake subwatershed and (B) lake watershed extent.
 Low connectivity lakes are represented by green symbols, and high connectivity lakes are represented by purple symbols.
-NWS is the lake network watershed extent.
-LWS is the lake watershed extent.
+WS is the lake watershed extent.
+SWS is the lake subwatershed extent.
 Connectivity metrics are defined in Figure 2.", warning=FALSE, message=FALSE}
@@
 ```{r 04_global_vollenweider, echo=FALSE, fig.cap="Residence time (yr) versus P retention for the NES dataset and the global model fit to the data ($R^{2}$ = 0.34, n = 129) where the solid line and shaded interval represents the median and central 95% interval estimates respectively (A).
-As above except that solid lines and shaded interval estimates represent hierarchical model fits to the data ($R^{2}$ = 0.41, n = 129) based on network watershed average link length, which had the strongest association of any connectivity metric relative to P retention (B).
+As above except that solid lines and shaded interval estimates represent hierarchical model fits to the data ($R^{2}$ = 0.41, n = 129) based on watershed average link length, which had the strongest association of any connectivity metric relative to P retention (B).
 Equations for these lines at median water residence time for low and high connectivity lakes are: Rp = 1 - (1 / (1 + 1.32 $\\tau^{0.4}$)) and Rp = 1 - (1 / (1 + 1.08 $\\tau^{0.4}$)) respectively.", warning=FALSE}
@@
 ```{r 06_k, echo=FALSE, message=FALSE, fig.cap="Distribution of the k parameter from Eq.
-1 in lakes of differing connectivity, depth, or baseflow at the (A) lake watershed and (B) lake network watershed extents.
+1 in lakes of differing connectivity, depth, or baseflow at the (A) lake subwatershed and (B) lake watershed extents.
 Green lines indicate lower connectivity lakes while purple lines indicate higher connectivity lakes.

### 2018-12-19 scripts/03_viz.R

@@ -286,7 +286,7 @@ iws_key <- rbind(iws_key,
                  data.frame(iws_names = c("lake_area_ha", 
                                           "p_pnt_source_pct", "iws_ha", 
                                           "p_percent_retention"), 
-                            abb = c("Lake Area", "Point Source P", "LWS area", 
+                            abb = c("Lake Area", "Point Source P", "SWS area", 
                                     "P Retention")))
 iws_key <- iws_key[!duplicated(iws_key),]
 names(nes_iws_sub) <- iws_key$abb
@@ -309,8 +309,8 @@ nws_key <- rbind(nws_key, data.frame(nws_names = c("lake_area_ha", "p_total",
                                                    "nws_ha", "retention_time_yr", 
                                                    "p_percent_retention"), 
                                      abb = c("Lake Area", "P Loading", 
-                                             "Point Source P", "LWS area", 
-                                             "NWS area", "Water Residence Time", 
+                                             "Point Source P", "SWS area", 
+                                             "WS area", "Water Residence Time", 
                                              "P Retention")))
 nws_key <- nws_key[!duplicated(nws_key),]
 names(nes_nws_sub) <- nws_key$abb

### 2018-12-19 scripts/04_tables.R

@@ -18,7 +18,7 @@ name_key <- data.frame(
     "Total Phosphorus (ug/L)", "Chlorophyll (ug/L)", "Secchi Depth (m)",
     "P Loading (kg/yr)", "P Retention", "Residence Time (yr)",
     "Lake Area (km2)", "Maximum Depth (m)", "Agricultural Landuse (%)", "Urban Landuse %", 
-    "Lake Watershed Area (km2)", "Network Watershed Area (km2)"), 
+    "Lake Subwatershed Area (km2)", "Lake Watershed Area (km2)"), 
   digits = c(2, 0, 2, 
              0, 2, 2, 
              2, 1, 2, 2, 

### 2018-12-19 figures/02_conny_metric_key.tex
call steam-based lake-stream-based
drop low vs high connctivity from fig 2

@@
       \begin{column}{0.25\textwidth}
-        \huge{Lower Connectivity}
+        \huge{Low}
       \end{column}
@@
       \begin{column}{0.25\textwidth}
-        \huge{Higher Connectivity}
+        \huge{High}
       \end{column}
@@
   \begin{column}{0.25\textwidth}
+    \begin{tikzpicture}[scale = 2]
+    %\draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
+        \draw [-,ultra thick, cyan] (2.0,2.5) to [out=270,in=90] (0.2,0);
+        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 3cm, xshift = 2cm] plot (\x:0.6+rnd*0.2);
+        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
+      \end{tikzpicture}
+  \end{column}
+
+  \begin{column}{0.25\textwidth}
   \vspace{2em}
@@
 
-  \begin{column}{0.25\textwidth}
-    \begin{tikzpicture}[scale = 2]
-        \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
-        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 5cm, xshift = 2cm] plot (\x:0.6+rnd*0.2);
-        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
-      \end{tikzpicture}
-  \end{column}
   \end{columns}
@@
     \begin{column}[b]{0.4\textwidth}
-      {\fontsize{65}{65}\textbf{Stream-based Metrics}}
+      {\fontsize{65}{65}\textbf{Lake-stream-based Metrics}}
       \vspace{2em}
@@
       \begin{tikzpicture}[scale = 2]
+        %   \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
+          \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+          \draw [-,ultra thick, cyan] (0.9,4) to [out=290,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+
+          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
+        \end{tikzpicture}
+    \end{column}
+
+    \begin{column}{0.25\textwidth}
+      \begin{tikzpicture}[scale = 2]
           %\draw[step=1cm,gray,very thin] (-4,-4) grid (4,4);
@@
 
-    \begin{column}{0.25\textwidth}
-      \begin{tikzpicture}[scale = 2]
-        %   \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
-          \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
-          \draw [-,ultra thick, cyan] (0.9,4) to [out=290,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
-
-          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
-        \end{tikzpicture}
-    \end{column}
     \end{columns}
@@
 Stream Order Ratio:} The total number of first order stream reaches divided by the total number of higher order stream reaches.
-In this example the lower connectivity lake has a stream order ratio of 3 whereas the higher connectivity lake has a stream order ratio of 2.}
+In this example the lower value lake has a stream order ratio of 2 whereas the higher value lake has a stream order ratio of 3.}
     \end{column}
@@
     \begin{column}{0.25\textwidth}
-    \vspace{2em}
+      \begin{tikzpicture}[scale = 2]
+        %   \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
+          \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+          \draw [-, ultra thick, cyan] (0.9,4) to [out=290,in=0] (1.1,1.9);
+          \draw [-,line width=7pt, cyan] (1.1,1.9) to [out=270,in=90] (0,0);
+
+          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
+        \end{tikzpicture}
+    \end{column}
+
+    \begin{column}{0.25\textwidth}
+    %\vspace{-2em}
+    \vspace{4em}
       \begin{tikzpicture}[scale = 2]
@@
 
-    \begin{column}{0.25\textwidth}
-    \vspace{-2em}
-      \begin{tikzpicture}[scale = 2]
-        %   \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
-          \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
-          \draw [-, ultra thick, cyan] (0.9,4) to [out=290,in=0] (1.1,1.9);
-          \draw [-,line width=7pt, cyan] (1.1,1.9) to [out=270,in=90] (0,0);
-
-          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
-        \end{tikzpicture}
-    \end{column}
     \end{columns}

### 2018-12-19 manuscript/figures.Rmd
drop low vs high connctivity from fig 2

@@
 
-```{r fig.cap="Connectivity metric definitions along with simplified examples of high and low connectivity lakes that might arise from a binary classification.
-Here, high connectivity lakes with respect to both lake-stream-based and stream-based metrics are associated with lower barriers to in-stream transport.
-For stream-based metrics, high connectivity lakes are associated with more direct transport of P from terrestrial runoff to streams.
+```{r fig.cap="Connectivity metric definitions along with simplified examples of high and low value lakes that might arise from a binary classification.
+Both lake-stream-based and stream-based metrics are associated with restrictions on  in-stream transport whereas stream-based metrics are associated with differences in transport of P from terrestrial runoff to streams.
 We use the term “first order stream” to describe a headwater stream.", echo=FALSE}

### 2018-12-19 figures/06_k.Rmd
drop low vs high connectivity from figure 7

@@
 
-```{r 06_k, echo=FALSE, message=FALSE, fig.cap="Distribution of the k parameter from the Vollenweider equation in low and high connectivity partitions at the (A) lake watershed and (B) network watershed scales.
+```{r 06_k, echo=FALSE, message=FALSE, fig.cap="Distribution of the k parameter from the Vollenweider equation in low and high connectivity metric partitions at the (A) lake watershed and (B) network watershed scales.
 Green symbols indicate the lower of the two partition groups while purple symbols represent the higher of the two partition groups (see Table 2).", fig.width=7, fig.height=3.8, warning=FALSE}
@@
 fit_df_iws$key <- factor(fit_df_iws$key, levels = c("k",
-                                                    "k1_sr", "k2_sr",
-                                                    "k1_bf", "k2_bf",
-                                                    "k2_md", "k1_md",
+                                                    "k1_sr", "k2_sr", # k2 is higer
+                                                    "k1_bf", "k2_bf", # k2 is higher
+                                                    "k1_md", "k2_md", # k2 is deeper
                                                     "k1_la", "k2_la",
-                                                    "k2_lc", "k1_lc",
-                                                    "k2_sd", "k1_sd",
+                                                    "k2_lc", "k1_lc", # k2 is dr_stream
+                                                    "k1_sd", "k2_sd", # k2 is more dense
                                                     "k1_cd", "k2_cd",
@@
                                                     "k1_bf", "k2_bf",
-                                                    "k2_md", "k1_md",
+                                                    "k1_md", "k2_md",
                                                     "k1_la", "k2_la",
                                                     "k2_lc", "k1_lc",
-                                                    "k2_sd", "k1_sd",
+                                                    "k1_sd", "k2_sd",
                                                     "k1_cd", "k2_cd",

### 2018-12-19 manuscript/figures.Rmd
drop low vs high connectivity from figure 7

@@
 As above except that solid lines and shaded interval estimates represent hierarchical model fits to the data ($R^{2}$ = 0.41, n = 129) based on watershed average link length, which had the strongest association of any connectivity metric relative to P retention (B).
-Equations for these lines at median water residence time for low and high connectivity lakes are: Rp = 1 - (1 / (1 + 1.32 $\\tau^{0.4}$)) and Rp = 1 - (1 / (1 + 1.08 $\\tau^{0.4}$)) respectively.", warning=FALSE}
+Equations for these lines at median water residence time for low and high link length lakes are: Rp = 1 - (1 / (1 + 1.32 $\\tau^{0.4}$)) and Rp = 1 - (1 / (1 + 1.08 $\\tau^{0.4}$)) respectively.", warning=FALSE}
 
@@
 1 in lakes of differing connectivity, depth, or baseflow at the (A) lake subwatershed and (B) lake watershed extents.
-Green lines indicate lower connectivity lakes while purple lines indicate higher connectivity lakes.
-For maximum depth, green lines indicate deeper lakes.
-For baseflow, green lines indicate higher baseflow.
+Lighter (green) lines indicate lakes with lower connectivity metrics values while darker (purple) lines indicate lakes with higher connectivity metrics values.
+For lake connection, lighter colored lines indicate lakes without upstream lakes.
 Connectivity metrics are defined in Figure 2.

### 2018-12-19 scripts/03_viz.R

@@ -7,7 +7,7 @@
 plot_grid(
   full_pred_plot(nes_iws, readRDS("../data/global_vollenweider.rds")),
   part_pred_plot(nes_nws, readRDS("../data/nws/ll_vollenweider.rds"),
-                 8, "B.", xl = TRUE, yl = FALSE, legend_title = "Link length \n (connectivity)"), 
+                 8, "B.", xl = TRUE, yl = FALSE, legend_title = "Link length"), 
   rel_widths = c(1, 0.9), 
   rel_heights = c(1, 1))
 

### 2018-12-19 figures/08_maps.Rmd
drop low vs high connectivity from fig 5

@@
 ```{r load_data, message=FALSE, results='hide', echo=FALSE, warning=FALSE}
+  # source("../scripts/99_utils.R")
   source("../scripts/01.5_loaddata.R")
@@
   pnames2 = c("sr", "bf", "la", "sd", "cd", "ll"), 
-  higher_connectivity = c("higher", "higher", "higher", "lower", "higher", "higher"))
+  higher_connectivity = c("higher", "higher", "higher", "higher", "higher", "higher"))
 
@@
                                           partition_splits[x, "higher_connectivity"])
+
+                           # print(paste0("lower = ", mean(
+                           #   st_drop_geometry(nes_sub)[
+                           #     ,as.character(partition_splits[x, "iws_names"])], 
+                           #      na.rm = TRUE)))
+                           # 
+                           # print(paste0("higher = ", mean(
+                           #   st_drop_geometry(nes_sf)[
+                           #     ,as.character(partition_splits[x, "nws_names"])], 
+                           #      na.rm = TRUE)))
 

### 2018-12-19 manuscript/figures.Rmd
drop low vs high connectivity from fig 5

@@
 
-```{r 08_maps, echo=FALSE, fig.cap="Locations of lakes of different connectivity classes at the (A) lake subwatershed and (B) lake watershed extent.
-Low connectivity lakes are represented by green symbols, and high connectivity lakes are represented by purple symbols.
+```{r 08_maps, echo=FALSE, fig.cap="Locations of lakes of with different connectivity metric values at the (A) lake subwatershed and (B) lake watershed extent.
+Low valued lakes are represented by lighter (green) symbols, and high values lakes are represented by darker (purple) symbols.
 WS is the lake watershed extent.

### 2018-12-19 figures/02_conny_metric_key.tex
recolor metric key

@@
 \input{beamer-lake-fig/beamer-lake-fig.tex}
+
+\definecolor{vhigh}{HTML}{440154}
+\definecolor{vlow}{HTML}{21908C}
 
@@
     %\draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
-        \draw [-,ultra thick, cyan] (2.0,2.5) to [out=270,in=90] (0.2,0);
-        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 3cm, xshift = 2cm] plot (\x:0.6+rnd*0.2);
-        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
+        \draw [-,line width = 4pt, vlow] (2.0,2.5) to [out=270,in=90] (0.2,0);
+        \draw[vlow, ultra thick, domain=0:350, smooth cycle, fill=vlow, yshift = 3cm, xshift = 2cm] plot (\x:0.6+rnd*0.2);
+        \draw[vlow!70!black!100, line width = 4pt, domain=0:350, smooth cycle, fill=vlow] plot (\x:1+rnd*0.5);
       \end{tikzpicture}
@@
         %\draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
-        \draw[-,ultra thick, cyan] plot [smooth, tension = 1] coordinates {(2.2,2.8) (1.3,1.6) (-0.3,2.7) (0,0)};
+        \draw[-,line width = 4pt, vhigh] plot [smooth, tension = 1] coordinates {(2.2,2.8) (1.3,1.6) (-0.3,2.7) (0,0)};
 
-        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 3cm, xshift = 2cm] plot (\x:0.6+rnd*0.2);
-        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
+        \draw[vhigh, ultra thick, domain=0:350, smooth cycle, fill=vhigh, yshift = 3cm, xshift = 2cm] plot (\x:0.6+rnd*0.2);
+        \draw[vhigh!70!black!100, line width = 4pt, domain=0:350, smooth cycle, fill=vhigh] plot (\x:1+rnd*0.5);
       \end{tikzpicture}
@@
       \begin{tikzpicture}[scale = 2]
-          \draw [-,ultra thick, cyan] (2.2,3.7) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
-          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 3.5cm, xshift = 2cm] plot (\x:0.5+rnd*0.2);
-          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
+          \draw [-,line width = 4pt, vlow] (2.2,3.7) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+          \draw[vlow, ultra thick, domain=0:350, smooth cycle, fill=vlow, yshift = 3.5cm, xshift = 2cm] plot (\x:0.5+rnd*0.2);
+          \draw[vlow!70!black!100, line width = 4pt, domain=0:350, smooth cycle, fill=vlow] plot (\x:1+rnd*0.5);
         \end{tikzpicture}
@@
       \begin{tikzpicture}[scale = 2]
-          \draw [-,ultra thick, cyan] (2.2,4.1) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
-          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan, yshift = 3.5cm, xshift = 2cm] plot (\x:0.9+rnd*0.2);
-          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
+          \draw [-,line width = 4pt, vhigh] (2.2,4.1) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+          \draw[vhigh, ultra thick, domain=0:350, smooth cycle, fill=vhigh, yshift = 3.5cm, xshift = 2cm] plot (\x:0.9+rnd*0.2);
+          \draw[vhigh!70!black!100, line width = 4pt, domain=0:350, smooth cycle, fill=vhigh] plot (\x:1+rnd*0.5);
         \end{tikzpicture}
@@
         %\draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
-        \draw [-,ultra thick, cyan] (1.6,2.4) to [out=180,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
-        \draw [-,ultra thick, cyan] (0.58,2.3) to [out=0,in=90] (1.1,1.9) to [out=270,in=90] (0,0);
+        \draw [-,line width = 4pt, vlow] (1.6,2.4) to [out=180,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
+        \draw [-,line width = 4pt, vlow] (0.58,2.3) to [out=0,in=90] (1.1,1.9) to [out=270,in=90] (0,0);
 
-        \draw [-,ultra thick, cyan] (-1.2,2.75) to [out=200,in=0] (-1.6,2.4) to [out=290,in=110] (-1.1,1.9) to [out=270,in=90] (0,0);        
-        \draw [-,ultra thick, cyan] (-0.58,2.3) to [out=250,in=70] (-1.1,1.9) to [out=270,in=90] (0,0);
+        \draw [-,line width = 4pt, vlow] (-1.2,2.75) to [out=200,in=0] (-1.6,2.4) to [out=290,in=110] (-1.1,1.9) to [out=270,in=90] (0,0);        
+        \draw [-,line width = 4pt, vlow] (-0.58,2.3) to [out=250,in=70] (-1.1,1.9) to [out=270,in=90] (0,0);
 
-        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
+        \draw[vlow!70!black!100, line width = 4pt, domain=0:350, smooth cycle, fill=vlow] plot (\x:1+rnd*0.5);
       \end{tikzpicture}
@@
            %\draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
-          \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
-          \draw [-,ultra thick, cyan] (0.9,4) to [out=290,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+          \draw [-,line width = 4pt, vhigh] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+          \draw [-,line width = 4pt, vhigh] (0.9,4) to [out=290,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
 
-          \draw [-,ultra thick, cyan] (-2.2,4.8) to [out=90,in=180] (-1.1,1.9) to [out=270,in=90] (0,0);
-          \draw [-,ultra thick, cyan] (-0.9,4) to [out=260,in=180] (-1.1,1.9) to [out=270,in=90] (0,0);
+          \draw [-,line width = 4pt, vhigh] (-2.2,4.8) to [out=90,in=180] (-1.1,1.9) to [out=270,in=90] (0,0);
+          \draw [-,line width = 4pt, vhigh] (-0.9,4) to [out=260,in=180] (-1.1,1.9) to [out=270,in=90] (0,0);
 
-          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
+          \draw[vhigh!70!black!100, line width = 4pt, domain=0:350, smooth cycle, fill=vhigh] plot (\x:1+rnd*0.5);
         \end{tikzpicture}
@@
         %   \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
-          \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
-          \draw [-,ultra thick, cyan] (0.9,4) to [out=290,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+        \draw[vlow!70!black!100, line width = 4pt, domain=0:350, smooth cycle, fill=vlow] plot (\x:1+rnd*0.5);
 
-          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
+        \draw [-,line width = 4pt, vlow] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+        \draw [-,line width = 4pt, vlow] (0.9,4) to [out=290,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
         \end{tikzpicture}
@@
           %\draw[step=1cm,gray,very thin] (-4,-4) grid (4,4);
-          \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
-          \draw [-,ultra thick, cyan] (0.9,4) to [out=290,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+          \draw [-,line width = 4pt, vhigh] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+          \draw [-,line width = 4pt, vhigh] (0.9,4) to [out=290,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
 
-          \draw [-,ultra thick, cyan] (2.9,3.4) to [out=290,in=40] (1.95,3);
-          \draw [-,ultra thick, cyan] (0.2,3.9) to [out=310,in=190] (1.25,3.2);
-          \draw [-,ultra thick, cyan] (1.6,4.8) to [out=290,in=85] (2.07,3.6);
+          \draw [-,line width = 4pt, vhigh] (2.9,3.4) to [out=290,in=40] (1.95,3);
+          \draw [-,line width = 4pt, vhigh] (0.2,3.9) to [out=310,in=190] (1.25,3.2);
+          \draw [-,line width = 4pt, vhigh] (1.6,4.8) to [out=290,in=85] (2.07,3.6);
 
-          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
+          \draw[vhigh!70!black!100, line width = 4pt, domain=0:350, smooth cycle, fill=vhigh] plot (\x:1+rnd*0.5);
         \end{tikzpicture}
@@
         %   \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
-          \draw [-,ultra thick, cyan] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
-          \draw [-, ultra thick, cyan] (0.9,4) to [out=290,in=0] (1.1,1.9);
-          \draw [-,line width=7pt, cyan] (1.1,1.9) to [out=270,in=90] (0,0);
+          \draw [-,line width = 4pt, vlow] (2.2,4.8) to [out=90,in=0] (1.1,1.9) to [out=270,in=90] (0,0);
+          \draw [-, line width = 4pt, vlow] (0.9,4) to [out=290,in=0] (1.1,1.9);
+          \draw [-,line width=4pt, vlow] (1.1,1.9) to [out=270,in=90] (0,0);
 
-          \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
+          \draw[vlow!70!black!100, line width = 4pt, domain=0:350, smooth cycle, fill=vlow] plot (\x:1+rnd*0.5);
         \end{tikzpicture}
@@
         % \draw[step=1cm,gray,very thin] (-4,-3) grid (4,4);
-        \draw [-,ultra thick, cyan] (2,3) to [out=180,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
-        \draw [-,ultra thick, cyan] (0.5,2.9) to [out=0,in=90] (1.1,1.9);
-        \draw [-, line width = 7pt, cyan] (1.1,1.9) to [out=270,in=90] (0,0);
-        \draw [-,ultra thick, cyan] (1.8, 2.1) to [out=290,in=0] (1,1.5);
+        \draw [-,line width = 4pt, vhigh] (2,3) to [out=180,in=0] (1.1,1.9) to [out=270,in=90] (0,0);        
+        \draw [-,line width = 4pt, vhigh] (0.5,2.9) to [out=0,in=90] (1.1,1.9);
+        \draw [-, line width = 8pt, vhigh] (1.1,1.9) to [out=270,in=90] (0,0);
+        \draw [-,line width = 4pt, vhigh] (1.8, 2.1) to [out=290,in=0] (1,1.5);
 
-        \draw [-,ultra thick, cyan] (-1,4) to [out=200,in=0] (-2,3) to [out=290,in=135] (-1.1,1.9);
-        \draw [-, line width = 7pt, cyan] (-1.1,1.9) to [out=270,in=90] (0,0);
-        \draw [-,ultra thick, cyan] (-0.5,2.9) to [out=250,in=250] (-1.1,1.9) to [out=270,in=90] (0,0);
-        \draw [-,ultra thick, cyan] (-1.8, 2.1) to [out=250,in=180] (-1,1.5);
+        \draw [-,line width = 4pt, vhigh] (-1,4) to [out=200,in=0] (-2,3) to [out=290,in=135] (-1.1,1.9);
+        \draw [-, line width = 8pt, vhigh] (-1.1,1.9) to [out=250,in=90] (0,0);
+        \draw [-,line width = 4pt, vhigh] (-0.5,2.9) to [out=250,in=250] (-1.06,1.95) to [out=250,in=70] (0,0);
+        \draw [-,line width = 4pt, vhigh] (-1.8, 2.1) to [out=250,in=180] (-1,1.5);
 
-        \draw[cyan, ultra thick, domain=0:350, smooth cycle, fill=cyan!70!black!100] plot (\x:1+rnd*0.5);
+        \draw[vhigh!70!black!100, line width = 4pt, domain=0:350, smooth cycle, fill=vhigh] plot (\x:1+rnd*0.5);
       \end{tikzpicture}

### 2019-01-15 manuscript/figures.Rmd
mention p values in fig 4 caption

@@
 ```{r 07_cor_mat_hmap, echo=FALSE, warning=FALSE, fig.cap="Correlation among connectivity metrics and selected lake characteristics.
-WS is the lake watershed extent whereas SWS is the lake subwatershed extent.
+Cell shading and color reflects the correlation coefficient value.
+Only coefficients accompanied by a significant p value < 0.05 are shown as text.
+Here, WS is the lake watershed extent whereas SWS is the lake subwatershed extent.
 Connectivity metrics are defined in Figure 2.", message=FALSE}

### 2019-01-15 scripts/05_result-stats.R
save plot to file

@@ -224,9 +224,13 @@ test <- nes_nws %>%
   mutate(retention_time_yr_manual = (1 / total_inflow) * volume) %>%
   # calculate p_total (p loading) from concentration and wrt
   mutate(tp_loading = p_total * 1000000) # kg to mg
-  
-plot(test$tp, test$tp_in)
-abline(0, 1)
+
+ggplot(data = test) + 
+  geom_point(aes(x = tp, y = tp_in)) + 
+  ylab("Inflow TP") + xlab("Lake TP") +
+  geom_abline(aes(slope = 1, intercept = 0))
+
+ggplot2::ggsave("../figures/tp-in_vs_tp-lake.png")
 
 plot(test$retention_time_yr, test$retention_time_yr_manual)
 abline(0, 1)

### 2019-01-19 manuscript/manuscript.Rmd
towards an initial Dockerfile and manuscript pdf

---
title: A Template for Two or One-Column Vignettes

liftr:
  maintainer: "Joseph Stachelek"
  email: "stachel2@msu.edu"
  from: "rocker/geospatial:latest"
  pandoc: true
  sysdeps: 
    - grass
  cran: 
    - LAGOSNE
    - brms
    - dplyr
    - tidyr
    - modelr
    - data.tree
    - ggplot2
    - tidybayes
    - cowplot
  remotes: 
    - "jsta/nhdR"
    - "jsta/spnetwork"
    - "jsta/streamnet"
    - "jsta/rgrass7sf"

# Use letters for affiliations
author:
  - name: Joseph Stachelek
    affiliation: a
  - name: Patricia A. Soranno
    affiliation: a
address:
  - code: a
    address: Institute of Smoke and Magic, University of Sometown, Sometown, XY, 12345

# Optional: line of arbitrary text with additional information.
# Could be used, for example, to mention the bibliographic info in a post-print.
# If not specified, defaults to "This version was compiled on \today"
#date_subtitle: Published in *Journal of Statistical Software*, 2018

# For footer text  TODO(fold into template, allow free form two-authors)
lead_author_surname: Stachelek and Soranno

# Place eg a DOI URL or CRAN Package URL here
doi_footer: "https://cran.r-project.org/package=YourPackage"

# Abstract
abstract: |
  Your abstract will be typeset here, and used by default a visually distinctive font.
  An abstract should explain to the general reader the major contributions of the article.

# Optional: Acknowledgements
acknowledgements: |
  This template package builds upon, and extends, the work of the excellent
  [rticles](https://cran.r-project.org/package=rticles) package, and both packages rely on the
  [PNAS LaTeX](http://www.pnas.org/site/authors/latex.xhtml) macros. Both these sources are
  gratefully acknowledged as this work would not have been possible without them.  Our extensions
  are under the same respective licensing term
  ([GPL-3](https://www.gnu.org/licenses/gpl-3.0.en.html) and
  [LPPL (>= 1.3)](https://www.latex-project.org/lppl/)).

# Optional: One or more keywords
keywords:
  - one
  - two
  - optional
  - keywords
  - here

# Paper size for the document, values of letterpaper and a4paper
papersize: letter

# Font size of the document, values of 9pt (default), 10pt, 11pt and 12pt
fontsize: 9pt

# Optional: Force one-column layout, default is two-column
#one_column: true

# Optional: Enables lineno mode, but only if one_column mode is also true
#lineno: true

# Optional: Enable one-sided layout, default is two-sided
#one_sided: true

# Optional: Enable section numbering, default is unnumbered
#numbersections: true

# Optional: Specify the depth of section number, default is 5
#secnumdepth: 5

# Optional: Skip inserting final break between acknowledgements, default is false
skip_final_break: true

# Optional: Bibliography 
bibliography: pinp
biblio-style: bioscience

# Optional: Enable a 'Draft' watermark on the document
watermark: true

# Customize footer, eg by referencing the vignette
footer_contents: "YourPackage Vignette"

# Produce a pinp document
output: pinp::pinp

# Required: Vignette metadata for inclusion in a package.
vignette: >
  %\VignetteIndexEntry{YourPackage-vignetteentry}
  %\VignetteKeywords{YourPackage, r, anotherkeyword}
  %\VignettePackage{YourPackage}
  %\VignetteEngine{knitr::rmarkdown}
---

## Introduction

This *pinp is not PNAS* template started when the introduction to
[Rcpp](http://dirk.eddelbuettel.com/code/rcpp.html) by \cite{cardilleCarbonWaterCycling2007} 
was converted into this updated
[Rcpp Introduction](https://eddelbuettel.github.io/pinp/Rcpp-introduction.pdf)
vignette.  It is based on the
[pnas_article](https://github.com/rstudio/rticles/tree/master/inst/rmarkdown/templates/pnas_article)
template of the wonderful [rticles](https://cran.r-project.org/package=rticles) package by
. The conversion from markdown to latex is facilitated by
[rmarkdown](https://cran.r-project.org/package=rmarkdown)
 and [knitr](https://cran.r-project.org/package=knitr)
\citep{cardilleCarbonWaterCycling2007}. The underlying LaTeX macros are from
[pnas.org](http://www.pnas.org/site/authors/latex.xhtml).

The remainder of the document carries over from the corresponding
[pnas_article](https://github.com/rstudio/rticles/tree/master/inst/rmarkdown/templates/pnas_article)
template document. but has been edited and updated to our use case.  A
few specific tips follow.  In general, for fine-tuning some knowledge
of LaTeX is helpful.

## Author Affiliations

Per common academic best practice, you can include your department,
institution, and complete address, with the ZIP/postal code, for each
author. Use lower case letters to match authors with institutions, as
shown in the example. Authors with an ORCID ID may supply this
information at submission.

## Document Options

We support several options via the YAML header

- Setting a DOI or URL footer, for example for the CRAN package URL,
  which is placed in the bottom-left footer of the title page and even pages;
- Setting a footer label, for example _YourPackage Vignette_ stating
  your package, which is placed in the bottom-right footer on odd
  pages;
- Setting a free-form author field used on the inside footer;
- Optional _Draft_ watermarking;
- Line of custom text in subtitle (`date_subtitle`) suitable to give publication info of the draft, e.g. journal name in a post-print.

## References

Here we differ from PNAS and suggest natbib. References will appear in
author-year form. Use `\citet{}`, `\citep{}`, etc as usual.

We default to the `jss.bst` style. To switch to a different bibliography
style, please use `biblio-style: style` in the YAML header.

## Inline R Code

The PNAS sample included a fixed PNG image here, but this document prefers
to show the results and embedding of _R_ code.

```{r figex, fig.width=3, fig.height=3, cache=TRUE, echo=TRUE, fig.cap="Narrow ggplot2 figure"}
library(ggplot2)
ggplot(mtcars, aes(wt, mpg)) +
    geom_point(size=3, aes(colour=factor(cyl))) +
    theme(legend.position="none")
```

Here we use a standard knitr bloc with explicit options for

- figure width and height (`fig.width`, `fig.height`), both set to three inches;
- whether the code is shown (`echo=TRUE`); and
- the caption (`fig.cap`) as shown above.

## Digital Figures

Markdown, Pandoc and LaTeX support `.eps` and `.pdf` files.

Figures and Tables should be labelled and referenced in the standard way
using the `\label{}` and `\ref{}` commands.

The R examples above show how to insert a column-wide
figure. To insert a figure wider than one column, please use the
`\begin{figure*}...\end{figure*}` environment.

One (roundabout) way of doing this is to _not_ actually plot a figure, but to
save it in a file as the following segment shows:

```{r densityPlot, echo=TRUE}
library(ggplot2)
p <- ggplot(data = midwest,
            mapping = aes(x = area,
                          fill = state,
                          color = state)) +
    geom_density(alpha = 0.3)
## save to file
suppressMessages(ggsave("densities.pdf", p))
```

This file is then included via standard LaTeX commands.

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.66\textwidth, height=3.5in]{densities} 
  \end{center}
  \caption{Wide ggplot2 figure}\label{fig}
\end{figure*}

## Typeset Code (But Do Not Run It)

We can also just show code.

```r
xx <- faithful[,"eruptions"]
fit <- density(xx)
plot(fit)
```

This simply used a pandoc bloc started and ended by three backticks,
with `r` as the language choice.  Similarly, _many_ other languages
can be typeset directly simply by relying on pandoc.

## Single column equations

Authors may use 1- or 2-column equations in their article, according to
their preference.

To allow an equation to span both columns, options are to use the
`\begin{figure*}...\end{figure*}` environment mentioned above for
figures, or to use the `\begin{widetext}...\end{widetext}` environment
as shown in equation \ref{eqn:example} below.

Please note that this option may run into problems with floats and
footnotes, as mentioned in the [cuted package
documentation](http://texdoc.net/pkg/cuted). In the case of problems
with footnotes, it may be possible to correct the situation using
commands `\footnotemark` and `\footnotetext`.

\begin{equation}
  \begin{aligned}
(x+y)^3&=(x+y)(x+y)^2\\
       &=(x+y)(x^2+2xy+y^2) \\
       &=x^3+3x^2y+3xy^3+x^3. 
       \label{eqn:example} 
  \end{aligned}
\end{equation}

<!-- pandoc writes all tables using longtable, which fails in 2-column mode

  Species                    CBS     CV     G3
  ----------------------- ------ ------ ------
  1\. Acetaldehyde           0.0    0.0    0.0
  2\. Vinyl alcohol          9.1    9.6   13.5
  3\. Hydroxyethylidene     50.8   51.2   54.0

  : Comparison of the fitted potential energy surfaces and ab initio
  benchmark electronic energy calculations

-->

### 2019-01-19 manuscript/manuscript.Rmd
fillin manuscript

@@
 ---
-title: A Template for Two or One-Column Vignettes
+title: Does freshwater connectivity influence phosphorus retention in lakes?
 
@@
   sysdeps: 
+    - apt-utils
     - grass
@@
   - code: a
-    address: Institute of Smoke and Magic, University of Sometown, Sometown, XY, 12345
+    address: Department of Fisheries and Wildlife, Michigan State University, 480 Wilson Rd., East Lansing, MI 48824, USA
 
@@
 # Place eg a DOI URL or CRAN Package URL here
-doi_footer: "https://cran.r-project.org/package=YourPackage"
+doi_footer: "https://doi.org/ZenodoDOI"
 
@@
 abstract: |
-  Your abstract will be typeset here, and used by default a visually distinctive font.
-  An abstract should explain to the general reader the major contributions of the article.
+  Lake water residence time and depth are known to be strong predictors of phosphorus (P) retention.
+However, there is substantial variation in P retention among lakes with the same depth and residence time.
+One potential explanatory factor for this variation is differences in freshwater connectivity of lakes (i.e.
+the type and amount of freshwater connections to a lake), which can influence watershed P trapping or the particulate load fraction of P delivered to lakes via stream connections.
+To examine the relationship between P retention and connectivity, we quantified several different measures of connectivity including those that reflect downstream transport of material (sediment, water, and nutrients) within lake-stream networks (lake-stream-based metrics) as well as those that reflect transport of material from hillslope and riparian areas adjacent to watershed stream networks (stream-based metrics).
+Because it is not always clear what spatial extent is appropriate for determining functional differences in connectivity among lakes, we compared connectivity metrics at two important spatial extents: the lake subwatershed extent and the lake watershed extent.
+We found that variation in P retention among lakes was more strongly associated with connectivity metrics measured at the broader lake watershed Fextent rather than metrics measured at the finer lake subwatershed extent.
+Our results suggest that both connectivity between lakes and streams as well as connectivity of lakes and their terrestrial watersheds influence P retention.
 
@@
 acknowledgements: |
-  This template package builds upon, and extends, the work of the excellent
-  [rticles](https://cran.r-project.org/package=rticles) package, and both packages rely on the
-  [PNAS LaTeX](http://www.pnas.org/site/authors/latex.xhtml) macros. Both these sources are
-  gratefully acknowledged as this work would not have been possible without them.  Our extensions
-  are under the same respective licensing term
-  ([GPL-3](https://www.gnu.org/licenses/gpl-3.0.en.html) and
-  [LPPL (>= 1.3)](https://www.latex-project.org/lppl/)).
+  This work was supported by the U.S.
+National Science Foundation’s Dynamics of Coupled Natural and Human Systems (CNH) e Program (award 1517823) and Macrosystems Biology Program (awards EF-1638679, EF-1638554, EF-1638539, and EF-1638550).
+PAS was also supported by the USDA National Institute of Food and Agriculture, Hatch project 1013544.
+We thank the following individuals for a friendly review of an earlier draft: K.S.
+Cheruvelil, I.M.
+McCullough, N.
+Smith, and A.
+Poisson.
 
@@
 keywords:
-  - one
-  - two
-  - optional
-  - keywords
-  - here
+  - phosphorus
+  - phosphorus retention
+  - aquatic connectivity 
+  - lake connectivity
+  - lakes
+  - Vollenweider model
 
@@
 # Customize footer, eg by referencing the vignette
-footer_contents: "YourPackage Vignette"
+footer_contents: "Connectivity and phosphorus retention"
 
@@
 
-This *pinp is not PNAS* template started when the introduction to
-[Rcpp](http://dirk.eddelbuettel.com/code/rcpp.html) by \cite{cardilleCarbonWaterCycling2007} 
-was converted into this updated
-[Rcpp Introduction](https://eddelbuettel.github.io/pinp/Rcpp-introduction.pdf)
-vignette.  It is based on the
-[pnas_article](https://github.com/rstudio/rticles/tree/master/inst/rmarkdown/templates/pnas_article)
-template of the wonderful [rticles](https://cran.r-project.org/package=rticles) package by
-. The conversion from markdown to latex is facilitated by
-[rmarkdown](https://cran.r-project.org/package=rmarkdown)
- and [knitr](https://cran.r-project.org/package=knitr)
-\citep{cardilleCarbonWaterCycling2007}. The underlying LaTeX macros are from
-[pnas.org](http://www.pnas.org/site/authors/latex.xhtml).
+<!-- Emails: JS, stachel2@msu.edu; PAS, soranno@msu.edu; -->
+<!-- ORCIDS: -->
+<!-- JS: https://orcid.org/0000-0002-5924-2464 -->
+<!-- PAS: https://orcid.org/0000-0003-1668-9271 -->
 
-The remainder of the document carries over from the corresponding
-[pnas_article](https://github.com/rstudio/rticles/tree/master/inst/rmarkdown/templates/pnas_article)
-template document. but has been edited and updated to our use case.  A
-few specific tips follow.  In general, for fine-tuning some knowledge
-of LaTeX is helpful.
+Lake phosphorus (P) retention is an important characteristic of lakes that can be used to predict P concentrations and to evaluate lake sensitivity to nutrient O loading and eutrophication (Alexander et al.
+2008; Milstead et al.
+2013).
+Specifically, P retention is an integrated measure of internal P losses including permanent sedimentation, biological uptake, and other processes that remove P from the water column \citep{chapra2008surface}.
+P retention has been well studied in lakes because P determines lake trophic status and downstream watershed yields (i.e.
+export to terminal lakes and coastal estuaries).
+Although previous studies have shown that lake P retention is related to water residence time (Vollenweider 1975), large uncertainties exist around this relationship (Brett and Benjamin 2007, Milstead et al.
+2013).
+These uncertainties can be large in lakes with intermediate water residence times, particularly compared to lakes with either extremely short or extremely long water residence times (Figure A1).
+For example, lakes with very long water residence times (on the order of a decade or longer) have complete or near complete P retention, while lakes with very short water residence times (on the order of days) have almost no P retention (Brett and Benjamin, 2007).
+The reason for the substantial uncertainty in lake P retention between these two extremes may be that predicting retention solely on the basis of water residence time does not capture many of the other factors and processes that affect P retention (Figure \ref{fig1}).
 
-## Author Affiliations
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.45\textwidth, height=3.5in,keepaspectratio]{../figures/01_conceptual_p-cycle_pt2} 
+  \end{center}
+  \caption{Major lake and watershed factors affecting lake P retention.
+Shaded symbols indicate factors typically considered in P retention models whereas open symbols indicate additional factors specific to the present study.
+Dashed lines indicate inferred relationships, which cannot be tested with available data, but are otherwise discussed herein.}\label{fig1}
+\end{figure}
 
-Per common academic best practice, you can include your department,
-institution, and complete address, with the ZIP/postal code, for each
-author. Use lower case letters to match authors with institutions, as
-shown in the example. Authors with an ORCID ID may supply this
-information at submission.
+One well-studied factor that has been shown to influence lake P retention is lake depth through its influence on internal processing of P loads (Søndergaard et al.
+2013; Vollenweider 1975).
+The mechanism for such an influence is that lake depth controls thermal stratification and material resuspension from the benthos.
+As a result, shallow lakes have a tendency to mix throughout the summer causing redistribution e of sedimented phosphorus throughout the mixed zone (Fee et al.
+1996).
+This mixing and redistribution of sedimented P often leads to tighter benthic-pelagic coupling and increased P recycling e (Cha et al.
+2013).
+Thus, depth is one example of a lake characteristic that is likely to influence P retention in concert with water residence time (Cheng et al.
+2010).
 
-## Document Options
+A primary tool for evaluating the influence of specific lake characteristics, like lake depth, on P retention is statistical phosphorus retention modelling.
+Although the form of such models is variable, many models estimate P retention as a function of water residence time and a parameter k that represents in-lake P decay (Chapra 2008, Vollenweider 1975).
+Many studies treat k as a constant global parameter (i.e., it has the same value for all lakes), which may be valid only for studies that consider small numbers of lakes in a limited geographic region, with similar characteristics.
+Few studies have modeled different k values based on lake or watershed characteristics, despite the many differences among lakes that likely influence their ability to process P (Cheng et al.
+2010).
 
-We support several options via the YAML header
+For example, there is evidence that the relative proportion of particulate versus dissolved P loads (hereafter, particulate load fraction), influences P retention in stream and wetland ecosystems (Jarvie et al.
+2011; Kronvang 1992; Russell et al.
+1998; Vanni et al.
+2001).
+However, evidence for particulate load fraction controls on P retention in lakes remains limited because of difficulties in tracking the fate of particulate loads after entering a lake (Brett and Benjamin 2007; Dillon and Molot 1996).
+Therefore, there is potential to further study particulate load Ffraction using proxies that may be closely related to it, such as the relative amounts of point and nonpoint nutrient sources to a lake subwatershed.
 
-- Setting a DOI or URL footer, for example for the CRAN package URL,
-  which is placed in the bottom-left footer of the title page and even pages;
-- Setting a footer label, for example _YourPackage Vignette_ stating
-  your package, which is placed in the bottom-right footer on odd
-  pages;
-- Setting a free-form author field used on the inside footer;
-- Optional _Draft_ watermarking;
-- Line of custom text in subtitle (`date_subtitle`) suitable to give publication info of the draft, e.g. journal name in a post-print.
+In general, point source inputs e to lakes are associated with increased dissolved P loads (Kronvang 1992; Russell et al.
+1998), whereas non-point source inputs to lakes, such as those in lake watersheds with high agricultural land e use cover, typically have higher particulate P loads (Carpenter et al.
+1998; Sharpley et al.
+1994).
+Exceptions to these generalizations have been observed in areas where increased dissolved P loading O occurs not as a result of point source nutrient inputs but rather as a result of non-point source runoff due to P saturated soils or legacy P release (Bennett and Carpenter 2001; Powers et al.
+2016).
+Despite the fact that particulate loads are usually related to non-point source inputs, the fraction of non-point source inputs that are in particulate form is highly variable and may depend on intra-annual flow variations as well as watershed erosion characteristics (Jarvie et al.
+2011).
+Furthermore, quantifying non-point source inputs at broad spatial scales is not commonly done due to logistical and sampling constraints (Guy et al.
+1994).
+As a result, studies often infer the relative amounts of particulate and dissolved loading from other available proxy data such as land-use cover (Ellison and Brett
+2006, Djodjic and Markensten 2018).
 
-## References
+Apart from land-use cover, another potential proxy for particulate load fraction entering lakes is the type and amount of freshwater connections to a lake, which we argue is easier to measure than other proxies, and could help to improve estimates of lake P retention, especially in lakes for which we lack P loading data (Figure 1).
+Although freshwater connectivity may be easy to measure from a logistical standpoint, there are still many ways to measure connectivity that likely represent different mechanisms of water and material flow (Figure 2).
+We broadly define and study two types of freshwater connectivity that correspond to either stream-based metrics or lake-stream-based metrics.
+First, lake-stream-based metrics measure the connections between a lake, other upstream lakes, and streams e in their watershed.
+This type of connectivity can be quantified by measuring the closest distance to an upstream stream-connected lake (Figure 2A), or by measuring the total upstream lake area e (Figure 2B).
+Second, stream-based metrics measure the connections between inflowing streams and their surrounding land whereby increasing stream connections lead to a greater abundance of land-water O interfaces and greater transport of material from hillslope and riparian areas adjacent to watershed stream networks (Figure 2C-E).
 
-Here we differ from PNAS and suggest natbib. References will appear in
-author-year form. Use `\citet{}`, `\citep{}`, etc as usual.
+In addition to variation among connectivity metrics and connectivity metric types, it is also not always clear which spatial extent is appropriate for determining functional differences in connectivity among lakes (Soranno et al.
+2015).
+Such information is needed to inform the design
+of regulatory frameworks balancing controls on cumulative nutrient transport along stream networks and controls on localized nutrient transport (Alexander et al.
+2008; Carpenter et al.
+1998; Withers and Jarvie 2008).
+To test the importance of different spatial extents, we examined connectivity metrics measured for both the lake subwatershed extent and the lake watershed extent (Figure 3).
+Here, the lake subwatershed extent includes the elements of the immediate watershed in the direct drainage of a lake whereas the lake watershed extent includes all of the elements in the entirety of the lake-stream network up to and including headwater streams (Figure 3).
+We propose that measures of freshwater connectivity are related to P retention in the following ways.
+First, some connectivity metrics reflect the proximity of terrestrial watershed areas to the stream network (Covino 2017).
+For example, lakes with a high watershed stream density should have increased particulate matter loading from terrestrial hillslope and riparian areas adjacent to watershed stream networks because particulate matter export is limited by overland distance (Gomi et al.
+2002).
+Second, connectivity metrics can reflect the configuration of lakes within lake-stream networks.
+e For example, lakes with upstream lakes in close proximity may receive P loads that have previously undergone in-lake processing whereby labile fractions have already been trapped in upstream lakes e (Cardille et al.
+2007).
+In contrast, lakes with more distant upstream lakes are more likely to receive the more labile fractions from terrestrial runoff that serve to increase P retention as opposed to receiving the more recalcitrant fractions that are resistant to biological uptake and are thus not retained.
+Although some connectivity metrics have an intuitive relation to P retention, it is not clear which specific measures of freshwater connectivity are important for transport of particulate matter.
+Therefore, our study is designed to examine and compare which measures of connectivity are more related to lake P retention.
+We addressed the above knowledge gaps by quantifying and comparing a range of freshwater connectivity measures at multiple spatial extents.
+Taken together, our suite of connectivity metrics reflect both freshwater connectivity in the direct drainage of lakes (i.e.
+the lake subwatershed extent) and freshwater connectivity of the entirety of the stream network up to and including watershed headwater areas (i.e.
+the lake watershed extent, Figure 3).
+Our motivation for measuring connectivity so many ways is that it is easy to measure connectivity of lakes with small watersheds situated at the beginning of lake chains but it is much more challenging to identify the type and extent of connectivity in larger, more complex lake networks.
+Another reason we examined relationships between P retention, multiple measures of connectivity, and multiple spatial extents is that many commonly used connectivity metrics merely reflect watershed size (spatial extent) rather than types of material transport or particulate load fraction (Leibowitz et al., 2018).
+Although lakes in larger watersheds have both a greater potential area from which to source particulate runoff and total phosphorus export from the watershed, we expect that delivery of sediment-bound phosphorus is dependent on connectivity-mediated trapping in the upstream watershed e (Prairie and Kalff 1986).
+We asked two questions in this  study: 1) Which measures of freshwater connectivity influence lake phosphorus retention?
+2) What e spatial extent of connectivity most strongly influences P retention?
+To answer these questions, we fit statistical P retention models in a Bayesian hierarchical framework following Cheng et O al.
+(2010) where 2 separate values of the k processing parameter were estimated for lakes with either high or low values of each connectivity metric.
+Using this approach, higher k values for a specific lake connectivity class indicates more extensive in-lake processing and higher P retention.
+We applied this model to a dataset of 129 lakes across a wide range of hydrologic, geologic, and climatic settings.
+We fit separate models using each combination of connectivity metric and spatial extent in an effort to determine whether P retention is more strongly controlled at the lake subwatershed extent or the lake watershed extent.
 
-We default to the `jss.bst` style. To switch to a different bibliography
-style, please use `biblio-style: style` in the YAML header.
+## Methods
 
-## Inline R Code
+### Dataset description
 
-The PNAS sample included a fixed PNG image here, but this document prefers
-to show the results and embedding of _R_ code.
+We used data on P retention, maximum depth, and water residence time from 129 lakes in the National Eutrophication Survey (USEPA 1975, Stachelek et al.
+2018).
+Mean annual P loading, P discharge, and P retention values in the National Eutrophication Survey (NES) dataset were calculated based on monthly sampling for P in tributary and outlet discharge points as well as
+any municipal waste discharges from 1972 to 1975.
+Here, P retention is a unitless value representing the fraction of incoming P loads.
+Sampling frequency for water discharge and residence time varied among o
+ lakes but details of these variations were not provided in the source
+rdataset (USEPA 1975, Stachelek et al. 2018). Estimates of water discharge and residence time in
+R
+the NES dataset represent normalized e mean flow estimates expected to occur during a period of
+average precipitation and hydrology v
+ (USEPA 1975). Water residence time for our study lakes
+iranged from 1 week to 17 years with an interquartile e range of 3 months to 1.8 years while P
+retention ranged from 0.06 to 0.99 with an w
+ interquartile range of 0.24 to 0.59 (Table 1).
+We supplemented the NES dataset with boundaries O for lake subwatersheds, as well as
+n
+estimates of stream density, upstream lake area, upstream lake connection(s), baseflow (an index
+ly
+of groundwater inputs), land-use cover, and other water quality measurements from the LAGOS-
+NE dataset (Table 1; Soranno et al. 2017). Our study lakes encompassed a wide range of land-
+use cover types and nutrient levels (Table 1). Although, lake subwatersheds were variable with
+respect to agricultural land use cover, we did not observe a strong relationship with lake P
+retention (Figure A2). On average, the water quality (total phosphorus, chlorophyll
+concentration, and Secchi depth) of the lakes in our study are similar to other US lakes as
+measured by the stratified random sampling design of the National Lakes Assessment (NLA) lake population (USEPA 2016). However, our lakes are substantially larger and deeper than most
+NLA lakes (Figure A3).
+We restricted the lakes in the study to those located within the footprint of LAGOS-NE
+which includes lakes located in 17 northeastern and midwestern US states (Soranno et al. 2017).
+We excluded lakes from our analysis if they had a surface area of greater than 1000 km2 or a
+surface area of less than 0.1 km2. We also excluded lakes if they had a maximum depth of greater
+than 70 m, lacked upstream surface water connections, or had one of the North American Great
+Lakes in its upstream watershed. A total of 129 out of 236 NES lakes met each of these selection criteria.
 
-```{r figex, fig.width=3, fig.height=3, cache=TRUE, echo=TRUE, fig.cap="Narrow ggplot2 figure"}
-library(ggplot2)
-ggplot(mtcars, aes(wt, mpg)) +
-    geom_point(size=3, aes(colour=factor(cyl))) +
-    theme(legend.position="none")
-```
+### Connectivity metrics and spatial extents
 
-Here we use a standard knitr bloc with explicit options for
+In addition to data from the NES and  LAGOS-NE datasets, we calculated several connectivity
+imetrics that we expected would be related e to lake P retention (Figure 2). Some of these metrics
+were stream-based with the goal of capturing w
+ aspects of the configuration of each lakes’
+upstream surface water network (Figure 2C-D). In particular, O we chose metrics that would
+n
+quantitatively approximate network complexity under the assumption that highly complex
+ly
+networks are also low connectivity networks. This assumption is supported by the findings of
+stream network simulations where increased network complexity leads to increased network
+resistance and ultimately decreases in network connectivity (Rodriguez-Iturbe and Rinaldo
+2001). In addition to stream-based metrics, we calculated lake-stream-based metrics that we
+expected would reflect the likelihood of P trapping in upstream lakes prior to arriving at a given
+focal lake via tributary flow (Figure 2A, 2B). A simple metric that captures this likelihood is the
+presence (or absence) of an upstream lake (greater than 4 ha) which we define as “lake
 
-- figure width and height (`fig.width`, `fig.height`), both set to three inches;
-- whether the code is shown (`echo=TRUE`); and
-- the caption (`fig.cap`) as shown above.
+connection” (Fergus et al. 2017). In addition to lake connection, we calculated related metrics
+such as total upstream lake area and the network distance to the closest upstream lake.
+To examine the importance of spatial extent relative to our connectivity metrics, we
+calculated each metric at multiple extents (Figure 3). First, we calculated connectivity metrics at
+the scale of individual lake subwatersheds. We defined a lake subwatershed as the area draining
+into a particular lake exclusive of any upstream areas that drain into a lake greater than or equal
+to 10 ha (0.1 km2). Next, we calculated connectivity metrics at the scale of entire upstream lake
+networks (lake watershed extent). We defined a lake watershed as the area draining into any part
+Fof the upstream network o
+ irrespective of the presence or absence of upstream lakes (Figure 3).
+rAll connectivity metrics were calculated using the high-resolution National Hydrography
+R
+Dataset (NHD) as a primary input (USGS e 2018). Average link length was calculated as the total
+stream length in a given watershed divided v
+ by the number of stream reaches after dissolving
+i(removing) any network points that do not e occur at a stream junction. Stream density was
+calculated as the length of all streams in the w
+ watershed (minus artificial lines through lakes)
+expressed in units of meters per hectare. Upstream lake O area was calculated as the sum of the
+n
+lake area in the upstream watershed expressed in square meters. Stream order ratio was defined
+ly
+as the number of headwater (first-order) streams in the upstream watershed of the focal lake
+divided by the total number of higher order (> 1) streams (Barbera and Rosso 1989). Closest
+distance to an upstream lake was defined as the shortest path-distance (rather than the straight-
+line distance) to a lake upstream from the focal lake.
+We calculated all connectivity metrics and lake watershed extents using the streamnet
+and nhdR R packages respectively (Stachelek 2018a, Stachelek 2018b). The algorithms in the
+streamnet package use the sf R package (Pebesma 2018) as well as the v.net and v.stream.order modules (Jasiewicz and Metz 2011) included in GRASS GIS (GRASS Development Team
+2017). All processed connectivity data and code are available at [Zenodo DOI].
 
-## Digital Figures
+### Modelling lake P retention
 
-Markdown, Pandoc and LaTeX support `.eps` and `.pdf` files.
+We modelled lake total phosphorus retention (hereafter, P retention) using the Vollenweider equation that models P retention as a function of water residence time and a parameter (k)
+conceptually representing in-lake P decay (Chapra 2008, Vollenweider 1975). Although there are
+several variants of this basic equation, we selected a 2-parameter form (equation 1) that has been
+Fshown to have good performance o
+ in multiple cross-sectional studies (Brett and Benjamin 2007,
+rCheng et al. 2010):
+R
+Ri = 1 ― 1 + 1
+ ktx
+ i
+ e Eq. 1
+v
+where Ri is P retention as a fraction of P inputs, i $\tau$ is water residence time, k is a unitless
+eparameter representing in-lake P decay, and w
+ x is a unitless parameter representing P export via
+hydrologic flushing. Here, higher values of k are associated with greater integrated P losses from
+Osedimentation and biological uptake resulting in greater P retention. Note that Eq 1 does not
+n
+include a recycling term. Therefore, our results represent net l P retention (as opposed to gross P
+y
+retention) under a steady state assumption where lakes are at equilibrium with respect to
+recycling (Vollenweider 1975). Note that although some forms of the Vollenweider equation use
+P loading as a predictor variable, it does not appear in Eq 1. The reason for this is two-fold. First,
+estimates of P loading are more difficult to obtain than estimates of water residence time and our
+aim was to develop a model than can be widely applied to lakes for which we lack detailed data
+on P loading. Second, loading based model forms have been shown to be mathematically
+equivalent to water residence time based model forms (Brett and Benjamin 2008).
+We used the model described by Eq 1 to compare lake P retention in lakes with different
+connectivity by fitting the model in two ways. First, we modelled the overall relationship
+between P retention and water residence time for all lakes in our dataset (global model). Second,
+we fit hierarchical versions of Eq. 1 where k was modelled separately (kj) as a function of a
+binary sub-population indicator gi denoting membership in one of two lake classes formed on the
+basis of specific connectivity metrics (or lake depth) and specific spatial extents:
+1
+Ri = 1 ―
+ 1 + kjtxi
+ F Eq. 2
+o
+kj = gi
+ rwhere greater differences in k between R
+ the two groups indicate greater support for a connectivity
+eeffect on P retention. Prior to model fitting, we examined the bivariate relationships between
+v
+each connectivity metric, water residence i time, P loading, and other factors related to P retention
+eusing Pearson’s correlation coefficients. The w
+ purpose of this exercise was twofold, to determine
+the potential for collinearity among any of the variables in Eq 2 and to identify any relationships
+Obetween P retention, water residence time, and other watershed and lake characteristics that were
+n
+not included in our model. As only one connectivity metric was l used to define g for each model
+y
+we did not use the results of this exercise to exclude variables from further investigation. We
+quantified the relative support for an effect of each connectivity metric on P retention in more
+detail by calculating the difference in the median value of the P decay parameter k between
+groups (i.e. $\delta$k). We used these median k values along with median estimates of x to determine
+how differences in k translated to differences in P retention (Eq 2). We judged significance by
+whether or not differences in group-wise P retention were greater than the measurement
+precision of P retention (> 0.01).
 
-Figures and Tables should be labelled and referenced in the standard way
-using the `\label{}` and `\ref{}` commands.
+We fit all models in a Bayesian framework using the non-linear extension to the brms
+package to interface with the Stan statistical program (Burkner 2017, Stan Development Team
+2017). In both models, we set a semi-informative prior on k and x of N(1.3, 0.1) and N(0.45, 0.1)
+respectively. These priors were based on the confidence intervals presented in Brett and
+Benjamin (2007) and qualitatively matched those used by Cheng et al. (2010). We used the
+default settings of brms and rstan to generate posterior estimates using four chains of 4,000
+iterations each with no thinning and initial parameter values drawn from a uniform distribution
+bounded between -2 and 2. We also used the brms package for model evaluation by computing a
+FBayesian R2 following o
+ the method of Gelman et al. (2017).
 
-The R examples above show how to insert a column-wide
-figure. To insert a figure wider than one column, please use the
-`\begin{figure*}...\end{figure*}` environment.
+### Lake connectivity classes
 
-One (roundabout) way of doing this is to _not_ actually plot a figure, but to
-save it in a file as the following segment shows:
+Our lake connectivity classes were formed by dividing the lake dataset into two classes for each
+iconnectivity metric based on the bivariate e relationship between each metric and P retention. Prior
+studies have used a similar binary splitting w
+ approach to examine the effect of various exogenous
+factors on lake P retention (Cheng et al. 2010; Shimoda O and Arhonditsis 2015). We determined
+n
+splitting criteria for each metric from the results of a random forest procedure incorporating
+ly
+conditional inference trees (ctree, Hothorn and Zeileis 2015). This procedure creates binary splits
+of the independent variables (i.e. each of the connectivity metrics), which are recursively
+repeated to find the split that maximizes association with the dependent variable (P retention).
+The advantage of the ctree technique over the more typical classification-regression tree (CART)
+technique is that tree growth stopping rules are pre-specified (Hothorn et al., 2006). As a result,
+some of subjectivity associated with post-hoc tree pruning is avoided.
 
-```{r densityPlot, echo=TRUE}
-library(ggplot2)
-p <- ggplot(data = midwest,
-            mapping = aes(x = area,
-                          fill = state,
-                          color = state)) +
-    geom_density(alpha = 0.3)
-## save to file
-suppressMessages(ggsave("densities.pdf", p))
-```
+## Results
 
-This file is then included via standard LaTeX commands.
+### Interactions between connectivity, hydrology, and P loading
 
-\begin{figure*}
-  \begin{center}
-    \includegraphics[width=0.66\textwidth, height=3.5in]{densities} 
-  \end{center}
-  \caption{Wide ggplot2 figure}\label{fig}
-\end{figure*}
+We examined the bivariate relationships between connectivity, water residence time, P loading and other factors related to P retention to determine the potential for strong relationships among
+any of the variables which were not accounted for by our model structure (Eq 2, Figure 4). We
+found evidence for some relationships among these variables, but none that suggest either
+redundancy among connectivity metrics or that otherwise limit our ability to infer relationships
+with P retention (Figure 4). For example, the Pearson correlation (r) between water residence
+Ftime and stream density, o
+ which is implicitly accounted for in our model structure, was 0.29 (p <
+r0.05). In contrast, the correlation between water residence time and upstream lake area, which is
+R
+unaccounted for in our model structure, e was only 0.10 (p > 0.05). Note that interactions between
+connectivity metrics and water residence v
+ time are accounted for in our hierarchical model
+istructure because Eq. 2 uses a global coefficient e x for water residence time that is estimated
+separately from the hierarchical and connectivity-dependent w
+ P decay coefficient k. This is
+conceptually similar to fitting the k-connectivity-P retention O relationship to the residuals of the
+n
+water residence time to P retention relationship. Perhaps surprisingly, we did not observe strong
+ly
+correlations between P loading and water residence time (r = 0.13, p > 0.05) or between lake
+depth and most connectivity metrics (r < 0.17). This suggests that our P retention results are not
+confounded by variations in lake depth, by interactions between connectivity and P loading, or
+by interactions between water residence time and P loading.
+A secondary purpose of examining the bivariate relationships between connectivity,
+water residence time, P loading and other factors related to P retention was to determine if our
+connectivity metrics were related to each other such that they provide similar information. With the exception of stream density and baseflow (r = -0.52, p < 0.05), correlations among
+connectivity metrics were low and of a similar magnitude as the correlations between
+connectivity metrics and water residence time (0.10 < r < 0.29). The strongest correlation
+between any connectivity metric or lake characteristic was upstream lake area and lake
+watershed area (r = 0.77, p < 0.05).
+We observed notably strong correlations between P loading and several lake
+characteristics not accounted for in Eq 2. These include the correlation between P loading and
+lake watershed area (r = 0.62, p < 0.05) as well as the correlation between P loading and lake
+Fsubwatershed area (r = o
+ 0.76, p < 0.05). In addition, the correlation between P loading and
+rupstream lake area was quite strong (r = 0.52, p < 0.05). Despite strong correlations between P
+R
+loading, watershed area, and upstream e lake area, we did not observe a strong correlation between
+P loading and P retention (r = 0.15, p > 0.05). Notably, this correlation was much weaker than the correlation between water residence time e and P retention (r = 0.44, p > 0.05). Our
+observation that the correlation between P w
+ retention and P loading was not appreciably stronger
+than correlations between P retention and our connectivity O metrics suggests that our estimates of
+n
+connectivity metric effects on P retention are not confounded by interactions between water
+ly
+residence time and P loading.
+Although we did not observe strong correlations among connectivity metrics, we found
+that lakes with similar connectivity metric values, were spatially clustered (Figure 5). In
+particular, we found that lakes were concentrated in either the southern or northern portions of
+our study area depending on their connectivity metric value (Figure 5). This observation is
+consistent with the findings of Fergus et al. (2017) that lakes in the northern portion of our study area have distinct freshwater connectivity as compared to lakes in the southern portion of our
+study area.
 
-## Typeset Code (But Do Not Run It)
+### Effects of connectivity on P retention
 
-We can also just show code.
+We found that freshwater connectivity metrics were associated with lake P retention (Figure 6,
+7). Across all connectivity metrics except stream order ratio, we found that the P decay
+coefficient k and thus P retention was associated with whether a lake had a high or low value of
+each connectivity metric. These findings matched our expectations in several ways. Most
+Fnotably, lakes with shorter o
+ average link lengths had higher P retention relative to lakes with
+rlonger average link lengths. In addition, lakes with less upstream lake area had higher P retention
+R
+than lakes with more upstream lake e area (Figure 6, 7).
+We found that some connectivity v
+ metrics were more strongly related to P retention than
+iothers. For example, the model R2 for network e average link length was higher (R2 = 0.41) than
+the global model (R2 = 0.34). For other connectivity w
+ metrics, such as network stream order ratio,
+goodness-of-fit (R2 = 0.36) was very similar to the global O model (R2 = 0.34). Model fit for other
+n
+connectivity metrics was in between these two extremes (0. 36 < R2 < 0.41). Overall, we found
+ly
+that all hierarchical models had at least a marginally better fit to the water residence time versus
+P retention relationship than a global model which does not account for connectivity (Figure 6).
+Although we found a discernable effect of connectivity metrics on lake P retention, the
+somewhat modest improvements in model fit may be due to the fact that water residence time
+remains a dominant effect even after accounting for freshwater connectivity.
 
-```r
-xx <- faithful[,"eruptions"]
-fit <- density(xx)
-plot(fit)
-```
+### Comparison across connectivity metrics and spatial extent
 
-This simply used a pandoc bloc started and ended by three backticks,
-with `r` as the language choice.  Similarly, _many_ other languages
-can be typeset directly simply by relying on pandoc.
+Differences in P retention among lakes with different connectivity metric values was reflected in
+differences among connectivity class-specific values of the P decay parameter k (Figure 7). The
+connectivity metric that had the most effect on k was average link length (Table 2). For instance,
+hierarchical models fit with the average link length metric had a median effect size of 0.23 and
+0.05 for k and P retention respectively (Table 2), which means that for this metric, lakes with
+shorter average link lengths retained 4.7 to 4.9 % more P than lakes with longer average link
+lengths. The influence of lake-stream-based connectivity metrics on lake P retention was similar
+to stream-based connectivity metrics (Figure 7). This suggests that both lake-stream-based
+Fconnectivity between lakes o
+ and streams as well as stream-based connectivity of lakes and their
+rterrestrial watersheds influence P retention (Figure 2).
+R
+We found that connectivity metrics e measured at the lake watershed extent were more
+strongly associated with P retention v
+ than metrics measured at the lake subwatershed extent
+i(Table 2, Figure 7). Specifically, the metrics e that had the strongest association with P retention
+such as average link length ($\delta$k = 0.23), closest w
+ lake distance ($\delta$k = 0.22), and stream density ($\delta$k
+= 0.20) also had a stronger association at the lake watershed O extent rather than at the lake
+n
+subwatershed extent (Table 2, Figure 7). An exception to this pattern was observed with the
+ly
+baseflow connectivity metric where although greater differences at the lake subwatershed extent
+were more strongly associated with P retention, the sign of the effect was variable depending on
+measurement extent (i.e. the value of the P decay parameter was positively related to
+connectivity metric values at the subwatershed extent but was negatively related at the watershed
+extent). For several connectivity metrics, we judged that differences in P decay among lakes with
+either low or high connectivity metric values were not significant because they translated to
+differences in P retention that were less than measurement precision (Table 2).
 
-## Single column equations
+## Discussion
+Although prior studies have found that lake P retention is related to water residence time (Brett
+and Benjamin, Cheng, et al. 2010, Vollenweider 1975), there is substantial variation around this
+relationship, particularly at intermediate water residence times. We found that some of this
+remaining variation could be explained using a hierarchical modelling framework that accounts
+for differences in freshwater connectivity among lakes. Although we found that the magnitude of
+this effect depends on the specific connectivity metric, our results are consistent with the findings of previous studies o
+ showing that connectivity metrics are associated with differences in
+rlake carbon input fluxes and differences in lake nitrogen output fluxes (Cardille et al. 2007;
+R
+Schmadel et al. 2018). We also found e important differences in the association between
+connectivity metrics and P retention v
+ at different measurement extents. Specifically, we found
+ithat P retention was more strongly associated e with connectivity measured at the broader lake
+watershed extent rather than connectivity measured w
+ at the finer lake subwatershed extent.
 
-Authors may use 1- or 2-column equations in their article, according to
-their preference.
+### Connectivity and P retention
 
-To allow an equation to span both columns, options are to use the
-`\begin{figure*}...\end{figure*}` environment mentioned above for
-figures, or to use the `\begin{widetext}...\end{widetext}` environment
-as shown in equation \ref{eqn:example} below.
+We found that differences in P retention among lake connectivity classes was influenced by
+specific connectivity metrics including average link length, closest lake distance, and stream
+density (Table 2, Figure 7). Indeed, these metrics were more strongly associated with P retention
+than covariates typically used in statistical P retention models (e.g. lake depth, Figure 1). Note
+that we were able to examine the influence of specific metrics as separate effects apart from
+water residence time because our model structure treats them as hierarchical coefficients on the P
+decay parameter k. As a result, although water residence time remains the dominant effect on
+lake P retention, we were able to estimate the specific influence of each metric in a way that is
+not possible using integrated water residence time and connectivity metrics such as watershed
+transport capacity (Fraterrigo and Downing 2008).
+Several of the connectivity metrics that were most strongly associated with P retention
+were weakly correlated with watershed size (Figure 4). The weak nature of these correlations are
+consistent with the mixed results of prior studies linking watershed size to lake processes. For
+example, Zimmer and McGlynn (2018) found that carbon export was related to watershed size,
+but Smith et al. (2003) found that the nitrogen flux was not strongly related to watershed size.
+FTaken together, our results o
+ and the results of prior studies suggest that watershed size and lake
+rdepth alone may not always reflect functional differences in potential material transport. One
+R
+consequence of a correlation between e connectivity metrics and watershed size is that metrics
+derived from watershed size, such as v
+ catchment to lake area ratio, are also likely to be associated
+iwith connectivity. Catchment to lake area e ratio in particular has been previously used as an
+approximation or proxy of water residence w
+ time (Rasmussen et al. 1989; Sobek et al. 2007).
+Although our results differ from those of Soranno et al.
+(2015) who found that the presence of an upstream lake connection was not strongly associated with catchment to lake area ratio, our results suggest that catchment to lake area ratio likely incorporates some connectivity information and caution is needed before using it as a proxy for water residence time.
+Another lake characteristic that was strongly related to watershed size was P loading. In
+particular, positive correlations between P loading and watershed size are consistent with the
+idea that lakes in larger watersheds receive greater P loading (Prairie and Kalff 1986). A related
+observation is that the correlation between P loading and upstream lake area was positive. This
+can be explained by the fact that larger watersheds often have greater numbers of lakes nested within them (Zhang et al. 2012). Another notable result is that we observed a weaker correlation
+between P loading and watershed area relative to the correlation between P loading and
+subwatershed area. One explanation for this result is that land-use cover at the finer lake
+subwatershed extent has more of an influence on P loading than land-use cover at the broader
+lake watershed extent (Soranno et al. 2015).
 
-Please note that this option may run into problems with floats and
-footnotes, as mentioned in the [cuted package
-documentation](http://texdoc.net/pkg/cuted). In the case of problems
-with footnotes, it may be possible to correct the situation using
-commands `\footnotemark` and `\footnotetext`.
+### Relative importance of connectivity spatial extent
 
-\begin{equation}
-  \begin{aligned}
-(x+y)^3&=(x+y)(x+y)^2\\
-       &=(x+y)(x^2+2xy+y^2) \\
-       &=x^3+3x^2y+3xy^3+x^3. 
-       \label{eqn:example} 
-  \end{aligned}
-\end{equation}
+One of the challenges in quantifying the effect of freshwater connectivity on lake P retention is that it is not always known what spatial extent of the watershed is functionally connected to a lake.
+We found that connectivity at the broader lake watershed extent rather than connectivity at the finer lake subwatershed extent was e more strongly associated with differences in lake P
+retention. In addition, we found that v
+ individual characteristics such as lake depth (or more
+idiscrete measures of connectivity such as e the presence of an upstream lake) were more strongly
+associated with P retention than any of the w
+ other connectivity metrics measured at the lake
+subwatershed extent (Table 2). These findings contrast O with Soranno et al. (2015) who examined
+n
+the association between lake nutrient concentrations (as opposed to retention) and land-use
+ly
+measured at varying spatial extents and found that measurements at the finer lake subwatershed
+extent rather than measurements at the broader lake watershed extent were more strongly
+associated with lake nutrient concentrations. One explanation for the difference between our
+results and those of Soranno et al. (2015) is that connectivity metrics may reflect long-range
+watershed processes to a greater degree than land-use cover. An alternative explanation is that
+controls of lake P retention may differ compared to controls on lake P concentration.
 
-<!-- pandoc writes all tables using longtable, which fails in 2-column mode
+### How connectivity metrics may influence P retention
 
-  Species                    CBS     CV     G3
-  ----------------------- ------ ------ ------
-  1\. Acetaldehyde           0.0    0.0    0.0
-  2\. Vinyl alcohol          9.1    9.6   13.5
-  3\. Hydroxyethylidene     50.8   51.2   54.0
+Prior studies at regional extents have shown that P retention in streams and rivers is largely determined by the fate of the particulate load fraction (Cushing et al.
+1994; Kronvang 1992; Russell et al.
+1998; Vanni et al.
+2001).
+For instance, the findings of Jarvie et al.
+(2011) show that riverine P loads can be controlled by nonpoint-source P delivery of particulate P.
+Therefore, it stands to reason that P retention in lakes may also be largely determined by the fate of the particulate load fraction.
+However, in the context of our broad-scale study it is difficult to examine this relationship because although we have estimates of nonpoint versus point source loading we do not have explicit estimates of particulate load fraction for large numbers of lakes.
+Unfortunately, we cannot use nonpoint source loading as a direct proxy for particulate load fraction because the two quantities do e not have a consistent relationship.
+For example, Russell et al.
+(1998) report that the particulate phosphorus fraction of nonpoint source loads can be anywhere between 62 - 90% while Djodjic e and Markensten (2018) report that this fraction can be anywhere between 33 and 80%.
+This may explain why prior broad scale studies that estimate lake P retention have not attempted to estimate separate effects of particulate versus dissolved loading (Alexander et al.
+2008, Brett and Benjamin 2008).
 
-  : Comparison of the fitted potential energy surfaces and ab initio
-  benchmark electronic energy calculations
+We developed a conceptual model that places particulate load fraction in context with other processes affecting P retention (Figure 1).
+We expected that both land-stream and stream-lake connectivity influences how much particulate P is transported into lakes, which in turn affects their P retention.
+This expectation is supported by the findings of Cushing et al.
+(1994) as well as Guy et al.
+(1994) showing that particulate P can be transported beyond the direct drainage from stream-adjacent hillslopes.
 
--->
+Despite our inability to test such differential transport processes across many lake watersheds at broad scales, we note that such processes are indirectly supported by our finding that connectivity metrics are associated with lake P retention.
+For example, differential transport of particulate matter whereby barriers to flux and differences in drainage path configuration only become apparent beyond fine spatial extents may explain why we observed stronger association of P retention with metrics measured at the broader lake watershed extent rather than metrics measured at the finer scale lake subwatershed extent.
+Another finding consistent with differential transport of particulate P is our observation that average link length, which approximates stream network structure and along-stream transport potential (Barbera and Rosso 1989), was one of the more strongly associated metrics with lake P retention.
+Finally, it is notable that our stream density metric was influential at thee lake watershed extent but not at the lake subwatershed extent.
+Given that the stream density metric captures the average distance or drainage potential between any streams in the network and their e adjacent hillslopes, floodplains, and wetlands (see Leibowitz et al.
+2018), this suggests that differences in terrestrial runoff of particulate matter from hillslope and riparian areas are likely to be important for P retention.
+
+Taken together, our findings are consistent with the idea that both connectivity between lakes and streams as well as connectivity of lakes and their terrestrial watersheds affect lake P retention.
+This conclusion matches that of prior studies showing that aquatic transport of phosphorus and nitrogen at the sub-continental scale is strongly controlled by processes affecting along-stream flux such as reservoir trapping (Alexander et al.
+2008, Schmadel et al.
+2018).
+
+## Conclusion
+
+We provide evidence that freshwater connectivity has an effect on lake P retention and that connectivity metrics measured at the broader lake watershed extent more strongly captures functional differences in the effect of connectivity on P retention among lakes compared to connectivity metrics measured at the finer lake subwatershed extents.
+Furthermore, our results suggest that lake P retention is related to both connectivity of lakes and streams as well as connectivity of lakes and their terrestrial watersheds.
+Taken together, our findings suggest that a broader network perspective would be useful for the design of regulatory frameworks and the development of best management practices focused on eutrophication, given the importance of lake P retention in determining the trophic state of lakes.
+Specifically, our findings highlight the need to consider cumulative network effects of P transport in addition to localized transport mechanisms.

### 2019-01-19 manuscript/manuscript.Rmd
format equations

@@
   from: "rocker/geospatial:latest"
-  pandoc: true
+  pandoc: false
   sysdeps: 
@@
 1994).
-As a result, studies often infer the relative amounts of particulate and dissolved loading from other available proxy data such as land-use cover (Ellison and Brett
-2006, Djodjic and Markensten 2018).
+As a result, studies often infer the relative amounts of particulate and dissolved loading from other available proxy data such as land-use cover (Ellison and Brett 2006, Djodjic and Markensten 2018).
 
@@
 2015).
-Such information is needed to inform the design
-of regulatory frameworks balancing controls on cumulative nutrient transport along stream networks and controls on localized nutrient transport (Alexander et al.
+Such information is needed to inform the design of regulatory frameworks balancing controls on cumulative nutrient transport along stream networks and controls on localized nutrient transport (Alexander et al.
 2008; Carpenter et al.
@@
 Here, the lake subwatershed extent includes the elements of the immediate watershed in the direct drainage of a lake whereas the lake watershed extent includes all of the elements in the entirety of the lake-stream network up to and including headwater streams (Figure 3).
+
 We propose that measures of freshwater connectivity are related to P retention in the following ways.
@@
 Therefore, our study is designed to examine and compare which measures of connectivity are more related to lake P retention.
+
 We addressed the above knowledge gaps by quantifying and comparing a range of freshwater connectivity measures at multiple spatial extents.
@@
 Another reason we examined relationships between P retention, multiple measures of connectivity, and multiple spatial extents is that many commonly used connectivity metrics merely reflect watershed size (spatial extent) rather than types of material transport or particulate load fraction (Leibowitz et al., 2018).
-Although lakes in larger watersheds have both a greater potential area from which to source particulate runoff and total phosphorus export from the watershed, we expect that delivery of sediment-bound phosphorus is dependent on connectivity-mediated trapping in the upstream watershed e (Prairie and Kalff 1986).
+Although lakes in larger watersheds have both a greater potential area from which to source particulate runoff and total phosphorus export from the watershed, we expect that delivery of sediment-bound phosphorus is dependent on connectivity-mediated trapping in the upstream watershed (Prairie and Kalff 1986).
+
 We asked two questions in this  study: 1) Which measures of freshwater connectivity influence lake phosphorus retention?
@@
 2018).
-Mean annual P loading, P discharge, and P retention values in the National Eutrophication Survey (NES) dataset were calculated based on monthly sampling for P in tributary and outlet discharge points as well as
-any municipal waste discharges from 1972 to 1975.
+Mean annual P loading, P discharge, and P retention values in the National Eutrophication Survey (NES) dataset were calculated based on monthly sampling for P in tributary and outlet discharge points as well as any municipal waste discharges from 1972 to 1975.
 Here, P retention is a unitless value representing the fraction of incoming P loads.
-Sampling frequency for water discharge and residence time varied among o
- lakes but details of these variations were not provided in the source
-rdataset (USEPA 1975, Stachelek et al. 2018). Estimates of water discharge and residence time in
-R
-the NES dataset represent normalized e mean flow estimates expected to occur during a period of
-average precipitation and hydrology v
- (USEPA 1975). Water residence time for our study lakes
-iranged from 1 week to 17 years with an interquartile e range of 3 months to 1.8 years while P
-retention ranged from 0.06 to 0.99 with an w
- interquartile range of 0.24 to 0.59 (Table 1).
-We supplemented the NES dataset with boundaries O for lake subwatersheds, as well as
-n
-estimates of stream density, upstream lake area, upstream lake connection(s), baseflow (an index
-ly
-of groundwater inputs), land-use cover, and other water quality measurements from the LAGOS-
-NE dataset (Table 1; Soranno et al. 2017). Our study lakes encompassed a wide range of land-
-use cover types and nutrient levels (Table 1). Although, lake subwatersheds were variable with
-respect to agricultural land use cover, we did not observe a strong relationship with lake P
-retention (Figure A2). On average, the water quality (total phosphorus, chlorophyll
-concentration, and Secchi depth) of the lakes in our study are similar to other US lakes as
-measured by the stratified random sampling design of the National Lakes Assessment (NLA) lake population (USEPA 2016). However, our lakes are substantially larger and deeper than most
-NLA lakes (Figure A3).
-We restricted the lakes in the study to those located within the footprint of LAGOS-NE
-which includes lakes located in 17 northeastern and midwestern US states (Soranno et al. 2017).
-We excluded lakes from our analysis if they had a surface area of greater than 1000 km2 or a
-surface area of less than 0.1 km2. We also excluded lakes if they had a maximum depth of greater
-than 70 m, lacked upstream surface water connections, or had one of the North American Great
-Lakes in its upstream watershed. A total of 129 out of 236 NES lakes met each of these selection criteria.
+Sampling frequency for water discharge and residence time varied among lakes but details of these variations were not provided in the source dataset (USEPA 1975, Stachelek et al.
+2018).
+Estimates of water discharge and residence time in the NES dataset represent normalized mean flow estimates expected to occur during a period of average precipitation and hydrology (USEPA 1975).
+Water residence time for our study lakes ranged from 1 week to 17 years with an interquartile e range of 3 months to 1.8 years while P retention ranged from 0.06 to 0.99 with an interquartile range of 0.24 to 0.59 (Table 1).
+
+We supplemented the NES dataset with boundaries O for lake subwatersheds, as well as estimates of stream density, upstream lake area, upstream lake connection(s), baseflow (an index of groundwater inputs), land-use cover, and other water quality measurements from the LAGOS-NE dataset (Table 1; Soranno et al.
+2017).
+Our study lakes encompassed a wide range of land-use cover types and nutrient levels (Table 1).
+Although, lake subwatersheds were variable with respect to agricultural land use cover, we did not observe a strong relationship with lake P retention (Figure A2).
+On average, the water quality (total phosphorus, chlorophyll concentration, and Secchi depth) of the lakes in our study are similar to other US lakes as measured by the stratified random sampling design of the National Lakes Assessment (NLA) lake population (USEPA 2016).
+However, our lakes are substantially larger and deeper than most NLA lakes (Figure A3).
+
+We restricted the lakes in the study to those located within the footprint of LAGOS-NE which includes lakes located in 17 northeastern and midwestern US states (Soranno et al.
+2017).
+We excluded lakes from our analysis if they had a surface area of greater than 1000 km2 or a surface area of less than 0.1 km2.
+We also excluded lakes if they had a maximum depth of greater than 70 m, lacked upstream surface water connections, or had one of the North American Great Lakes in its upstream watershed.
+A total of 129 out of 236 NES lakes met each of these selection criteria.
 
@@
 
-In addition to data from the NES and  LAGOS-NE datasets, we calculated several connectivity
-imetrics that we expected would be related e to lake P retention (Figure 2). Some of these metrics
-were stream-based with the goal of capturing w
- aspects of the configuration of each lakes’
-upstream surface water network (Figure 2C-D). In particular, O we chose metrics that would
-n
-quantitatively approximate network complexity under the assumption that highly complex
-ly
-networks are also low connectivity networks. This assumption is supported by the findings of
-stream network simulations where increased network complexity leads to increased network
-resistance and ultimately decreases in network connectivity (Rodriguez-Iturbe and Rinaldo
-2001). In addition to stream-based metrics, we calculated lake-stream-based metrics that we
-expected would reflect the likelihood of P trapping in upstream lakes prior to arriving at a given
-focal lake via tributary flow (Figure 2A, 2B). A simple metric that captures this likelihood is the
-presence (or absence) of an upstream lake (greater than 4 ha) which we define as “lake
-
-connection” (Fergus et al. 2017). In addition to lake connection, we calculated related metrics
-such as total upstream lake area and the network distance to the closest upstream lake.
-To examine the importance of spatial extent relative to our connectivity metrics, we
-calculated each metric at multiple extents (Figure 3). First, we calculated connectivity metrics at
-the scale of individual lake subwatersheds. We defined a lake subwatershed as the area draining
-into a particular lake exclusive of any upstream areas that drain into a lake greater than or equal
-to 10 ha (0.1 km2). Next, we calculated connectivity metrics at the scale of entire upstream lake
-networks (lake watershed extent). We defined a lake watershed as the area draining into any part
-Fof the upstream network o
- irrespective of the presence or absence of upstream lakes (Figure 3).
-rAll connectivity metrics were calculated using the high-resolution National Hydrography
-R
-Dataset (NHD) as a primary input (USGS e 2018). Average link length was calculated as the total
-stream length in a given watershed divided v
- by the number of stream reaches after dissolving
-i(removing) any network points that do not e occur at a stream junction. Stream density was
+In addition to data from the NES and  LAGOS-NE datasets, we calculated several connectivity metrics that we expected would be related e to lake P retention (Figure 2).
+Some of these metrics were stream-based with the goal of capturing  aspects of the configuration of each lakes’ upstream surface water network (Figure 2C-D).
+In particular, we chose metrics that would quantitatively approximate network complexity under the assumption that highly complex networks are also low connectivity networks.
+This assumption is supported by the findings of stream network simulations where increased network complexity leads to increased network resistance and ultimately decreases in network connectivity (Rodriguez-Iturbe and Rinaldo 2001).
+In addition to stream-based metrics, we calculated lake-stream-based metrics that we
+expected would reflect the likelihood of P trapping in upstream lakes prior to arriving at a given focal lake via tributary flow (Figure 2A, 2B).
+A simple metric that captures this likelihood is the presence (or absence) of an upstream lake (greater than 4 ha) which we define as “lake connection” (Fergus et al.
+2017).
+In addition to lake connection, we calculated related metrics such as total upstream lake area and the network distance to the closest upstream lake.
+To examine the importance of spatial extent relative to our connectivity metrics, we calculated each metric at multiple extents (Figure 3).
+First, we calculated connectivity metrics at the scale of individual lake subwatersheds.
+We defined a lake subwatershed as the area draining into a particular lake exclusive of any upstream areas that drain into a lake greater than or equal
+to 10 ha (0.1 km2). Next, we calculated connectivity metrics at the scale of entire upstream lake networks (lake watershed extent). We defined a lake watershed as the area draining into any part
+Fof the upstream network irrespective of the presence or absence of upstream lakes (Figure 3).
+All connectivity metrics were calculated using the high-resolution National Hydrography Dataset (NHD) as a primary input (USGS e 2018).
+Average link length was calculated as the total stream length in a given watershed divided v
+ by the number of stream reaches after dissolving (removing) any network points that do not e occur at a stream junction. Stream density was
 calculated as the length of all streams in the w
@@
 
-We modelled lake total phosphorus retention (hereafter, P retention) using the Vollenweider equation that models P retention as a function of water residence time and a parameter (k)
-conceptually representing in-lake P decay (Chapra 2008, Vollenweider 1975). Although there are
-several variants of this basic equation, we selected a 2-parameter form (equation 1) that has been
-Fshown to have good performance o
- in multiple cross-sectional studies (Brett and Benjamin 2007,
-rCheng et al. 2010):
-R
-Ri = 1 ― 1 + 1
- ktx
- i
- e Eq. 1
-v
-where Ri is P retention as a fraction of P inputs, i $\tau$ is water residence time, k is a unitless
-eparameter representing in-lake P decay, and w
- x is a unitless parameter representing P export via
-hydrologic flushing. Here, higher values of k are associated with greater integrated P losses from
-Osedimentation and biological uptake resulting in greater P retention. Note that Eq 1 does not
-n
-include a recycling term. Therefore, our results represent net l P retention (as opposed to gross P
-y
-retention) under a steady state assumption where lakes are at equilibrium with respect to
-recycling (Vollenweider 1975). Note that although some forms of the Vollenweider equation use
-P loading as a predictor variable, it does not appear in Eq 1. The reason for this is two-fold. First,
-estimates of P loading are more difficult to obtain than estimates of water residence time and our
-aim was to develop a model than can be widely applied to lakes for which we lack detailed data
-on P loading. Second, loading based model forms have been shown to be mathematically
+We modelled lake total phosphorus retention (hereafter, P retention) using the Vollenweider equation that models P retention as a function of water residence time and a parameter (k) conceptually representing in-lake P decay (Chapra 2008, Vollenweider 1975).
+Although there are several variants of this basic equation, we selected a 2-parameter form (equation 1) that has been
+shown to have good performance in multiple cross-sectional studies (Brett and Benjamin 2007, Cheng et al. 2010):
+
+$$
+Ri = 1 - \frac{1}{1 + kt^{x}_{i}}
+$$
+
+where $R_i$ is P retention as a fraction of P inputs, i $\tau$ is water residence time, k is a unitless parameter representing in-lake P decay, and w
+ x is a unitless parameter representing P export via hydrologic flushing.
+Here, higher values of k are associated with greater integrated P losses from sedimentation and biological uptake resulting in greater P retention.
+Note that Eq 1 does not include a recycling term.
+Therefore, our results represent net l P retention (as opposed to gross P retention) under a steady state assumption where lakes are at equilibrium with respect to recycling (Vollenweider 1975).
+Note that although some forms of the Vollenweider equation use P loading as a predictor variable, it does not appear in Eq 1.
+The reason for this is two-fold.
+First, estimates of P loading are more difficult to obtain than estimates of water residence time and our aim was to develop a model than can be widely applied to lakes for which we lack detailed data on P loading.
+Second, loading based model forms have been shown to be mathematically
 equivalent to water residence time based model forms (Brett and Benjamin 2008).
@@
 basis of specific connectivity metrics (or lake depth) and specific spatial extents:
-1
-Ri = 1 ―
- 1 + kjtxi
- F Eq. 2
-o
-kj = gi
- rwhere greater differences in k between R
- the two groups indicate greater support for a connectivity
-eeffect on P retention. Prior to model fitting, we examined the bivariate relationships between
-v
-each connectivity metric, water residence i time, P loading, and other factors related to P retention
-eusing Pearson’s correlation coefficients. The w
- purpose of this exercise was twofold, to determine
+
+$$
+Ri = 1 - \frac{1}{1 + k_{j}t^{x}_{i}}
+$$
+$$
+k_{j} = g_{i}
+$$
+
+where greater differences in k between R the two groups indicate greater support for a connectivity effect on P retention.
+Prior to model fitting, we examined the bivariate relationships between each connectivity metric, water residence i time, P loading, and other factors related to P retention
+eusing Pearson’s correlation coefficients. The purpose of this exercise was twofold, to determine
 the potential for collinearity among any of the variables in Eq 2 and to identify any relationships

### 2019-01-19 manuscript/manuscript.Rmd
fight with dockerhub

@@
   pandoc: false
+  texlive: true
   sysdeps: 
@@
 
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.4\textwidth,keepaspectratio]{../figures/02_conny_metric_key_crop_small} 
+  \end{center}
+  \caption{Connectivity metric definitions along with simplified examples of high and low value lakes that might arise from a binary classification.
+Both lake-stream-based and stream-based metrics are associated with restrictions on  in-stream transport whereas stream-based metrics are associated with differences in transport of P from terrestrial runoff to streams.
+We use the term "first order stream" to describe a headwater stream.}\label{fig2}
+\end{figure}
+
 In addition to variation among connectivity metrics and connectivity metric types, it is also not always clear which spatial extent is appropriate for determining functional differences in connectivity among lakes (Soranno et al.
@@
 Here, the lake subwatershed extent includes the elements of the immediate watershed in the direct drainage of a lake whereas the lake watershed extent includes all of the elements in the entirety of the lake-stream network up to and including headwater streams (Figure 3).
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.5\textwidth,keepaspectratio]{../figures/03_iws_nws} 
+  \end{center}
+  \caption{Diagram showing the lake subwatershed and lake watershed of three lakes.
+Here the lake subwatershed of lake 3 encompasses the lake subwatershed of lake 2 because it is smaller than 10 ha but it does not encompass the lake subwatershed of lake 1 because it has an area of at least 10 ha.
+In contrast to the lake subwatershed boundaries, the lake watershed boundaries extend to the headwaters of the lake chain.}\label{fig3}
+\end{figure}
 
@@
 We defined a lake subwatershed as the area draining into a particular lake exclusive of any upstream areas that drain into a lake greater than or equal
-to 10 ha (0.1 km2). Next, we calculated connectivity metrics at the scale of entire upstream lake networks (lake watershed extent). We defined a lake watershed as the area draining into any part
-Fof the upstream network irrespective of the presence or absence of upstream lakes (Figure 3).
+to 10 ha (0.1 km2).
+Next, we calculated connectivity metrics at the scale of entire upstream lake networks (lake watershed extent).
+We defined a lake watershed as the area draining into any part of the upstream network irrespective of the presence or absence of upstream lakes (Figure 3).
 All connectivity metrics were calculated using the high-resolution National Hydrography Dataset (NHD) as a primary input (USGS e 2018).
 Average link length was calculated as the total stream length in a given watershed divided v
- by the number of stream reaches after dissolving (removing) any network points that do not e occur at a stream junction. Stream density was
-calculated as the length of all streams in the w
- watershed (minus artificial lines through lakes)
-expressed in units of meters per hectare. Upstream lake O area was calculated as the sum of the
-n
-lake area in the upstream watershed expressed in square meters. Stream order ratio was defined
-ly
-as the number of headwater (first-order) streams in the upstream watershed of the focal lake
-divided by the total number of higher order (> 1) streams (Barbera and Rosso 1989). Closest
-distance to an upstream lake was defined as the shortest path-distance (rather than the straight-
-line distance) to a lake upstream from the focal lake.
-We calculated all connectivity metrics and lake watershed extents using the streamnet
-and nhdR R packages respectively (Stachelek 2018a, Stachelek 2018b). The algorithms in the
-streamnet package use the sf R package (Pebesma 2018) as well as the v.net and v.stream.order modules (Jasiewicz and Metz 2011) included in GRASS GIS (GRASS Development Team
-2017). All processed connectivity data and code are available at [Zenodo DOI].
+ by the number of stream reaches after dissolving (removing) any network points that do not e occur at a stream junction.
+Stream density was calculated as the length of all streams in the watershed (minus artificial lines through lakes)
+expressed in units of meters per hectare.
+Upstream lake area was calculated as the sum of the lake area in the upstream watershed expressed in square meters.
+Stream order ratio was defined as the number of headwater (first-order) streams in the upstream watershed of the focal lake divided by the total number of higher order (> 1) streams (Barbera and Rosso 1989).
+Closest distance to an upstream lake was defined as the shortest path-distance (rather than the straight-line distance) to a lake upstream from the focal lake.
+We calculated all connectivity metrics and lake watershed extents using the `streamnet` and `nhdR` R packages respectively (Stachelek 2018a, Stachelek 2018b).
+The algorithms in the `streamnet` package use the `sf` R package (Pebesma 2018) as well as the `v.net` and `v.stream.order` modules (Jasiewicz and Metz 2011) included in GRASS GIS (GRASS Development Team 2017).
+All processed connectivity data and code are available at [Zenodo DOI].
 
@@
 First, estimates of P loading are more difficult to obtain than estimates of water residence time and our aim was to develop a model than can be widely applied to lakes for which we lack detailed data on P loading.
-Second, loading based model forms have been shown to be mathematically
-equivalent to water residence time based model forms (Brett and Benjamin 2008).
-We used the model described by Eq 1 to compare lake P retention in lakes with different
-connectivity by fitting the model in two ways. First, we modelled the overall relationship
-between P retention and water residence time for all lakes in our dataset (global model). Second,
-we fit hierarchical versions of Eq. 1 where k was modelled separately (kj) as a function of a
-binary sub-population indicator gi denoting membership in one of two lake classes formed on the
+Second, loading based model forms have been shown to be mathematically equivalent to water residence time based model forms (Brett and Benjamin 2008).
+We used the model described by Eq 1 to compare lake P retention in lakes with different connectivity by fitting the model in two ways.
+First, we modelled the overall relationship between P retention and water residence time for all lakes in our dataset (global model).
+Second, we fit hierarchical versions of Eq.
+1 where k was modelled separately (kj) as a function of a binary sub-population indicator gi denoting membership in one of two lake classes formed on the
 basis of specific connectivity metrics (or lake depth) and specific spatial extents:
@@
 Prior to model fitting, we examined the bivariate relationships between each connectivity metric, water residence i time, P loading, and other factors related to P retention
-eusing Pearson’s correlation coefficients. The purpose of this exercise was twofold, to determine
-the potential for collinearity among any of the variables in Eq 2 and to identify any relationships
-Obetween P retention, water residence time, and other watershed and lake characteristics that were
-n
-not included in our model. As only one connectivity metric was l used to define g for each model
-y
-we did not use the results of this exercise to exclude variables from further investigation. We
-quantified the relative support for an effect of each connectivity metric on P retention in more
-detail by calculating the difference in the median value of the P decay parameter k between
-groups (i.e. $\delta$k). We used these median k values along with median estimates of x to determine
-how differences in k translated to differences in P retention (Eq 2). We judged significance by
-whether or not differences in group-wise P retention were greater than the measurement
-precision of P retention (> 0.01).
+eusing Pearson’s correlation coefficients.
+The purpose of this exercise was twofold, to determine the potential for collinearity among any of the variables in Eq 2 and to identify any relationships between P retention, water residence time, and other watershed and lake characteristics that were not included in our model.
+As only one connectivity metric was used to define g for each model we did not use the results of this exercise to exclude variables from further investigation.
+We quantified the relative support for an effect of each connectivity metric on P retention in more detail by calculating the difference in the median value of the P decay parameter k between groups (i.e.
+$\Delta$k).
+We used these median k values along with median estimates of x to determine how differences in k translated to differences in P retention (Eq 2).
+We judged significance by whether or not differences in group-wise P retention were greater than the measurement precision of P retention (> 0.01).
 
-We fit all models in a Bayesian framework using the non-linear extension to the brms
-package to interface with the Stan statistical program (Burkner 2017, Stan Development Team
-2017). In both models, we set a semi-informative prior on k and x of N(1.3, 0.1) and N(0.45, 0.1)
-respectively. These priors were based on the confidence intervals presented in Brett and
-Benjamin (2007) and qualitatively matched those used by Cheng et al. (2010). We used the
-default settings of brms and rstan to generate posterior estimates using four chains of 4,000
-iterations each with no thinning and initial parameter values drawn from a uniform distribution
-bounded between -2 and 2. We also used the brms package for model evaluation by computing a
-FBayesian R2 following o
- the method of Gelman et al. (2017).
+We fit all models in a Bayesian framework using the non-linear extension to the brms package to interface with the Stan statistical program (Burkner 2017, Stan Development Team 2017).
+In both models, we set a semi-informative prior on k and x of N(1.3, 0.1) and N(0.45, 0.1) respectively.
+These priors were based on the confidence intervals presented in Brett and Benjamin (2007) and qualitatively matched those used by Cheng et al.
+(2010).
+We used the default settings of brms and rstan to generate posterior estimates using four chains of 4,000 iterations each with no thinning and initial parameter values drawn from a uniform distribution bounded between -2 and 2.
+We also used the brms package for model evaluation by computing a Bayesian $R^{2}$ following the method of Gelman et al.
+(2017).
 
@@
 
-Our lake connectivity classes were formed by dividing the lake dataset into two classes for each
-iconnectivity metric based on the bivariate e relationship between each metric and P retention. Prior
-studies have used a similar binary splitting w
- approach to examine the effect of various exogenous
-factors on lake P retention (Cheng et al. 2010; Shimoda O and Arhonditsis 2015). We determined
-n
-splitting criteria for each metric from the results of a random forest procedure incorporating
-ly
-conditional inference trees (ctree, Hothorn and Zeileis 2015). This procedure creates binary splits
-of the independent variables (i.e. each of the connectivity metrics), which are recursively
-repeated to find the split that maximizes association with the dependent variable (P retention).
-The advantage of the ctree technique over the more typical classification-regression tree (CART)
-technique is that tree growth stopping rules are pre-specified (Hothorn et al., 2006). As a result,
-some of subjectivity associated with post-hoc tree pruning is avoided.
+Our lake connectivity classes were formed by dividing the lake dataset into two classes for each connectivity metric based on the bivariate e relationship between each metric and P retention.
+Prior studies have used a similar binary splitting approach to examine the effect of various exogenous factors on lake P retention (Cheng et al.
+2010; Shimoda O and Arhonditsis 2015).
+We determined splitting criteria for each metric from the results of a random forest procedure incorporating conditional inference trees (ctree, Hothorn and Zeileis 2015).
+This procedure creates binary splits of the independent variables (i.e.
+each of the connectivity metrics), which are recursively repeated to find the split that maximizes association with the dependent variable (P retention).
+The advantage of the ctree technique over the more typical classification-regression tree (CART) technique is that tree growth stopping rules are pre-specified (Hothorn et al., 2006).
+As a result, some of subjectivity associated with post-hoc tree pruning is avoided.
 
@@
 
-We examined the bivariate relationships between connectivity, water residence time, P loading and other factors related to P retention to determine the potential for strong relationships among
-any of the variables which were not accounted for by our model structure (Eq 2, Figure 4). We
-found evidence for some relationships among these variables, but none that suggest either
-redundancy among connectivity metrics or that otherwise limit our ability to infer relationships
-with P retention (Figure 4). For example, the Pearson correlation (r) between water residence
-Ftime and stream density, o
- which is implicitly accounted for in our model structure, was 0.29 (p <
-r0.05). In contrast, the correlation between water residence time and upstream lake area, which is
-R
-unaccounted for in our model structure, e was only 0.10 (p > 0.05). Note that interactions between
-connectivity metrics and water residence v
- time are accounted for in our hierarchical model
-istructure because Eq. 2 uses a global coefficient e x for water residence time that is estimated
-separately from the hierarchical and connectivity-dependent w
- P decay coefficient k. This is
-conceptually similar to fitting the k-connectivity-P retention O relationship to the residuals of the
-n
-water residence time to P retention relationship. Perhaps surprisingly, we did not observe strong
-ly
-correlations between P loading and water residence time (r = 0.13, p > 0.05) or between lake
-depth and most connectivity metrics (r < 0.17). This suggests that our P retention results are not
-confounded by variations in lake depth, by interactions between connectivity and P loading, or
-by interactions between water residence time and P loading.
-A secondary purpose of examining the bivariate relationships between connectivity,
-water residence time, P loading and other factors related to P retention was to determine if our
-connectivity metrics were related to each other such that they provide similar information. With the exception of stream density and baseflow (r = -0.52, p < 0.05), correlations among
-connectivity metrics were low and of a similar magnitude as the correlations between
-connectivity metrics and water residence time (0.10 < r < 0.29). The strongest correlation
-between any connectivity metric or lake characteristic was upstream lake area and lake
-watershed area (r = 0.77, p < 0.05).
-We observed notably strong correlations between P loading and several lake
-characteristics not accounted for in Eq 2. These include the correlation between P loading and
-lake watershed area (r = 0.62, p < 0.05) as well as the correlation between P loading and lake
-Fsubwatershed area (r = o
- 0.76, p < 0.05). In addition, the correlation between P loading and
-rupstream lake area was quite strong (r = 0.52, p < 0.05). Despite strong correlations between P
-R
-loading, watershed area, and upstream e lake area, we did not observe a strong correlation between
-P loading and P retention (r = 0.15, p > 0.05). Notably, this correlation was much weaker than the correlation between water residence time e and P retention (r = 0.44, p > 0.05). Our
-observation that the correlation between P w
- retention and P loading was not appreciably stronger
-than correlations between P retention and our connectivity O metrics suggests that our estimates of
-n
-connectivity metric effects on P retention are not confounded by interactions between water
-ly
-residence time and P loading.
-Although we did not observe strong correlations among connectivity metrics, we found
-that lakes with similar connectivity metric values, were spatially clustered (Figure 5). In
-particular, we found that lakes were concentrated in either the southern or northern portions of
-our study area depending on their connectivity metric value (Figure 5). This observation is
-consistent with the findings of Fergus et al. (2017) that lakes in the northern portion of our study area have distinct freshwater connectivity as compared to lakes in the southern portion of our
-study area.
+We examined the bivariate relationships between connectivity, water residence time, P loading and other factors related to P retention to determine the potential for strong relationships among any of the variables which were not accounted for by our model structure (Eq 2, Figure 4).
+We found evidence for some relationships among these variables, but none that suggest either redundancy among connectivity metrics or that otherwise limit our ability to infer relationships with P retention (Figure 4).
+For example, the Pearson correlation (r) between water residence time and stream density, which is implicitly accounted for in our model structure, was 0.29 (p < 0.05).
+In contrast, the correlation between water residence time and upstream lake area, which is unaccounted for in our model structure, e was only 0.10 (p > 0.05).
+Note that interactions between connectivity metrics and water residence time are accounted for in our hierarchical model structure because Eq.
+2 uses a global coefficient e x for water residence time that is estimated separately from the hierarchical and connectivity-dependent P decay coefficient k.
+This is conceptually similar to fitting the k-connectivity-P retention O relationship to the residuals of the water residence time to P retention relationship.
+Perhaps surprisingly, we did not observe strong correlations between P loading and water residence time (r = 0.13, p > 0.05) or between lake depth and most connectivity metrics (r < 0.17).
+This suggests that our P retention results are not confounded by variations in lake depth, by interactions between connectivity and P loading, or by interactions between water residence time and P loading.
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.5\textwidth,keepaspectratio]{../figures/07_cor_mat_hmap-1} 
+  \end{center}
+  \caption{Correlation among connectivity metrics and selected lake characteristics.
+Cell shading and color reflects the correlation coefficient value.
+Only coefficients accompanied by a significant p value < 0.05 are shown as text.
+Here, WS is the lake watershed extent whereas SWS is the lake subwatershed extent.
+Connectivity metrics are defined in Figure 2.}\label{fig4}
+\end{figure}
+
+A secondary purpose of examining the bivariate relationships between connectivity, water residence time, P loading and other factors related to P retention was to determine if our connectivity metrics were related to each other such that they provide similar information.
+With the exception of stream density and baseflow (r = -0.52, p < 0.05), correlations among connectivity metrics were low and of a similar magnitude as the correlations between connectivity metrics and water residence time (0.10 < r < 0.29).
+The strongest correlation between any connectivity metric or lake characteristic was upstream lake area and lake watershed area (r = 0.77, p < 0.05).
+We observed notably strong correlations between P loading and several lake characteristics not accounted for in Eq 2.
+These include the correlation between P loading and lake watershed area (r = 0.62, p < 0.05) as well as the correlation between P loading and lake subwatershed area (r = o
+ 0.76, p < 0.05).
+In addition, the correlation between P loading and upstream lake area was quite strong (r = 0.52, p < 0.05).
+Despite strong correlations between P loading, watershed area, and upstream e lake area, we did not observe a strong correlation between P loading and P retention (r = 0.15, p > 0.05).
+Notably, this correlation was much weaker than the correlation between water residence time e and P retention (r = 0.44, p > 0.05).
+Our observation that the correlation between P retention and P loading was not appreciably stronger
+than correlations between P retention and our connectivity O metrics suggests that our estimates of connectivity metric effects on P retention are not confounded by interactions between water residence time and P loading.
+Although we did not observe strong correlations among connectivity metrics, we found that lakes with similar connectivity metric values, were spatially clustered (Figure 5).
+In particular, we found that lakes were concentrated in either the southern or northern portions of our study area depending on their connectivity metric value (Figure 5).
+This observation is consistent with the findings of Fergus et al.
+(2017) that lakes in the northern portion of our study area have distinct freshwater connectivity as compared to lakes in the southern portion of our study area.
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.5\textwidth,keepaspectratio]{../figures/08_maps-1} 
+  \end{center}
+  \caption{Locations of lakes of with different connectivity metric values at the (A) lake subwatershed and (B) lake watershed extent.
+Low valued lakes are represented by lighter (green) symbols, and high values lakes are represented by darker (purple) symbols.
+WS is the lake watershed extent.
+SWS is the lake subwatershed extent.
+Connectivity metrics are defined in Figure 2.}\label{fig5}
+\end{figure}
 
@@
 
-We found that freshwater connectivity metrics were associated with lake P retention (Figure 6,
-7). Across all connectivity metrics except stream order ratio, we found that the P decay
-coefficient k and thus P retention was associated with whether a lake had a high or low value of
-each connectivity metric. These findings matched our expectations in several ways. Most
-Fnotably, lakes with shorter o
- average link lengths had higher P retention relative to lakes with
-rlonger average link lengths. In addition, lakes with less upstream lake area had higher P retention
-R
-than lakes with more upstream lake e area (Figure 6, 7).
-We found that some connectivity v
- metrics were more strongly related to P retention than
-iothers. For example, the model R2 for network e average link length was higher (R2 = 0.41) than
-the global model (R2 = 0.34). For other connectivity w
- metrics, such as network stream order ratio,
-goodness-of-fit (R2 = 0.36) was very similar to the global O model (R2 = 0.34). Model fit for other
-n
-connectivity metrics was in between these two extremes (0. 36 < R2 < 0.41). Overall, we found
-ly
-that all hierarchical models had at least a marginally better fit to the water residence time versus
-P retention relationship than a global model which does not account for connectivity (Figure 6).
-Although we found a discernable effect of connectivity metrics on lake P retention, the
-somewhat modest improvements in model fit may be due to the fact that water residence time
-remains a dominant effect even after accounting for freshwater connectivity.
+We found that freshwater connectivity metrics were associated with lake P retention (Figure 6, 7).
+Across all connectivity metrics except stream order ratio, we found that the P decay coefficient k and thus P retention was associated with whether a lake had a high or low value of each connectivity metric.
+These findings matched our expectations in several ways.
+Most
+Fnotably, lakes with shorter average link lengths had higher P retention relative to lakes with longer average link lengths.
+In addition, lakes with less upstream lake area had higher P retention than lakes with more upstream lake area (Figure 6, 7).
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.5\textwidth,keepaspectratio]{../figures/04_global_vollenweider-1} 
+  \end{center}
+  \caption{Residence time (yr) versus P retention for the NES dataset and the global model fit to the data ($R^{2}$ = 0.34, n = 129) where the solid line and shaded interval represents the median and central 95% interval estimates respectively (A).
+As above except that solid lines and shaded interval estimates represent hierarchical model fits to the data ($R^{2}$ = 0.41, n = 129) based on watershed average link length, which had the strongest association of any connectivity metric relative to P retention (B).
+Equations for these lines at median water residence time for low and high link length lakes are: Rp = 1 - (1 / (1 + 1.32 $\protect\tau^{0.4}$)) and Rp = 1 - (1 / (1 + 1.08 $\protect\tau^{0.4}$)) respectively.}\label{fig6}
+\end{figure}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.5\textwidth,keepaspectratio]{../figures/06_k-3} 
+  \end{center}
+  \caption{Distribution of the k parameter from Eq.
+1 in lakes of differing connectivity, depth, or baseflow at the (A) lake subwatershed and (B) lake watershed extents.
+Lighter (green) lines indicate lakes with lower connectivity metrics values while darker (purple) lines indicate lakes with higher connectivity metrics values.
+For lake connection, lighter colored lines indicate lakes without upstream lakes.
+Connectivity metrics are defined in Figure 2.
+Labels associated with models where differences in k translated to significant differences in P retention are bolded and starred.}\label{fig7}
+\end{figure}
+
+We found that some connectivity metrics were more strongly related to P retention than others.
+For example, the model $R^{2}$ for network e average link length was higher ($R^{2}$ = 0.41) than the global model ($R^{2}$ = 0.34).
+For other connectivity metrics, such as network stream order ratio,
+goodness-of-fit ($R^{2}$ = 0.36) was very similar to the global O model ($R^{2}$ = 0.34).
+Model fit for other connectivity metrics was in between these two extremes (0.
+36 < $R^{2}$ < 0.41).
+Overall, we found that all hierarchical models had at least a marginally better fit to the water residence time versus P retention relationship than a global model which does not account for connectivity (Figure 6).
+Although we found a discernable effect of connectivity metrics on lake P retention, the somewhat modest improvements in model fit may be due to the fact that water residence time remains a dominant effect even after accounting for freshwater connectivity.
 
@@
 
-Differences in P retention among lakes with different connectivity metric values was reflected in
-differences among connectivity class-specific values of the P decay parameter k (Figure 7). The
-connectivity metric that had the most effect on k was average link length (Table 2). For instance,
-hierarchical models fit with the average link length metric had a median effect size of 0.23 and
-0.05 for k and P retention respectively (Table 2), which means that for this metric, lakes with
-shorter average link lengths retained 4.7 to 4.9 % more P than lakes with longer average link
-lengths. The influence of lake-stream-based connectivity metrics on lake P retention was similar
-to stream-based connectivity metrics (Figure 7). This suggests that both lake-stream-based
-Fconnectivity between lakes o
- and streams as well as stream-based connectivity of lakes and their
-rterrestrial watersheds influence P retention (Figure 2).
-R
-We found that connectivity metrics e measured at the lake watershed extent were more
-strongly associated with P retention v
- than metrics measured at the lake subwatershed extent
-i(Table 2, Figure 7). Specifically, the metrics e that had the strongest association with P retention
-such as average link length ($\delta$k = 0.23), closest w
- lake distance ($\delta$k = 0.22), and stream density ($\delta$k
-= 0.20) also had a stronger association at the lake watershed O extent rather than at the lake
-n
-subwatershed extent (Table 2, Figure 7). An exception to this pattern was observed with the
-ly
-baseflow connectivity metric where although greater differences at the lake subwatershed extent
-were more strongly associated with P retention, the sign of the effect was variable depending on
-measurement extent (i.e. the value of the P decay parameter was positively related to
-connectivity metric values at the subwatershed extent but was negatively related at the watershed
-extent). For several connectivity metrics, we judged that differences in P decay among lakes with
-either low or high connectivity metric values were not significant because they translated to
-differences in P retention that were less than measurement precision (Table 2).
+Differences in P retention among lakes with different connectivity metric values was reflected in differences among connectivity class-specific values of the P decay parameter k (Figure 7).
+The connectivity metric that had the most effect on k was average link length (Table 2).
+For instance, hierarchical models fit with the average link length metric had a median effect size of 0.23 and 0.05 for k and P retention respectively (Table 2), which means that for this metric, lakes with shorter average link lengths retained 4.7 to 4.9 % more P than lakes with longer average link lengths.
+The influence of lake-stream-based connectivity metrics on lake P retention was similar
+to stream-based connectivity metrics (Figure 7).
+This suggests that both lake-stream-based connectivity between lakes and streams as well as stream-based connectivity of lakes and their terrestrial watersheds influence P retention (Figure 2).
+
+We found that connectivity metrics e measured at the lake watershed extent were more strongly associated with P retention than metrics measured at the lake subwatershed extent (Table 2, Figure 7).
+Specifically, the metrics e that had the strongest association with P retention such as average link length ($\Delta$k = 0.23), closest lake distance ($\Delta$k = 0.22), and stream density ($\Delta$k = 0.20) also had a stronger association at the lake watershed O extent rather than at the lake subwatershed extent (Table 2, Figure 7).
+An exception to this pattern was observed with the baseflow connectivity metric where although greater differences at the lake subwatershed extent
+were more strongly associated with P retention, the sign of the effect was variable depending on measurement extent (i.e.
+the value of the P decay parameter was positively related to connectivity metric values at the subwatershed extent but was negatively related at the watershed extent).
+For several connectivity metrics, we judged that differences in P decay among lakes with either low or high connectivity metric values were not significant because they translated to differences in P retention that were less than measurement precision (Table 2).
 
 ## Discussion
-Although prior studies have found that lake P retention is related to water residence time (Brett
-and Benjamin, Cheng, et al. 2010, Vollenweider 1975), there is substantial variation around this
-relationship, particularly at intermediate water residence times. We found that some of this
-remaining variation could be explained using a hierarchical modelling framework that accounts
-for differences in freshwater connectivity among lakes. Although we found that the magnitude of
-this effect depends on the specific connectivity metric, our results are consistent with the findings of previous studies o
- showing that connectivity metrics are associated with differences in
-rlake carbon input fluxes and differences in lake nitrogen output fluxes (Cardille et al. 2007;
-R
-Schmadel et al. 2018). We also found e important differences in the association between
-connectivity metrics and P retention v
- at different measurement extents. Specifically, we found
-ithat P retention was more strongly associated e with connectivity measured at the broader lake
-watershed extent rather than connectivity measured w
- at the finer lake subwatershed extent.
+
+Although prior studies have found that lake P retention is related to water residence time (Brett and Benjamin, Cheng, et al.
+2010, Vollenweider 1975), there is substantial variation around this relationship, particularly at intermediate water residence times.
+We found that some of this remaining variation could be explained using a hierarchical modelling framework that accounts for differences in freshwater connectivity among lakes.
+Although we found that the magnitude of this effect depends on the specific connectivity metric, our results are consistent with the findings of previous studies  showing that connectivity metrics are associated with differences in lake carbon input fluxes and differences in lake nitrogen output fluxes (Cardille et al.
+2007; Schmadel et al.
+2018).
+We also found e important differences in the association between connectivity metrics and P retention at different measurement extents.
+Specifically, we found that P retention was more strongly associated e with connectivity measured at the broader lake watershed extent rather than connectivity measured at the finer lake subwatershed extent.
 
@@
 
-We found that differences in P retention among lake connectivity classes was influenced by
-specific connectivity metrics including average link length, closest lake distance, and stream
-density (Table 2, Figure 7). Indeed, these metrics were more strongly associated with P retention
-than covariates typically used in statistical P retention models (e.g. lake depth, Figure 1). Note
-that we were able to examine the influence of specific metrics as separate effects apart from
-water residence time because our model structure treats them as hierarchical coefficients on the P
-decay parameter k. As a result, although water residence time remains the dominant effect on
-lake P retention, we were able to estimate the specific influence of each metric in a way that is
-not possible using integrated water residence time and connectivity metrics such as watershed
-transport capacity (Fraterrigo and Downing 2008).
-Several of the connectivity metrics that were most strongly associated with P retention
-were weakly correlated with watershed size (Figure 4). The weak nature of these correlations are
-consistent with the mixed results of prior studies linking watershed size to lake processes. For
-example, Zimmer and McGlynn (2018) found that carbon export was related to watershed size,
+We found that differences in P retention among lake connectivity classes was influenced by specific connectivity metrics including average link length, closest lake distance, and stream density (Table 2, Figure 7).
+Indeed, these metrics were more strongly associated with P retention than covariates typically used in statistical P retention models (e.g.
+lake depth, Figure 1).
+Note that we were able to examine the influence of specific metrics as separate effects apart from water residence time because our model structure treats them as hierarchical coefficients on the P decay parameter k.
+As a result, although water residence time remains the dominant effect on lake P retention, we were able to estimate the specific influence of each metric in a way that is not possible using integrated water residence time and connectivity metrics such as watershed transport capacity (Fraterrigo and Downing 2008).
+Several of the connectivity metrics that were most strongly associated with P retention were weakly correlated with watershed size (Figure 4).
+The weak nature of these correlations are consistent with the mixed results of prior studies linking watershed size to lake processes.
+For example, Zimmer and McGlynn (2018) found that carbon export was related to watershed size,
 but Smith et al. (2003) found that the nitrogen flux was not strongly related to watershed size.
-FTaken together, our results o
- and the results of prior studies suggest that watershed size and lake
-rdepth alone may not always reflect functional differences in potential material transport. One
-R
-consequence of a correlation between e connectivity metrics and watershed size is that metrics
-derived from watershed size, such as v
- catchment to lake area ratio, are also likely to be associated
-iwith connectivity. Catchment to lake area e ratio in particular has been previously used as an
-approximation or proxy of water residence w
+Taken together, our results and the results of prior studies suggest that watershed size and lake depth alone may not always reflect functional differences in potential material transport.
+One consequence of a correlation between e connectivity metrics and watershed size is that metrics derived from watershed size, such as catchment to lake area ratio, are also likely to be associated with connectivity.
+Catchment to lake area e ratio in particular has been previously used as an approximation or proxy of water residence w
  time (Rasmussen et al. 1989; Sobek et al. 2007).
+
 Although our results differ from those of Soranno et al.
 (2015) who found that the presence of an upstream lake connection was not strongly associated with catchment to lake area ratio, our results suggest that catchment to lake area ratio likely incorporates some connectivity information and caution is needed before using it as a proxy for water residence time.
-Another lake characteristic that was strongly related to watershed size was P loading. In
-particular, positive correlations between P loading and watershed size are consistent with the
-idea that lakes in larger watersheds receive greater P loading (Prairie and Kalff 1986). A related
-observation is that the correlation between P loading and upstream lake area was positive. This
-can be explained by the fact that larger watersheds often have greater numbers of lakes nested within them (Zhang et al. 2012). Another notable result is that we observed a weaker correlation
-between P loading and watershed area relative to the correlation between P loading and
-subwatershed area. One explanation for this result is that land-use cover at the finer lake
-subwatershed extent has more of an influence on P loading than land-use cover at the broader
-lake watershed extent (Soranno et al. 2015).
+Another lake characteristic that was strongly related to watershed size was P loading.
+In particular, positive correlations between P loading and watershed size are consistent with the idea that lakes in larger watersheds receive greater P loading (Prairie and Kalff 1986).
+A related observation is that the correlation between P loading and upstream lake area was positive.
+This can be explained by the fact that larger watersheds often have greater numbers of lakes nested within them (Zhang et al.
+2012).
+Another notable result is that we observed a weaker correlation between P loading and watershed area relative to the correlation between P loading and subwatershed area.
+One explanation for this result is that land-use cover at the finer lake subwatershed extent has more of an influence on P loading than land-use cover at the broader lake watershed extent (Soranno et al.
+2015).
 
@@
 One of the challenges in quantifying the effect of freshwater connectivity on lake P retention is that it is not always known what spatial extent of the watershed is functionally connected to a lake.
-We found that connectivity at the broader lake watershed extent rather than connectivity at the finer lake subwatershed extent was e more strongly associated with differences in lake P
-retention. In addition, we found that v
- individual characteristics such as lake depth (or more
-idiscrete measures of connectivity such as e the presence of an upstream lake) were more strongly
-associated with P retention than any of the w
- other connectivity metrics measured at the lake
-subwatershed extent (Table 2). These findings contrast O with Soranno et al. (2015) who examined
-n
-the association between lake nutrient concentrations (as opposed to retention) and land-use
-ly
-measured at varying spatial extents and found that measurements at the finer lake subwatershed
-extent rather than measurements at the broader lake watershed extent were more strongly
-associated with lake nutrient concentrations. One explanation for the difference between our
-results and those of Soranno et al. (2015) is that connectivity metrics may reflect long-range
-watershed processes to a greater degree than land-use cover. An alternative explanation is that
-controls of lake P retention may differ compared to controls on lake P concentration.
+We found that connectivity at the broader lake watershed extent rather than connectivity at the finer lake subwatershed extent was more strongly associated with differences in lake P retention.
+In addition, we found that individual characteristics such as lake depth (or more discrete measures of connectivity such as e the presence of an upstream lake) were more strongly associated with P retention than any of the other connectivity metrics measured at the lake subwatershed extent (Table 2).
+These findings contrast O with Soranno et al.
+(2015) who examined the association between lake nutrient concentrations (as opposed to retention) and land-use measured at varying spatial extents and found that measurements at the finer lake subwatershed extent rather than measurements at the broader lake watershed extent were more strongly associated with lake nutrient concentrations.
+One explanation for the difference between our results and those of Soranno et al.
+(2015) is that connectivity metrics may reflect long-range watershed processes to a greater degree than land-use cover.
+An alternative explanation is that controls of lake P retention may differ compared to controls on lake P concentration.
 

### 2019-01-20 manuscript/manuscript.Rmd
install 7zip

@@
   sysdeps: 
-    - apt-utils
     - grass
+    - p7zip-full
   cran: 
@@
   This work was supported by the U.S.
-National Science Foundation’s Dynamics of Coupled Natural and Human Systems (CNH) e Program (award 1517823) and Macrosystems Biology Program (awards EF-1638679, EF-1638554, EF-1638539, and EF-1638550).
+National Science Foundation’s Dynamics of Coupled Natural and Human Systems (CNH) Program (award 1517823) and Macrosystems Biology Program (awards EF-1638679, EF-1638554, EF-1638539, and EF-1638550).
 PAS was also supported by the USDA National Institute of Food and Agriculture, Hatch project 1013544.
@@
 
-Lake phosphorus (P) retention is an important characteristic of lakes that can be used to predict P concentrations and to evaluate lake sensitivity to nutrient O loading and eutrophication (Alexander et al.
+<!-- \bibliography{pinp} --->
+
+Lake phosphorus (P) retention is an important characteristic of lakes that can be used to predict P concentrations and to evaluate lake sensitivity to nutrient loading and eutrophication (Alexander et al.
 2008; Milstead et al.
@@
 export to terminal lakes and coastal estuaries).
-Although previous studies have shown that lake P retention is related to water residence time (Vollenweider 1975), large uncertainties exist around this relationship (Brett and Benjamin 2007, Milstead et al.
+Although previous studies have shown that lake P retention is related to water residence time \citep{vollenweiderInputoutputModels1975}, large uncertainties exist around this relationship (Brett and Benjamin 2007, Milstead et al.
 2013).
@@
 The mechanism for such an influence is that lake depth controls thermal stratification and material resuspension from the benthos.
-As a result, shallow lakes have a tendency to mix throughout the summer causing redistribution e of sedimented phosphorus throughout the mixed zone (Fee et al.
+As a result, shallow lakes have a tendency to mix throughout the summer causing redistribution of sedimented phosphorus throughout the mixed zone (Fee et al.
 1996).
-This mixing and redistribution of sedimented P often leads to tighter benthic-pelagic coupling and increased P recycling e (Cha et al.
+This mixing and redistribution of sedimented P often leads to tighter benthic-pelagic coupling and increased P recycling (Cha et al.
 2013).
@@
 
-In general, point source inputs e to lakes are associated with increased dissolved P loads (Kronvang 1992; Russell et al.
-1998), whereas non-point source inputs to lakes, such as those in lake watersheds with high agricultural land e use cover, typically have higher particulate P loads (Carpenter et al.
+In general, point source inputs to lakes are associated with increased dissolved P loads (Kronvang 1992; Russell et al.
+1998), whereas non-point source inputs to lakes, such as those in lake watersheds with high agricultural land use cover, typically have higher particulate P loads (Carpenter et al.
 1998; Sharpley et al.
 1994).
-Exceptions to these generalizations have been observed in areas where increased dissolved P loading O occurs not as a result of point source nutrient inputs but rather as a result of non-point source runoff due to P saturated soils or legacy P release (Bennett and Carpenter 2001; Powers et al.
+Exceptions to these generalizations have been observed in areas where increased dissolved P loading occurs not as a result of point source nutrient inputs but rather as a result of non-point source runoff due to P saturated soils or legacy P release (Bennett and Carpenter 2001; Powers et al.
 2016).
@@
 We broadly define and study two types of freshwater connectivity that correspond to either stream-based metrics or lake-stream-based metrics.
-First, lake-stream-based metrics measure the connections between a lake, other upstream lakes, and streams e in their watershed.
-This type of connectivity can be quantified by measuring the closest distance to an upstream stream-connected lake (Figure 2A), or by measuring the total upstream lake area e (Figure 2B).
-Second, stream-based metrics measure the connections between inflowing streams and their surrounding land whereby increasing stream connections lead to a greater abundance of land-water O interfaces and greater transport of material from hillslope and riparian areas adjacent to watershed stream networks (Figure 2C-E).
+First, lake-stream-based metrics measure the connections between a lake, other upstream lakes, and streams in their watershed.
+This type of connectivity can be quantified by measuring the closest distance to an upstream stream-connected lake (Figure 2A), or by measuring the total upstream lake area (Figure 2B).
+Second, stream-based metrics measure the connections between inflowing streams and their surrounding land whereby increasing stream connections lead to a greater abundance of land-water interfaces and greater transport of material from hillslope and riparian areas adjacent to watershed stream networks (Figure 2C-E).
 
@@
 Second, connectivity metrics can reflect the configuration of lakes within lake-stream networks.
-e For example, lakes with upstream lakes in close proximity may receive P loads that have previously undergone in-lake processing whereby labile fractions have already been trapped in upstream lakes e (Cardille et al.
+For example, lakes with upstream lakes in close proximity may receive P loads that have previously undergone in-lake processing whereby labile fractions have already been trapped in upstream lakes (Cardille et al.
 2007).
@@
 We asked two questions in this study: 1) Which measures of freshwater connectivity influence lake phosphorus retention?
-2) What e spatial extent of connectivity most strongly influences P retention?
-To answer these questions, we fit statistical P retention models in a Bayesian hierarchical framework following Cheng et O al.
+2) What spatial extent of connectivity most strongly influences P retention?
+To answer these questions, we fit statistical P retention models in a Bayesian hierarchical framework following Cheng et al.
 (2010) where 2 separate values of the k processing parameter were estimated for lakes with either high or low values of each connectivity metric.
@@
 Estimates of water discharge and residence time in the NES dataset represent normalized mean flow estimates expected to occur during a period of average precipitation and hydrology (USEPA 1975).
-Water residence time for our study lakes ranged from 1 week to 17 years with an interquartile e range of 3 months to 1.8 years while P retention ranged from 0.06 to 0.99 with an interquartile range of 0.24 to 0.59 (Table 1).
+Water residence time for our study lakes ranged from 1 week to 17 years with an interquartile range of 3 months to 1.8 years while P retention ranged from 0.06 to 0.99 with an interquartile range of 0.24 to 0.59 (Table 1).
 
-We supplemented the NES dataset with boundaries O for lake subwatersheds, as well as estimates of stream density, upstream lake area, upstream lake connection(s), baseflow (an index of groundwater inputs), land-use cover, and other water quality measurements from the LAGOS-NE dataset (Table 1; Soranno et al.
+We supplemented the NES dataset with boundaries for lake subwatersheds, as well as estimates of stream density, upstream lake area, upstream lake connection(s), baseflow (an index of groundwater inputs), land-use cover, and other water quality measurements from the LAGOS-NE dataset (Table 1; Soranno et al.
 2017).
@@
 
-In addition to data from the NES and  LAGOS-NE datasets, we calculated several connectivity metrics that we expected would be related e to lake P retention (Figure 2).
+In addition to data from the NES and LAGOS-NE datasets, we calculated several connectivity metrics that we expected would be related to lake P retention (Figure 2).
 Some of these metrics were stream-based with the goal of capturing aspects of the configuration of each lakes’ upstream surface water network (Figure 2C-D).
@@
 We defined a lake watershed as the area draining into any part of the upstream network irrespective of the presence or absence of upstream lakes (Figure 3).
-All connectivity metrics were calculated using the high-resolution National Hydrography Dataset (NHD) as a primary input (USGS e 2018).
+All connectivity metrics were calculated using the high-resolution National Hydrography Dataset (NHD) as a primary input (USGS 2018).
 Average link length was calculated as the total stream length in a given watershed divided v
- by the number of stream reaches after dissolving (removing) any network points that do not e occur at a stream junction.
+ by the number of stream reaches after dissolving (removing) any network points that do not occur at a stream junction.
 Stream density was calculated as the length of all streams in the watershed (minus artificial lines through lakes)
@@
 
-Our lake connectivity classes were formed by dividing the lake dataset into two classes for each connectivity metric based on the bivariate e relationship between each metric and P retention.
+Our lake connectivity classes were formed by dividing the lake dataset into two classes for each connectivity metric based on the bivariate relationship between each metric and P retention.
 Prior studies have used a similar binary splitting approach to examine the effect of various exogenous factors on lake P retention (Cheng et al.
-2010; Shimoda O and Arhonditsis 2015).
+2010; Shimoda and Arhonditsis 2015).
 We determined splitting criteria for each metric from the results of a random forest procedure incorporating conditional inference trees (ctree, Hothorn and Zeileis 2015).
@@
 For example, the Pearson correlation (r) between water residence time and stream density, which is implicitly accounted for in our model structure, was 0.29 (p < 0.05).
-In contrast, the correlation between water residence time and upstream lake area, which is unaccounted for in our model structure, e was only 0.10 (p > 0.05).
+In contrast, the correlation between water residence time and upstream lake area, which is unaccounted for in our model structure, was only 0.10 (p > 0.05).
 Note that interactions between connectivity metrics and water residence time are accounted for in our hierarchical model structure because Eq.
-2 uses a global coefficient e x for water residence time that is estimated separately from the hierarchical and connectivity-dependent P decay coefficient k.
-This is conceptually similar to fitting the k-connectivity-P retention O relationship to the residuals of the water residence time to P retention relationship.
+2 uses a global coefficient x for water residence time that is estimated separately from the hierarchical and connectivity-dependent P decay coefficient k.
+This is conceptually similar to fitting the k-connectivity-P retention relationship to the residuals of the water residence time to P retention relationship.
 Perhaps surprisingly, we did not observe strong correlations between P loading and water residence time (r = 0.13, p > 0.05) or between lake depth and most connectivity metrics (r < 0.17).
@@
 In addition, the correlation between P loading and upstream lake area was quite strong (r = 0.52, p < 0.05).
-Despite strong correlations between P loading, watershed area, and upstream e lake area, we did not observe a strong correlation between P loading and P retention (r = 0.15, p > 0.05).
-Notably, this correlation was much weaker than the correlation between water residence time e and P retention (r = 0.44, p > 0.05).
+Despite strong correlations between P loading, watershed area, and upstream lake area, we did not observe a strong correlation between P loading and P retention (r = 0.15, p > 0.05).
+Notably, this correlation was much weaker than the correlation between water residence time and P retention (r = 0.44, p > 0.05).
 Our observation that the correlation between P retention and P loading was not appreciably stronger
-than correlations between P retention and our connectivity O metrics suggests that our estimates of connectivity metric effects on P retention are not confounded by interactions between water residence time and P loading.
+than correlations between P retention and our connectivity metrics suggests that our estimates of connectivity metric effects on P retention are not confounded by interactions between water residence time and P loading.
 Although we did not observe strong correlations among connectivity metrics, we found that lakes with similar connectivity metric values, were spatially clustered (Figure 5).
@@
 We found that some connectivity metrics were more strongly related to P retention than others.
-For example, the model $R^{2}$ for network e average link length was higher ($R^{2}$ = 0.41) than the global model ($R^{2}$ = 0.34).
+For example, the model $R^{2}$ for network average link length was higher ($R^{2}$ = 0.41) than the global model ($R^{2}$ = 0.34).
 For other connectivity metrics, such as network stream order ratio,
-goodness-of-fit ($R^{2}$ = 0.36) was very similar to the global O model ($R^{2}$ = 0.34).
+goodness-of-fit ($R^{2}$ = 0.36) was very similar to the global model ($R^{2}$ = 0.34).
 Model fit for other connectivity metrics was in between these two extremes (0.
@@
 
-We found that connectivity metrics e measured at the lake watershed extent were more strongly associated with P retention than metrics measured at the lake subwatershed extent (Table 2, Figure 7).
-Specifically, the metrics e that had the strongest association with P retention such as average link length ($\Delta$k = 0.23), closest lake distance ($\Delta$k = 0.22), and stream density ($\Delta$k = 0.20) also had a stronger association at the lake watershed O extent rather than at the lake subwatershed extent (Table 2, Figure 7).
+We found that connectivity metrics measured at the lake watershed extent were more strongly associated with P retention than metrics measured at the lake subwatershed extent (Table 2, Figure 7).
+Specifically, the metrics that had the strongest association with P retention such as average link length ($\Delta$k = 0.23), closest lake distance ($\Delta$k = 0.22), and stream density ($\Delta$k = 0.20) also had a stronger association at the lake watershed extent rather than at the lake subwatershed extent (Table 2, Figure 7).
 An exception to this pattern was observed with the baseflow connectivity metric where although greater differences at the lake subwatershed extent
@@
 2018).
-We also found e important differences in the association between connectivity metrics and P retention at different measurement extents.
-Specifically, we found that P retention was more strongly associated e with connectivity measured at the broader lake watershed extent rather than connectivity measured at the finer lake subwatershed extent.
+We also found important differences in the association between connectivity metrics and P retention at different measurement extents.
+Specifically, we found that P retention was more strongly associated with connectivity measured at the broader lake watershed extent rather than connectivity measured at the finer lake subwatershed extent.
 
@@
 Taken together, our results and the results of prior studies suggest that watershed size and lake depth alone may not always reflect functional differences in potential material transport.
-One consequence of a correlation between e connectivity metrics and watershed size is that metrics derived from watershed size, such as catchment to lake area ratio, are also likely to be associated with connectivity.
-Catchment to lake area e ratio in particular has been previously used as an approximation or proxy of water residence w
+One consequence of a correlation between connectivity metrics and watershed size is that metrics derived from watershed size, such as catchment to lake area ratio, are also likely to be associated with connectivity.
+Catchment to lake area ratio in particular has been previously used as an approximation or proxy of water residence w
  time (Rasmussen et al. 1989; Sobek et al. 2007).
@@
 We found that connectivity at the broader lake watershed extent rather than connectivity at the finer lake subwatershed extent was more strongly associated with differences in lake P retention.
-In addition, we found that individual characteristics such as lake depth (or more discrete measures of connectivity such as e the presence of an upstream lake) were more strongly associated with P retention than any of the other connectivity metrics measured at the lake subwatershed extent (Table 2).
-These findings contrast O with Soranno et al.
+In addition, we found that individual characteristics such as lake depth (or more discrete measures of connectivity such as the presence of an upstream lake) were more strongly associated with P retention than any of the other connectivity metrics measured at the lake subwatershed extent (Table 2).
+These findings contrast with Soranno et al.
 (2015) who examined the association between lake nutrient concentrations (as opposed to retention) and land-use measured at varying spatial extents and found that measurements at the finer lake subwatershed extent rather than measurements at the broader lake watershed extent were more strongly associated with lake nutrient concentrations.
@@
 However, in the context of our broad-scale study it is difficult to examine this relationship because although we have estimates of nonpoint versus point source loading we do not have explicit estimates of particulate load fraction for large numbers of lakes.
-Unfortunately, we cannot use nonpoint source loading as a direct proxy for particulate load fraction because the two quantities do e not have a consistent relationship.
+Unfortunately, we cannot use nonpoint source loading as a direct proxy for particulate load fraction because the two quantities do not have a consistent relationship.
 For example, Russell et al.
-(1998) report that the particulate phosphorus fraction of nonpoint source loads can be anywhere between 62 - 90% while Djodjic e and Markensten (2018) report that this fraction can be anywhere between 33 and 80%.
+(1998) report that the particulate phosphorus fraction of nonpoint source loads can be anywhere between 62 - 90% while Djodjic and Markensten (2018) report that this fraction can be anywhere between 33 and 80%.
 This may explain why prior broad scale studies that estimate lake P retention have not attempted to estimate separate effects of particulate versus dissolved loading (Alexander et al.
@@
 Finally, it is notable that our stream density metric was influential at thee lake watershed extent but not at the lake subwatershed extent.
-Given that the stream density metric captures the average distance or drainage potential between any streams in the network and their e adjacent hillslopes, floodplains, and wetlands (see Leibowitz et al.
+Given that the stream density metric captures the average distance or drainage potential between any streams in the network and their adjacent hillslopes, floodplains, and wetlands (see Leibowitz et al.
 2018), this suggests that differences in terrestrial runoff of particulate matter from hillslope and riparian areas are likely to be important for P retention.

### 2019-01-20 manuscript/manuscript.Rmd
fill-in citations

@@
     - cowplot
+    - nesRdata
+    - partykit
+    - ggridges
+    - pinp
   remotes:
@@
 
-Lake phosphorus (P) retention is an important characteristic of lakes that can be used to predict P concentrations and to evaluate lake sensitivity to nutrient loading and eutrophication (Alexander et al.
-2008; Milstead et al.
-2013).
+Lake phosphorus (P) retention is an important characteristic of lakes that can be used to predict P concentrations and to evaluate lake sensitivity to nutrient loading and eutrophication \citep{alexander2008, milstead2013}.
 Specifically, P retention is an integrated measure of internal P losses including permanent sedimentation, biological uptake, and other processes that remove P from the water column \citep{chapra2008surface}.
@@
 export to terminal lakes and coastal estuaries).
-Although previous studies have shown that lake P retention is related to water residence time \citep{vollenweiderInputoutputModels1975}, large uncertainties exist around this relationship (Brett and Benjamin 2007, Milstead et al.
-2013).
+Although previous studies have shown that lake P retention is related to water residence time \citep{vollenweiderInputoutputModels1975}, large uncertainties exist around this relationship \citep{brett2008, milstead2013}.
 These uncertainties can be large in lakes with intermediate water residence times, particularly compared to lakes with either extremely short or extremely long water residence times (Figure A1).
-For example, lakes with very long water residence times (on the order of a decade or longer) have complete or near complete P retention, while lakes with very short water residence times (on the order of days) have almost no P retention (Brett and Benjamin, 2007).
+For example, lakes with very long water residence times (on the order of a decade or longer) have complete or near complete P retention, while lakes with very short water residence times (on the order of days) have almost no P retention \citep{brett2008}.
 The reason for the substantial uncertainty in lake P retention between these two extremes may be that predicting retention solely on the basis of water residence time does not capture many of the other factors and processes that affect P retention (Figure \ref{fig1}).
@@
 
-One well-studied factor that has been shown to influence lake P retention is lake depth through its influence on internal processing of P loads (Søndergaard et al.
-2013; Vollenweider 1975).
+One well-studied factor that has been shown to influence lake P retention is lake depth through its influence on internal processing of P loads \citep{sondergaard2013, vollenweiderInputoutputModels1975}.
 The mechanism for such an influence is that lake depth controls thermal stratification and material resuspension from the benthos.
-As a result, shallow lakes have a tendency to mix throughout the summer causing redistribution of sedimented phosphorus throughout the mixed zone (Fee et al.
-1996).
-This mixing and redistribution of sedimented P often leads to tighter benthic-pelagic coupling and increased P recycling (Cha et al.
-2013).
-Thus, depth is one example of a lake characteristic that is likely to influence P retention in concert with water residence time (Cheng et al.
-2010).
+As a result, shallow lakes have a tendency to mix throughout the summer causing redistribution of sedimented phosphorus throughout the mixed zone \citep{fee1996}.
+This mixing and redistribution of sedimented P often leads to tighter benthic-pelagic coupling and increased P recycling \citep{cha2013}.
+Thus, depth is one example of a lake characteristic that is likely to influence P retention in concert with water residence time \citep{cheng2010}.
 
 A primary tool for evaluating the influence of specific lake characteristics, like lake depth, on P retention is statistical phosphorus retention modelling.
-Although the form of such models is variable, many models estimate P retention as a function of water residence time and a parameter k that represents in-lake P decay (Chapra 2008, Vollenweider 1975).
+Although the form of such models is variable, many models estimate P retention as a function of water residence time and a parameter k that represents in-lake P decay \citep{chapra2008surface, vollenweiderInputoutputModels1975}.
 Many studies treat k as a constant global parameter (i.e., it has the same value for all lakes), which may be valid only for studies that consider small numbers of lakes in a limited geographic region, with similar characteristics.
-Few studies have modeled different k values based on lake or watershed characteristics, despite the many differences among lakes that likely influence their ability to process P (Cheng et al.
-2010).
+Few studies have modeled different k values based on lake or watershed characteristics, despite the many differences among lakes that likely influence their ability to process P \citep{cheng2010}.
 
-For example, there is evidence that the relative proportion of particulate versus dissolved P loads (hereafter, particulate load fraction), influences P retention in stream and wetland ecosystems (Jarvie et al.
-2011; Kronvang 1992; Russell et al.
-1998; Vanni et al.
-2001).
-However, evidence for particulate load fraction controls on P retention in lakes remains limited because of difficulties in tracking the fate of particulate loads after entering a lake (Brett and Benjamin 2007; Dillon and Molot 1996).
+For example, there is evidence that the relative proportion of particulate versus dissolved P loads (hereafter, particulate load fraction), influences P retention in stream and wetland ecosystems \citep{jarvie2011, kronvang1992, russell1998, vanni2001}.
+However, evidence for particulate load fraction controls on P retention in lakes remains limited because of difficulties in tracking the fate of particulate loads after entering a lake \citep{brett2008, dillon1996}.
 Therefore, there is potential to further study particulate load Ffraction using proxies that may be closely related to it, such as the relative amounts of point and nonpoint nutrient sources to a lake subwatershed.
 
-In general, point source inputs to lakes are associated with increased dissolved P loads (Kronvang 1992; Russell et al.
-1998), whereas non-point source inputs to lakes, such as those in lake watersheds with high agricultural land use cover, typically have higher particulate P loads (Carpenter et al.
-1998; Sharpley et al.
-1994).
-Exceptions to these generalizations have been observed in areas where increased dissolved P loading occurs not as a result of point source nutrient inputs but rather as a result of non-point source runoff due to P saturated soils or legacy P release (Bennett and Carpenter 2001; Powers et al.
-2016).
-Despite the fact that particulate loads are usually related to non-point source inputs, the fraction of non-point source inputs that are in particulate form is highly variable and may depend on intra-annual flow variations as well as watershed erosion characteristics (Jarvie et al.
-2011).
-Furthermore, quantifying non-point source inputs at broad spatial scales is not commonly done due to logistical and sampling constraints (Guy et al.
-1994).
+In general, point source inputs to lakes are associated with increased dissolved P loads \citep{kronvang1992, russell1998}, whereas non-point source inputs to lakes, such as those in lake watersheds with high agricultural land use cover, typically have higher particulate P loads \citep{carpenter1998, sharpley1994}.
+Exceptions to these generalizations have been observed in areas where increased dissolved P loading occurs not as a result of point source nutrient inputs but rather as a result of non-point source runoff due to P saturated soils or legacy P release \citep{bennet2001, powers2015}.
+Despite the fact that particulate loads are usually related to non-point source inputs, the fraction of non-point source inputs that are in particulate form is highly variable and may depend on intra-annual flow variations as well as watershed erosion characteristics \citep{jarvie2011}.
+Furthermore, quantifying non-point source inputs at broad spatial scales is not commonly done due to logistical and sampling constraints \citep{guy1994}.
 As a result, studies often infer the relative amounts of particulate and dissolved loading from other available proxy data such as land-use cover (Ellison and Brett 2006, Djodjic and Markensten 2018).

### 2019-01-20 manuscript/manuscript.Rmd
add curl and pdfcrop

@@
     - p7zip-full
+    - curl
+    - texlive-extra-utils 
   cran:

### 2019-01-20 manuscript/manuscript.Rmd
fight with docker

--- 2019-01-20 manuscript/manuscript.Rmd
@@
   sysdeps:
-    - grass
+    - grass-dev
     - p7zip-full
+    - curl
+    - texlive-base
+    - texlive-extra-utils 
   cran:

### 2019-01-22 manuscript/manuscript.Rmd
fill out refs, enlargen last figs

@@
 Furthermore, quantifying non-point source inputs at broad spatial scales is not commonly done due to logistical and sampling constraints \citep{guy1994}.
-As a result, studies often infer the relative amounts of particulate and dissolved loading from other available proxy data such as land-use cover (Ellison and Brett 2006, Djodjic and Markensten 2018).
+As a result, studies often infer the relative amounts of particulate and dissolved loading from other available proxy data such as land-use cover \citep{ellisonParticulatePhosphorusBioavailability2006, djodjicSingleFieldsRiver2018}.
 
-Apart from land-use cover, another potential proxy for particulate load fraction entering lakes is the type and amount of freshwater connections to a lake, which we argue is easier to measure than other proxies, and could help to improve estimates of lake P retention, especially in lakes for which we lack P loading data (Figure 1).
-Although freshwater connectivity may be easy to measure from a logistical standpoint, there are still many ways to measure connectivity that likely represent different mechanisms of water and material flow (Figure 2).
+Apart from land-use cover, another potential proxy for particulate load fraction entering lakes is the type and amount of freshwater connections to a lake, which we argue is easier to measure than other proxies, and could help to improve estimates of lake P retention, especially in lakes for which we lack P loading data (Figure \ref{fig1}).
+Although freshwater connectivity may be easy to measure from a logistical standpoint, there are still many ways to measure connectivity that likely represent different mechanisms of water and material flow (Figure \ref{fig2}).
 We broadly define and study two types of freshwater connectivity that correspond to either stream-based metrics or lake-stream-based metrics.
 First, lake-stream-based metrics measure the connections between a lake, other upstream lakes, and streams in their watershed.
-This type of connectivity can be quantified by measuring the closest distance to an upstream stream-connected lake (Figure 2A), or by measuring the total upstream lake area (Figure 2B).
-Second, stream-based metrics measure the connections between inflowing streams and their surrounding land whereby increasing stream connections lead to a greater abundance of land-water interfaces and greater transport of material from hillslope and riparian areas adjacent to watershed stream networks (Figure 2C-E).
+This type of connectivity can be quantified by measuring the closest distance to an upstream stream-connected lake (Figure \ref{fig2}A), or by measuring the total upstream lake area (Figure \ref{fig2}B).
+Second, stream-based metrics measure the connections between inflowing streams and their surrounding land whereby increasing stream connections lead to a greater abundance of land-water interfaces and greater transport of material from hillslope and riparian areas adjacent to watershed stream networks (Figure \ref{fig2}C-E).
 
@@
 
-In addition to variation among connectivity metrics and connectivity metric types, it is also not always clear which spatial extent is appropriate for determining functional differences in connectivity among lakes (Soranno et al.
-2015).
-Such information is needed to inform the design of regulatory frameworks balancing controls on cumulative nutrient transport along stream networks and controls on localized nutrient transport (Alexander et al.
-2008; Carpenter et al.
-1998; Withers and Jarvie 2008).
-To test the importance of different spatial extents, we examined connectivity metrics measured for both the lake subwatershed extent and the lake watershed extent (Figure 3).
-Here, the lake subwatershed extent includes the elements of the immediate watershed in the direct drainage of a lake whereas the lake watershed extent includes all of the elements in the entirety of the lake-stream network up to and including headwater streams (Figure 3).
+In addition to variation among connectivity metrics and connectivity metric types, it is also not always clear which spatial extent is appropriate for determining functional differences in connectivity among lakes \citep{soranno2015}.
+Such information is needed to inform the design of regulatory frameworks balancing controls on cumulative nutrient transport along stream networks and controls on localized nutrient transport \citep{alexander2008, carpenter1998, withersDeliveryCyclingPhosphorus2008}.
+To test the importance of different spatial extents, we examined connectivity metrics measured for both the lake subwatershed extent and the lake watershed extent (Figure \ref{fig3}).
+Here, the lake subwatershed extent includes the elements of the immediate watershed in the direct drainage of a lake whereas the lake watershed extent includes all of the elements in the entirety of the lake-stream network up to and including headwater streams (Figure \ref{fig3}).
 
@@
 We propose that measures of freshwater connectivity are related to P retention in the following ways.
-First, some connectivity metrics reflect the proximity of terrestrial watershed areas to the stream network (Covino 2017).
-For example, lakes with a high watershed stream density should have increased particulate matter loading from terrestrial hillslope and riparian areas adjacent to watershed stream networks because particulate matter export is limited by overland distance (Gomi et al.
-2002).
+First, some connectivity metrics reflect the proximity of terrestrial watershed areas to the stream network \citep{covino2017}.
+For example, lakes with a high watershed stream density should have increased particulate matter loading from terrestrial hillslope and riparian areas adjacent to watershed stream networks because particulate matter export is limited by overland distance \citep{gomi2002}.
 Second, connectivity metrics can reflect the configuration of lakes within lake-stream networks.
@@
 
-\begin{figure}
+\begin{figure*}
   \begin{center}
-    \includegraphics[width=0.5\textwidth,keepaspectratio]{../figures/08_maps-1}
+    \includegraphics[width=0.6\textwidth,keepaspectratio]{../figures/08_maps-1}
   \end{center}
@@
 Connectivity metrics are defined in Figure 2.}\label{fig5}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{figure}
+\begin{figure*}
   \begin{center}
-    \includegraphics[width=0.5\textwidth,keepaspectratio]{../figures/06_k-3}
+    \includegraphics[width=0.9\textwidth,keepaspectratio]{../figures/06_k-3}
   \end{center}
@@
 Labels associated with models where differences in k translated to significant differences in P retention are bolded and starred.}\label{fig7}
-\end{figure}
+\end{figure*}
 

### 2019-01-22 manuscript/manuscript.Rmd
towards including tables
add citations

@@
 
+  \begin{center}
+    \includegraphics[width=0.5\textwidth,keepaspectratio]{../tables/crop/01_lake_characteristics_table} \label{table1}
+  \end{center}
+
 We supplemented the NES dataset with boundaries for lake subwatersheds, as well as estimates of stream density, upstream lake area, upstream lake connection(s), baseflow (an index of groundwater inputs), land-use cover, and other water quality measurements from the LAGOS-NE dataset (Table 1; Soranno et al.
@@
 
-We modelled lake total phosphorus retention (hereafter, P retention) using the Vollenweider equation that models P retention as a function of water residence time and a parameter (k) conceptually representing in-lake P decay (Chapra 2008, Vollenweider 1975).
+We modelled lake total phosphorus retention (hereafter, P retention) using the Vollenweider equation that models P retention as a function of water residence time and a parameter (k) conceptually representing in-lake P decay \citep{chapra2008surface, vollenweiderInputoutputModels1975}.
 Although there are several variants of this basic equation, we selected a 2-parameter form (equation 1) that has been
-shown to have good performance in multiple cross-sectional studies (Brett and Benjamin 2007, Cheng et al. 2010):
+shown to have good performance in multiple cross-sectional studies \citep{brett2008, cheng2010}:
 
@@
 
-where $R_i$ is P retention as a fraction of P inputs, i $\tau$ is water residence time, k is a unitless parameter representing in-lake P decay, and w
- x is a unitless parameter representing P export via hydrologic flushing.
+where $R_i$ is P retention as a fraction of P inputs, i $\tau$ is water residence time, $k$ is a unitless parameter representing in-lake P decay, and $x$ is a unitless parameter representing P export via hydrologic flushing.
 Here, higher values of k are associated with greater integrated P losses from sedimentation and biological uptake resulting in greater P retention.
 Note that Eq 1 does not include a recycling term.
-Therefore, our results represent net l P retention (as opposed to gross P retention) under a steady state assumption where lakes are at equilibrium with respect to recycling (Vollenweider 1975).
+Therefore, our results represent net P retention (as opposed to gross P retention) under a steady state assumption where lakes are at equilibrium with respect to recycling \citep{vollenweiderInputoutputModels1975}.
 Note that although some forms of the Vollenweider equation use P loading as a predictor variable, it does not appear in Eq 1.
@@
 First, estimates of P loading are more difficult to obtain than estimates of water residence time and our aim was to develop a model than can be widely applied to lakes for which we lack detailed data on P loading.
-Second, loading based model forms have been shown to be mathematically equivalent to water residence time based model forms (Brett and Benjamin 2008).
+Second, loading based model forms have been shown to be mathematically equivalent to water residence time based model forms \citep{brett2008}.
 We used the model described by Eq 1 to compare lake P retention in lakes with different connectivity by fitting the model in two ways.
@@
 Second, we fit hierarchical versions of Eq.
-1 where k was modelled separately (kj) as a function of a binary sub-population indicator gi denoting membership in one of two lake classes formed on the
-basis of specific connectivity metrics (or lake depth) and specific spatial extents:
+1 where $k$ was modelled separately ($k_{j}$) as a function of a binary sub-population indicator $g_{i}$ denoting membership in one of two lake classes formed on the basis of specific connectivity metrics (or lake depth) and specific spatial extents:
 
@@
 
-where greater differences in k between R the two groups indicate greater support for a connectivity effect on P retention.
-Prior to model fitting, we examined the bivariate relationships between each connectivity metric, water residence i time, P loading, and other factors related to P retention
-eusing Pearson’s correlation coefficients.
+where greater differences in $k$ between R the two groups indicate greater support for a connectivity effect on P retention.
+Prior to model fitting, we examined the bivariate relationships between each connectivity metric, water residence time, P loading, and other factors related to P retention using Pearson’s correlation coefficients.
 The purpose of this exercise was twofold, to determine the potential for collinearity among any of the variables in Eq 2 and to identify any relationships between P retention, water residence time, and other watershed and lake characteristics that were not included in our model.
@@
 
-We fit all models in a Bayesian framework using the non-linear extension to the brms package to interface with the Stan statistical program (Burkner 2017, Stan Development Team 2017).
-In both models, we set a semi-informative prior on k and x of N(1.3, 0.1) and N(0.45, 0.1) respectively.
-These priors were based on the confidence intervals presented in Brett and Benjamin (2007) and qualitatively matched those used by Cheng et al.
-(2010).
+We fit all models in a Bayesian framework using the non-linear extension to the `brms` package to interface with the Stan statistical program \citep{burkner2017brms, stan2017}.
+In both models, we set a semi-informative prior on $k$ and $x$ of N(1.3, 0.1) and N(0.45, 0.1) respectively.
+These priors were based on the confidence intervals presented in \citet{brett2008} and qualitatively matched those used by \citet{cheng2010}.
 We used the default settings of brms and rstan to generate posterior estimates using four chains of 4,000 iterations each with no thinning and initial parameter values drawn from a uniform distribution bounded between -2 and 2.
-We also used the brms package for model evaluation by computing a Bayesian $R^{2}$ following the method of Gelman et al.
-(2017).
+We also used the brms package for model evaluation by computing a Bayesian $R^{2}$ following the method of \citet{gelmanRsquaredBayesianRegression2017}.
 
@@
 Our lake connectivity classes were formed by dividing the lake dataset into two classes for each connectivity metric based on the bivariate relationship between each metric and P retention.
-Prior studies have used a similar binary splitting approach to examine the effect of various exogenous factors on lake P retention (Cheng et al.
-2010; Shimoda and Arhonditsis 2015).
-We determined splitting criteria for each metric from the results of a random forest procedure incorporating conditional inference trees (ctree, Hothorn and Zeileis 2015).
+Prior studies have used a similar binary splitting approach to examine the effect of various exogenous factors on lake P retention \citep{cheng2010, shimodaIntegratingHierarchicalBayes2015}.
+We determined splitting criteria for each metric from the results of a random forest procedure incorporating conditional inference trees \citep[ctree,]{hothorn2015partykit}.
 This procedure creates binary splits of the independent variables (i.e.
 each of the connectivity metrics), which are recursively repeated to find the split that maximizes association with the dependent variable (P retention).
-The advantage of the ctree technique over the more typical classification-regression tree (CART) technique is that tree growth stopping rules are pre-specified (Hothorn et al., 2006).
+The advantage of the ctree technique over the more typical classification-regression tree (CART) technique is that tree growth stopping rules are pre-specified \citep{hothorn2006unbiased}.
 As a result, some of subjectivity associated with post-hoc tree pruning is avoided.
@@
 Notably, this correlation was much weaker than the correlation between water residence time and P retention (r = 0.44, p > 0.05).
-Our observation that the correlation between P retention and P loading was not appreciably stronger
-than correlations between P retention and our connectivity metrics suggests that our estimates of connectivity metric effects on P retention are not confounded by interactions between water residence time and P loading.
+Our observation that the correlation between P retention and P loading was not appreciably stronger than correlations between P retention and our connectivity metrics suggests that our estimates of connectivity metric effects on P retention are not confounded by interactions between water residence time and P loading.
 Although we did not observe strong correlations among connectivity metrics, we found that lakes with similar connectivity metric values, were spatially clustered (Figure 5).
 In particular, we found that lakes were concentrated in either the southern or northern portions of our study area depending on their connectivity metric value (Figure 5).
-This observation is consistent with the findings of Fergus et al.
-(2017) that lakes in the northern portion of our study area have distinct freshwater connectivity as compared to lakes in the southern portion of our study area.
+This observation is consistent with the findings of \citet{fergusFreshwaterLandscapeLake2017} that lakes in the northern portion of our study area have distinct freshwater connectivity as compared to lakes in the southern portion of our study area.
 
 \begin{figure*}
-  \begin{center}
+  \begin{raggedleft}
     \includegraphics[width=0.6\textwidth,keepaspectratio]{../figures/08_maps-1}
-  \end{center}
+  \end{raggedleft}
   \caption{Locations of lakes of with different connectivity metric values at the (A) lake subwatershed and (B) lake watershed extent.
@@
   \end{center}
-  \caption{Residence time (yr) versus P retention for the NES dataset and the global model fit to the data ($R^{2}$ = 0.34, n = 129) where the solid line and shaded interval represents the median and central 95% interval estimates respectively (A).
+  \caption{Residence time (yr) versus P retention for the NES dataset and the global model fit to the data ($R^{2}$ = 0.34, n = 129) where the solid line and shaded interval represents the median and central 95\% interval estimates respectively (A).
 As above except that solid lines and shaded interval estimates represent hierarchical model fits to the data ($R^{2}$ = 0.41, n = 129) based on watershed average link length, which had the strongest association of any connectivity metric relative to P retention (B).
@@
 The connectivity metric that had the most effect on k was average link length (Table 2).
-For instance, hierarchical models fit with the average link length metric had a median effect size of 0.23 and 0.05 for k and P retention respectively (Table 2), which means that for this metric, lakes with shorter average link lengths retained 4.7 to 4.9 % more P than lakes with longer average link lengths.
+For instance, hierarchical models fit with the average link length metric had a median effect size of 0.23 and 0.05 for k and P retention respectively (Table \ref{table2}{2}), which means that for this metric, lakes with shorter average link lengths retained 4.7 to 4.9 % more P than lakes with longer average link lengths.
 The influence of lake-stream-based connectivity metrics on lake P retention was similar
@@
 This suggests that both lake-stream-based connectivity between lakes and streams as well as stream-based connectivity of lakes and their terrestrial watersheds influence P retention (Figure 2).
+
+\begin{center}
+  \includegraphics[width=0.5\textwidth,keepaspectratio]{../tables/crop/02_model_results_table} \label{table2}
+\end{center}
 
@@
 
-Although prior studies have found that lake P retention is related to water residence time (Brett and Benjamin, Cheng, et al.
-2010, Vollenweider 1975), there is substantial variation around this relationship, particularly at intermediate water residence times.
+Although prior studies have found that lake P retention is related to water residence time \citep{brett2008, cheng2010, vollenweiderInputoutputModels1975}, there is substantial variation around this relationship, particularly at intermediate water residence times.
 We found that some of this remaining variation could be explained using a hierarchical modelling framework that accounts for differences in freshwater connectivity among lakes.
-Although we found that the magnitude of this effect depends on the specific connectivity metric, our results are consistent with the findings of previous studies showing that connectivity metrics are associated with differences in lake carbon input fluxes and differences in lake nitrogen output fluxes (Cardille et al.
-2007; Schmadel et al.
-2018).
+Although we found that the magnitude of this effect depends on the specific connectivity metric, our results are consistent with the findings of previous studies showing that connectivity metrics are associated with differences in lake carbon input fluxes and differences in lake nitrogen output fluxes \citep{cardilleCarbonWaterCycling2007, schmadelThresholdsLakeReservoir2018}.
 We also found important differences in the association between connectivity metrics and P retention at different measurement extents.
@@
 Note that we were able to examine the influence of specific metrics as separate effects apart from water residence time because our model structure treats them as hierarchical coefficients on the P decay parameter k.
-As a result, although water residence time remains the dominant effect on lake P retention, we were able to estimate the specific influence of each metric in a way that is not possible using integrated water residence time and connectivity metrics such as watershed transport capacity (Fraterrigo and Downing 2008).
+As a result, although water residence time remains the dominant effect on lake P retention, we were able to estimate the specific influence of each metric in a way that is not possible using integrated water residence time and connectivity metrics such as watershed transport capacity \citep{fraterrigoInfluenceLandUse2008}.
 Several of the connectivity metrics that were most strongly associated with P retention were weakly correlated with watershed size (Figure 4).
 The weak nature of these correlations are consistent with the mixed results of prior studies linking watershed size to lake processes.
-For example, Zimmer and McGlynn (2018) found that carbon export was related to watershed size,
-but Smith et al. (2003) found that the nitrogen flux was not strongly related to watershed size.
+For example, \citet{zimmerLateralVerticalLongitudinal2018} found that carbon export was related to watershed size, but \citet{smithEutrophicationFreshwaterCoastal2003} found that the nitrogen flux was not strongly related to watershed size.
 Taken together, our results and the results of prior studies suggest that watershed size and lake depth alone may not always reflect functional differences in potential material transport.
 One consequence of a correlation between connectivity metrics and watershed size is that metrics derived from watershed size, such as catchment to lake area ratio, are also likely to be associated with connectivity.
-Catchment to lake area ratio in particular has been previously used as an approximation or proxy of water residence w
- time (Rasmussen et al. 1989; Sobek et al. 2007).
+Catchment to lake area ratio in particular has been previously used as an approximation or proxy of water residence time \citep{rasmussenHumicContentLake1989, sobekPatternsRegulationDissolved2007}.
 
-Although our results differ from those of Soranno et al.
-(2015) who found that the presence of an upstream lake connection was not strongly associated with catchment to lake area ratio, our results suggest that catchment to lake area ratio likely incorporates some connectivity information and caution is needed before using it as a proxy for water residence time.
+Although our results differ from those of \citet{soranno2015} who found that the presence of an upstream lake connection was not strongly associated with catchment to lake area ratio, our results suggest that catchment to lake area ratio likely incorporates some connectivity information and caution is needed before using it as a proxy for water residence time.
 Another lake characteristic that was strongly related to watershed size was P loading.
-In particular, positive correlations between P loading and watershed size are consistent with the idea that lakes in larger watersheds receive greater P loading (Prairie and Kalff 1986).
+In particular, positive correlations between P loading and watershed size are consistent with the idea that lakes in larger watersheds receive greater P loading \citep{t-prairieEffectCatchmentSize1986}.
 A related observation is that the correlation between P loading and upstream lake area was positive.
@@
 Another notable result is that we observed a weaker correlation between P loading and watershed area relative to the correlation between P loading and subwatershed area.
-One explanation for this result is that land-use cover at the finer lake subwatershed extent has more of an influence on P loading than land-use cover at the broader lake watershed extent (Soranno et al.
-2015).
+One explanation for this result is that land-use cover at the finer lake subwatershed extent has more of an influence on P loading than land-use cover at the broader lake watershed extent \citep{soranno2015}.
 
@@
 In addition, we found that individual characteristics such as lake depth (or more discrete measures of connectivity such as the presence of an upstream lake) were more strongly associated with P retention than any of the other connectivity metrics measured at the lake subwatershed extent (Table 2).
-These findings contrast with Soranno et al.
-(2015) who examined the association between lake nutrient concentrations (as opposed to retention) and land-use measured at varying spatial extents and found that measurements at the finer lake subwatershed extent rather than measurements at the broader lake watershed extent were more strongly associated with lake nutrient concentrations.
-One explanation for the difference between our results and those of Soranno et al.
-(2015) is that connectivity metrics may reflect long-range watershed processes to a greater degree than land-use cover.
+These findings contrast with \citet{soranno2015} who examined the association between lake nutrient concentrations (as opposed to retention) and land-use measured at varying spatial extents and found that measurements at the finer lake subwatershed extent rather than measurements at the broader lake watershed extent were more strongly associated with lake nutrient concentrations.
+One explanation for the difference between our results and those of \citet{soranno2015} is that connectivity metrics may reflect long-range watershed processes to a greater degree than land-use cover.
 An alternative explanation is that controls of lake P retention may differ compared to controls on lake P concentration.
@@
 
-Prior studies at regional extents have shown that P retention in streams and rivers is largely determined by the fate of the particulate load fraction (Cushing et al.
-1994; Kronvang 1992; Russell et al.
-1998; Vanni et al.
-2001).
-For instance, the findings of Jarvie et al.
-(2011) show that riverine P loads can be controlled by nonpoint-source P delivery of particulate P.
+Prior studies at regional extents have shown that P retention in streams and rivers is largely determined by the fate of the particulate load fraction \citep{cushingTransportDynamicsFine1993, kronvang1992, russell1998, vanni2001}.
+For instance, the findings of \citet{jarvie2011} show that riverine P loads can be controlled by nonpoint-source P delivery of particulate P.
 Therefore, it stands to reason that P retention in lakes may also be largely determined by the fate of the particulate load fraction.
@@
 Unfortunately, we cannot use nonpoint source loading as a direct proxy for particulate load fraction because the two quantities do not have a consistent relationship.
-For example, Russell et al.
-(1998) report that the particulate phosphorus fraction of nonpoint source loads can be anywhere between 62 - 90% while Djodjic and Markensten (2018) report that this fraction can be anywhere between 33 and 80%.
-This may explain why prior broad scale studies that estimate lake P retention have not attempted to estimate separate effects of particulate versus dissolved loading (Alexander et al.
-2008, Brett and Benjamin 2008).
+For example, \citet{russell1998} report that the particulate phosphorus fraction of nonpoint source loads can be anywhere between 62 - 90% while \citet{djodjicSingleFieldsRiver2018} report that this fraction can be anywhere between 33 and 80%.
+This may explain why prior broad scale studies that estimate lake P retention have not attempted to estimate separate effects of particulate versus dissolved loading \citep{alexander2008, brett2008}.
 
@@
 We expected that both land-stream and stream-lake connectivity influences how much particulate P is transported into lakes, which in turn affects their P retention.
-This expectation is supported by the findings of Cushing et al.
-(1994) as well as Guy et al.
-(1994) showing that particulate P can be transported beyond the direct drainage from stream-adjacent hillslopes.
+This expectation is supported by the findings of \citet{cushingTransportDynamicsFine1993} as well as \citet{guy1994} showing that particulate P can be transported beyond the direct drainage from stream-adjacent hillslopes.
 
@@
 For example, differential transport of particulate matter whereby barriers to flux and differences in drainage path configuration only become apparent beyond fine spatial extents may explain why we observed stronger association of P retention with metrics measured at the broader lake watershed extent rather than metrics measured at the finer scale lake subwatershed extent.
-Another finding consistent with differential transport of particulate P is our observation that average link length, which approximates stream network structure and along-stream transport potential (Barbera and Rosso 1989), was one of the more strongly associated metrics with lake P retention.
+Another finding consistent with differential transport of particulate P is our observation that average link length, which approximates stream network structure and along-stream transport potential \citep{labarberaFractalDimensionStream1989}, was one of the more strongly associated metrics with lake P retention.
 Finally, it is notable that our stream density metric was influential at thee lake watershed extent but not at the lake subwatershed extent.
-Given that the stream density metric captures the average distance or drainage potential between any streams in the network and their adjacent hillslopes, floodplains, and wetlands (see Leibowitz et al.
-2018), this suggests that differences in terrestrial runoff of particulate matter from hillslope and riparian areas are likely to be important for P retention.
+Given that the stream density metric captures the average distance or drainage potential between any streams in the network and their adjacent hillslopes, floodplains, and wetlands \citep[see]{leibowitzConnectivityStreamsWetlands2018}, this suggests that differences in terrestrial runoff of particulate matter from hillslope and riparian areas are likely to be important for P retention.
 
 Taken together, our findings are consistent with the idea that both connectivity between lakes and streams as well as connectivity of lakes and their terrestrial watersheds affect lake P retention.
-This conclusion matches that of prior studies showing that aquatic transport of phosphorus and nitrogen at the sub-continental scale is strongly controlled by processes affecting along-stream flux such as reservoir trapping (Alexander et al.
-2008, Schmadel et al.
-2018).
+This conclusion matches that of prior studies showing that aquatic transport of phosphorus and nitrogen at the sub-continental scale is strongly controlled by processes affecting along-stream flux such as reservoir trapping \citep{alexander2008, schmadelThresholdsLakeReservoir2018}.
 

### 2019-01-22 manuscript/manuscript.Rmd
update refs

@@
 This assumption is supported by the findings of stream network simulations where increased network complexity leads to increased network resistance and ultimately decreases in network connectivity (Rodriguez-Iturbe and Rinaldo 2001).
-In addition to stream-based metrics, we calculated lake-stream-based metrics that we
-expected would reflect the likelihood of P trapping in upstream lakes prior to arriving at a given focal lake via tributary flow (Figure 2A, 2B).
+In addition to stream-based metrics, we calculated lake-stream-based metrics that we expected would reflect the likelihood of P trapping in upstream lakes prior to arriving at a given focal lake via tributary flow (Figure 2A, 2B).
 A simple metric that captures this likelihood is the presence (or absence) of an upstream lake (greater than 4 ha) which we define as “lake connection” (Fergus et al.
@@
 First, we calculated connectivity metrics at the scale of individual lake subwatersheds.
-We defined a lake subwatershed as the area draining into a particular lake exclusive of any upstream areas that drain into a lake greater than or equal
-to 10 ha (0.1 km2).
+We defined a lake subwatershed as the area draining into a particular lake exclusive of any upstream areas that drain into a lake greater than or equal to 10 ha (0.1 $km^{2}$).
 Next, we calculated connectivity metrics at the scale of entire upstream lake networks (lake watershed extent).
 We defined a lake watershed as the area draining into any part of the upstream network irrespective of the presence or absence of upstream lakes (Figure 3).
-All connectivity metrics were calculated using the high-resolution National Hydrography Dataset (NHD) as a primary input (USGS 2018).
-Average link length was calculated as the total stream length in a given watershed divided v
- by the number of stream reaches after dissolving (removing) any network points that do not occur at a stream junction.
-Stream density was calculated as the length of all streams in the watershed (minus artificial lines through lakes)
-expressed in units of meters per hectare.
+All connectivity metrics were calculated using the high-resolution National Hydrography Dataset (NHD) as a primary input \citep{usgsNationalHydrographyDataset2018}.
+Average link length was calculated as the total stream length in a given watershed divided by the number of stream reaches after dissolving (removing) any network points that do not occur at a stream junction.
+Stream density was calculated as the length of all streams in the watershed (minus artificial lines through lakes) expressed in units of meters per hectare.
 Upstream lake area was calculated as the sum of the lake area in the upstream watershed expressed in square meters.
-Stream order ratio was defined as the number of headwater (first-order) streams in the upstream watershed of the focal lake divided by the total number of higher order (> 1) streams (Barbera and Rosso 1989).
+Stream order ratio was defined as the number of headwater (first-order) streams in the upstream watershed of the focal lake divided by the total number of higher order (> 1) streams \citep{labarberaFractalDimensionStream1989}.
 Closest distance to an upstream lake was defined as the shortest path-distance (rather than the straight-line distance) to a lake upstream from the focal lake.
-We calculated all connectivity metrics and lake watershed extents using the `streamnet` and `nhdR` R packages respectively (Stachelek 2018a, Stachelek 2018b).
-The algorithms in the `streamnet` package use the `sf` R package (Pebesma 2018) as well as the `v.net` and `v.stream.order` modules (Jasiewicz and Metz 2011) included in GRASS GIS (GRASS Development Team 2017).
+We calculated all connectivity metrics and lake watershed extents using the `streamnet` and `nhdR` R packages respectively \citep{R-streamnet, R-nhdR}.
+The algorithms in the `streamnet` package use the `sf` R package \citep{pebesma2018} as well as the `v.net` and `v.stream.order` modules \citep{jasiewiczNewGRASSGIS2011} included in GRASS GIS \citep{GRASS_GIS_software}.
 All processed connectivity data and code are available at [Zenodo DOI].
@@
 where $R_i$ is P retention as a fraction of P inputs, i $\tau$ is water residence time, $k$ is a unitless parameter representing in-lake P decay, and $x$ is a unitless parameter representing P export via hydrologic flushing.
-Here, higher values of k are associated with greater integrated P losses from sedimentation and biological uptake resulting in greater P retention.
+Here, higher values of $k$ are associated with greater integrated P losses from sedimentation and biological uptake resulting in greater P retention.
 Note that Eq 1 does not include a recycling term.
@@
 The purpose of this exercise was twofold, to determine the potential for collinearity among any of the variables in Eq 2 and to identify any relationships between P retention, water residence time, and other watershed and lake characteristics that were not included in our model.
-As only one connectivity metric was used to define g for each model we did not use the results of this exercise to exclude variables from further investigation.
-We quantified the relative support for an effect of each connectivity metric on P retention in more detail by calculating the difference in the median value of the P decay parameter k between groups (i.e.
+As only one connectivity metric was used to define $g$ for each model we did not use the results of this exercise to exclude variables from further investigation.
+We quantified the relative support for an effect of each connectivity metric on P retention in more detail by calculating the difference in the median value of the P decay parameter $k$ between groups (i.e.
 $\Delta$k).
-We used these median k values along with median estimates of x to determine how differences in k translated to differences in P retention (Eq 2).
+We used these median k values along with median estimates of $x$ to determine how differences in $k$ translated to differences in P retention (Eq 2).
 We judged significance by whether or not differences in group-wise P retention were greater than the measurement precision of P retention (> 0.01).

### 2019-01-23 manuscript/manuscript.Rmd
specify lno doi

@@
 Second, connectivity metrics can reflect the configuration of lakes within lake-stream networks.
-For example, lakes with upstream lakes in close proximity may receive P loads that have previously undergone in-lake processing whereby labile fractions have already been trapped in upstream lakes (Cardille et al.
-2007).
+For example, lakes with upstream lakes in close proximity may receive P loads that have previously undergone in-lake processing whereby labile fractions have already been trapped in upstream lakes \citep{cardilleCarbonWaterCycling2007}.
 In contrast, lakes with more distant upstream lakes are more likely to receive the more labile fractions from terrestrial runoff that serve to increase P retention as opposed to receiving the more recalcitrant fractions that are resistant to biological uptake and are thus not retained.
@@
 2) What spatial extent of connectivity most strongly influences P retention?
-To answer these questions, we fit statistical P retention models in a Bayesian hierarchical framework following Cheng et al.
-(2010) where 2 separate values of the k processing parameter were estimated for lakes with either high or low values of each connectivity metric.
+To answer these questions, we fit statistical P retention models in a Bayesian hierarchical framework following \citet{cheng2010} where 2 separate values of the $k$ processing parameter were estimated for lakes with either high or low values of each connectivity metric.
 Using this approach, higher k values for a specific lake connectivity class indicates more extensive in-lake processing and higher P retention.
@@
 
-We used data on P retention, maximum depth, and water residence time from 129 lakes in the National Eutrophication Survey (USEPA 1975, Stachelek et al.
-2018).
+We used data on P retention, maximum depth, and water residence time from 129 lakes in the National Eutrophication Survey \citep{usepa1975, stachelek_national_2018}.
 Mean annual P loading, P discharge, and P retention values in the National Eutrophication Survey (NES) dataset were calculated based on monthly sampling for P in tributary and outlet discharge points as well as any municipal waste discharges from 1972 to 1975.
 Here, P retention is a unitless value representing the fraction of incoming P loads.
-Sampling frequency for water discharge and residence time varied among lakes but details of these variations were not provided in the source dataset (USEPA 1975, Stachelek et al.
-2018).
-Estimates of water discharge and residence time in the NES dataset represent normalized mean flow estimates expected to occur during a period of average precipitation and hydrology (USEPA 1975).
+Sampling frequency for water discharge and residence time varied among lakes but details of these variations were not provided in the source dataset \citep{usepa1975, stachelek_national_2018}.
+Estimates of water discharge and residence time in the NES dataset represent normalized mean flow estimates expected to occur during a period of average precipitation and hydrology \citep{usepa1975}.
 Water residence time for our study lakes ranged from 1 week to 17 years with an interquartile range of 3 months to 1.8 years while P retention ranged from 0.06 to 0.99 with an interquartile range of 0.24 to 0.59 (Table 1).
@@
 
-We supplemented the NES dataset with boundaries for lake subwatersheds, as well as estimates of stream density, upstream lake area, upstream lake connection(s), baseflow (an index of groundwater inputs), land-use cover, and other water quality measurements from the LAGOS-NE dataset (Table 1; Soranno et al.
-2017).
+We supplemented the NES dataset with boundaries for lake subwatersheds, as well as estimates of stream density, upstream lake area, upstream lake connection(s), baseflow (an index of groundwater inputs), land-use cover, and other water quality measurements from the LAGOS-NE dataset \citep[Table 1; ]{sorannoLAGOSNEMultiscaledGeospatial2017}.
 Our study lakes encompassed a wide range of land-use cover types and nutrient levels (Table 1).
 Although, lake subwatersheds were variable with respect to agricultural land use cover, we did not observe a strong relationship with lake P retention (Figure A2).
-On average, the water quality (total phosphorus, chlorophyll concentration, and Secchi depth) of the lakes in our study are similar to other US lakes as measured by the stratified random sampling design of the National Lakes Assessment (NLA) lake population (USEPA 2016).
+On average, the water quality (total phosphorus, chlorophyll concentration, and Secchi depth) of the lakes in our study are similar to other US lakes as measured by the stratified random sampling design of the National Lakes Assessment (NLA) lake population \citep{usepa_nla2012}.
 However, our lakes are substantially larger and deeper than most NLA lakes (Figure A3).
 
-We restricted the lakes in the study to those located within the footprint of LAGOS-NE which includes lakes located in 17 northeastern and midwestern US states (Soranno et al.
-2017).
-We excluded lakes from our analysis if they had a surface area of greater than 1000 km2 or a surface area of less than 0.1 km2.
+We restricted the lakes in the study to those located within the footprint of LAGOS-NE which includes lakes located in 17 northeastern and midwestern US states \citep{sorannoLAGOSNEMultiscaledGeospatial2017}.
+We excluded lakes from our analysis if they had a surface area of greater than 1000 $km^{2}$ or a surface area of less than 0.1 $km^{2}$.
 We also excluded lakes if they had a maximum depth of greater than 70 m, lacked upstream surface water connections, or had one of the North American Great Lakes in its upstream watershed.
@@
 In particular, we chose metrics that would quantitatively approximate network complexity under the assumption that highly complex networks are also low connectivity networks.
-This assumption is supported by the findings of stream network simulations where increased network complexity leads to increased network resistance and ultimately decreases in network connectivity (Rodriguez-Iturbe and Rinaldo 2001).
+This assumption is supported by the findings of stream network simulations where increased network complexity leads to increased network resistance and ultimately decreases in network connectivity \citep{rodriguez2001fractal}.
 In addition to stream-based metrics, we calculated lake-stream-based metrics that we expected would reflect the likelihood of P trapping in upstream lakes prior to arriving at a given focal lake via tributary flow (Figure 2A, 2B).
-A simple metric that captures this likelihood is the presence (or absence) of an upstream lake (greater than 4 ha) which we define as “lake connection” (Fergus et al.
-2017).
+A simple metric that captures this likelihood is the presence (or absence) of an upstream lake (greater than 4 ha) which we define as “lake connection” \citep{fergusFreshwaterLandscapeLake2017}.
 In addition to lake connection, we calculated related metrics such as total upstream lake area and the network distance to the closest upstream lake.

### 2019-01-23 manuscript/manuscript.Rmd
add more ref links

@@
 the lake subwatershed extent) and freshwater connectivity of the entirety of the stream network up to and including watershed headwater areas (i.e.
-the lake watershed extent, Figure 3).
+the lake watershed extent, Figure \ref{fig3}).
 Our motivation for measuring connectivity so many ways is that it is easy to measure connectivity of lakes with small watersheds situated at the beginning of lake chains but it is much more challenging to identify the type and extent of connectivity in larger, more complex lake networks.
 Another reason we examined relationships between P retention, multiple measures of connectivity, and multiple spatial extents is that many commonly used connectivity metrics merely reflect watershed size (spatial extent) rather than types of material transport or particulate load fraction (Leibowitz et al., 2018).
-Although lakes in larger watersheds have both a greater potential area from which to source particulate runoff and total phosphorus export from the watershed, we expect that delivery of sediment-bound phosphorus is dependent on connectivity-mediated trapping in the upstream watershed (Prairie and Kalff 1986).
+Although lakes in larger watersheds have both a greater potential area from which to source particulate runoff and total phosphorus export from the watershed, we expect that delivery of sediment-bound phosphorus is dependent on connectivity-mediated trapping in the upstream watershed \citep{tprairieEffectCatchmentSize1986}.
 
@@
 
-In addition to data from the NES and LAGOS-NE datasets, we calculated several connectivity metrics that we expected would be related to lake P retention (Figure 2).
-Some of these metrics were stream-based with the goal of capturing aspects of the configuration of each lakes’ upstream surface water network (Figure 2C-D).
+In addition to data from the NES and LAGOS-NE datasets, we calculated several connectivity metrics that we expected would be related to lake P retention (Figure \ref{fig2}).
+Some of these metrics were stream-based with the goal of capturing aspects of the configuration of each lakes’ upstream surface water network (Figure \ref{fig2}C-D).
 In particular, we chose metrics that would quantitatively approximate network complexity under the assumption that highly complex networks are also low connectivity networks.
 This assumption is supported by the findings of stream network simulations where increased network complexity leads to increased network resistance and ultimately decreases in network connectivity \citep{rodriguez2001fractal}.
-In addition to stream-based metrics, we calculated lake-stream-based metrics that we expected would reflect the likelihood of P trapping in upstream lakes prior to arriving at a given focal lake via tributary flow (Figure 2A, 2B).
+In addition to stream-based metrics, we calculated lake-stream-based metrics that we expected would reflect the likelihood of P trapping in upstream lakes prior to arriving at a given focal lake via tributary flow (Figure \ref{fig2}A, 2B).
 A simple metric that captures this likelihood is the presence (or absence) of an upstream lake (greater than 4 ha) which we define as “lake connection” \citep{fergusFreshwaterLandscapeLake2017}.
 In addition to lake connection, we calculated related metrics such as total upstream lake area and the network distance to the closest upstream lake.
-To examine the importance of spatial extent relative to our connectivity metrics, we calculated each metric at multiple extents (Figure 3).
+To examine the importance of spatial extent relative to our connectivity metrics, we calculated each metric at multiple extents (Figure \ref{fig3}).
 First, we calculated connectivity metrics at the scale of individual lake subwatersheds.
@@
 Next, we calculated connectivity metrics at the scale of entire upstream lake networks (lake watershed extent).
-We defined a lake watershed as the area draining into any part of the upstream network irrespective of the presence or absence of upstream lakes (Figure 3).
+We defined a lake watershed as the area draining into any part of the upstream network irrespective of the presence or absence of upstream lakes (Figure \ref{fig3}).
 All connectivity metrics were calculated using the high-resolution National Hydrography Dataset (NHD) as a primary input \citep{usgsNationalHydrographyDataset2018}.
@@
 
-We examined the bivariate relationships between connectivity, water residence time, P loading and other factors related to P retention to determine the potential for strong relationships among any of the variables which were not accounted for by our model structure (Eq 2, Figure 4).
-We found evidence for some relationships among these variables, but none that suggest either redundancy among connectivity metrics or that otherwise limit our ability to infer relationships with P retention (Figure 4).
+We examined the bivariate relationships between connectivity, water residence time, P loading and other factors related to P retention to determine the potential for strong relationships among any of the variables which were not accounted for by our model structure (Eq 2, Figure \ref{fig4}).
+We found evidence for some relationships among these variables, but none that suggest either redundancy among connectivity metrics or that otherwise limit our ability to infer relationships with P retention (Figure \ref{fig4}).
 For example, the Pearson correlation (r) between water residence time and stream density, which is implicitly accounted for in our model structure, was 0.29 (p < 0.05).
@@
 Here, WS is the lake watershed extent whereas SWS is the lake subwatershed extent.
-Connectivity metrics are defined in Figure 2.}\label{fig4}
+Connectivity metrics are defined in Figure \ref{fig2}.}\label{fig4}
 \end{figure}
@@
 Our observation that the correlation between P retention and P loading was not appreciably stronger than correlations between P retention and our connectivity metrics suggests that our estimates of connectivity metric effects on P retention are not confounded by interactions between water residence time and P loading.
-Although we did not observe strong correlations among connectivity metrics, we found that lakes with similar connectivity metric values, were spatially clustered (Figure 5).
-In particular, we found that lakes were concentrated in either the southern or northern portions of our study area depending on their connectivity metric value (Figure 5).
+Although we did not observe strong correlations among connectivity metrics, we found that lakes with similar connectivity metric values, were spatially clustered (Figure \ref{fig5}).
+In particular, we found that lakes were concentrated in either the southern or northern portions of our study area depending on their connectivity metric value (Figure \ref{fig5}).
 This observation is consistent with the findings of \citet{fergusFreshwaterLandscapeLake2017} that lakes in the northern portion of our study area have distinct freshwater connectivity as compared to lakes in the southern portion of our study area.
@@
 SWS is the lake subwatershed extent.
-Connectivity metrics are defined in Figure 2.}\label{fig5}
+Connectivity metrics are defined in Figure \ref{fig2}.}\label{fig5}
 \end{figure*}
@@
 These findings matched our expectations in several ways.
-Most
-Fnotably, lakes with shorter average link lengths had higher P retention relative to lakes with longer average link lengths.
-In addition, lakes with less upstream lake area had higher P retention than lakes with more upstream lake area (Figure 6, 7).
+Most notably, lakes with shorter average link lengths had higher P retention relative to lakes with longer average link lengths.
+In addition, lakes with less upstream lake area had higher P retention than lakes with more upstream lake area (Figure \ref{fig6}, \ref{fig7}).
 
@@
 For instance, hierarchical models fit with the average link length metric had a median effect size of 0.23 and 0.05 for k and P retention respectively (Table \ref{table2}{2}), which means that for this metric, lakes with shorter average link lengths retained 4.7 to 4.9 % more P than lakes with longer average link lengths.
-The influence of lake-stream-based connectivity metrics on lake P retention was similar
-to stream-based connectivity metrics (Figure 7).
-This suggests that both lake-stream-based connectivity between lakes and streams as well as stream-based connectivity of lakes and their terrestrial watersheds influence P retention (Figure 2).
+The influence of lake-stream-based connectivity metrics on lake P retention was similar to stream-based connectivity metrics (Figure 7).
+This suggests that both lake-stream-based connectivity between lakes and streams as well as stream-based connectivity of lakes and their terrestrial watersheds influence P retention (Figure \ref{fig2}).
 
@@
 
-We found that connectivity metrics measured at the lake watershed extent were more strongly associated with P retention than metrics measured at the lake subwatershed extent (Table 2, Figure 7).
-Specifically, the metrics that had the strongest association with P retention such as average link length ($\Delta$k = 0.23), closest lake distance ($\Delta$k = 0.22), and stream density ($\Delta$k = 0.20) also had a stronger association at the lake watershed extent rather than at the lake subwatershed extent (Table 2, Figure 7).
-An exception to this pattern was observed with the baseflow connectivity metric where although greater differences at the lake subwatershed extent
-were more strongly associated with P retention, the sign of the effect was variable depending on measurement extent (i.e.
+We found that connectivity metrics measured at the lake watershed extent were more strongly associated with P retention than metrics measured at the lake subwatershed extent (Table 2, Figure \ref{fig7}).
+Specifically, the metrics that had the strongest association with P retention such as average link length ($\Delta$k = 0.23), closest lake distance ($\Delta$k = 0.22), and stream density ($\Delta$k = 0.20) also had a stronger association at the lake watershed extent rather than at the lake subwatershed extent (Table 2, Figure \ref{fig7}).
+An exception to this pattern was observed with the baseflow connectivity metric where although greater differences at the lake subwatershed extent were more strongly associated with P retention, the sign of the effect was variable depending on measurement extent (i.e.
 the value of the P decay parameter was positively related to connectivity metric values at the subwatershed extent but was negatively related at the watershed extent).
@@
 
-We found that differences in P retention among lake connectivity classes was influenced by specific connectivity metrics including average link length, closest lake distance, and stream density (Table 2, Figure 7).
+We found that differences in P retention among lake connectivity classes was influenced by specific connectivity metrics including average link length, closest lake distance, and stream density (Table 2, Figure \ref{fig7}).
 Indeed, these metrics were more strongly associated with P retention than covariates typically used in statistical P retention models (e.g.
-lake depth, Figure 1).
-Note that we were able to examine the influence of specific metrics as separate effects apart from water residence time because our model structure treats them as hierarchical coefficients on the P decay parameter k.
+lake depth, Figure \ref{fig1}).
+Note that we were able to examine the influence of specific metrics as separate effects apart from water residence time because our model structure treats them as hierarchical coefficients on the P decay parameter $k$.
 As a result, although water residence time remains the dominant effect on lake P retention, we were able to estimate the specific influence of each metric in a way that is not possible using integrated water residence time and connectivity metrics such as watershed transport capacity \citep{fraterrigoInfluenceLandUse2008}.
-Several of the connectivity metrics that were most strongly associated with P retention were weakly correlated with watershed size (Figure 4).
+Several of the connectivity metrics that were most strongly associated with P retention were weakly correlated with watershed size (Figure \ref{fig4}).
 The weak nature of these correlations are consistent with the mixed results of prior studies linking watershed size to lake processes.
@@
 A related observation is that the correlation between P loading and upstream lake area was positive.
-This can be explained by the fact that larger watersheds often have greater numbers of lakes nested within them (Zhang et al.
-2012).
+This can be explained by the fact that larger watersheds often have greater numbers of lakes nested within them \citep{zhangEvaluatingEffectsUpstream2012}.
 Another notable result is that we observed a weaker correlation between P loading and watershed area relative to the correlation between P loading and subwatershed area.

### 2019-01-23 manuscript/manuscript.Rmd
add table captions

@@
   \begin{center}
-    \includegraphics[width=0.45\textwidth, height=3.5in,keepaspectratio]{../figures/01_conceptual_p-cycle_pt2}
+    \includegraphics[width=0.4\textwidth, height=3.5in,keepaspectratio]{../figures/01_conceptual_p-cycle_pt2}
   \end{center}
@@
 
+\begin{figure} \ContinuedFloat
   \begin{center}
-    \includegraphics[width=0.5\textwidth,keepaspectratio]{../tables/crop/01_lake_characteristics_table} \label{table1}
+    \includegraphics[width=0.5\textwidth,keepaspectratio]{../tables/crop/01_lake_characteristics_table} 
+    \captionsetup{labelformat=empty}
+    \caption{\textbf{Table 1. } Minimum, median, maximum, and interquartile range of selected characteristics of the study lakes (N = 129).}\label{table1}    
   \end{center}
+\end{figure}
 
@@
 In addition to stream-based metrics, we calculated lake-stream-based metrics that we expected would reflect the likelihood of P trapping in upstream lakes prior to arriving at a given focal lake via tributary flow (Figure \ref{fig2}A, 2B).
-A simple metric that captures this likelihood is the presence (or absence) of an upstream lake (greater than 4 ha) which we define as “lake connection” \citep{fergusFreshwaterLandscapeLake2017}.
+A simple metric that captures this likelihood is the presence (or absence) of an upstream lake (greater than 4 ha) which we define as "lake connection" \citep{fergusFreshwaterLandscapeLake2017}.
 In addition to lake connection, we calculated related metrics such as total upstream lake area and the network distance to the closest upstream lake.
+
 To examine the importance of spatial extent relative to our connectivity metrics, we calculated each metric at multiple extents (Figure \ref{fig3}).
@@
 We defined a lake watershed as the area draining into any part of the upstream network irrespective of the presence or absence of upstream lakes (Figure \ref{fig3}).
+
 All connectivity metrics were calculated using the high-resolution National Hydrography Dataset (NHD) as a primary input \citep{usgsNationalHydrographyDataset2018}.
@@
 Closest distance to an upstream lake was defined as the shortest path-distance (rather than the straight-line distance) to a lake upstream from the focal lake.
+
 We calculated all connectivity metrics and lake watershed extents using the `streamnet` and `nhdR` R packages respectively \citep{R-streamnet, R-nhdR}.
@@
 We modelled lake total phosphorus retention (hereafter, P retention) using the Vollenweider equation that models P retention as a function of water residence time and a parameter (k) conceptually representing in-lake P decay \citep{chapra2008surface, vollenweiderInputoutputModels1975}.
-Although there are several variants of this basic equation, we selected a 2-parameter form (equation 1) that has been
+Although there are several variants of this basic equation, we selected a 2-parameter form (equation \ref{eq1}) that has been
 shown to have good performance in multiple cross-sectional studies \citep{brett2008, cheng2010}:
 
-$$
-Ri = 1 - \frac{1}{1 + kt^{x}_{i}}
-$$
+\begin{align}
+  Ri = 1 - \frac{1}{1 + kt^{x}_{i}} \label{eq1}
+\end{align}
 
-where $R_i$ is P retention as a fraction of P inputs, i $\tau$ is water residence time, $k$ is a unitless parameter representing in-lake P decay, and $x$ is a unitless parameter representing P export via hydrologic flushing.
+where $R_i$ is P retention as a fraction of P inputs, $i$ $\tau$ is water residence time, $k$ is a unitless parameter representing in-lake P decay, and $x$ is a unitless parameter representing P export via hydrologic flushing.
 Here, higher values of $k$ are associated with greater integrated P losses from sedimentation and biological uptake resulting in greater P retention.
-Note that Eq 1 does not include a recycling term.
+Note that Eq \ref{eq1} does not include a recycling term.
 Therefore, our results represent net P retention (as opposed to gross P retention) under a steady state assumption where lakes are at equilibrium with respect to recycling \citep{vollenweiderInputoutputModels1975}.
-Note that although some forms of the Vollenweider equation use P loading as a predictor variable, it does not appear in Eq 1.
+Note that although some forms of the Vollenweider equation use P loading as a predictor variable, it does not appear in Eq \ref{eq1}.
 The reason for this is two-fold.
@@
 Second, loading based model forms have been shown to be mathematically equivalent to water residence time based model forms \citep{brett2008}.
+
 We used the model described by Eq 1 to compare lake P retention in lakes with different connectivity by fitting the model in two ways.
@@
 
-$$
-Ri = 1 - \frac{1}{1 + k_{j}t^{x}_{i}}
-$$
-$$
+\begin{align}
+  Ri = 1 - \frac{1}{1 + k_{j}t^{x}_{i}} \label{eq2} \\
   k_{j} = g_{i}
-$$
+\end{align}
 
@@
 Prior studies have used a similar binary splitting approach to examine the effect of various exogenous factors on lake P retention \citep{cheng2010, shimodaIntegratingHierarchicalBayes2015}.
-We determined splitting criteria for each metric from the results of a random forest procedure incorporating conditional inference trees \citep[ctree,]{hothorn2015partykit}.
+We determined splitting criteria for each metric from the results of a random forest procedure incorporating conditional inference trees \citep[][ctree, ]{hothorn2015partykit}.
 This procedure creates binary splits of the independent variables (i.e.
@@
 The strongest correlation between any connectivity metric or lake characteristic was upstream lake area and lake watershed area (r = 0.77, p < 0.05).
+
 We observed notably strong correlations between P loading and several lake characteristics not accounted for in Eq 2.
-These include the correlation between P loading and lake watershed area (r = 0.62, p < 0.05) as well as the correlation between P loading and lake subwatershed area (r = o
- 0.76, p < 0.05).
+These include the correlation between P loading and lake watershed area (r = 0.62, p < 0.05) as well as the correlation between P loading and lake subwatershed area (r = 0.76, p < 0.05).
 In addition, the correlation between P loading and upstream lake area was quite strong (r = 0.52, p < 0.05).
@@
 Our observation that the correlation between P retention and P loading was not appreciably stronger than correlations between P retention and our connectivity metrics suggests that our estimates of connectivity metric effects on P retention are not confounded by interactions between water residence time and P loading.
+
 Although we did not observe strong correlations among connectivity metrics, we found that lakes with similar connectivity metric values, were spatially clustered (Figure \ref{fig5}).
@@
 \begin{figure*}
-  \begin{raggedleft}
+  \begin{center}
     \includegraphics[width=0.6\textwidth,keepaspectratio]{../figures/08_maps-1}
-  \end{raggedleft}
+  \end{center}
   \caption{Locations of lakes of with different connectivity metric values at the (A) lake subwatershed and (B) lake watershed extent.
@@
 For example, the model $R^{2}$ for network average link length was higher ($R^{2}$ = 0.41) than the global model ($R^{2}$ = 0.34).
-For other connectivity metrics, such as network stream order ratio,
-goodness-of-fit ($R^{2}$ = 0.36) was very similar to the global model ($R^{2}$ = 0.34).
+For other connectivity metrics, such as network stream order ratio, goodness-of-fit ($R^{2}$ = 0.36) was very similar to the global model ($R^{2}$ = 0.34).
 Model fit for other connectivity metrics was in between these two extremes (0.
@@
 
+\begin{figure*} \ContinuedFloat
   \begin{center}
-  \includegraphics[width=0.5\textwidth,keepaspectratio]{../tables/crop/02_model_results_table} \label{table2}
+    \includegraphics[width=0.85\textwidth,keepaspectratio]{../tables/crop/02_model_results_table} 
+    \captionsetup{labelformat=empty}
+    \caption{\textbf{Table 2.
+} Connectivity class split values and samples sizes for connectivity metrics and lake depth ranked according to the difference in median $k$ (P decay parameter, $\Delta$k) values.
+Differences in $\Delta$k that translate to differences in P retention greater than measurement precision are marked with an asterisk.
+Here, WS is the lake watershed extent whereas SWS is the lake subwatershed extent.
+Lakes with metric values above or equal to the split value were assigned to a separate connectivity class relative to lakes below the split value.
+N is sample size.
+Connectivity metrics are defined in Figure 2.}\label{table2}
   \end{center}
+\end{figure*}
 
@@
 As a result, although water residence time remains the dominant effect on lake P retention, we were able to estimate the specific influence of each metric in a way that is not possible using integrated water residence time and connectivity metrics such as watershed transport capacity \citep{fraterrigoInfluenceLandUse2008}.
+
 Several of the connectivity metrics that were most strongly associated with P retention were weakly correlated with watershed size (Figure \ref{fig4}).
@@
 Catchment to lake area ratio in particular has been previously used as an approximation or proxy of water residence time \citep{rasmussenHumicContentLake1989, sobekPatternsRegulationDissolved2007}.
+Although our results differ from those of \citet{soranno2015} who found that the presence of an upstream lake connection was not strongly associated with catchment to lake area ratio, our results suggest that catchment to lake area ratio likely incorporates some connectivity information and caution is needed before using it as a proxy for water residence time.
 
-Although our results differ from those of \citet{soranno2015} who found that the presence of an upstream lake connection was not strongly associated with catchment to lake area ratio, our results suggest that catchment to lake area ratio likely incorporates some connectivity information and caution is needed before using it as a proxy for water residence time.
 Another lake characteristic that was strongly related to watershed size was P loading.
@@
 
-We developed a conceptual model that places particulate load fraction in context with other processes affecting P retention (Figure 1).
+We developed a conceptual model that places particulate load fraction in context with other processes affecting P retention (Figure \ref{fig1}).
 We expected that both land-stream and stream-lake connectivity influences how much particulate P is transported into lakes, which in turn affects their P retention.

### 2019-01-23 manuscript/manuscript.Rmd
fight with docker permissions

@@
 Unfortunately, we cannot use nonpoint source loading as a direct proxy for particulate load fraction because the two quantities do not have a consistent relationship.
-For example, \citet{russell1998} report that the particulate phosphorus fraction of nonpoint source loads can be anywhere between 62 - 90% while \citet{djodjicSingleFieldsRiver2018} report that this fraction can be anywhere between 33 and 80%.
+For example, \citet{russell1998} report that the particulate phosphorus fraction of nonpoint source loads can be anywhere between 62 - 90\% while \citet{djodjicSingleFieldsRiver2018} report that this fraction can be anywhere between 33 and 80\%.
 This may explain why prior broad scale studies that estimate lake P retention have not attempted to estimate separate effects of particulate versus dissolved loading \citep{alexander2008, brett2008}.

### 2019-01-23 manuscript/manuscript.Rmd
typo fixes

@@
 Because it is not always clear what spatial extent is appropriate for determining functional differences in connectivity among lakes, we compared connectivity metrics at two important spatial extents: the lake subwatershed extent and the lake watershed extent.
-We found that variation in P retention among lakes was more strongly associated with connectivity metrics measured at the broader lake watershed Fextent rather than metrics measured at the finer lake subwatershed extent.
+We found that variation in P retention among lakes was more strongly associated with connectivity metrics measured at the broader lake watershed extent rather than metrics measured at the finer lake subwatershed extent.
 Our results suggest that both connectivity between lakes and streams as well as connectivity of lakes and their terrestrial watersheds influence P retention.
@@
 # Optional: Enable a 'Draft' watermark on the document
-watermark: true
+watermark: false
 
@@
 A primary tool for evaluating the influence of specific lake characteristics, like lake depth, on P retention is statistical phosphorus retention modelling.
-Although the form of such models is variable, many models estimate P retention as a function of water residence time and a parameter k that represents in-lake P decay \citep{chapra2008surface, vollenweiderInputoutputModels1975}.
-Many studies treat k as a constant global parameter (i.e., it has the same value for all lakes), which may be valid only for studies that consider small numbers of lakes in a limited geographic region, with similar characteristics.
-Few studies have modeled different k values based on lake or watershed characteristics, despite the many differences among lakes that likely influence their ability to process P \citep{cheng2010}.
+Although the form of such models is variable, many models estimate P retention as a function of water residence time and a parameter $k$ that represents in-lake P decay \citep{chapra2008surface, vollenweiderInputoutputModels1975}.
+Many studies treat $k$ as a constant global parameter (i.e., it has the same value for all lakes), which may be valid only for studies that consider small numbers of lakes in a limited geographic region, with similar characteristics.
+Few studies have modeled different $k$ values based on lake or watershed characteristics, despite the many differences among lakes that likely influence their ability to process P \citep{cheng2010}.
 
@@
 In general, point source inputs to lakes are associated with increased dissolved P loads \citep{kronvang1992, russell1998}, whereas non-point source inputs to lakes, such as those in lake watersheds with high agricultural land use cover, typically have higher particulate P loads \citep{carpenter1998, sharpley1994}.
-Exceptions to these generalizations have been observed in areas where increased dissolved P loading occurs not as a result of point source nutrient inputs but rather as a result of non-point source runoff due to P saturated soils or legacy P release \citep{bennet2001, powers2015}.
+Exceptions to these generalizations have been observed in areas where increased dissolved P loading occurs not as a result of point source nutrient inputs but rather as a result of non-point source runoff due to P saturated soils or legacy P release \citep{bennett2001, powers2015}.
 Despite the fact that particulate loads are usually related to non-point source inputs, the fraction of non-point source inputs that are in particulate form is highly variable and may depend on intra-annual flow variations as well as watershed erosion characteristics \citep{jarvie2011}.
@@
 To answer these questions, we fit statistical P retention models in a Bayesian hierarchical framework following \citet{cheng2010} where 2 separate values of the $k$ processing parameter were estimated for lakes with either high or low values of each connectivity metric.
-Using this approach, higher k values for a specific lake connectivity class indicates more extensive in-lake processing and higher P retention.
+Using this approach, higher $k$ values for a specific lake connectivity class indicates more extensive in-lake processing and higher P retention.
 We applied this model to a dataset of 129 lakes across a wide range of hydrologic, geologic, and climatic settings.
@@
 $\Delta$k).
-We used these median k values along with median estimates of $x$ to determine how differences in $k$ translated to differences in P retention (Eq 2).
+We used these median $k$ values along with median estimates of $x$ to determine how differences in $k$ translated to differences in P retention (Eq 2).
 We judged significance by whether or not differences in group-wise P retention were greater than the measurement precision of P retention (> 0.01).
@@
 We found that freshwater connectivity metrics were associated with lake P retention (Figure 6, 7).
-Across all connectivity metrics except stream order ratio, we found that the P decay coefficient k and thus P retention was associated with whether a lake had a high or low value of each connectivity metric.
+Across all connectivity metrics except stream order ratio, we found that the P decay coefficient $k$ and thus P retention was associated with whether a lake had a high or low value of each connectivity metric.
 These findings matched our expectations in several ways.
@@
   \end{center}
-  \caption{Distribution of the k parameter from Eq.
+  \caption{Distribution of the $k$ parameter from Eq.
 1 in lakes of differing connectivity, depth, or baseflow at the (A) lake subwatershed and (B) lake watershed extents.
@@
 Connectivity metrics are defined in Figure 2.
-Labels associated with models where differences in k translated to significant differences in P retention are bolded and starred.}\label{fig7}
+Labels associated with models where differences in $k$ translated to significant differences in P retention are bolded and starred.}\label{fig7}
 \end{figure*}
@@
 
-Differences in P retention among lakes with different connectivity metric values was reflected in differences among connectivity class-specific values of the P decay parameter k (Figure 7).
-The connectivity metric that had the most effect on k was average link length (Table 2).
-For instance, hierarchical models fit with the average link length metric had a median effect size of 0.23 and 0.05 for k and P retention respectively (Table \ref{table2}{2}), which means that for this metric, lakes with shorter average link lengths retained 4.7 to 4.9 % more P than lakes with longer average link lengths.
+Differences in P retention among lakes with different connectivity metric values was reflected in differences among connectivity class-specific values of the P decay parameter $k$ (Figure 7).
+The connectivity metric that had the most effect on $k$ was average link length (Table 2).
+For instance, hierarchical models fit with the average link length metric had a median effect size of 0.23 and 0.05 for $k$ and P retention respectively (Table \ref{table2}{2}), which means that for this metric, lakes with shorter average link lengths retained 4.7 to 4.9\% more P than lakes with longer average link lengths.
 The influence of lake-stream-based connectivity metrics on lake P retention was similar to stream-based connectivity metrics (Figure 7).
@@
 Another lake characteristic that was strongly related to watershed size was P loading.
-In particular, positive correlations between P loading and watershed size are consistent with the idea that lakes in larger watersheds receive greater P loading \citep{t-prairieEffectCatchmentSize1986}.
+In particular, positive correlations between P loading and watershed size are consistent with the idea that lakes in larger watersheds receive greater P loading \citep{tprairieEffectCatchmentSize1986}.
 A related observation is that the correlation between P loading and upstream lake area was positive.

### 2019-01-23 manuscript/manuscript.Rmd
update tables to accepted formatting

@@
 The connectivity metric that had the most effect on $k$ was average link length (Table 2).
-For instance, hierarchical models fit with the average link length metric had a median effect size of 0.23 and 0.05 for $k$ and P retention respectively (Table \ref{table2}{2}), which means that for this metric, lakes with shorter average link lengths retained 4.7 to 4.9\% more P than lakes with longer average link lengths.
+For instance, hierarchical models fit with the average link length metric had a median effect size of 0.23 and 0.05 for $k$ and P retention respectively (Table \ref{table2}), which means that for this metric, lakes with shorter average link lengths retained 4.7 to 4.9\% more P than lakes with longer average link lengths.
 The influence of lake-stream-based connectivity metrics on lake P retention was similar to stream-based connectivity metrics (Figure 7).
@@
 N is sample size.
-Connectivity metrics are defined in Figure 2.}\label{table2}
+Connectivity metrics are defined in Figure \ref{fig2}.}\customlabel{table2}{2}
   \end{center}

### 2019-01-23 scripts/04_tables.R

@@ -18,7 +18,7 @@ name_key <- data.frame(
     "Total Phosphorus (ug/L)", "Chlorophyll (ug/L)", "Secchi Depth (m)",
     "P Loading (kg/yr)", "P Retention", "Residence Time (yr)",
     "Lake Area (km2)", "Maximum Depth (m)", "Agricultural Landuse (%)", "Urban Landuse %", 
-    "Lake Subwatershed Area (km2)", "Lake Watershed Area (km2)"), 
+    "Lake Subwatershed Area (${km^2}$)", "Lake Watershed Area (${km^2}$)"), 
   digits = c(2, 0, 2, 
              0, 2, 2, 
              2, 1, 2, 2, 
@@ -83,6 +83,7 @@ knitr::kable(res, format = 'pandoc', align = c("lllll"))
 # ---- model_results_table ----
 # table showing model results
 # setwd("scripts/")
+# source("99_utils.R")
 library(dplyr)
 library(kableExtra)
 
@@ -90,8 +91,11 @@ res <- read.csv("../scripts/table_1.csv", stringsAsFactors = FALSE)
 res <- res[, c("parameter", "units", "scale", "conny_type", "d_k", "splits", "n_low", "n_high")]
 model_signif <- read.csv("../scripts/model_signif.csv", 
                          stringsAsFactors = FALSE)
-model_signif$scale[model_signif$scale == "iws"] <- "lws"
+model_signif$scale[model_signif$scale == "iws"] <- "SWS"
+model_signif$scale[model_signif$scale == "nws"] <- "WS"
 model_signif$scale[is.na(model_signif$scale)] <- "focal"
+res$scale[res$scale == "lws"] <- "SWS"
+res$scale[res$scale == "nws"] <- "WS"
 
 key2 <- data.frame(conny_type = unique(as.character(res$conny_type)), 
                    conny_full = c("Longitudinal", "Lateral", "-"))

### 2019-01-23 manuscript/manuscript.Rmd
formatting, concatente with appendix

@@
 title: Does freshwater connectivity influence phosphorus retention in lakes?
-
-liftr:
-  maintainer: "Joseph Stachelek"
-  email: "stachel2@msu.edu"
-  from: "rocker/geospatial:latest"
-  pandoc: false
-  texlive: true
-  sysdeps:
-    - grass-dev
-    - p7zip-full
-    - curl
-    - texlive-base
-    - texlive-extra-utils 
-  cran:
-    - LAGOSNE
-    - brms
-    - dplyr
-    - tidyr
-    - modelr
-    - data.tree
-    - ggplot2
-    - tidybayes
-    - cowplot
-    - nesRdata
-    - partykit
-    - ggridges
-    - pinp
-  remotes:
-    - "jsta/nhdR"
-    - "jsta/spnetwork"
-    - "jsta/streamnet"
-    - "jsta/rgrass7sf"
 
@@
 # If not specified, defaults to "This version was compiled on \today"
-#date_subtitle: Published in *Journal of Statistical Software*, 2018
+date_subtitle: > 
+  *In Press* at *Limnology and Oceanography*, \href{https://doi.org/10.1002/lno.11137}{DOI: 10.1002/lno.11137}
 
@@
 Estimates of water discharge and residence time in the NES dataset represent normalized mean flow estimates expected to occur during a period of average precipitation and hydrology \citep{usepa1975}.
-Water residence time for our study lakes ranged from 1 week to 17 years with an interquartile range of 3 months to 1.8 years while P retention ranged from 0.06 to 0.99 with an interquartile range of 0.24 to 0.59 (Table 1).
+Water residence time for our study lakes ranged from 1 week to 17 years with an interquartile range of 3 months to 1.8 years while P retention ranged from 0.06 to 0.99 with an interquartile range of 0.24 to 0.59 (Table \ref{table1}).
 
@@
     \captionsetup{labelformat=empty}
-    \caption{\textbf{Table 1. } Minimum, median, maximum, and interquartile range of selected characteristics of the study lakes (N = 129).}\label{table1}    
+    \caption{\textbf{Table 1. } Minimum, median, maximum, and interquartile range of selected characteristics of the study lakes (N = 129).}\customlabel{table1}{1}
   \end{center}
@@
 
-We supplemented the NES dataset with boundaries for lake subwatersheds, as well as estimates of stream density, upstream lake area, upstream lake connection(s), baseflow (an index of groundwater inputs), land-use cover, and other water quality measurements from the LAGOS-NE dataset \citep[Table 1; ]{sorannoLAGOSNEMultiscaledGeospatial2017}.
-Our study lakes encompassed a wide range of land-use cover types and nutrient levels (Table 1).
+We supplemented the NES dataset with boundaries for lake subwatersheds, as well as estimates of stream density, upstream lake area, upstream lake connection(s), baseflow (an index of groundwater inputs), land-use cover, and other water quality measurements from the LAGOS-NE dataset \citep[Table \ref{table1}; ][]{sorannoLAGOSNEMultiscaledGeospatial2017}.
+Our study lakes encompassed a wide range of land-use cover types and nutrient levels (Table \ref{table1}).
 Although, lake subwatersheds were variable with respect to agricultural land use cover, we did not observe a strong relationship with lake P retention (Figure A2).
@@
 
-We modelled lake total phosphorus retention (hereafter, P retention) using the Vollenweider equation that models P retention as a function of water residence time and a parameter (k) conceptually representing in-lake P decay \citep{chapra2008surface, vollenweiderInputoutputModels1975}.
+We modelled lake total phosphorus retention (hereafter, P retention) using the Vollenweider equation that models P retention as a function of water residence time and a parameter ($k$) conceptually representing in-lake P decay \citep{chapra2008surface, vollenweiderInputoutputModels1975}.
 Although there are several variants of this basic equation, we selected a 2-parameter form (equation \ref{eq1}) that has been
@@
 
-where $R_i$ is P retention as a fraction of P inputs, $i$ $\tau$ is water residence time, $k$ is a unitless parameter representing in-lake P decay, and $x$ is a unitless parameter representing P export via hydrologic flushing.
+where $R_i$ is P retention as a fraction of P inputs, $\tau$ is water residence time, $k$ is a unitless parameter representing in-lake P decay, and $x$ is a unitless parameter representing P export via hydrologic flushing.
 Here, higher values of $k$ are associated with greater integrated P losses from sedimentation and biological uptake resulting in greater P retention.
@@
 
-where greater differences in $k$ between R the two groups indicate greater support for a connectivity effect on P retention.
+where greater differences in $k$ between the two groups indicate greater support for a connectivity effect on P retention.
 Prior to model fitting, we examined the bivariate relationships between each connectivity metric, water residence time, P loading, and other factors related to P retention using Pearson’s correlation coefficients.
@@
 These priors were based on the confidence intervals presented in \citet{brett2008} and qualitatively matched those used by \citet{cheng2010}.
-We used the default settings of brms and rstan to generate posterior estimates using four chains of 4,000 iterations each with no thinning and initial parameter values drawn from a uniform distribution bounded between -2 and 2.
-We also used the brms package for model evaluation by computing a Bayesian $R^{2}$ following the method of \citet{gelmanRsquaredBayesianRegression2017}.
+We used the default settings of `brms` and `rstan` to generate posterior estimates using four chains of 4,000 iterations each with no thinning and initial parameter values drawn from a uniform distribution bounded between -2 and 2.
+We also used the `brms` package for model evaluation by computing a Bayesian $R^{2}$ following the method of \citet{gelmanRsquaredBayesianRegression2017}.
 
@@
 Prior studies have used a similar binary splitting approach to examine the effect of various exogenous factors on lake P retention \citep{cheng2010, shimodaIntegratingHierarchicalBayes2015}.
-We determined splitting criteria for each metric from the results of a random forest procedure incorporating conditional inference trees \citep[][ctree, ]{hothorn2015partykit}.
+We determined splitting criteria for each metric from the results of a random forest procedure incorporating conditional inference trees \citep{hothorn2015partykit}.
 This procedure creates binary splits of the independent variables (i.e.
@@
 Note that interactions between connectivity metrics and water residence time are accounted for in our hierarchical model structure because Eq.
-2 uses a global coefficient x for water residence time that is estimated separately from the hierarchical and connectivity-dependent P decay coefficient k.
+2 uses a global coefficient $x$ for water residence time that is estimated separately from the hierarchical and connectivity-dependent P decay coefficient k.
 This is conceptually similar to fitting the k-connectivity-P retention relationship to the residuals of the water residence time to P retention relationship.
@@
 
-Differences in P retention among lakes with different connectivity metric values was reflected in differences among connectivity class-specific values of the P decay parameter $k$ (Figure 7).
-The connectivity metric that had the most effect on $k$ was average link length (Table 2).
+Differences in P retention among lakes with different connectivity metric values was reflected in differences among connectivity class-specific values of the P decay parameter $k$ (Figure \ref{fig7}).
+The connectivity metric that had the most effect on $k$ was average link length (Table \ref{table2}).
 For instance, hierarchical models fit with the average link length metric had a median effect size of 0.23 and 0.05 for $k$ and P retention respectively (Table \ref{table2}), which means that for this metric, lakes with shorter average link lengths retained 4.7 to 4.9\% more P than lakes with longer average link lengths.
-The influence of lake-stream-based connectivity metrics on lake P retention was similar to stream-based connectivity metrics (Figure 7).
+The influence of lake-stream-based connectivity metrics on lake P retention was similar to stream-based connectivity metrics (Figure \ref{fig7}).
 This suggests that both lake-stream-based connectivity between lakes and streams as well as stream-based connectivity of lakes and their terrestrial watersheds influence P retention (Figure \ref{fig2}).
@@
   \begin{center}
-    \includegraphics[width=0.85\textwidth,keepaspectratio]{../tables/crop/02_model_results_table} 
+    \includegraphics[width=0.65\textwidth,keepaspectratio]{../tables/crop/02_model_results_table} 
     \captionsetup{labelformat=empty}
@@
 
-We found that connectivity metrics measured at the lake watershed extent were more strongly associated with P retention than metrics measured at the lake subwatershed extent (Table 2, Figure \ref{fig7}).
-Specifically, the metrics that had the strongest association with P retention such as average link length ($\Delta$k = 0.23), closest lake distance ($\Delta$k = 0.22), and stream density ($\Delta$k = 0.20) also had a stronger association at the lake watershed extent rather than at the lake subwatershed extent (Table 2, Figure \ref{fig7}).
+We found that connectivity metrics measured at the lake watershed extent were more strongly associated with P retention than metrics measured at the lake subwatershed extent (Table \ref{table2}, Figure \ref{fig7}).
+Specifically, the metrics that had the strongest association with P retention such as average link length ($\Delta$k = 0.23), closest lake distance ($\Delta$k = 0.22), and stream density ($\Delta$k = 0.20) also had a stronger association at the lake watershed extent rather than at the lake subwatershed extent (Table \ref{table2}, Figure \ref{fig7}).
 An exception to this pattern was observed with the baseflow connectivity metric where although greater differences at the lake subwatershed extent were more strongly associated with P retention, the sign of the effect was variable depending on measurement extent (i.e.
 the value of the P decay parameter was positively related to connectivity metric values at the subwatershed extent but was negatively related at the watershed extent).
-For several connectivity metrics, we judged that differences in P decay among lakes with either low or high connectivity metric values were not significant because they translated to differences in P retention that were less than measurement precision (Table 2).
+For several connectivity metrics, we judged that differences in P decay among lakes with either low or high connectivity metric values were not significant because they translated to differences in P retention that were less than measurement precision (Table \ref{table2}).
 
@@
 
-We found that differences in P retention among lake connectivity classes was influenced by specific connectivity metrics including average link length, closest lake distance, and stream density (Table 2, Figure \ref{fig7}).
+We found that differences in P retention among lake connectivity classes was influenced by specific connectivity metrics including average link length, closest lake distance, and stream density (Table \ref{table2}, Figure \ref{fig7}).
 Indeed, these metrics were more strongly associated with P retention than covariates typically used in statistical P retention models (e.g.
@@
 We found that connectivity at the broader lake watershed extent rather than connectivity at the finer lake subwatershed extent was more strongly associated with differences in lake P retention.
-In addition, we found that individual characteristics such as lake depth (or more discrete measures of connectivity such as the presence of an upstream lake) were more strongly associated with P retention than any of the other connectivity metrics measured at the lake subwatershed extent (Table 2).
+In addition, we found that individual characteristics such as lake depth (or more discrete measures of connectivity such as the presence of an upstream lake) were more strongly associated with P retention than any of the other connectivity metrics measured at the lake subwatershed extent (Table \ref{table2}).
 These findings contrast with \citet{soranno2015} who examined the association between lake nutrient concentrations (as opposed to retention) and land-use measured at varying spatial extents and found that measurements at the finer lake subwatershed extent rather than measurements at the broader lake watershed extent were more strongly associated with lake nutrient concentrations.
@@
 Another finding consistent with differential transport of particulate P is our observation that average link length, which approximates stream network structure and along-stream transport potential \citep{labarberaFractalDimensionStream1989}, was one of the more strongly associated metrics with lake P retention.
-Finally, it is notable that our stream density metric was influential at thee lake watershed extent but not at the lake subwatershed extent.
-Given that the stream density metric captures the average distance or drainage potential between any streams in the network and their adjacent hillslopes, floodplains, and wetlands \citep[see]{leibowitzConnectivityStreamsWetlands2018}, this suggests that differences in terrestrial runoff of particulate matter from hillslope and riparian areas are likely to be important for P retention.
+Finally, it is notable that our stream density metric was influential at the lake watershed extent but not at the lake subwatershed extent.
+Given that the stream density metric captures the average distance or drainage potential between any streams in the network and their adjacent hillslopes, floodplains, and wetlands \citep[see ][]{leibowitzConnectivityStreamsWetlands2018}, this suggests that differences in terrestrial runoff of particulate matter from hillslope and riparian areas are likely to be important for P retention.
 

### 2019-01-24 manuscript/manuscript.Rmd
add disclaimer, missing links

@@
 date_subtitle: > 
-  *In Press* at *Limnology and Oceanography*, \href{https://doi.org/10.1002/lno.11137}{DOI: 10.1002/lno.11137}
+  This is the accepted version of the following article: J.
+Stachelek and P.A.
+Soranno, Limnology and Oceanography.
+In Press, which has been published in final form at DOI:  [10.1002/lno.11137](https://doi.org/10.1002/lno.11137).
+This article may be used for non-commercial purposes in accordance with Wiley Terms and Conditions for Use of Self-Archived Versions.
 
@@
 Our motivation for measuring connectivity so many ways is that it is easy to measure connectivity of lakes with small watersheds situated at the beginning of lake chains but it is much more challenging to identify the type and extent of connectivity in larger, more complex lake networks.
-Another reason we examined relationships between P retention, multiple measures of connectivity, and multiple spatial extents is that many commonly used connectivity metrics merely reflect watershed size (spatial extent) rather than types of material transport or particulate load fraction (Leibowitz et al., 2018).
+Another reason we examined relationships between P retention, multiple measures of connectivity, and multiple spatial extents is that many commonly used connectivity metrics merely reflect watershed size (spatial extent) rather than types of material transport or particulate load fraction \citep{leibowitzConnectivityStreamsWetlands2018}.
 Although lakes in larger watersheds have both a greater potential area from which to source particulate runoff and total phosphorus export from the watershed, we expect that delivery of sediment-bound phosphorus is dependent on connectivity-mediated trapping in the upstream watershed \citep{tprairieEffectCatchmentSize1986}.
@@
 
-We found that freshwater connectivity metrics were associated with lake P retention (Figure 6, 7).
+We found that freshwater connectivity metrics were associated with lake P retention (Figure \ref{fig6}, \ref{fig7}).
 Across all connectivity metrics except stream order ratio, we found that the P decay coefficient $k$ and thus P retention was associated with whether a lake had a high or low value of each connectivity metric.
@@
 36 < $R^{2}$ < 0.41).
-Overall, we found that all hierarchical models had at least a marginally better fit to the water residence time versus P retention relationship than a global model which does not account for connectivity (Figure 6).
+Overall, we found that all hierarchical models had at least a marginally better fit to the water residence time versus P retention relationship than a global model which does not account for connectivity (Figure \ref{fig6}).
 Although we found a discernable effect of connectivity metrics on lake P retention, the somewhat modest improvements in model fit may be due to the fact that water residence time remains a dominant effect even after accounting for freshwater connectivity.

### 2019-01-30 manuscript/appendix.Rmd
rule out dplyr namespace clobbering

@@
 
-tp <- select(nla$waterchem_wide, PTL_RESULT, UID) %>%
+tp <- dplyr::select(nla$waterchem_wide, PTL_RESULT, UID) %>%
       left_join(select(nla$wide_siteinfo, AREA_HA, SITE_ID, UID)) %>%
@@
 
-chl  <- select(nla$chla_wide, CHLX_RESULT, UID)  %>%
+chl  <- dplyr::select(nla$chla_wide, CHLX_RESULT, UID)  %>%
         left_join(select(nla$wide_siteinfo, SITE_ID, UID)) %>%
@@
 
-secchi  <- select(nla$secchi, SECCHI, SITE_ID)  %>%
+secchi  <- dplyr::select(nla$secchi, SECCHI, SITE_ID)  %>%
            group_by(SITE_ID) %>%
@@
 
-depth <- select(nla$wide_phab, DEPTH_AT_STATION, SITE_ID)  %>%
+depth <- dplyr::select(nla$wide_phab, DEPTH_AT_STATION, SITE_ID)  %>%
            group_by(SITE_ID) %>%
@@
 
-nes <- select(nes_iws, tp, area = surface_area, chl, secchi, depth = maxdepth)
+nes <- dplyr::select(nes_iws, tp, area = surface_area, chl, secchi, depth = maxdepth)
 nes$tp <- 1000 * nes$tp # mg to ug

### 2019-01-31 manuscript/appendix.Rmd
bib file name has changed
approve nhd downloads

@@
     fig_caption: yes
-bibliography: bibliography.bib
+bibliography: pinp.bib
 ---
@@
 
-  nhd <- nhdR::nhd_load(state.abb[tolower(state.name) %in% states$ID], "NHDWaterbody")
+  nhd <- nhdR::nhd_load(state.abb[tolower(state.name) %in% states$ID], "NHDWaterbody", 
+                        approve_all_dl = TRUE)
   nhd$GNIS_ID <- sapply(as.character(nhd$GNIS_ID), function(x) substring(x, 3, nchar(x)))
@@
   xlab("Percent Agriculture") + ylab("P Retention")
-
 ```
@@
 ```{r nes_vs_nla, fig.cap="\\label{fig:fig3}Comparison of selected lake characteristics among the stratified random sampling design of the National Lakes Assessment (nla) and the haphazard sampling of the National Eutrophication Survey (nes) lakes analyzed in the present study.", fig.height=4, warning=FALSE, message=FALSE}
-# , message=FALSE, warning=FALSE
-nla <- nla_load(2012)
+nla <- nlaR::nla_load(2012)
 

### 2019-02-08 manuscript/manuscript.Rmd
enable showing ref dois
insert zenodo doi

@@
 # Place eg a DOI URL or CRAN Package URL here
-doi_footer: "https://doi.org/ZenodoDOI"
+doi_footer: "https://doi.org/10.5281/zenodo.2554212"
 
@@
 bibliography: pinp
-biblio-style: bioscience
+biblio-style: elsarticle-harv
 
@@
 The algorithms in the `streamnet` package use the `sf` R package \citep{pebesma2018} as well as the `v.net` and `v.stream.order` modules \citep{jasiewiczNewGRASSGIS2011} included in GRASS GIS \citep{GRASS_GIS_software}.
-All processed connectivity data and code are available at [Zenodo DOI].
+All processed connectivity data and code are available at https://doi.org/10.5281/zenodo.2554212.
 

### 2020-06-10 manuscript/appendix.Rmd
fix appendix citekeys, closes #4

@@
 bibliography: pinp.bib
+editor_options: 
+  chunk_output_type: console
 ---
@@
 It is difficult to examine the uncertainties surrounding the relationship between water residence time and lake P retention because empirical measures of these quantities do not exist for many lakes.
-One of the few comprehensive sources of these data is modelling studies which produce largely unverified estimates of water residence time and P retention [@milsteadEstimatingSummerNutrient2013].
+One of the few comprehensive sources of these data is modelling studies which produce largely unverified estimates of water residence time and P retention [@milstead2013].
 Such model output data may not be appropriate for statistical P retention modelling because P retention and water residence time values are not independently estimated.
@@
 Here, we examined whether a strong relationship of lake P retention with agricultural land use cover could be obscuring relationships with connectivity metrics.
-We used P retention data from the National Eutrophication Survey [@stachelek_national_2017] and land cover data from the 1992 National Land Cover Database clipped to lake watersheds and available in the LAGOS-NE dataset [@sorannoLAGOSNEMultiscaledGeospatial2017].
+We used P retention data from the National Eutrophication Survey [@stachelek_national_2018] and land cover data from the 1992 National Land Cover Database clipped to lake watersheds and available in the LAGOS-NE dataset [@sorannoLAGOSNEMultiscaledGeospatial2017].
 
@@
 Our lakes are similar in most respects except that they are substantially larger and deeper than most NLA lakes.
-
-## References
 
@@
 ```
+
+\newpage
+
+## References
